### 2011-04-19 Paper.tex
drafting crappy paper

\documentclass[12pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url}
\usepackage[sort,round]{natbib}
\usepackage[margin=1in]{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\frenchspacing
\onehalfspacing

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{E}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\ols}{\textsc{ols}}

\begin{document}

\author{Gray Calhoun}
\title{A comment on ``Approximately normal tests for equal predictive
  accuracy in nested models''}
\date{\today}
\maketitle

\begin{abstract} 
  \noindent This paper proposes a slight modification of
  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
  to estimate the alternative model under a fixed-length rolling
  window, but estimate the benchmark model under a recursive
  window. The resulting statistic gives an asymptotically normal test
  statistic that the benchmark model is correctly specified, even when
  it is nested in the alternative.  Moreover, the alternative model
  can be estimated using populare model selection methods, such as the
  \aic\ or \bic.

\strut

\noindent Keywords: Out-of-Sample

\strut

\noindent JEL Classification Numbers:

\end{abstract}

\newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
an out-of-sample test of the null hypothesis that a small benchmark
model is correctly specified.  Their test compares the forecasting
performance of a pair of nested models, and the null hypothesis is
that the innovations in the smaller model are a martingale difference
sequence.  This test procedure is quite popular,\footnote{As of 19
  April 2011, \citet{ClW:06} has been cited by 25 papers indexed by
  the ISI Web of Knowledge, and \citet{ClW:07} by 35.} and one assumes
that this is due in part to the statistic's convenience.  The
statistic is approximately normal after adjusting for the estimation
error of the larger model.  Normality comes from a fixed-length
rolling window, as in \citet{GiW:06}, and the adjustment centers the
statistic at the appropriate population quantities.  This statistic is
especially convenient because other tests for similar hypotheses
\citep[see][among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01}
lead to a nonstandard limit distribution and place restrictions on the
models under consideration, while other asymptotically normal
statistics \citep{GiW:06} test a different null hypothesis.

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present monte carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal when the benchmark model is a random walk
\citep{ClW:06}. Estimating the parameters of the smaller model
invalidates the proof.

In this note, I prove that a slightly modified version of their
statistic is asymptotically normal even when the smaller model is
estimated.  Essentially, we need a consistent estimate of the forecast
errors of the pseudo-true version of the benchmark models, while
maintaining inconsistent estimates of the larger model's errors so
that we can ignore the fact that the models are nested.  We can meet
both needs by using different window strategies for each model.  We
estimate the benchmark model using a recursive window scheme, and
estimate the alternative using a fixed-length rolling window.

Mixing window strategies is uncommon but it shouldn't be. In most
applications, the null hypothesis imposes both equal accuracy between
the two models and stability.  The benchmark model rarely allows for
breaks, parameter drift, or other instability,\footnote{An exception
  might be \possessivecite{StW:08} IMA(1,1) model of inflation.} but
the researcher is typically concerned about instability.  Indeed,
concern about instability is often given as a reason for doing an
out-of-sample analysis, especially with a short rolling window
\citep{GiW:06,GiR:09,GiR:10}.  So using a different window strategy
for each model--a recursive window for the model that imposes
stability, and a rolling window for the model that relaxes
stability--is a natural approach and is similar in spirit to the
Likelihood Ratio Test\footnote{Using a rolling window for both models
  would be analagous to a Wald test and using recursive window for
  both would be like the LM test.}

Our statistic has a substantial advantage over existing out-of-sample
statistics for nested models: the benchmark can be essentially
arbitrary, as long as it obeys the necessary moment conditions.  In
particular, it can use model selection techniques like the \aic\ or
\bic\ to determine things like the number of lags to include, the
particular exogenous variables to include, etc.  Other methods that
test a similar hypothesis are unable to handle these models
\citep[except][which does not allow the benchmark to be
estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
both the alternative and the benchmark, but they test a different
aspect of forecasting performance.

We'll present our results as a single theorem.  The conditions are
essentially the same as
\citet{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a modified
window scheme.  We require that the benchmark model be estimated by
least squares, but that is for convenience and could be relaxed.
Changing the estimation strategy of the benchmark model would amount
to changing the null hypothesis.

\begin{thm}\label{thm:1}
  Suppose that the following hold:
  \begin{enumerate}
  \item The coefficients for the benchmark forecast,
    $\hat{y}_{1,t}(\beta_1)$, are estimated with least-squares over a
    recursive window:
    \[\hat{\beta}_{1t} = \argmin_{\beta} \sum_{s=1}^{t} (y_t -
    \hat{y}_{1t}(\beta))^2, \qquad t = R,\dots,T-1.\]
  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
    a rolling window of fixed length $R$: $\hat{y}_{2,t} \in
    \sigma(y_{t-R+1},\dots,y_t)$
  \item $z_t \equiv (y_t, \hat{y}_{1,t}(\beta_1^{*}), \hat{y}_{2t})$
    is strong mixing of size $-r/(r-2)$ and has uniformly bounded
    $r+\delta$ moments for some positive $\delta$, with $\beta^{*} =
    \argmin_{\beta} \E (y_t - \hat{y}_{1t}(\beta))^2$.

  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
  martingale difference sequence, $\sqrt{P} \bar f / \hat{\sigma}
  \to^d N(0,1)$, where
  \begin{align*}
  \bar f
  &\equiv P^{-1} \sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}),&  \hat{\sigma} &\equiv \Big(P^{-1}
  \sum_{t=R+1}^T (f_t(\hat{\beta}_{t-1}) - \bar f)^2\Big)^{1/2},
  \end{align*}
 and    
  \begin{equation*}
    f_t(\hat{\beta}_{t-1}) \equiv (y_t - \hat{y}_{1t}(\hat{\beta}_{t-1}))^2
    - (y_t - \hat{y}_{2t})^2 +
    (\hat{y}_{1t}(\hat{\beta}_{1,t-1}) - \hat{y}_{2t})^2
  \end{equation*}
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy $\tilde{R}_T \to \infty$ and
  $\tilde{R}_T/T \to 0$ and define $\tilde{P} = T - \tilde{R}$ Then
  \begin{equation*}
    P^{-1/2}\sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}) = \tilde{P}^{-1/2}
    \sum_{t=\tilde{R}+1}^T f_t(\hat{\beta}_{t-1}) + o_p(T^{-1/2}).
  \end{equation*}
  Now, $\hat{\beta}_t = B(t) H(t)$ with
  \begin{gather*}
    B(t) = \Big(t^{-1} \sum_{s=1}^t \Big\{\Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)
    \Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)' - (y_t -
    \hat{y}_{1t}(\bar{\beta}_t))\frac{\partial^2}{\partial\beta \partial\beta'}
    \hat{y}_{1t}(\bar{\beta}_t)\Big\}\Big)^{-1}, \\
    H(t) = t^{-1} \sum_{s=1}^t (y_t - \hat{y}_{1t}(\beta^{*}))
    \dd{\beta} \hat{y}_{1t}(\beta^{*}),
  \end{gather*}
  where $\bar{\beta}_t$ is between $\beta^{*}$ and $\hat{\beta}_t$
  element-by-element.  Then our new out-of-sample average satisfies
  the conditions of \citet[Theorem 4.1]{Wes:96} (with the moment and
  weak dependence conditions weakened as in \citet[Theorem
  2.3.1]{Mcc:00}).
\end{proof}

\input{mc}

\bibliography{AllRefs}

\end{document}

### 2011-04-19 mc.Rnw
drafting crappy paper

We will also conduct a brief Monte Carlo experiment to demonstrate
that this modified statistic performs essentially the same as Clark
and West's.  We draw observations from their \dgp\ 1:

\begin{gather*}
  y_t = 0.5 + \gamma^{*} z_{t-1} + e_t \qquad\qquad
  z_t = 0.15 + 0.95 z_{t-1} + v_t \\
  (e_t, v_t)' \sim iid\ N(0, \begin{pmatrix} 18 & - 0.5 \\ \cdot & 0.025 \end{pmatrix}.
\end{gather*}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We run the same size and power simulations as
\citet{ClW:07}; $\gamma^{*}$ equals zero for the size simulations and
0.35 in the power simulations.

### 2011-04-19 MakeScript.R

@@ -1,0 +1,53 @@
+# The basic idea of this python script is to set up the right
+# dependencies for GNU make so that the monte carlo simulations are
+# run in parallel.  Running this file will print out text for a
+# makefile, so it might be easiest to just look at its output.
+
+nsims <- 1000  # this is the number of simulations
+njobs <- 8     # I set this to equal the number of processors on my 
+               # computer.  Changing its value will change the results
+               # of the simulations, since they'll be seeded differently.
+
+### split the simulations across the jobs
+remainder <- nsims %% njobs
+jsims = rep(nsims %/% njobs, njobs) + c(rep(1, remainder), rep(0, njobs - remainder))
+### check for dumb errors
+stopifnot(sum(jsims) == nsims)
+
+dbdir <- "db"
+
+dbnames <- function(table)
+  sapply(seq.int(njobs), function(i) paste(table, i, sep = ""))
+dbfiles <- function(filename)
+  paste(dbdir, "/", filename, ".db", sep = "")
+
+mkline <- function(...)
+    cat(paste("\n\t$(sqlite) $(sqliteflags) stardata.db \"",
+              paste(...,sep = ""), ";\"", sep = ""))
+
+mergetables <- function(table) {
+  dbn <- dbnames(table)
+  dbf <- dbfiles(dbn)
+  cat(sprintf("\ndb/%s.done: %s", table, dbf), sep = "")
+  mkline(paste(sprintf("attach database '%s' as %s;", dbf, dbn), collapse = " "),
+         sprintf("drop table if exists main.%s; ", table),
+         sprintf("create table main.%s as %s;",
+                 table, paste(sprintf("select * from %s.%s", dbn, table),
+                              collapse = " union all ")),
+         paste(sprintf("detach database %s;", dbn), collapse = " "))
+  cat("\n\ttouch $@")
+}
+
+writeMake <- function(x, Rfile, seed) {
+  ## This is the set of make commands to create the individual databases.
+  dbn <- dbnames(x)
+  dbf <- dbfiles(dbn)
+  cat("\n.SECONDARY: ", dbf, collapse = "", sep = " ")
+  mergetables(x)
+  for (job in seq.int(njobs)) {
[…]

### 2011-04-19 R/montecarlo.R

@@ -1,0 +1,63 @@
+## seed, jjob, dbtable, and nsim are set in the file mc-setup.R
+## for debugging:
+## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
+set.seed(seed)
+set.seed(sample(1:10000000, jjob)[jjob],
+         kind = 'Mersenne-Twister', normal.kind = 'Inversion')
+
+library(MASS)
+library(OOS)
+library(dbframe)
+
+mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
+                  overwrite = TRUE)
+clear(mcdata)
+
+mcdesign <- expand.grid(P = c(120, 240, 360, 720), R = c(120, 240),
+                        gam = c(0, 0.35))
+
+## really basic function to generate our data; this could be written
+## much better.
+rdgp <- function(n, gam) {
+  ## The processes are
+  ## y_t = a %*% c(1, z_{t-1}) + e1
+  ## z_t = b %*% c(1, z_{t-1}) + e2
+  ## with 
+  ## (e1, e2) ~ N(0, v)
+  a <- c(.5, gam)
+  b <- c(.15, .95)
+  v <- matrix(c(18, -.5, -.5, .025), 2)
+  
+  Ez <- b[1] / (1 - b[2])
+  Ey <- a[1] + a[2] * Ez
+
+  ## elements of the variance-covariance matrix
+  Vz <- v[2,2] / (1 - b[2]^2)
+  Vy <- v[1,1] + gam^2 * Vz
+  Cyz <- a[2] * b[2] * Vz + v[1,2]
+
+  ## we're going to let x_t = (y_t, z_t); draw from the stationary
+  ## distribution and then populate the rest of the matrix with the
+  ## innovations.
+  x <- rbind(mvrnorm(1, c(Ey, Ez), matrix(c(Vy, Cyz, Cyz, Vz), 2)),
+             mvrnorm(n, c(0,0), v))
+  A <- matrix(c(0, 0, a[2], b[2]), 2)
+  for (i in 1 + (1:n)) {
+    x[i,] = drop(c(a[1], b[1]) + A %*% x[i-1,] + x[i,])
+  }
+  data.frame(y = x[-1,1], zlag = x[-n,2])
+}
+
+bench <- function(d) lm(y ~ 1, data = d)
+alter <- function(d) lm(y ~ zlag, data = d)
+
+r <- mcdesign[1,]
+
[…]

### 2011-08-03 Paper.tex
Submitted abstract to the MEG conference

@@
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx}
 \usepackage[sort,round]{natbib}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1.25in]{geometry}
 \usepackage[small]{caption}
@@
 \bibliographystyle{abbrvnat}
-\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
+\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
+\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
+\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
 \frenchspacing
@@
 \newtheorem{cor}[thm]{Corollary}
-\newtheorem{asmp}{Assumption}
+\newtheorem{lema}{Lemma}[section]
+\newtheorem{alg}{Algorithm}
+\newtheorem{asmp}{Assumption}[section]
+
+\theoremstyle{definition}
+
 \newtheorem{example}{Example}
 \newtheorem{defn}{Definition}
+\newtheorem{rem}{Remark}
 
@@
 \DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\var}{var}
+\DeclareMathOperator{\cov}{cov}
+%\DeclareMathOperator{\vec}{vec}
+\DeclareMathOperator{\vech}{vech}
+
+\DeclareMathOperator{\pr}{Pr}
+
+\newcommand{\X}{\ensuremath{\mathrm{X}}}
+\newcommand{\R}{\ensuremath{\mathrm{R}}}
+\newcommand{\p}{\ensuremath{\mathrm{P}}}
+
 \newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
+\newcommand{\ned}{\textsc{ned}}
+\newcommand{\clt}{\textsc{clt}}
+\newcommand{\fclt}{\textsc{fclt}}
 \newcommand{\aic}{\textsc{aic}}
@@
 \newcommand{\ols}{\textsc{ols}}
+\newcommand{\mds}{\textsc{mds}}
+\newcommand{\oos}{\textsc{oos}}
+\newcommand{\gdp}{\textsc{gdp}}
+\newcommand{\hac}{\textsc{hac}}
+\newcommand{\fwe}{\textsc{fwe}}
+\newcommand{\cdf}{\textsc{cdf}}
+\newcommand{\ma}{\textsc{ma}}
+
+\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
 
@@
 
-\author{Gray Calhoun}
-\title{A comment on ``Approximately normal tests for equal predictive
-  accuracy in nested models''}
-\date{\today}
+\author{Gray
+  Calhoun\thanks{\texttt{http://www.econ.iastate.edu/$\sim$gcalhoun};
+    Economics Department; Iowa State University; Ames, IA 50011.
+    Telephone: (515) 294-6271.  Email: \texttt{gcalhoun@iastate.edu}.}
+  \\ Iowa State University}
+
+\title{An asymptotically normal out-of-sample
+  test of equal predictive accuracy for nested models} \date{\today}
 \maketitle
@@
 \begin{abstract} 
-  \noindent This paper proposes a slight modification of
-  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
-  to estimate the alternative model under a fixed-length rolling
-  window, but estimate the benchmark model under a recursive
-  window. The resulting statistic gives an asymptotically normal test
-  statistic that the benchmark model is correctly specified, even when
-  it is nested in the alternative.  Moreover, the alternative model
-  can be estimated using populare model selection methods, such as the
-  \aic\ or \bic.
+  \noindent This paper proposes a modification of \citepos[\textit{J.
+      Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
+  alternative model is still estimated with a fixed-length rolling
+  window, but the benchmark is estimated with a recursive window. The
+  resulting statistic is asymptotically normal even when the models
+  are nested.  Moreover, the alternative model can be estimated using
+  popular model selection methods, such as the \aic\ or \bic.  This
+  paper also presents a new bootstrap procedure based on
+  \citet[\textit{Econometrica}]{RoW:05} to compare multiple models
+  while controlling family-wise error that substantially improves
+  existing block bootstrap methods for out-of-sample statistics.  This
+  procedure is then used to analyze
+  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.
 
@@
 
-\noindent Keywords: Out-of-Sample
+\noindent Keywords: Forecast Evaluation, Martingale Difference
+Sequence, Model Selection, Family-Wise Error Rate; Multiple Testing;
+Bootstrap; Reality Check
 
@@
 
-\noindent JEL Classification Numbers:
+\noindent JEL Classification Numbers: C22, C53
 
@@
 \newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
-an out-of-sample test of the null hypothesis that a small benchmark
-model is correctly specified.  Their test compares the forecasting
-performance of a pair of nested models, and the null hypothesis is
-that the innovations in the smaller model are a martingale difference
-sequence.  This test procedure is quite popular,\footnote{As of 19
-  April 2011, \citet{ClW:06} has been cited by 25 papers indexed by
-  the ISI Web of Knowledge, and \citet{ClW:07} by 35.} and one assumes
-that this is due in part to the statistic's convenience.  The
-statistic is approximately normal after adjusting for the estimation
-error of the larger model.  Normality comes from a fixed-length
-rolling window, as in \citet{GiW:06}, and the adjustment centers the
-statistic at the appropriate population quantities.  This statistic is
-especially convenient because other tests for similar hypotheses
-\citep[see][among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01}
-lead to a nonstandard limit distribution and place restrictions on the
-models under consideration, while other asymptotically normal
-statistics \citep{GiW:06} test a different null hypothesis.
+an out-of-sample (\oos) test of the null hypothesis that a small
+benchmark model is correctly specified.  Their test compares the
+forecasting performance of a pair of nested models, and the null
+hypothesis is that the innovations in the smaller model form a
+martingale difference sequence.  This test procedure is
+popular,\footnote{As of 03 June 2011, \citet{ClW:06} has been cited by
+  26 papers indexed by the \textsc{isi} Web of Knowledge, and
+  \citet{ClW:07} by 37. They have been cited by 113 and 165 papers
+  respectively indexed by Google Scholar.} and one assumes that this
+is due in part to the statistic's convenience.  The statistic is
+approximately normal after adjusting for the estimation error of the
+larger model.  Normality comes from a fixed-length rolling window, as
+in \citet{GiW:06}, and the adjustment centers the statistic
+appropriately.  This statistic is especially convenient because other
+tests for similar hypotheses \citep[among
+  others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
+nonstandard limit distribution and place restrictions on the models
+under consideration, while other asymptotically normal statistics test
+a different null hypothesis \citep{GiW:06} or place assumptions on the
+models and \dgp\ that are rarely appropriate in empirical work
+\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.
 
 However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present monte carlo evidence of
+in an informal sense.  Clark and West present Monte Carlo evidence of
 the statistic's distribution, but only prove that the statistic is
@@
 \citep{ClW:06}. Estimating the parameters of the smaller model
-invalidates the proof.
+invalidates their proof.
 
-In this note, I prove that a slightly modified version of their
-statistic is asymptotically normal even when the smaller model is
-estimated.  Essentially, we need a consistent estimate of the forecast
-errors of the pseudo-true version of the benchmark models, while
-maintaining inconsistent estimates of the larger model's errors so
-that we can ignore the fact that the models are nested.  We can meet
-both needs by using different window strategies for each model.  We
-estimate the benchmark model using a recursive window scheme, and
-estimate the alternative using a fixed-length rolling window.
+In this paper, I show that a modified version of their statistic is
+asymptotically normal even when the smaller model is estimated.  To
+achieve normality, we need a consistent estimate of the pseudo-true
+benchmark model, while maintaining an inconsistent estimate of the
+larger model so that we can ignore nesting.  We can meet both needs by
+using different window strategies for each model; the benchmark model
+is estimated using a recursive window and the alternative with a
+fixed-length rolling window.
 
-Mixing window strategies is uncommon but it shouldn't be. In most
+Mixing window strategies is uncommon but needn't be. In most
 applications, the null hypothesis imposes both equal accuracy between
 the two models and stability.  The benchmark model rarely allows for
-breaks, parameter drift, or other instability,\footnote{An exception
-  might be \possessivecite{StW:08} IMA(1,1) model of inflation.} but
-the researcher is typically concerned about instability.  Indeed,
-concern about instability is often given as a reason for doing an
-out-of-sample analysis, especially with a short rolling window
-\citep{GiW:06,GiR:09,GiR:10}.  So using a different window strategy
-for each model--a recursive window for the model that imposes
-stability, and a rolling window for the model that relaxes
-stability--is a natural approach and is similar in spirit to the
-Likelihood Ratio Test\footnote{Using a rolling window for both models
-  would be analagous to a Wald test and using recursive window for
-  both would be like the LM test.}
+breaks, parameter drift, or other forms of
+instability,\footnote{Exceptions are \citepos{StW:07}
+  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
+researcher is typically concerned about instability.  Indeed, concern
+about instability is often given as a reason for doing an \oos\
+analysis, especially with a short rolling window.\footnote{This
+  motivation is discussed in \citet{StW:03}, \citet{PeT:05,PeT:07},
+  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
+  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
+stability on both models by using a recursive window or relax
+stability for both by using a rolling window; both approaches should
+not affect the test's size, but may affect power.  But the researcher
+could instead impose stability on the benchmark and relax it for the
+alternative by using a recursive window for the benchmark and a
+rolling window for the alternative model.  This approach could have a
+power advantage and is similar in spirit to using a likelihood ratio
+test instead of an \textsc{lm} or Wald test.
 
-Our statistic has a substantial advantage over existing out-of-sample
-statistics for nested models: the benchmark can be essentially
+This statistic has a substantial advantage over existing \oos\
+statistics for nested models: the alternative can be essentially
 arbitrary, as long as it obeys the necessary moment conditions.  In
-particular, it can use model selection techniques like the \aic\ or
-\bic\ to determine things like the number of lags to include, the
+particular, researchers can use model selection techniques like the
+\aic\ or \bic\ to determine the number of lags to include, the
 particular exogenous variables to include, etc.  Other methods that
@@
 estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
-both the alternative and the benchmark, but they test a different
-aspect of forecasting performance.
+both the alternative and the benchmark but, as mentioned earlier, they
+test a different aspect of forecasting performance.
 
-We'll present our results as a single theorem.  The conditions are
-essentially the same as
-\citet{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a modified
-window scheme.  We require that the benchmark model be estimated by
-least squares, but that is for convenience and could be relaxed.
-Changing the estimation strategy of the benchmark model would amount
-to changing the null hypothesis.
+This paper focuses on nested models, as they have received the most
+attention in the empirical and theoretical literature, but the
+statistic can be used with non-nested models as well.  This generality
+is useful, since \citepos{Wes:96} results do not apply to non-nested
+models if they both encompass the true \dgp, which is allowable under
+the null: in the limit, both models will converge to the \dgp\ and
+give identical forecasts.  Consequently, the naive \oos\ $t$-test is
+invalid, even after correcting the standard error to reflect parameter
+uncertainty.  Constructing an \oos\ test for non-nested models using
+\citepos{ClM:01} approach would be difficult.  To my knowledge, this
+paper gives the first \oos\ test of equal predictive ability for
+non-nested models that does not implicitly rule out both models
+encompassing the \dgp.\footnote{Again, \citet{GiW:06} does not make
+  this implicit assumption, but their statistic tests a different null
+  hypothesis.}
 
-\begin{thm}\label{thm:1}
-  Suppose that the following hold:
+Statistics for comparing two models are useful, but a researcher often
+has a set of potential models, and wants to know which of them
+significantly outperform the benchmark.  As \citet{Whi:00} shows,
+looking at the naive $p$-values is misleading, but bootstrapping the
+statistics can lead to a valid test (White calls this procedure the
+``bootstrap reality check'').  So I present a test for equal
+predictive ability of multiple models based on \citepos{RoW:05} StepM,
+which uses a step-down procedure that iteratively rejects models to
+achieve higher power than the reality check (see Theorem~\ref{res:2}
+for details) and will indicate which of the models improves on the
+benchmark.
+
+I also present a new result for the validity of using the stationary
+boostrap with \oos\ statistics, which is necessary to verify that the
+StepM is appropriate.  Existing results on boostrapping
+\oos\ statistics have some drawbacks.  \citet{Whi:00} and
+\citet{Han:05} use the stationary bootstrap, but require the test
+sample to be much smaller than the training sample, which is obviously
+inappropriate here.  \citet{CoS:07} relax that requirement, but only
+consider the moving block bootstrap \citep{LiS:92,Kun:89} and make the
+statistic more complicated than necessary by adjusting the objective
+function of the bootstrapped statistic to center it
+correctly.\footnote{Their recentering is required for consistency and
+  does not give higher order accuracy.}  A parametric bootstrap, such
+as that used by \citet{ClM:11}, would be difficult to implement here
+since we want to test whether several different null hypotheses hold
+individually (as I'll discuss later, Clark and McCracken test a single
+null hypothesis that describes the behavior of all of the models under
+consideration and does not let the researcher know which of the models
+outperforms, only that at least one does).  So this paper's result for
+the stationary bootstrap of \oos\ statistics considerably improves on
+existing procedures.
+
+The next section presents our theoretical result and
+Section~\ref{sec:2} presents two simulations that compare our pairwise
+\oos\ test to \poscw\ original statistic.  Section~\ref{sec:3}
+demonstrates the use of our statistic by reanalyzing \citepos{GoW:08}
+study of excess return predictability. Section~\ref{sec:4} concludes.
+
+\section{Theoretical Results}\label{sec:1}
+The first result modifies \citepos{ClW:07} so that it is
+asymptotically normal. The conditions are essentially the same in
+existing papers
+\citep[e.g.][]{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a
+modified window scheme.  Our result follows from \citet{Wes:96},
+treating the alternative model's forecasts as additional data. Note
+that asymptotic equivalence does not hold so we need to account for
+parameter estimation error.
+
+\begin{thm}\label{res:1}
+  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
+  forecast the variable $y_t$, and have observations for
+  $t=1,\dots,T+1$.  Assume the following hold:
   \begin{enumerate}
-  \item The coefficients for the benchmark forecast,
-    $\hat{y}_{1,t}(\beta_1)$, are estimated with least-squares over a
-    recursive window:
-    \[\hat{\beta}_{1t} = \argmin_{\beta} \sum_{s=1}^{t} (y_t -
-    \hat{y}_{1t}(\beta))^2, \qquad t = R,\dots,T-1.\]
-  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
-    a rolling window of fixed length $R$: $\hat{y}_{2,t} \in
-    \sigma(y_{t-R+1},\dots,y_t)$
-  \item $z_t \equiv (y_t, \hat{y}_{1,t}(\beta_1^{*}), \hat{y}_{2t})$
-    is strong mixing of size $-r/(r-2)$ and has uniformly bounded
-    $r+\delta$ moments for some positive $\delta$, with $\beta^{*} =
-    \argmin_{\beta} \E (y_t - \hat{y}_{1t}(\beta))^2$.
-
+  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
+    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
+    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
+    \begin{equation}
+      \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
+      \sum_{s=2}^t x_{t-1} y_t, \qquad t = R,\dots,T.
+    \end{equation}
+    Also define $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1}
+    x_{t-1}'\big)^{-1} \sum_{t=2}^T \E x_{t-1} y_t$.
+  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
+    estimated using a rolling window of fixed length $R$ (which is
+    less than $T$), so $\hat{y}_{1,t+1} =
+    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
+    function and $z_t$ is a sequence of predictors that includes
+    $x_t$.
+  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
+    $-1/2$ on a strong mixing series of size $-r/(r-2)$ for $r>2$ or a
+    uniform mixing series of size $-r/2(r-1)$.  Also, $y_t$,
+    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
+    moments for some positive $\delta$.
+  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
+    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
+    $\bar{f}(\beta) = P^{-1} \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
+    P^{-1} \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
+    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
+    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
+    long run variance.
   \end{enumerate}
-  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
-  martingale difference sequence, $\sqrt{P} \bar f / \hat{\sigma}
-  \to^d N(0,1)$, where
+  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
+  martingale difference sequence with respect to the filtration
+  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$, $\sqrt{P} \bar f /
+  \hat{\sigma} \to^d N(0,1)$, where
   \begin{align*}
-  \bar f
-  &\equiv P^{-1} \sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}),&  \hat{\sigma} &\equiv \Big(P^{-1}
-  \sum_{t=R+1}^T (f_t(\hat{\beta}_{t-1}) - \bar f)^2\Big)^{1/2},
+    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
+    \hat{S}_{ff} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
+    f)^2, \\
+    \hat{S}_{fg} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
+    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
+    \hat{S}_{gg} &= \frac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
+    g)(g_t(\hat{\beta}_t) - \bar g)',
   \end{align*}
- and    
+  $\Pi = 1 - (R/P) \log(1 + P/R)$, $\bar{g} = T^{-1}
+  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
   \begin{equation*}
-    f_t(\hat{\beta}_{t-1}) \equiv (y_t - \hat{y}_{1t}(\hat{\beta}_{t-1}))^2
-    - (y_t - \hat{y}_{2t})^2 +
-    (\hat{y}_{1t}(\hat{\beta}_{1,t-1}) - \hat{y}_{2t})^2
+  g_t(\beta) = \Bigg\{\frac{2}{P}\sum_{t=R}^{T-1} x_t (2 x_t'\beta -
+    y_{t+1} - \hat{y}_{1,t+1}) \Bigg\} \big(\X'\X / T \big)^{-1}  x_t(y_{t+1} - x_t'\beta).
   \end{equation*}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy $\tilde{R}_T \to \infty$ and
-  $\tilde{R}_T/T \to 0$ and define $\tilde{P} = T - \tilde{R}$ Then
+The following remarks are relevant to Theorem~\ref{res:1}:
+
+\begin{rem}
+  Forecasters will almost always be interested in the one-sided
+  alternative that $\E f_t(\beta_0) > 0$; i.e. that the alternative
+  model is expected to forecast better than the benchmark.
+\end{rem}
+
+\begin{rem}
+  These results are presented for one-period-ahead forecasting for
+  simplicity.  They can be extended to forecasting at a longer horizon
+  by appropriately modifying the variance-covariance matrix to account
+  for the correlation structure of the forecast errors. (i.e. for
+  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
+\end{rem}
+
+\begin{rem}
+  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
+  uniformly positive is much less restrictive than in \cite{Wes:96}.
+  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
+  serves to rule out pathological cases---for example, letting both
+  the benchmark and the alternative model be white noise. In
+  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
+  well as the forecasting models, but in this paper it is a
+  restriction only on the models.
+\end{rem}
+
+\begin{rem}
+  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
+  fixed.  But using West's general formula for $\Pi$ (which holds when
+  $P/R$ converges as $T \to \infty$) can improve the statistic in
+  practice, since researchers often invoke ``fixed $R$'' asymptotics
+  when $R$ is large.  Section~\ref{sec:2} shows via Monte Carlo that
+  this approximation can be accurate even when $R$ and $P$ are equal.
+\end{rem}
+
+\begin{rem}
+  If one wants to test the less restrictive null hypothesis that
+  $y_{t1} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
+  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with \hac\
+  counterparts.  Lemma~\ref{res:a5} presents a more general version of
+  the theorem that can cover this case.
+\end{rem}
+
+\begin{rem}
+  The statistic we present tests the null hypothesis that the forecast
+  errors from the population version of the benchmark model are a
+  martingale difference sequence.  This may not be appropriate,
+  depending on the loss function or utility function of interest.  Our
+  statistic can be modified to test implications of optimal forecasts
+  under other loss functions \citep[see][]{PaT:07,PaT:07b}.  Again,
+  Lemma~\ref{res:a5} can cover these other applications.
+\end{rem}
+
+I also use Lemma~\ref{res:1} to test multiple models at once.  There
+are two approaches one can take.  The first is to test whether any of
+the models can improve on the benchmark; \citet{Whi:00},
+\citet{Han:05}, and \citet{ClM:11} take this approach.  This approach
+requires testing a single null hypothesis, that the best model is no
+better than the benchmark, and one wants a test statistic to control
+size as usual.  The second approach, taken by \citet{RoW:05}, is to
+try to determine which models outperform the benchmark, and to find as
+many as possible that do.  Now there are as many hypotheses as there
+are models, so we need to control a quantity similar to size, the
+family-wise error rate, which is the probability that one or more true
+hypotheses is rejected.  To appreciate the difference between these
+two approaches, suppose that there are two models and the first
+outperforms a benchmark but the second doesn't.  Under the first
+approach, finding that both models outperform the benchmark is fine:
+the null (that none of them do) is false so we want to reject.  But
+under the second approach, this finding is a failure, as we
+incorrectly believe that the second model beats the benchmark.
+
+While methods like \citepos{Whi:00} and \citepos{Han:05} control the
+family-wise error, \citepos{RoW:05} StepM procedure will typically find
+more outperforming models while still controlling the family-wise error
+rate.  All of these methods rely on the bootstrap to estimate the
+joint dependence between the test statistic associated with each
+model.  The bootstrap we will use in this paper is new, and is
+outlined in Algorithm~\ref{alg:1}.
+\begin{alg}\label{alg:1}
+  \begin{enumerate}
+  \item Define the data matrices $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} =
+    (X_{R+1},\dots,X_{T-1})$ with
     \begin{equation*}
-    P^{-1/2}\sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}) = \tilde{P}^{-1/2}
-    \sum_{t=\tilde{R}+1}^T f_t(\hat{\beta}_{t-1}) + o_p(T^{-1/2}).
+      X_t = \begin{cases}
+        (y_{t+1}, x_t')' & t \leq R \\
+        (y_{t+1}, x_t', \hat{y}_{1,t+1})' & t > R.
+      \end{cases}
     \end{equation*}
-  Now, $\hat{\beta}_t = B(t) H(t)$ with
-  \begin{gather*}
-    B(t) = \Big(t^{-1} \sum_{s=1}^t \Big\{\Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)
-    \Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)' - (y_t -
-    \hat{y}_{1t}(\bar{\beta}_t))\frac{\partial^2}{\partial\beta \partial\beta'}
-    \hat{y}_{1t}(\bar{\beta}_t)\Big\}\Big)^{-1}, \\
-    H(t) = t^{-1} \sum_{s=1}^t (y_t - \hat{y}_{1t}(\beta^{*}))
-    \dd{\beta} \hat{y}_{1t}(\beta^{*}),
-  \end{gather*}
-  where $\bar{\beta}_t$ is between $\beta^{*}$ and $\hat{\beta}_t$
-  element-by-element.  Then our new out-of-sample average satisfies
-  the conditions of \citet[Theorem 4.1]{Wes:96} (with the moment and
-  weak dependence conditions weakened as in \citet[Theorem
-  2.3.1]{Mcc:00}).
+  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
+    stationary bootstrap with expected block size $b$ and denote each
+    sample as $\X_{\p, l}^{*}$; let $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
+  \item Estimate $\bar{f}^{*}_l$ and $\hat{\sigma}_l^{*}$ as in
+    Theorem~\ref{res:1} for each bootstrap sample $\X^{*}_l$.
+  \end{enumerate}
+\end{alg}
+
+Theorem~\ref{res:2} details the final procedure.
+
+\begin{thm}\label{res:2}
+  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
+  on the alternative model, $\hat{y}_{1t}$, holding for each of the
+  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$, let the subscript
+  $l$ denote the different quantities associated with $\hat{y}_{lt}$
+  (i.e. $\mathcal{F}_{lt}$, etc.), and let $H_l$ be the null
+  hypothesis that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
+  $F_{lt}$.  Also assume that the long-run variance-covariance matrix
+  of the vector $(\bar{f}_1,\dots,\bar{f}_m)'$ is uniformly positive
+  definite.
+
+  Let the $*$-superscript denote a random variable with the
+  distribution induced by the stationary bootstrap of
+  Algorithm~\ref{alg:1}, letting $X_t = (y_{t+1}, x_t', \hat{y}_{1,t+1},
+  \dots, \hat{y}_{m, t+1})'$ for $t > R$ (and unchanged for $t \leq
+  R$).  Define $M_j$ as follows:
+  \begin{enumerate}
+  \item define $M_0 = \emptyset$,
+  \item for $j = 1,2,\dots,m$, let $M_j = \{i : \bar{f}_{i} /
+    \hat{\sigma}_i > \hat{d}_j\}$, where $\hat{d}_j$ is the $1-\alpha$
+    quantile of $\max_{i \notin M_{j-1}} (\bar{f}_{i}^{*} -
+    \bar{f_i}(\hat{\beta}_{T+1})) / \hat{\sigma}_i^{*}$,
+  \end{enumerate}
+  and reject all of the hypotheses $H_i$ with $i \in \bigcup_{j=0}^m
+  M_j$.
+
+  If $b \to \infty$ and $b/P \to 0$, this algorithm controls the
+  \fwe\ at level $\alpha$ for the family of null hypotheses $H_i$
+  ($i=1,\dots,m$): the probability of rejecting any true $H_i$ is less
+  than or equal to $\alpha$.  Moreover, the probability that $H_i$ is
+  rejected converges to one if $y_{t} - \hat{y}_{0t}(\beta_0)$ and
+  $\hat{y}_{it}$ have nonzero correlation.
+\end{thm}
+
+The following remarks apply to Theorem~\ref{res:2}.
+
+\begin{rem}
+  The bootstrap does not and should not exploit the \mds\ null
+  hypotheses, even though the individual variance estimators do.
+  Imposing this null hypothesis (potentially through a parametric
+  bootstrap, as in \citen{ClM:11}) requires that $y_t - \hat{y}_{0t}$
+  be an \mds\ with respect to the filtration \[\sigma((y_t, z_{1,t-1},
+  \dots, z_{m,t-1}), (y_{t-1}, z_{1,t-2}, \dots, z_{m,t-2}), \dots)\]
+  which is stronger than even the composite null that it is an \mds\
+  with respect to all of the $m$ filtrations $\sigma(y_t, z_{i,t-1},
+  y_{t-1}, z_{i,t-2}, \dots)$ for $i = 1,\dots,m$.  Using a bootstrap
+  that imposes the null will give us a correct approximation to the
+  marginal distribution of each test statistic individual test
+  statistic, $\bar{f}_i / \hat{\sigma}_i$, but it will not necessarily
+  get their joint distribution correct.
+\end{rem}
+
+\begin{rem}
+  If calculating $\hat{\sigma}_i$ is burdensome, one can do the same
+  bootstrap without studentizing the statistics.  This procedure is
+  likely to have worse size and power properties, but may be more
+  convenient.  One could also estimate the variance with a second
+  bootstrap step, but execution might take too long to be practical
+  See \citet{Han:05} and \citet[Section~4.2]{RoW:05} for a discussion
+  of the benefits of studentization.
+\end{rem}
+
+\begin{rem}
+  Since the distribution of $\bar{f}_i$ is affected by the error in
+  estimating $\beta_0$, we need to re-estimate the benchmark model
+  in each bootstrap sample, unlike \citet{Whi:00}, \citet{Han:05}, or
+  \citet{HuW:10}.  But we do not need to re-estimate the alternative
+  models, so the additional computational burden is relatively small.
+\end{rem}
+
+\begin{rem}
+  How we handle the first $R$ observations does not affect the
+  asymptotic properties since $R$ is finite.  I've chosen to put them
+  at the beginning of each bootstrap sample so that sample means
+  correspond to population means of the bootstrap distribution.  Note
+  that the alternative forecasts are not defined for the first $R$
+  observations, so running the stationary bootstrap over the full
+  dataset is not possible.
+\end{rem}
+
+\begin{rem}
+  See \citet{RoW:05,RoW:06} for guidance on block length
+  selection.
+\end{rem}
+
+\begin{rem}
+  If the number of alternative models is large, controlling the \fwe\
+  may be too strict a criterion.  \citet{RSW:08} discuss procedures to
+  control criteria other than the \fwe, and one can use their
+  generalizations of the StepM procedure here as well.
+\end{rem}
+
+\section{General Results for the Bootstrap}\label{sec:1b}
+The validity of the stationary boostrap in Theorem~\ref{res:2} is a
+special case of a result of independent interest---the validity in
+general of the stationary bootstrap when \oos\ statistics are
+asymptotically normal.  Existing results---\citet{Whi:00},
+\citet{Han:05}, and \citet{CoS:07}---are not appropriate here;
+\citet{Whi:00} and \citet{Han:05} require that $R$ be very large,
+while this paper requires $R$ to be finite; and \citet{CoS:07} require
+a complicated modification of the statistic of interest be used to
+create the bootstrap distribution.  Instead of using these results,
+I'll present one more general.  The proof largely follows the approach
+of \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}, using the
+arguments of \citet{Cal:11d} for asymptotic normality.
+
+In this section, let $\to^{p^{*}}$ and $\to^{d^{*}}$ refer to
+convergence in probability or distribution conditional on the observed
+data.  Similarly, $\E^{*}$, $\var^{*}$, and $\cov^{*}$ refer to the
+expectation, variance, and covariance with respect to the probability
+measure induced by the stationary bootstrap, and $y_t^{*}$, etc. is
+the random variable $y_t$ but under the bootstrap-induced \cdf.
+
+Note that the notation in this section is more general than that of
+Section~\ref{sec:1}.  The assumptions required are generalizations of
+the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
+\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
+discussion of these conditions, as theirs are nearly identical.
+
+\begin{asmp}\label{asmp:a1} 
+  Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-1/2$ on a
+  strong mixing series $\{V_t\}$ of size $-r/(r-2)$, with $r > 2$.
+\end{asmp}
+
+\begin{asmp}\label{asmp:a2}  This assumption defines the series of
+  estimators $\hat{\beta}_t$.  We'll use two versions of this
+  assumption; the first is identical to \citepos{Wes:96} Assumption 2.
+  The second imposes more structure so that we can work out properties
+  of the estimator under the bootstrap induced probability measure.
+  \begin{enumerate}
+  \item[a.] The estimator $\hat{\beta}_t$ of $\beta_0$ satisfies
+    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$;
+    $\hat{B}_{t}$ is a sequence of $k$ by $q$ matrices that converges
+    almost surely to the deterministic sequence $B_{t}$, in the sense
+    that $\sup_{t \in \{S_T,\dots,T\}} | \hat{B}_{t} - B | \to 0$
+    almost surely for any sequence $S_T$ that diverges to $\infty$
+    with $T$; $H_{t}$ is a sequence of $q$-vectors such that $H_{t}
+    = (1/t) \sum_{s=1}^t h_{s}(\beta_{0})$, $h_{s}(\beta) =
+    h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0}) = 0$ for all
+    $s$.
+  \item[b.] In addition to part a, $B = B(\beta_{0}) =
+    \phi((1/T) \E \sum_{t=1}^T \Psi(y_{t}, z_{t},
+    \beta_{0}))$ and $\hat{B}_{t} =
+    \hat{B}_{t}(\hat{\beta}_{t}) = \phi((1/t) \sum_{s=1}^t \Psi(y_{t},
+    z_{t}, \hat{\beta}_{t}))$ for some known function $\Psi$ and
+    a known, continuous, and invertible function $\phi$.
+  \end{enumerate}
+\end{asmp}
+
+\begin{asmp}\label{asmp:a3}
+  Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector, where
+  $y_{t}$ and $z_{t}$ are from Assumption~\ref{asmp:a1} and $\beta$ is
+  a $k$-vector.  Then $\| \sup_{\beta \in N} f_{t}(\beta)
+  \|_{r+\delta}$ and $\| \sup_{\beta \in N} h_{t}(\beta)
+  \|_{r+\delta}$ are uniformly finite in $t$, where $N$ is an open
+  neighborhood of $\beta_{0}$ and $r$ is defined in
+  Assumption~\ref{asmp:a1}.
+\end{asmp}
+
+\begin{asmp}\label{asmp:a4}
+  Each element of $\E f_{t}(\beta)$ is continuously differentiable in
+  the neighborhood $N$.  Moreover, $\sup_{\beta \in N} |
+  F_{t}(\beta) |$ is uniformly finite in $t$ with
+  $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
+\end{asmp}
+
+\begin{asmp}\label{asmp:a5}
+  There exist finite constants $C$, $\phi > 0$, and $Q \geq r$ such
+  that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
+  \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) -
+  f_{t} \|_Q \leq C \epsilon^{\phi}\]
+  and \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
+  \sup_{\beta \in N(\beta_{0}, \epsilon)} h_{t}(\beta) -
+  h_{t} \|_Q \leq C \epsilon^{\phi},\] where $N(\beta, \epsilon) =
+  \{b : |b - \beta| < \epsilon\}$.
+\end{asmp}
+
+\begin{thm}\label{res:3}
+  If Assumptions~\ref{asmp:a1}--\ref{asmp:a5} hold , $P, b \to \infty$
+  and $b/P \to 0$ as $T \to \infty$, and (p.d. assumption holds) then
+  \begin{equation}
+    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
+        \leq x] - \pr[\sqrt{P}( \bar{f} - \E f(\beta_0)) \leq x] | >
+      \epsilon] \to 0
+  \end{equation}
+  for all $\epsilon > 0$.
+\end{thm}
+
+\begin{rem}
+  \citet{Whi:00}, \citet{Han:05}, and \citet{CoS:07} use the
+  distribution of $\sqrt{P}(\bar{f}^{*} - \bar{f})$ to approximate
+  that of $\sqrt{P}(\bar{f} - \E \bar{f}(\beta_0))$, while
+  Lemma~\ref{res:3} uses the distribution of $\sqrt{P}(\bar{f}^{*} -
+  \bar{f}(\hat{\beta}_{T+1}))$; $\hat{\beta}_{T+1}$ plays the same
+  role as $\beta_0$ under the bootstrap-induced probability measure.
+  Since $\hat{\beta}_t - \hat{\beta}_{T+1} = O_p(\sqrt{T-t})$, using
+  their bootstrap distribution is inconsistent unless $P/T$ vanishes
+  asymptotically, as in White and Hansen's
+  papers\footnote{\citet{Whi:00} and \citet{Han:05} actually require
+    that $P$ grow a little bit slower than $o(T)$.} or unless
+  $\hat{\beta}_t^{*}$ is further modified, as in Corradi and Swanson's
+  paper.
+\end{rem}
+
+\section{Monte Carlo Results}\label{sec:2}
+\input{mc}
+\section{Empirical Illustration}\label{sec:3}
+\input{empirics}
+\section{Conclusion}\label{sec:4}
+In this paper, we present an \oos\ test statistic similar to \poscw\
+that is asymptotically normal when comparing nested models.  We do so
+by estimating the alternative model using a fixed-length rolling
+window---as Clark and West do---but estimating the benchmark model
+with a recursive window.  We also present simulations that indicate
+the new statistic behaves similarly to Clark and West's original test,
+suggesting that the new statistic is a suitable replacement in applied
+research.
+
+\appendix
+\section*{Appendix}
+
+This Appendix restates \citepos{Mcc:00} results (which themselves
+weaken \citepos{Wes:96} assumptions) under the dependence conditions of
+Theorem~\ref{res:1}, which is fairly trivial.  It also presents a new
+stationary bootstrap for \oos\ statistics based on the recursive
+window that uses results in \citet{GoJ:03} to weaken \citepos{CoS:07}
+assumptions.  I'll use the same notation as in the main body of the
+paper, but functional forms and definitions are different here to
+reflect the increased generality.  By and large, a variable in the
+main paper (say $f_t$) is a special case of the same variable in this
+subsection.  We'll also use array notation in this section.
+
+\section{General Results}
+
+\begin{lema}\label{res:a2}
+  Suppose $a \in [0,1/2)$.
+  \begin{enumerate}
+  \item Under Assumptions~\ref{asmp:a1}a and~\ref{asmp:a2}a, $P^a
+    \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
+    \to^{p^{*}} 0$.
+  \item Under Assumptions~\ref{asmp:a1}b and~\ref{asmp:a2}b,
+    $\sup_{\beta \in N} \sup_t | \hat{B}_{t}^{*}(\beta) - B^{*}(\beta)
+    | \to^{p^{*}} 0$.
+  \item Under Assumptions~\ref{asmp:a1}a and~\ref{asmp:a2}a, $P^a
+    \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and, under
+    Assumptions~\ref{asmp:a1}b and~\ref{asmp:a2}b, $P^a \sup_t |
+    \hat{\beta}^{*}_{t} - \hat{\beta}_{T+1} | \to^{p^{*}} 0$.
+  \end{enumerate}
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a2}]
+  \begin{enumerate}
+  \item[1.] The process $h_{s} / \sqrt{T}$
+    satisfies \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
+    \begin{equation}
+      P^a \sup_t \Big| (1/t) \sum_{s=1}^t h_{s} \Big| =
+      P^a \sup_{\gamma \in [0,1]} \Bigg| \frac{1}{\lfloor \gamma
+        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Bigg| \to^{p} 0
+    \end{equation}
+    with the convergence following from the continuous mapping
+    theorem.  Now, let $U_t$ denote the number of blocks randomly
+    selected by the stationary bootstrap through period $t$, let $L_1,
+    \dots, L_{U_t}$ denote their lengths, and define $K_i =
+    \sum_{j=0}^{i-1} L_j$ (with $L_0 = 0$).  Conditional on
+    $L_1,\dots,L_{U_t}$, the sum
+    \begin{equation}
+      \frac{1}{t} \sum_{s=1}^t h_t^{*} = \frac{1}{N_t}
+      \sum_{i=1}^{N_t} \Bigg( \frac{N_t}{t} \sum_{t= K_{i-1} + 1}^{K_i}
+      h_t^{*} \Bigg)
+    \end{equation}
+    is the summation of independent random variables.  Define
+    \begin{equation}
+      \eta^{*2} = \var^{*}\Big(T^{-1/2} \sum_{t=1}^T h_t^{*} \,\Big|\,
+      L_1,\dots,L_T \Big);
+    \end{equation}
+    then $\eta^{*-1} T^{-1/2} \sum_{t=1}^{\gamma T} h_t^{*}$ converges
+    in distribution to a Brownian Motion conditional on the data and
+    the block lengths.  Since the limiting distribution does not
+    depend on the block lengths, we have unconditional convergence in
+    distribution as well, and repeating the argument for $\sup_t
+    |H_t|$ completes the proof.
+  \item As for part 1, we can break up the summation into its
+    independent blocks:
+    \begin{multline}
+      \sup_{\beta} \sup_t \Big| \sum_{s=1}^{t} \big(\Psi(y_t^{*},
+      z_t^{*},
+      \beta) - \E^{*} \Psi(y_t^{*}, z_t^{*}, \beta)\big) \Big| \leq \\
+      \sup_t \sum_{i=1}^{N_t} \sup_{\beta} \Big| \sum_{t =
+        K_{i-1}+1}^{K_i} \big(\Psi(y_t^{*}, z_t^{*}, \beta) - \E^{*}
+      \Psi(y_t^{*}, z_t^{*}, \beta)\big) \Big|
+    \end{multline}
+    And I need to finish this proof.
+  \item We have
+    \begin{multline}
+      P^a \sup_{t \in S_T} | \hat{\beta}_t - \beta_0 | = P^a \sup_{t
+        \in S_T} |\hat{B}_{t} H_{t}| \\ \leq \sup_{t,u \in S_T} \Big|
+      [ \hat{B}_u - B] (P^a/t) \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
+      B (P^a/t) \sum_{s=1}^t h_{s} \Big|
+    \end{multline}
+    and both terms converge to zero in (conditional) probability by
+    the previous argument and Assumption~\ref{asmp:a2}.  The same
+    argument holds for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ using
+    part 2.
+  \end{enumerate}
 \end{proof}
 
-\input{mc}
+\begin{lema}\label{res:a3}
+  Let $g_{t}' = (f_{t}' - \E f_{t}', a_t h_{t}')$ and $a_t =
+  \sum_{s=\max(R,t)}^T s^{-1}$.  Under Assumptions~\ref{asmp:a1}b,
+  \ref{asmp:a2}a, and~\ref{asmp:a3}
+  \begin{equation}
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ T^{-1/2} \sum_t^T g_{t}^{*}
+    \leq x \Big] - \pr\Big[ T^{-1/2} \sum_{t=1}^T g_{t}
+    \leq x \Big] \Big| > \epsilon \Big] \to 0
+  \end{equation}
+  for all positive $\epsilon$.
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a3}]
+  This result is an immediate consequence of \citet[Theorem 2]{GoJ:03}.
+\end{proof}
+
+The next Lemma restates \citepos{Mcc:00} Theorem 2.3.1 under our weak
+dependence conditions.  Note that we allow $R$ to diverge to infinity
+or to remain finite.
+
+\begin{lema}\label{res:a5}
+  If Assumptions~\ref{asmp:a1}, \ref{asmp:a3}, \ref{asmp:a4}, and
+  \ref{asmp:a5} hold, and instead of \ref{asmp:a2} we have the weaker
+  condition: The estimator $\hat{\beta}_t$ of $\beta_0$ satisfies
+  $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is a
+  sequence of $k$ by $q$ matrices that converges almost surely to the
+  deterministic sequence $B_{t}$, in the sense that $\sup_{t \in
+    \{S_T,\dots,T\}} | \hat{B}_{t} - B | \to 0$ almost surely for any
+  sequence $S_T$ that diverges to $\infty$ with $T$; $H_{t}$ is a
+  sequence of $q$-vectors such that $H_{t} = (1/t) \sum_{s=1}^t
+  h_{s}(\beta_{0})$, $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E
+  h_{s}(\beta_{0}) = 0$ for all $s$.  And $P \to \infty$ as $T \to
+  \infty$, (add p.d. assumption too) then
+  \begin{equation}
+    P^{-1/2} \sum_{t=R+1}^T
+    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
+  \end{equation}
+  with
+  \begin{align}
+    \Omega =     
+  \end{align}
+\end{lema}
+\begin{proof}[Proof of Lemma~\ref{res:a5}]
+  Let $R'$ satisfy $R' \to \infty$ as $T \to \infty$ and $R'/T \to 0$
+  and define $P' = T - R'$.  Then we can replace $P$ and $R$ with $P'$
+  and $R'$ in the preceding equations without changing the asymptotic
+  distributions of the statistics.  Note that $P'/R' \to \infty$.  The
+  proof then follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}
+\end{proof}
+
+\section{Proofs of Main Theoretical Results}
+
+\begin{proof}[Proof of Theorem \ref{res:1}]
+  The theorem is an immediate consequence of Lemma~\ref{asmp:a4}.
+  Note that \[f_t(\beta_0)= 2 (y_{t+1} - x_t'\beta_0)(x_t'\beta_0 -
+  \hat{y}_{1,t+1}) \quad \text{a.s.},\] as in \citet{ClW:07}, so we do
+  not need to use a \hac\ estimator of the variance under the null.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{res:2}]
+  The result for unstudentized statistics holds from Lemma~\ref{res:3}
+  and Theorem~3.1 of \citet{RoW:05}.  For studentized statistics, note
+  that
+  \begin{equation}
+    \hat{\sigma}_i^{*} = P^{-1} \sum_{t=R+1}^T (f_{it}(\hat{\beta}_t)
+    - \bar{f}_i(\hat{\beta}_T))^2 + o_{p^{*}},
+  \end{equation}
+  which converges to the same limit as $\hat{\sigma}_i$.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{res:3}]
+  Replace $R$ and $P$ with $R'$ and $P'$ as in the proof
+  of Lemma~\ref{res:a5}, and expand $\E^{*}
+  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
+  \begin{equation}
+    \sqrt{P'} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
+    \frac{1}{\sqrt{P'}} \sum_{t=R'+1}^T
+    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
+    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
+  \end{equation}
+  with the proof following exactly in \citet[Theorem 2.3.1]{Mcc:00}.
+  Note that $F^{*} = \hat{F} + o_{p}$ and $B^{*} = \hat{B}_{T+1} +
+  o_{p}$.  The result then follows from Lemma~\ref{res:a3} and the
+  consistency of these estimators.
+\end{proof}
 
 \bibliography{AllRefs}
+\end{document}
 
-\end{document}
+% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
+% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
+% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
+% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
+% LocalWords:  Corradi unstudentized studentized fg gg GoJ

### 2011-08-03 MakeScript.R

@@ -3,7 +3,7 @@
 # run in parallel.  Running this file will print out text for a
 # makefile, so it might be easiest to just look at its output.
 
-nsims <- 800  # this is the number of simulations
+nsims <- 5000  # this is the number of simulations
 njobs <- 8     # I set this to equal the number of processors on my 
                # computer.  Changing its value will change the results
                # of the simulations, since they'll be seeded differently.

### 2011-11-19 Paper.tex
Edited the paper and code

--- 2011-04-19 Paper.tex
@@
-\documentclass[12pt]{article}
+\documentclass[10pt,fleqn,draft]{article}
 
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage[nolists,nomarkers]{endfloat}
 \usepackage[sort,round]{natbib}
-\usepackage[margin=1in]{geometry}
+\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
 \usepackage[small]{caption}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
 
 \bibliographystyle{abbrvnat}
-\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
+\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
+\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
+\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
 \frenchspacing
-\onehalfspacing
+\input{tex/simulationdefinitions}
+\input{tex/empiricalresults}
+
+% redfine heading styles
+\makeatletter
+\renewcommand\section{\@startsection%
+{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
+{\normalfont\normalsize\bfseries\large\raggedright}}
+\makeatother
 
@@
 \DeclareMathOperator{\E}{E}
-\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
+\DeclareMathOperator{\var}{var}
+\DeclareMathOperator{\cov}{cov}
+%\DeclareMathOperator{\vec}{vec}
+\DeclareMathOperator{\vech}{vech}
+
+\DeclareMathOperator{\pr}{Pr}
+
+\newcommand{\X}{\ensuremath{\mathrm{X}}}
+\newcommand{\R}{\ensuremath{\mathrm{R}}}
+\newcommand{\p}{\ensuremath{\mathrm{P}}}
+
 \newcommand{\aic}{\textsc{aic}}
 \newcommand{\bic}{\textsc{bic}}
+\newcommand{\brc}{\textsc{brc}}
+\newcommand{\cdf}{\textsc{cdf}}
+\newcommand{\clt}{\textsc{clt}}
+\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
 \newcommand{\dgp}{\textsc{dgp}}
+\newcommand{\fclt}{\textsc{fclt}}
+\newcommand{\fwe}{\textsc{fwe}}
+\newcommand{\gdp}{\textsc{gdp}}
+\newcommand{\hac}{\textsc{hac}}
+\newcommand{\ma}{\textsc{ma}}
+\newcommand{\mds}{\textsc{mds}}
+\newcommand{\ned}{\textsc{ned}}
 \newcommand{\ols}{\textsc{ols}}
+\newcommand{\oos}{\textsc{oos}}
+\newcommand{\sfwe}{\textsc{sfwe}}
+\newcommand{\spa}{\textsc{spa}}
+\newcommand{\wfwe}{\textsc{wfwe}}
+
+\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
+
+\renewcommand{\topfraction}{.85}
+\renewcommand{\bottomfraction}{.7}
+\renewcommand{\textfraction}{.15}
+\renewcommand{\floatpagefraction}{.66}
+\renewcommand{\dbltopfraction}{.66}
+\renewcommand{\dblfloatpagefraction}{.66}
+\setcounter{topnumber}{9}
+\setcounter{bottomnumber}{9}
+\setcounter{totalnumber}{20}
+\setcounter{dbltopnumber}{9}
 
@@
 
-\author{Gray Calhoun}
-\title{A comment on ``Approximately normal tests for equal predictive
-  accuracy in nested models''}
-\date{\today}
+\author{Gray Calhoun\thanks{ Economics Department; Iowa State
+    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
+    \texttt{gcalhoun@iastate.edu}.  Web:
+    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
+    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
+    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
+    participants at the 2011 Midwest Econometrics Group meeting for
+    helpful comments.  I'd also like to thank Amit Goyal for providing
+    computer code and data for his 2008 \textsc{rfs} paper with Ivo
+    Welch \citep{GoW:08}.} \\
+  Iowa State University}
+
+\title{An asymptotically normal out-of-sample
+  test of equal predictive accuracy for nested models} \date{\today}
 \maketitle
@@
 \begin{abstract} 
-  \noindent This paper proposes a slight modification of
-  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
-  to estimate the alternative model under a fixed-length rolling
-  window, but estimate the benchmark model under a recursive
-  window. The resulting statistic gives an asymptotically normal test
-  statistic that the benchmark model is correctly specified, even when
-  it is nested in the alternative.  Moreover, the alternative model
-  can be estimated using populare model selection methods, such as the
-  \aic\ or \bic.
+  \noindent This paper proposes a modification of \citepos[\textit{J.
+    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
+  alternative model is still estimated with a fixed-length rolling
+  window, but the benchmark is estimated with a recursive window. The
+  resulting statistic is asymptotically normal even when the models
+  are nested.  Moreover, the alternative model can be estimated using
+  common model selection methods, such as the \aic\ or \bic.  This
+  paper also presents a method to compare multiple models
+  simultaneously while controlling familywise error, and
+  substantially improves existing block bootstrap methods for
+  out-of-sample statistics.  This procedure is then used to analyze
+  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.
 
@@
 
-\newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
-an out-of-sample test of the null hypothesis that a small benchmark
-model is correctly specified.  Their test compares the forecasting
-performance of a pair of nested models, and the null hypothesis is
-that the innovations in the smaller model are a martingale difference
-sequence.  This test procedure is quite popular,\footnote{As of 19
-  April 2011, \citet{ClW:06} has been cited by 25 papers indexed by
-  the ISI Web of Knowledge, and \citet{ClW:07} by 35.} and one assumes
-that this is due in part to the statistic's convenience.  The
-statistic is approximately normal after adjusting for the estimation
-error of the larger model.  Normality comes from a fixed-length
-rolling window, as in \citet{GiW:06}, and the adjustment centers the
-statistic at the appropriate population quantities.  This statistic is
-especially convenient because other tests for similar hypotheses
-\citep[see][among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01}
-lead to a nonstandard limit distribution and place restrictions on the
-models under consideration, while other asymptotically normal
-statistics \citep{GiW:06} test a different null hypothesis.
+\newpage \noindent This paper proposes an out-of-sample (\oos) test
+statistic that is asymptotically normal with mean zero even when the
+models studied are nested, proves that common block bootstrap methods
+consistently estimate the statistic's distribution, and shows how the
+statistic can be used to study many models simultaneously while
+maintaining strong control of the familywise error (\fwe),
+i.e. ensuring that the probability that the hypothesis that the model
+has equal predictive ability to a benchmark is incorrectly rejected
+for any of the models is no higher than a prespecified level.  \oos\
+tests are commonly used in International Macroeconomics,
+Macroeconomics, and Finance \citep[see, for
+example,][]{MeR:83,StW:03,GoW:08} and there is a substantial
+literature developing the theoretical properties of these statistics,
+beginning primarily with \citet{DiM:95} and
+\citet{Wes:96}.\footnote{Other papers in this literature include
+  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
+  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
+  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
+  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
+  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
+  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
+  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
+  reviews of this literature and additional references, see
+  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
+  \citet{CoD:11}, and \citet{Gia:11}}
+
+In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
+the null hypothesis that a small benchmark model is correctly
+specified.  Their test compares the forecasting performance of a pair
+of nested models, and the null hypothesis is that the innovations in
+the smaller model form a martingale difference sequence.  This test
+procedure is popular, and one assumes that this is due in part to the
+statistic's convenience.  The statistic is approximately normal after
+adjusting for the estimation error of the larger model.  Normality
+comes from a fixed-length rolling window, as in \citet{GiW:06}, and
+the adjustment centers the statistic appropriately.  This statistic is
+especially convenient because other \oos\ tests for similar hypotheses
+\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
+nonstandard limit distribution and place restrictions on the models
+under consideration, while other asymptotically normal statistics test
+a different null hypothesis \citep{GiW:06} or place assumptions on the
+models and \dgp\ that are often violated in empirical work
+\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.\footnote{\citet{DiM:95} assume
+  that the models are not estimated. \citet{Wes:96,WeM:98,Mcc:00}
+  implicitly assume that the models do not converge to the same limit,
+  which rules out nesting.}
 
 However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present monte carlo evidence of
+in an informal sense.  Clark and West present Monte Carlo evidence of
 the statistic's distribution, but only prove that the statistic is
-asymptotically normal when the benchmark model is a random walk
-\citep{ClW:06}. Estimating the parameters of the smaller model
-invalidates the proof.
+asymptotically normal with mean zero when the benchmark model is a
+random walk \citep{ClW:06}. Estimating the parameters of the smaller
+model invalidates their proof.
 
-In this note, I prove that a slightly modified version of their
-statistic is asymptotically normal even when the smaller model is
-estimated.  Essentially, we need a consistent estimate of the forecast
-errors of the pseudo-true version of the benchmark models, while
-maintaining inconsistent estimates of the larger model's errors so
-that we can ignore the fact that the models are nested.  We can meet
-both needs by using different window strategies for each model.  We
-estimate the benchmark model using a recursive window scheme, and
-estimate the alternative using a fixed-length rolling window.
+In this paper, I show that a modified version of their statistic is
+asymptotically normal even when the smaller model is estimated.  To
+achieve normality, we need a consistent estimate of the pseudo-true
+benchmark model, while maintaining an inconsistent estimate of the
+larger model so that we can ignore nesting.  We can meet both needs by
+using different window strategies for each model: the benchmark model
+is estimated using a recursive window and the alternative with a
+fixed-length rolling window.
 
-Mixing window strategies is uncommon but it shouldn't be. In most
-applications, the null hypothesis imposes both equal accuracy between
-the two models and stability.  The benchmark model rarely allows for
-breaks, parameter drift, or other instability,\footnote{An exception
-  might be \possessivecite{StW:08} IMA(1,1) model of inflation.} but
-the researcher is typically concerned about instability.  Indeed,
-concern about instability is often given as a reason for doing an
-out-of-sample analysis, especially with a short rolling window
-\citep{GiW:06,GiR:09,GiR:10}.  So using a different window strategy
-for each model--a recursive window for the model that imposes
-stability, and a rolling window for the model that relaxes
-stability--is a natural approach and is similar in spirit to the
-Likelihood Ratio Test\footnote{Using a rolling window for both models
-  would be analagous to a Wald test and using recursive window for
-  both would be like the LM test.}
+Mixing window strategies is uncommon but needn't be. In most
+applications, the null hypothesis imposes stability as well as equal
+accuracy between the two models.  The benchmark model rarely allows
+for breaks, parameter drift, or other forms of
+instability,\footnote{Exceptions are \citepos{StW:07}
+  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
+researcher is typically concerned about instability.  Indeed, concern
+about instability is often given as a reason for doing an \oos\
+analysis, especially with a short rolling window.\footnote{This
+  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
+  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
+  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
+stability on both models by using a recursive window or relax
+stability for both by using a rolling window; either approach should
+not affect the test's size, but may affect power.  But the researcher
+could instead impose stability on the benchmark and relax it for the
+alternative by using a recursive window for the benchmark and a
+rolling window for the alternative model.  This approach could have a
+power advantage and is similar in spirit to using a likelihood ratio
+test instead of an \textsc{lm} or Wald test, which depend on just the
+restricted or unrestricted model respectively.  Simulations presented
+in Section~\ref{sec:2} show that mixing window strategies gives a
+substantial power advantage when there are breaks.
 
-Our statistic has a substantial advantage over existing out-of-sample
-statistics for nested models: the benchmark can be essentially
-arbitrary, as long as it obeys the necessary moment conditions.  In
-particular, it can use model selection techniques like the \aic\ or
-\bic\ to determine things like the number of lags to include, the
-particular exogenous variables to include, etc.  Other methods that
-test a similar hypothesis are unable to handle these models
-\citep[except][which does not allow the benchmark to be
-estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
-both the alternative and the benchmark, but they test a different
-aspect of forecasting performance.
+This paper's statistic has a substantial advantage over existing \oos\
+tests for nested models: the alternative can be essentially arbitrary,
+as long as it obeys the necessary moment conditions.  In particular,
+researchers can use model selection techniques like the \aic\ or \bic\
+to determine the number of lags to include, the particular exogenous
+variables to include, etc.  Other methods that test a similar
+hypothesis are unable to handle these models \citep[except][which does
+not allow the benchmark to be estimated]{ClW:06}; \citet{GiW:06} are
+able to handle such models for both the alternative and the benchmark
+but, as mentioned earlier, they test a different aspect of forecasting
+performance.
 
-We'll present our results as a single theorem.  The conditions are
-essentially the same as
-\citet{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a modified
-window scheme.  We require that the benchmark model be estimated by
-least squares, but that is for convenience and could be relaxed.
-Changing the estimation strategy of the benchmark model would amount
-to changing the null hypothesis.
+This paper focuses on nested models, as they have received the most
+attention in the empirical and theoretical literature, but the
+statistic can be used with non-nested models as well.  This generality
+is useful, since \citepos{Wes:96} results do not apply to non-nested
+models if they both encompass the true \dgp,\footnote{\citet{ClM:11b}
+  call this scenario, ``overlapping models.''} which is allowable
+under the null: in the limit, both models will converge to the \dgp\
+and give identical forecasts.  Consequently, the naive \oos\ $t$-test
+is invalid, even after correcting the standard error if necessary to
+reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
+window \oos\ $t$-test remains normal for these models but the
+recursive and rolling windows (with the window size increasing to
+$\infty$) do not, and provide a procedure for pointwise (but not
+uniformly) valid tests for the recursive and rolling windows and
+uniformly valid tests for the fixed window.  The test proposed in this
+paper is uniformly valid and places fewer assumptions on the models
+under study and the true \dgp.
 
-\begin{thm}\label{thm:1}
-  Suppose that the following hold:
+Since researchers often have a set of potential models and want to
+know which of them significantly outperform the benchmark, procedures
+that compare a single pair of models are of limited practical use.  As
+\citet{Whi:00} demonstrates, looking at the naive $p$-values of the
+individual tests is misleading, but researchers can get a valid test
+by using the bootstrap to approximate the distribution of the largest
+individual test statistic under the null (White calls this procedure
+the ``bootstrap reality check'' or \brc).  This paper presents a test
+for equal predictive ability of multiple models based on
+\citepos{RoW:05} StepM, which uses a step-down procedure that
+iteratively rejects models to achieve higher power than the \brc\ and
+indicate which of the models improves on the benchmark (see
+Theorem~\ref{res:2} for details).  Since this paper is concerned with
+one-sided testing, I use the modified StepM procedure proposed by
+\citet{Cal:11e}; the original StepM procedure unnecessarily sacrifices
+power when testing one-sided hypotheses because, as \citet{Han:05}
+points out for \citepos{Whi:00} \brc, alternative models that
+substantially under-perform increase the test's critical values too
+much.\footnote{Note that the modification suggested by \citet{Cal:11e}
+  is different than \citepos{Han:05} and is explicitly designed for
+  stepwise testing.}
+
+This paper also presents a new result for the validity of block
+bootstraps with \oos\ statistics, which is necessary to verify that
+the StepM is valid.  Existing results on bootstrapping \oos\
+statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
+the stationary bootstrap, but require the test sample to be much
+smaller than the training sample, which is obviously inappropriate
+here.  \citet{CoS:07} relax that requirement, but make the statistic
+more complicated than necessary by adjusting the objective function of
+the bootstrapped statistic to center it correctly.\footnote{Their
+  recentering is required for consistency and does not give higher
+  order accuracy.}  A parametric bootstrap, such as that used by
+\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:11}, is an alternative
+method, but requires the benchmark model to be correctly specified.
+Although I focus on the null hypothesis that the benchmark is
+correctly specified, this paper's block bootstrap methods remain valid
+when the benchmark is misspecified and are relatively easy to
+implement.  So this paper's result for bootstrapping \oos\ statistics
+considerably improves on existing procedures.
+
+The next section presents our new statistics and Section~\ref{sec:1b}
+our block bootstrap result.  Section~\ref{sec:2} presents two
+simulations that compare our pairwise \oos\ test to \poscw\ original
+statistic.  Section~\ref{sec:3} demonstrates the use of our statistic
+by reanalyzing \citepos{GoW:08} study of excess return
+predictability. Section~\ref{sec:4} concludes.
+
+\section{Out-of-Sample Model Comparisons}\label{sec:1}
+This section presents the new \oos\ statistic.  I'll present the
+single-comparison statistic first and then the extension to multiple
+comparisons.  Suppose for now that a researcher is interested in
+predicting the target variable $y_{t+1}$ with a vector of regressors
+$x_t$; further, let $v_t$ be another random process and suppose that
+$(y_t, x_t, v_t)$ is stationary and weakly dependent
+(Theorem~\ref{res:1} lists the detailed assumptions required).  In
+addition, let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the
+pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
+define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
+model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
+difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
+y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
+\begin{equation}
+  \label{eq:4}
+  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
+  - v_t) 
+\end{equation}
+with $R$ an arbitrary starting value\footnote{You will see momentarily
+  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
+obeys an \mds\ \clt\ (assuming that its variance is uniformly
+positive) and is asymptotically normal as $P \to \infty$.
+Straightforward algebra \citep{ClW:07} shows that
+\begin{equation}
+  \label{eq:5}
+  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
+  - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
+  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
+\end{equation}
+
+\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
+of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
+the size of the test sample used to evaluate the forecasting models.
+\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
+use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
+function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
+$z_{t-R}$ where $z_t$ is another weakly dependent random process),
+which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
+the weak dependence properties of the variables used to estimate it.
+Moreover, keeping $R$ finite ensures that the conditional variance
+remains positive, so the \clt\ holds.  This method of ensuring
+normality was introduced by \citet{GiW:06}.  The coefficients
+$\beta_0$ are assumed to be zero so $\varepsilon_{t+1}$ is observed
+directly (under the null hypothesis) and they propose using this
+statistic to test the null that $\beta_0 = 0$.  In \citet{ClW:07},
+$\beta_0$ is unknown but is estimated with a fixed-length rolling
+window as well, so
+\begin{equation*}
+  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{t-1} x_{t-1}'\Big)^{-1}
+  \sum_{s=t-R+1}^t x_{t-1} y_t
+\end{equation*}
+and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
+$\varepsilon_{t+1}$ in the test statistic for $\beta_0 = 0$.
+Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an \mds, so the
+statistic is no longer asymptotically mean-zero normal, even though
+this approximation performs well in the simulations reported by
+\citet{ClW:07}.
+
+This paper proposes using the same basic \oos\ statistic, 
+but using a recursive window to estimate $\beta_0$ and produce
+$\hat{\varepsilon}_{t+1}$; i.e.
+\begin{equation}
+  \label{eq:8}
+  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
+  \sum_{s=2}^t x_{t-1} y_t.
+\end{equation}
+\citepos{Wes:96} Theorem 4.1 implies that
+\begin{equation*}
+  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
+  x_t\hat{\beta}_t)^2 + (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
+\end{equation*}
+is asymptotically normal for fairly arbitrary processes $v_t$, as long
+as $v_t$ is weakly dependent and the \oos\ statistic has uniformly
+positive variance.  Just as in \citet{ClW:06}, these conditions are
+ensured if $v_t$ is another forecast of $y_{t+1}$ based on a fixed
+length rolling window.  Theorem~\ref{res:1} presents the details of
+this result.  The assumptions required are essentially the same in
+existing papers (e.g. \citealp{Wes:96}; \citealp{WeM:98};
+\citealp{Mcc:00}; \citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
+Please see the original papers for a discussion of these assumptions.
+
+\begin{thm}\label{res:1}
+  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
+  forecast the variable $y_t$, and have observations for
+  $t=1,\dots,T+1$.  Assume the following hold:
   \begin{enumerate}
-  \item The coefficients for the benchmark forecast,
-    $\hat{y}_{1,t}(\beta_1)$, are estimated with least-squares over a
-    recursive window:
-    \[\hat{\beta}_{1t} = \argmin_{\beta} \sum_{s=1}^{t} (y_t -
-    \hat{y}_{1t}(\beta))^2, \qquad t = R,\dots,T-1.\]
-  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
-    a rolling window of fixed length $R$: $\hat{y}_{2,t} \in
-    \sigma(y_{t-R+1},\dots,y_t)$
-  \item $z_t \equiv (y_t, \hat{y}_{1,t}(\beta_1^{*}), \hat{y}_{2t})$
-    is strong mixing of size $-r/(r-2)$ and has uniformly bounded
-    $r+\delta$ moments for some positive $\delta$, with $\beta^{*} =
-    \argmin_{\beta} \E (y_t - \hat{y}_{1t}(\beta))^2$.
-
+  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
+    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
+    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
+    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
+    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
+    \sum_{t=2}^T \E x_{t-1} y_t$.
+  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
+    estimated using a rolling window of fixed length $R$ (which is
+    less than $T$), so $\hat{y}_{1,t+1} =
+    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
+    function and $z_t$ is a sequence of predictors that includes
+    $x_t$.
+  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
+    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
+    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
+    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
+    moments for some positive $\delta$.
+  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
+    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
+    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
+    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
+    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
+    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
+    long run variance.
   \end{enumerate}
-  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
-  martingale difference sequence, $\sqrt{P} \bar f / \hat{\sigma}
-  \to^d N(0,1)$, where
+  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
+  martingale difference sequence with respect to the filtration
+  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
+  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
   \begin{align*}
-  \bar f
-  &\equiv P^{-1} \sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}),&  \hat{\sigma} &\equiv \Big(P^{-1}
-  \sum_{t=R+1}^T (f_t(\hat{\beta}_{t-1}) - \bar f)^2\Big)^{1/2},
+    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
+    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
+    f)^2, \\
+    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
+    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
+    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
+    g)(g_t(\hat{\beta}_t) - \bar g)',
   \end{align*}
- and    
+  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
+  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
   \begin{equation*}
-    f_t(\hat{\beta}_{t-1}) \equiv (y_t - \hat{y}_{1t}(\hat{\beta}_{t-1}))^2
-    - (y_t - \hat{y}_{2t})^2 +
-    (\hat{y}_{1t}(\hat{\beta}_{1,t-1}) - \hat{y}_{2t})^2
+    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
+    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
+    x_t(y_{t+1} - x_t'\beta).
   \end{equation*}
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy $\tilde{R}_T \to \infty$ and
-  $\tilde{R}_T/T \to 0$ and define $\tilde{P} = T - \tilde{R}$ Then
+The following remarks are relevant to Theorem~\ref{res:1}:
+
+\begin{rem}
+  Forecasters will be interested in the one-sided alternative that $\E
+  f_t(\beta_0) > 0$; i.e. that the alternative model is expected to
+  forecast better than the benchmark.
+\end{rem}
+
+\begin{rem}
+  These results are presented for one-period-ahead forecasting for
+  simplicity.  They can be extended to forecasting at a longer horizon
+  by appropriately modifying the variance-covariance matrix to account
+  for the correlation structure of the forecast errors. (i.e. for
+  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
+\end{rem}
+
+\begin{rem}
+  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
+  uniformly positive is much less restrictive than in \cite{Wes:96}.
+  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
+  serves to rule out pathological cases---for example, letting both
+  the benchmark and the alternative model be white noise. In
+  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
+  well as the forecasting models, but in this paper it is a
+  restriction only on the models.
+\end{rem}
+
+\begin{rem}
+  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
+  fixed.  But using West's general formula for $\Pi$ (which holds when
+  $\lim \tfrac{P}{R} \in [0,\infty]$) can improve the statistic in practice,
+  since researchers often invoke ``fixed $R$'' asymptotics when $R$ is
+  large.  Section~\ref{sec:2} shows via Monte Carlo that this
+  approximation can be accurate even when $R$ and $P$ are equal.
+\end{rem}
+
+\begin{rem}
+  If one wants to test the less restrictive null hypothesis that
+  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
+  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with their
+  \hac\ counterparts.  Lemma~\ref{res:a5} presents a more general
+  version of the theorem that can cover this case.
+\end{rem}
+
+\begin{rem}
+  The statistic we present tests the null hypothesis that the forecast
+  errors from the population version of the benchmark model are a
+  martingale difference sequence.  This hypothesis may not be
+  appropriate, depending on the loss function or utility function of
+  interest.  Our statistic can be modified to test implications of
+  optimal forecasts under other loss functions
+  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
+  a forecast encompassing test using the models' generalized forecast
+  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
+  Again, Lemma~\ref{res:a5} can cover these other applications.
+\end{rem}
+
+\begin{rem}
+  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
+  window but claim that their results hold for a fixed-length fixed
+  window as well, where the unknown coefficients are estimated only
+  once using the first $R$ observations.  This claim is true but not
+  obviously so.  The proof for the rolling window is based on the idea
+  that the forecast errors are weakly dependent because they are a
+  function of a finite number of consecutive weakly dependent
+  observations.  But using a fixed window introduces another source of
+  dependence.  All of the forecasts depend on the same coefficient
+  estimates.  One can prove that their results apply to fixed window
+  forecasts by using a coupling argument similar to \citepos{Cal:11}.
+  Interested readers should refer to \citet{Cal:11} for the argument
+  and to \citet{MeP:02} for a review of the necessary coupling
+  results.
+\end{rem}
+
+Since most empirical papers study more than one alternative model,
+Theorem~\ref{sec:1} is of limited use on its own.\footnote{Moreover,
+  we would need to account for the existence of multiple models even if
+each paper considers a single model, since there are many papers
+studying the same data.}  It can, however, be
+used as the basis for a procedure that allows researchers to make
+multiple comparisons.  Before presenting a theoretical result, I'll
+discuss some issues related to multiple hypothesis testing.
+
+Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
+clear that testing each hypothesis individually will often have a
+probability greater than the tests' nominal size of rejecting at least
+once.\footnote{Unless the statistics used for each test are completely
+  interdependent, the probability will be strictly greater than the
+  nominal size.}  Econometricians, e.g. \citet{Whi:00},
+\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
+statistics that test families of hypotheses that control the
+probability any hypothesis is rejected given that they all are true,
+known as \textit{weak control of familywise error}
+(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
+  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
+  control \sfwe\ for certain families of one-sided tests.}  This paper
+focuses instead on controlling the probability that at least one true
+hypothesis is rejected given any combination of true and false
+hypotheses, known as \textit{strong control of familywise error}
+(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
+even though these papers only prove \wfwe, statistics based on
+nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
+control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
+and those based on the parametric bootstrap \citep{ClM:11} essentially
+control \sfwe\ if the individual null hypotheses are strengthened
+slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
+well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
+construct critical values from the asymptotic joint distribution of
+the test statistics and can control \sfwe\ as long as there is a
+consistent estimate of that distribution.
+
+Only tests that have \sfwe\ can tell researchers which of the
+hypotheses are false.  To see why, imagine that there are only two
+hypotheses: $H_1$ is true and $H_2$ is false.  A test that rejects the
+true hypothesis, $H_1$, with arbitrarily high probability still can
+satisfy \wfwe: since not all of the hypotheses are true, the behavior
+of tests with weak control is essentially unconstrained.  Such a test
+would not satisfy \sfwe, though.  For \sfwe\ in this setting, a test
+must reject $H_1$ with probability at most $\alpha$ (letting $\alpha$
+be the desired level of control).  In most research, we would view
+rejection of the true hypothesis $H_1$ a mistake.
+
+This paper uses a variation of \citepos{RoW:05} StepM procedure, which
+is an iterated extension of \citepos{Whi:00} Reality Check designed to
+reject as many false hypotheses as possible while achieving \sfwe.
+This method relies on the bootstrap to estimate the joint dependence
+between the test statistic associated with each model.  The bootstrap
+used in this paper is new, and is outlined in Algorithm~\ref{alg:1}.
+Algorithm~\ref{alg:1} actually presents a more general version of the
+bootstrap that remains valid with a misspecified benchmark model.
+Imposing the null hypothesis of \mds\ leads to simpler version that
+will be discussed later.
+\begin{alg}\label{alg:1}
+  Suppose that there are $m$ alternative forecasting models,
+  $\hat{y}_{1t},\dots, \hat{y}_{mt}$, and define the data matrices
+  $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} = (X_{R+1},\dots,X_{T-1})$
+  with
   \begin{equation*}
-    P^{-1/2}\sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}) = \tilde{P}^{-1/2}
-    \sum_{t=\tilde{R}+1}^T f_t(\hat{\beta}_{t-1}) + o_p(T^{-1/2}).
+    X_t = \begin{cases}
+      (y_{t+1}, x_t')' & t \leq R \\
+      (y_{t+1}, x_t', \hat{y}_{1,t+1}, \dots, \hat{y}_{m,t+1})' & t > R.
+    \end{cases}
   \end{equation*}
-  Now, $\hat{\beta}_t = B(t) H(t)$ with
-  \begin{gather*}
-    B(t) = \Big(t^{-1} \sum_{s=1}^t \Big\{\Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)
-    \Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)' - (y_t -
-    \hat{y}_{1t}(\bar{\beta}_t))\frac{\partial^2}{\partial\beta \partial\beta'}
-    \hat{y}_{1t}(\bar{\beta}_t)\Big\}\Big)^{-1}, \\
-    H(t) = t^{-1} \sum_{s=1}^t (y_t - \hat{y}_{1t}(\beta^{*}))
-    \dd{\beta} \hat{y}_{1t}(\beta^{*}),
-  \end{gather*}
-  where $\bar{\beta}_t$ is between $\beta^{*}$ and $\hat{\beta}_t$
-  element-by-element.  Then our new out-of-sample average satisfies
-  the conditions of \citet[Theorem 4.1]{Wes:96} (with the moment and
-  weak dependence conditions weakened as in \citet[Theorem
-  2.3.1]{Mcc:00}).
+  \begin{enumerate}
+  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
+    moving or circular blocks bootstrap with block length $b$ or the
+    stationary bootstrap with geometric block lengths with success
+    probability $p$.  Denote each sample as $\X_{\p, l}^{*}$ and let
+    $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
+  \item Estimate $\bar{f}^{*}_{li}$ and $\hat{\sigma}_{li}^{*}$ as in
+    Theorem~\ref{res:1} for each bootstrap sample, $\X^{*}_l$, and each
+    alternative model, $\hat{y}_{it}$.
+  \end{enumerate}
+\end{alg}
+
+This procedure exploits the fact that $R$ is finite in
+Theorem~\ref{res:1} and that the expected block length will grow with
+$T$.  Under these asymptotics, a growing proportion of the
+rolling-window forecasts are the same if we bootstrap the forecasts as
+if we bootstrap the empirical data and reestimate the models.
+Bootstrapping the forecasts makes the computations faster and easier,
+but requires us to drop the first $R$ observations from the bootstrap
+(the alternative forecasts are not defined for the first $R$
+observations).  I add those observations to the beginning of each
+bootstrap sample so that population means under the bootstrap-induced
+probability distribution equal sample means.  Note that the benchmark
+model needs to be reestimated in each bootstrap sample.
+
+Theorem~\ref{res:2} presents the final procedure.
+
+\begin{thm}\label{res:2}
+  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
+  on the alternative model, $\hat{y}_{1t}$, holding for each of the
+  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
+  $l$ denote the different quantities associated with $\hat{y}_{lt}$
+  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
+  variance-covariance matrix of the vector
+  $(\bar{f}_1(\beta_0),\dots,\bar{f}_m(\beta_0))'$ is uniformly
+  positive definite.
+
+  Let the $*$-superscript denote a random variable with the
+  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
+  consider the following procedure:
+  \begin{enumerate}
+  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
+    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
+    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
+      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
+    \bar{f_i}(\hat{\beta}_{T+1})|$.
+  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
+    and $\bar f_i > 0$.
+  \end{enumerate}
+  The following conclusions hold:
+  \begin{enumerate}[i.]
+  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
+    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
+    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
+    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
+    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
+    procedure outlined above, but using the moving block bootstrap
+    with block length $1$, has probability at most $\alpha$ of rejecting
+    one or more models in $I$.
+  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
+    \hat{y}_{0t}$ is an \textsl{\mds} with respect to $\mathcal{F}_{lt}$
+    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
+    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
+    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
+    (for the moving or circular block bootstraps) then the procedure
+    outlined above controls \sfwe\ at level $\alpha$ for the family of
+    null hypotheses $H_1,\dots,H_m$.
+  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
+    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
+    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
+    and $P p \to \infty$ as $T \to \infty$ (for the stationary
+    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
+    moving or circular block bootstraps) then the procedure outlined
+    above controls \sfwe\ at level $\alpha$ for the family of null
+    hypotheses $H_1,\dots,H_m$.
+  \end{enumerate}
+\end{thm}
+
+The following remarks apply to Theorem~\ref{res:2}.
+
+\begin{rem}
+It is worth emphasizing that this procedure is very easy to use under
+the null hypothesis of correct specification (Part~\ref{it:1}).  The
+researcher can use a standard estimate of the statistic's asymptotic
+variance (not a \hac\ estimator) and an i.i.d. bootstrap.  Even
+better, the alternative forecasts only need to be estimated once,
+before the bootstrap.
+\end{rem}
+
+\begin{rem}\label{rem:2}
+  The key difference between Parts~(\ref{it:1}) and~(\ref{it:2}) is
+  that, in Part~(\ref{it:2}), the forecast error is an \mds\ with
+  respect to several individual series, but not necessarily with
+  respect to the pooled information set generated by all of those
+  series together.\footnote{It is straightforward to construct three
+    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
+    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
+    $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
+    $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
+    This is essentially the scenario imposed in Part~(\ref{it:2}).}
+  Using $b = 1$ would consistently estimate the marginal distribution
+  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
+  hypothesis, but would not necessarily estimate the joint
+  distribution of two or more of those terms correctly (in particular,
+  the covariance could be wrong).  The stronger null hypothesis
+  imposed in Part~\ref{it:1} ensures that resampling with $b = 1$
+  estimates the joint distribution correctly as well.
+
+  The same reasoning implies that a parametric bootstrap
+  \citep[i.e.][]{ClM:11} achieves control of \sfwe\ only under the
+  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
+  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
+  so researchers can make use of the considerable simplifications that
+  occur in that setting.
+\end{rem}
+
+\begin{rem}
+  If calculating $\hat{\sigma}_i$ is burdensome, one can do the same
+  bootstrap without studentizing the statistics.  This procedure is
+  likely to have worse size and power properties, but may be more
+  convenient.  One could also estimate the variance with a second
+  bootstrap step, but execution might take too long to be practical,
+  or use a convenient but inconsistent approximation of the variance.
+  The estimator of the variance in Part~\ref{it:3} should have the
+  best performance if it is \hac\ \cite[the results of][may be
+  relevant]{GoK:96}, but that is not necessary for validity.
+  See \citet{Han:05} and \citet[Section~4.2]{RoW:05} for a discussion
+  of the benefits of studentization.
+\end{rem}
+
+\begin{rem}
+  If the number of alternative models is large, controlling the \fwe\
+  may be too strict a criterion.  \citet{RSW:08} discuss procedures to
+  control criteria other than the \fwe, and one can use their
+  generalizations of the StepM procedure here as well.
+\end{rem}
+
+\begin{rem}\label{rem:01}
+  \citet{Pin:11} raises the issue that, since there are often several
+  models that could be used as the benchmark, researchers may want to
+  control for data snooping over the null hypotheses as well as the
+  alternatives.  For example, one could use either \citepos{AtO:01}
+  random walk or \citepos{StW:07} \textsc{ima}(1,1) as benchmark
+  inflation models, so it might make sense to require an alternative
+  model to outperform them both.\footnote{\citet{Pin:11} studies tests
+    that reject if the alternative model outperforms either of the
+    models, so the details are somewhat different in our papers.}
+  Allowing multiple benchmark models can be expressed as an
+  Intersection-Union test, so Theorem~\ref{res:2}'s procedure
+  (Part~(\ref{it:3})) easily accommodates this extension by taking
+  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
+  $q$-vector;\footnote{If a researcher uses multiple benchmark models,
+    it would be a mistake to assume that they are all correctly
+    specified, so only the null hypothesis of Part~(\ref{it:3}) is
+    appropriate.} the first element of $\bar f_{i}$ compares the first
+  benchmark model to the $i$th alternative and the first element of
+  $\hat{\sigma}_i^2$ is the corresponding estimate of asymptotic
+  variance, the second element corresponds to the second benchmark
+  model, etc.
+
+  Steps 1 and 2 of Theorem~\ref{res:2}'s procedure now become:
+  \begin{enumerate}
+  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
+    \{(i,k): \tfrac1{\hat\sigma_{ik}} |\bar{f}_{ik}| > \hat{d}_j\}$,
+    where $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{(i,k)
+      \notin M_{j-1}} \tfrac1{\hat\sigma_{ik}^*} |\bar{f}_{ik}^{*} -
+    \bar{f}_{ik}(\hat{\beta}_{k,T+1})|$.
+  \item Reject all of the hypotheses $H_i$ such that $(i,k) \in
+    \bigcup_{j=1}^m M_j$ and $\bar{f}_{ik} > 0$ for all
+    $k$.\footnote{This approach is motivated by \citepos{DoH:11}
+      extension of Wolak's \citeyearpar{Wol:89b,Wol:91} tests of
+      inequality constraints.  Donald and Hsu use a threshold rule
+      based on \citepos{Han:05} \spa\ to discard nonbinding
+      inequalities.  One could, of course, use the two-sided stepdown
+      method proposed in this paper instead of the \spa\ to increase
+      the power of Donald and Hsu's test.}
+  \end{enumerate}
+  Also note that the asymptotic variance-covariance matrix of each
+  $\bar f_i$ does not need to be positive definite as long as the
+  variance of each of its elements is positive.  A formal statement of
+  this result is given in Appendix~\ref{sec:B}.
+\end{rem}
+
+\section{The Bootstrap for Out-of-Sample Statistics}\label{sec:1b}
+The validity of the bootstrap in Theorem~\ref{res:2} is a special case
+of a result of independent interest---the validity in general of block
+bootstraps for asymptotically normal \oos\ statistics.  This section
+presents the general result.  In this section, let $\to^{p^{*}}$ and
+$\to^{d^{*}}$ refer to convergence in probability or distribution
+conditional on the observed data.  Similarly, $\E^{*}$, $\var^{*}$,
+and $\cov^{*}$ refer to the expectation, variance, and covariance with
+respect to the probability measure induced by the bootstrap, and
+$y_t^{*}$, etc. is the random variable $y_t$ but under the
+bootstrap-induced \cdf.
+
+Note that the notation in this section is more general than that of
+Section~\ref{sec:1}.  The assumptions required are generalizations of
+the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
+\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
+discussion of these conditions, as theirs are nearly identical.
+Theorem~\ref{res:3} gives the result.
+
+\begin{thm}\label{res:3}
+  Suppose the following conditions hold:
+  \begin{enumerate}
+  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
+    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
+    > 2$.
+  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
+    recursive, rolling, or fixed estimation window and satisfies
+    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
+    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
+    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
+    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
+    \begin{equation}
+      H_{t} = \begin{cases} 
+        \tfrac1t \sum_{s=1}^t h_{s}(\beta_{0}) & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_{0}) & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}(\beta_{0}) & \text{fixed window} \\
+      \end{cases}
+    \end{equation}
+    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0})
+    = 0$ for all $s$.
+  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector.
+    Then $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
+    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
+    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
+  \item Each element of $\E f_{t}(\beta)$ is continuously
+    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
+      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
+    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
+  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
+    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
+    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
+    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
+      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
+    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
+    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
+  \item $R, P \to \infty$ as $T \to \infty$.
+  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
+    circular blocks, or stationary bootstrap with block lengths drawn
+    from the geometric distribution, and $b$ satisfies $b \to \infty$
+    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
+    circular blocks bootstraps and is the expected block length of the
+    stationary bootstrap.
+  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
+    uniformly positive definite.
+  \end{enumerate}
+  Then
+  \begin{equation}
+    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
+        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
+      \epsilon] \to 0
+  \end{equation}
+  for all $\epsilon > 0$.
+\end{thm}
+
+\begin{rem}
+  \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
+  reestimate any of them which requires the additional assumption that
+  $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
+  have no estimated parameters.\footnote{\citet{Whi:00} lists several
+    different sets of assumptions that give the same result, but these
+    seem to be the most general.}
+\end{rem}
+
+\begin{rem}
+  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
+  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
+  \bar{f}(\beta_0))$.  But it is clear that
+  $\bar{f}(\hat{\beta}_{T+1})$ is the bootstrap analogue of $\E
+  \bar{f}(\beta_0)$, the parameter of interest.  Because their
+  bootstrap is miscentered, \citet{CoS:07} must redefine
+  $\hat{\beta}_t^{*}$ to achieve consistency.  In this paper, though,
+  consistency arises naturally.
+\end{rem}
+
+\begin{rem}
+  It may be unnecessary to assume that $\bar{f}(\beta_0)$ has positive
+  definite asymptotic variance; if so, the bootstrap would work in the
+  setup of \citet{ClM:05,ClM:01} and \citet{Mcc:07}.  That question is
+  left to future research.
+\end{rem}
+
+\section{Monte Carlo Results}\label{sec:2}
+I'll conduct two brief Monte Carlo experiments to demonstrate that the
+modified version of \citepos{ClW:07} statistic performs similarly to
+their original test in the situations they study.\footnote{All of
+  these simulations were programmed in R \citep[version 2.14.0]{R} and
+  use the \textsc{MASS} \citep[version info]{VeR:02}, xtable
+  \citep[version info]{Dah:09}, and dbframe \citep[version
+  0.2.1]{Cal:10b} packages.  For details on the programming, please
+  see the supplemental appendices \citep{Cal:11f,Cal:11g,Cal:11h}.}
+I'll use both of the \dgp s they consider as well as a modification to
+study the performance of the statistics if there is instability.
+
+The first \dgp\ has three different parametrizations; one to study the
+tests' size, one to study power under stationarity, and one to study
+power if there is a single break in the relationship between the
+target and predictors.  The \dgp\ is:
+\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
+  y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
+  \gamma^{*}_t &=
+  \begin{cases}
+    0    & \text{size simulations} \\
+    0.35 & \text{power (stable)} \\
+    0    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
+    0.70 & t > \tfrac{T}{2} \quad \text{power (break)}
+  \end{cases}\\\nonumber
+  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
+  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
+  \end{pmatrix}
+   , \begin{pmatrix} 18 & -
+    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
+\end{align}
+Both models are estimated by \ols. The benchmark model regresses $y_t$
+on a constant, and the alternative regresses $y_t$ on a constant and
+$z_{t-1}$.  We use both \poscw\ original statistic and the new
+statistic to test the null that the benchmark model's innovation is an
+\mds.\footnote{\citet{ClW:07} report the performance of the tests
+  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
+  based on the naive Gaussian statistic.}  \citet{ClW:06,ClW:07} only
+look at the stable case.
+
+\begin{table}[tb]
+  \centering
+  \input{floats/simulation1}
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; and Pr[disagree]
+  gives the fraction of simulations in which this paper's test and
+  Clark and West's (2007) give different conclusions.}
+\label{tab:mc1}
+\end{table}
+
+The second \dgp\ is
+\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
+  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
+  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
+  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
+  z_{t-4} + v_{t} \nonumber \\
+  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
+  \begin{pmatrix}
+    0 \\ 0
+  \end{pmatrix},
+  \begin{pmatrix}
+    10.505 & 1.036 \\ 1.036 & 0.366
+  \end{pmatrix}
+  \Bigg) \nonumber\\\nonumber
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations}\\
+    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
+  \end{cases}
+\end{align}
+The benchmark model for $y_{t}$ is an AR(1) and the alternative model
+includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
+120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
+first \dgp\ mimics an asset pricing application and the second mimics
+\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
+National Activity Index.
+
+\begin{table}[tb]
+  \centering
+  \input{floats/simulation2}
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; Pr[disagree] gives
+  the fraction of simulations in which this paper's test and Clark and
+  West's (2007) give different conclusions.}
+\label{tab:mc2}
+\end{table}
+
+Table~\ref{tab:mc1} presents the simulation results
+for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
+all of the stable parameter values, the proposed new statistic has
+similar rejection probability to \citepos{ClW:07}.  Clark and West's
+test is slightly more undersized than the new test, but has a little
+higher power under the alternative.  Moreover, the statistics give
+different results in less than 10\% of the simulations for most
+parametrizations of the \dgp s.  In general, the statistics perform
+similarly well.
+
+For the simulations with a single break, the new statistic has about
+twice the power of \poscw\ original test.  For most parametrizations
+of \dgp\ 1, the new test rejects over 90\% of the time, while Clark
+and West's test rejects about 40\% of the time.  So mixing window
+strategies can give a substantial power advantage when testing for
+time-varying predictability, and performs similarly to the original
+test when testing for stable outperformance.
+
+\section{Empirical Illustration}\label{sec:3}
+
+This section demonstrates the use of the statistics introduced earlier
+in the paper by revisiting \citepos{GoW:08} study of excess stock
+returns.  Goyal and Welch argue that many variables thought to predict
+excess returns (measured as the difference between the yearly log
+return of the S\&P 500 index and the T-bill interest rate) on the
+basis of in-sample evidence fail to do so out-of-sample.  To show
+this, Goyal and Welch look at the forecasting performance of models
+using a lag of the variable of interest, and show that these models do
+not significantly outperform the excess return's recursive sample mean.
+
+Here, I conduct the same analysis, but using this paper's \mds\ test.
+The benchmark model is the excess return's sample mean (as in the
+original) and the alternative models are of the form
+\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
+\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
+$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
+predictors used are listed in the ``predictor'' column of
+Table~\ref{tab:em1} \citep[see][for a detailed description of the
+variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
+correction to the models, that the forecasts be bounded below by zero
+since negative forecasts are incredible, as well as two simple
+combination forecasts, the mean and the median (over both the original
+and the non-negative forecasts).  The data set is annual data
+beginning in 1927 and ending in 2009, and the rolling window uses 10
+observations.\footnote{This statistical analysis was conducted in R
+  \citep{R} using the xtable \citep[version]{Dah:09}, Hmisc
+  \citep[version]{Har:10}, and dbframe \citep[version 0.2.1]{Cal:10b}
+  packages; please see the supplemental appendices for details on the
+  programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
+
+Table~\ref{tab:em1} presents the results for each model.  The column
+``value'' gives the value of the test statistic for each model, while
+the ``naive'' and ``corrected'' columns indicate whether the statistic
+is greater than the standard size-10\% critical value (1.28) and the
+critical value estimated by the procedure of Theorem~\ref{res:2}
+(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
+  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
+  of Theorem~\ref{res:2}.}  Three predictors are significant at the
+naive critical values for both the original and bounded forecasts: the
+dividend yield, long term interest rate, and book to market ratio.
+But none are significant after accounting for data snooping, which
+highlights the importance of these methods.  The median forecast is
+significant using conventional critical values as well, but not the
+corrected values.
+
+\begin{table}[tb!]
+  \centering
+  \empiricaltable
+\caption{Results from \oos\ comparison of equity premium prediction
+  models; the benchmark is the recursive sample mean of the equity
+  premium and each alternative model is a constant and single lag of
+  the variable listed in the ``predictor'' column.  The dataset begins
+  in 1927 and ends in 2009 and is annual data. The ``value'' column
+  lists the value of this paper's \oos\ statistic, the ``naive''
+  column indicates whether the statistic is significant at standard
+  critical values, and the ``corrected'' column indicates significance
+  using the critical values proposed in Theorem~\ref{res:2} that
+  account for the number of models.  See Section~\ref{sec:3} for details.}
+\label{tab:em1}
+\end{table}
+
+\section{Conclusion}\label{sec:4}
+This paper presents an \oos\ test statistic similar to \poscw\ that is
+asymptotically normal when comparing nested or non-nested models.
+Normality is achieved by estimating the alternative model using a
+fixed-length rolling window---as do Clark and West---but estimating
+the benchmark model with a recursive window.  Simulations indicate
+that the new statistic behaves similarly to Clark and West's original
+test when the \dgp\ is stable, but can have much higher power when the
+predictability varies over time, suggesting that the new statistic is
+a suitable replacement in applied research.  The paper also presents a
+method for comparing the benchmark model to several alternative models
+simultaneously and improves block bootstrap procedures of \oos\
+statistics.
+
+\appendix
+\section{Supporting Results}
+This Appendix restates \citepos{Mcc:00} results, which themselves
+weaken \citepos{Wes:96} assumptions, under the dependence conditions
+of Theorem~\ref{res:1}.  It also proves some of the Lemmas required
+for that result and the results in the main paper.
+
+\begin{lema}\label{res:a2}
+  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
+  hold.
+  \begin{enumerate}
+  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
+    \to^{p^{*}} 0$.
+  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
+    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_{T+1} |
+    \to^{p^{*}} 0$.
+  \end{enumerate}
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a2}] \quad
+  \begin{enumerate}
+  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies \citepos[Theorem
+    3.1]{JoD:00b} functional \clt.  So
+    \begin{equation}
+      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
+      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
+        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
+    \end{equation}
+    with the convergence following from the continuous mapping
+    theorem.  \citepos{Cal:11d} Theorem~1 ensures the same argument
+    holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
+  \item We have
+    \begin{multline}
+      P^a \sup_{t \in S_T} | \hat{\beta}_t - \beta_0 | = P^a \sup_{t
+        \in S_T} |\hat{B}_{t} H_{t}| \\ \leq \sup_{t,u \in S_T} \Big|
+      [ \hat{B}_u - B] \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
+      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
+    \end{multline}
+    and both terms converge to zero in (conditional) probability by
+    the previous argument and by assumption.  The same argument holds
+    for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ as well.
+  \end{enumerate}
 \end{proof}
 
-\input{mc}
+\begin{lema}\label{res:a3}
+  Suppose the conditions of Theorem~\ref{res:3} hold; let $g_{t} =
+  (f_{t}' - \E f_{t}', a_t h_{t}')'$, $g_t^{*} =
+  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})', a_t
+  h_t^{*\prime})'$, and $a_t = \sum_{s=\max(R,t)}^T \tfrac{1}{s}$.  Then
+  \begin{equation}\label{eq:1}
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T g_{t}^{*}
+    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T g_{t}
+    \leq x \Big] \Big| > \epsilon \Big] \to 0
+  \end{equation}
+  for all positive $\epsilon$.
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a3}]
+  Note that $g_t$ satisfies the conditions of a \clt,
+  \citep[Theorem~2]{Jon:97}, and so it suffices to prove that the
+  bootstrap average obeys a \clt\ as well.
+
+  Suppose that $g_t^{**}$ is generated by the stationary bootstrap but
+  with exactly $\lfloor p P \rfloor$ full blocks of length
+  $M_1,\dots,M_{\lfloor p P \rfloor}$ (so that the number of
+  observations $P^{**}$ is random).  As in \citet{Cal:11d}, $\sqrt{P}
+  \bar{g}^{*}$ and $\sqrt{P^{**}} \bar{g}^{**}$ converge in
+  distribution to the same limit; moreover, $P^{**} \bar{g}^{**}$ is a
+  sum of $\lfloor p P \rfloor$ independent blocks that obey a central
+  limit theorem conditional on $\mathcal{M} = (M_1,\dots,M_{\lfloor p
+    P \rfloor}$), and the result follows if $P^{**}
+  \E^{**}(\bar{g}^{**} \bar{g}^{**\prime} \mid \mathcal{M}) \to^p
+  \Sigma$ where $\Sigma = P \E(\bar{g} \bar{g}')$.
+
+  For $\tau = 1,\dots,P^{**}$, let $\kappa$ denote the block
+  containing $\tau$, so $\sum_{i=1}^{\kappa-1} M_i < \tau \leq
+  \sum_{i=1}^{\kappa} M_i$, and let $K_{\tau,i} = \sum_{j=\kappa+1}^i
+  M_{(j \mod \lfloor p P \rfloor) + 1}$, $K_{\tau,0} = 0$.  Then we have
+  \begin{multline}
+    P^{**} \E^{**}(\bar{g}^{**} \bar{g}^{**\prime} \mid \mathcal{M})
+    = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor} 
+    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \hat{g}_s \hat{g}_t' 
+    \\ = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}
+    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \big[g_s g_t' + g_s(\hat{g}_t
+    - g_{t})' + (\hat{g}_s - g_{s}) g_{t}' + (\hat{g}_s -
+    g_{s})(\hat{g}_t - g_{t}) \big],
+  \end{multline}
+  with the first equality from \citet{Cal:11d} and $\hat{g}_s =
+  (f_t(\hat{\beta}_{T+1})' - \bar f(\hat{\beta}_{T+1})', h_t')'$.
+  Now, $\frac{1}{P^{**}} \sum_i \sum_{s,t} g_s g_t \to^p \var(\sqrt{P} \bar{g})$
+  \citep[Lemma~5]{Cal:11d}, so it suffices to show that the remaining
+  terms vanish, which is equivalent to showing
+  \begin{equation}\label{eq:3}
+    \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}\sum_{s,t =
+      K_{\tau,i-1}}^{K_{\tau,i}} (f_s(\hat{\beta}_{T+1}) -
+    f_s(\beta_0)) (f_t(\hat{\beta}_{T+1}) - f_t(\beta_0))
+    \to^p 0
+  \end{equation}
+  and
+  \begin{equation}\label{eq:2}
+    (\bar{f}(\hat{\beta}_{T+1}) - \E
+    \bar{f}(\beta_0)) (\bar{f}(\hat{\beta}_{T+1}) - \E
+    \bar{f}(\beta_0))' \to^p 0.
+  \end{equation}
+  Proving~\eqref{eq:3} uses the same argument as~\citet[Lemma
+  A.3]{Mcc:00} and~\eqref{eq:2} follows a streamlined version of the
+  argument of~\ref{res:a5}, completing the proof.  The proofs for the
+  moving and circular block bootstraps are the same.
+\end{proof}
+
+\begin{lema}\label{res:a5}
+  If the conditions of Theorem~\ref{res:3} hold\footnote{The
+    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
+  \begin{equation}
+    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
+  \end{equation}
+  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
+\end{lema}
+\begin{proof}[Proof of Lemma~\ref{res:a5}]
+  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}.
+\end{proof}
+
+\section{Proofs of Main Theoretical Results}\label{sec:B}
+
+\begin{proof}[Proof of Theorem \ref{res:1}]
+  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
+  statistic; this substitution does not affect its asymptotic
+  distribution; the theorem is now an immediate consequence of
+  Lemma~\ref{res:a5}.  Note that \[f_t(\beta_0)= 2 (y_{t+1} -
+  x_t'\beta_0)(x_t'\beta_0 - \hat{y}_{1,t+1}) \quad \text{a.s.},\] as
+  in \citet{ClW:07}, which is an \mds, so we do not need to use a
+  \hac\ estimator of the variance under the null.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{res:2}]
+  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
+  Theorem~\ref{res:3} of this paper, Theorem~3.1 and~4.1 of
+  \citet{RoW:05}, and Theorem~1 of \citet{Cal:11e} complete the proof.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{res:3}] Expand $\E^{*}
+  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
+  \begin{equation}
+    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
+    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
+    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
+  \end{equation}
+  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same as
+  in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
+  o_{p} = F + o_p$ and $B^{*} = B + o_{p}$.  The result then follows
+  from Lemma~\ref{res:a3}.
+\end{proof}
+
+\begin{lem}[Formalization of Remark~\ref{rem:01}]
+  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
+  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
+  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
+  uniformly positive definite for each $k$.  Then the procedure
+  described in Remark~\ref{rem:01} achieves \sfwe.
+\end{lem}
+
+The proof is similar to that of Theorem~\ref{res:2}. Note that we
+allow $\sqrt{P}(\bar{f}_{i1}(\beta_1),\dots,\bar{f}_{iq}(\beta_q))$ to
+converge to a normal with singular variance-covariance matrix as long
+as each element has positive variance.
 
 \bibliography{AllRefs}
+\end{document}
 
-\end{document}
+% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
+% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
+% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
+% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
+% LocalWords:  Corradi unstudentized studentized fg gg GoJ gcalhoun HLN li PoW
+% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
+% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
+% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
+% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
+% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
+% LocalWords:  outperformance Hmisc Har

### 2011-11-26 Paper.tex
Rewrote code because of changes in other packages; debugged too

@@
 \input{tex/simulationdefinitions}
+\input{tex/empiricsdefinitions}
 \input{tex/empiricalresults}
@@
   \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
-  10\% confidence.  These percentages are calculated from 5000
+    \testsize\% confidence.  These percentages are calculated from \totalsims\
     samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
@@
   \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
-  10\% confidence.  These percentages are calculated from 5000
+    \testsize\% confidence.  These percentages are calculated from \totalsims\
     samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
@@
 \text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
-$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
-predictors used are listed in the ``predictor'' column of
+$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
+The predictors used are listed in the ``predictor'' column of
 Table~\ref{tab:em1} \citep[see][for a detailed description of the
@@
 and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses 10
-observations.\footnote{This statistical analysis was conducted in R
-  \citep{R} using the xtable \citep[version]{Dah:09}, Hmisc
-  \citep[version]{Har:10}, and dbframe \citep[version 0.2.1]{Cal:10b}
-  packages; please see the supplemental appendices for details on the
-  programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
+beginning in 1927 and ending in 2009, and the rolling window uses
+\windowlength\ observations.\footnote{This statistical analysis was
+  conducted in R \citep{R} using the xtable \citep[version]{Dah:09},
+  Hmisc \citep[version]{Har:10}, and dbframe \citep[version
+  0.2.1]{Cal:10b} packages; please see the supplemental appendices for
+  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
 
@@
 the ``naive'' and ``corrected'' columns indicate whether the statistic
-is greater than the standard size-10\% critical value (1.28) and the
-critical value estimated by the procedure of Theorem~\ref{res:2}
-(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
-  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
-  of Theorem~\ref{res:2}.}  Three predictors are significant at the
-naive critical values for both the original and bounded forecasts: the
-dividend yield, long term interest rate, and book to market ratio.
-But none are significant after accounting for data snooping, which
-highlights the importance of these methods.  The median forecast is
-significant using conventional critical values as well, but not the
-corrected values.
+is greater than the standard size-\bootsize\% critical value (1.28)
+and the critical value estimated by the procedure of
+Theorem~\ref{res:2} (\empiricalcriticalvalue).\footnote{The bootstrap
+  uses \nboot\ replications with i.i.d. sampling, as proposed in
+  Part~(\ref{it:1}) of Theorem~\ref{res:2}.}  Three predictors are
+significant at the naive critical values for both the original and
+bounded forecasts: the dividend yield, long term interest rate, and
+book to market ratio.  But none are significant after accounting for
+data snooping, which highlights the importance of these methods.  The
+median forecast is significant using conventional critical values as
+well, but not the corrected values.
 

### 2012-03-30 Paper.tex
Consolidated and cleaned up source files
- Added DELETE_ON_ERROR target to makefile
- switched versioning to date-based and put in its own file
Added material for multiple tests and for empirics

--- 2011-08-03 Paper.tex
@@
 
-\author{Gray
-  Calhoun\thanks{\texttt{http://www.econ.iastate.edu/$\sim$gcalhoun};
-    Economics Department; Iowa State University; Ames, IA 50011.
-    Telephone: (515) 294-6271.  Email: \texttt{gcalhoun@iastate.edu}.}
-  \\ Iowa State University}
+\author{Gray Calhoun\thanks{Address: 467 Heady Hall, Economics
+    Department; Iowa State University; Ames, IA 50011. Telephone:
+    (515) 294-6271.  Email: \texttt{gcalhoun@iastate.edu}.} \\ Iowa
+  State University}
 
@@
 \begin{abstract} 
-  \noindent This paper proposes a modification of \citepos[\textit{J.
-      Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
+  \noindent This paper proposes a modification of \citepos[J.
+  Econom.]{ClW:07} adjusted out-of-sample $t$-test.  The
   alternative model is still estimated with a fixed-length rolling
@@
   paper also presents a new bootstrap procedure based on
-  \citet[\textit{Econometrica}]{RoW:05} to compare multiple models
-  while controlling family-wise error that substantially improves
-  existing block bootstrap methods for out-of-sample statistics.  This
-  procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.
+  \citet[Econometrica]{RoW:05} to compare multiple models while
+  controlling family-wise error, and demonstrates this procedure by
+  analyzing \citepos[Rev. Finan. Stud.]{GoW:08} excess returns dataset.
 
@@
 \noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Family-Wise Error Rate; Multiple Testing;
+Sequence, Model Selection, Family-wise Error; Multiple Testing;
 Bootstrap; Reality Check
@@
 larger model.  Normality comes from a fixed-length rolling window, as
-in \citet{GiW:06}, and the adjustment centers the statistic
-appropriately.  This statistic is especially convenient because other
-tests for similar hypotheses \citep[among
-  others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
-nonstandard limit distribution and place restrictions on the models
-under consideration, while other asymptotically normal statistics test
-a different null hypothesis \citep{GiW:06} or place assumptions on the
+in \citet{GiW:06}, and the adjustment centers the statistic at the
+appropriate population quantities.  This statistic is especially
+convenient because other tests for similar hypotheses \citep[among
+others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a nonstandard
+limit distribution and place restrictions on the models under
+consideration, while other asymptotically normal statistics test a
+different null hypothesis \citep{GiW:06} or place assumptions on the
 models and \dgp\ that are rarely appropriate in empirical work
@@
 
-In this paper, I show that a modified version of their statistic is
+In this paper, I prove that a modified version of their statistic is
 asymptotically normal even when the smaller model is estimated.  To
@@
 looking at the naive $p$-values is misleading, but bootstrapping the
-statistics can lead to a valid test (White calls this procedure the
+statistics can give a valid test (White calls this procedure the
 ``bootstrap reality check'').  So I present a test for equal
@@
 boostrap with \oos\ statistics, which is necessary to verify that the
-StepM is appropriate.  Existing results on boostrapping
-\oos\ statistics have some drawbacks.  \citet{Whi:00} and
-\citet{Han:05} use the stationary bootstrap, but require the test
-sample to be much smaller than the training sample, which is obviously
-inappropriate here.  \citet{CoS:07} relax that requirement, but only
-consider the moving block bootstrap \citep{LiS:92,Kun:89} and make the
-statistic more complicated than necessary by adjusting the objective
-function of the bootstrapped statistic to center it
-correctly.\footnote{Their recentering is required for consistency and
-  does not give higher order accuracy.}  A parametric bootstrap, such
-as that used by \citet{ClM:11}, would be difficult to implement here
-since we want to test whether several different null hypotheses hold
-individually (as I'll discuss later, Clark and McCracken test a single
-null hypothesis that describes the behavior of all of the models under
-consideration and does not let the researcher know which of the models
-outperforms, only that at least one does).  So this paper's result for
-the stationary bootstrap of \oos\ statistics considerably improves on
-existing procedures.
+StepM is appropriate.  Existing results on boostrapping \oos\
+statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
+the stationary bootstrap, but require the test sample to be much
+smaller than the training sample, which is obviously inappropriate
+here.  \citet{CoS:07} relax that requirement, but only consider the
+moving block bootstrap \citep{LiS:92,Kun:89} and make the statistic
+more complicated than necessary by adjusting the objective function of
+the bootstrapped statistic to center it correctly.\footnote{Their
+  recentering is required for consistency and does not give higher
+  order accuracy.}  A parametric bootstrap, such as that used by
+\citet{ClM:11}, would be difficult to implement here since we want to
+test whether several different null hypotheses hold individually (as
+I'll discuss later, Clark and McCracken test a single null hypothesis
+that describes the behavior of all of the models under consideration).
+So this paper's result for the stationary bootstrap of \oos\ statistics
+improves on existing procedures.
 
@@
   \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
-    $-1/2$ on a strong mixing series of size $-r/(r-2)$ for $r>2$ or a
-    uniform mixing series of size $-r/2(r-1)$.  Also, $y_t$,
-    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
-    moments for some positive $\delta$.
+    $-1/2$ on a strong mixing series of size $-r/(r-2)$ for $r>2$.
+    Also, $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2
+    r+\delta$ moments for some positive $\delta$.
   \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
@@
     P^{-1} \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
-    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
+    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta)_0$ are
     covariance stationary and $\bar f(\beta_0)$ has uniformly positive
@@
 
-I also use Lemma~\ref{res:1} to test multiple models at once.  There
-are two approaches one can take.  The first is to test whether any of
-the models can improve on the benchmark; \citet{Whi:00},
+Before presenting the method for testing multiple models, I'll give a
+version of \citepos{PoR:94} stationary bootstrap for the \oos\
+statistic of Theorem~\ref{res:1}.  Note that the result holds as well
+for the moving blocks bootstrap of \citet{Kun:89} and \citet{LiS:92}.
+This result will be used in Theorem~\ref{res:2} to derive the joint
+distribution of several models' \oos\ statistics.  The
+boostrap-induced probability measure is denoted $\pr^{*}$.
+
+\begin{lem}\label{res:3}
+  Suppose the conditions of Theorem~\ref{res:1} hold, but strengthen
+  condition~\ref{item:3} so that $y_t$ and $z_t$ are \ned\ of size
+  $-1$ on a strong mixing series of size $-(2r + \rho)/(r-2)$ with
+  $\rho > 0$ and $r > 2$.  Consider the following procedure:
+  \begin{enumerate}
+  \item Define the data matrices $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} =
+    (X_{R+1},\dots,X_{T-1})$ with
+    \begin{equation*}
+      X_t = \begin{cases}
+        (y_{t+1}, x_t')' & t \leq R \\
+        (y_{t+1}, x_t', \hat{y}_{1,t+1})' & t > R.
+      \end{cases}
+    \end{equation*}
+  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
+    stationary bootstrap with expected block size $b$ and denote each
+    sample as $\X_{\p, l}^{*}$; let $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
+  \item Estimate $\bar{f}^{*}_l$ and $\hat{\sigma}_l^{*}$ as in
+    Theorem~\ref{res:1} for each bootstrap sample $\X^{*}_l$.
+  \end{enumerate}
+
+  Let $(\bar{f}^{*},\hat{\sigma}^{*})$ be random variables with the
+  same (conditional) distribution as $(\bar{f}_l^{*},
+  \hat{\sigma}^{*}_l)$.  If $b \to \infty$ and $b^2/P \to 0$
+  \begin{gather}
+    \pr\big[\sup_x \big| \pr^{*}\big[\sqrt{P}(\bar{f}^{*} -
+    \bar{f}(\hat{\beta}_{T+1})) \leq x \big] - \pr\big[\sqrt{P}
+    (\bar{f} - \E \bar{f}(\beta_0)) \leq x\big] \big| > \epsilon\big]
+    \to 0 \intertext{and} \pr\Bigg[\sup_x \Bigg|
+    \pr^{*}\Bigg[\frac{\bar{f}^{*} -
+      \bar{f}(\hat{\beta}_{T+1})}{\hat{\sigma}^{*}/\sqrt{P}} \leq x
+    \Bigg] - \pr\Bigg[\frac{\bar{f} - \E
+      \bar{f}(\beta_0)}{\hat{\sigma}/\sqrt{P}} \leq x\Bigg] \Bigg| >
+    \epsilon\Bigg] \to 0
+  \end{gather}
+  for all $\epsilon>0$.
+\end{lem}
+
+\begin{rem}
+  \citet{Whi:00}, \citet{Han:05}, and \citet{CoS:07} use the
+  distribution of $\sqrt{P}(\bar{f}^{*} - \bar{f})$ to approximate
+  that of $\sqrt{P}(\bar{f} - \E \bar{f}(\beta_0))$, while
+  Lemma~\ref{res:3} uses the distribution of $\sqrt{P}(\bar{f}^{*} -
+  \bar{f}(\hat{\beta}_{T+1}))$; $\hat{\beta}_{T+1}$ plays the same
+  role as $\beta_0$ under the bootstrap-induced probability measure.
+  Since $\hat{\beta}_t - \hat{\beta}_{T+1} = O_p(\sqrt{T-t})$, using
+  their bootstrap distribution is inconsistent unless $P/T$ vanishes
+  asymptotically, as in White and Hansen's
+  papers\footnote{\citet{Whi:00} and \citet{Han:05} actually require
+    that $P$ grow a little bit slower than $o(T)$.} or unless
+  $\hat{\beta}_t^{*}$ is further modified, as in Corradi and Swanson's
+  paper.
+\end{rem}
+
+\begin{rem}
+  It is likely that Lemma~\ref{res:3} holds even if $\sqrt{P} \bar{f}$
+  is not asymptotically normal, but I leave that case to future
+  research as it's not necessary for this paper's results.
+\end{rem}
+
+\begin{rem}
+  How we handle the first $R$ observations does not affect the
+  asymptotic properties since $R$ is finite.  I've chosen to put them
+  at the beginning of each bootstrap sample so that sample means
+  correspond to population means of the bootstrap distribution.  Note
+  that the alternative forecasts are not defined for the first $R$
+  observations, so running the stationary bootstrap over the full
+  dataset is not possible.
+\end{rem}
+
+\begin{rem}
+  See \citet{RoW:05,RoW:06} for guidance on block length
+  selection.
+\end{rem}
+
+Finally, I use Lemma~\ref{res:3} to test multiple models at once.
+There are two approaches one can take.  The first is to test whether
+any of the models can improve on the benchmark; \citet{Whi:00},
 \citet{Han:05}, and \citet{ClM:11} take this approach.  This approach
@@
 more outperforming models while still controlling the family-wise error
-rate.  All of these methods rely on the bootstrap to estimate the
-joint dependence between the test statistic associated with each
-model.  The bootstrap we will use in this paper is new, and is
-outlined in Algorithm~\ref{alg:1}.
-\begin{alg}\label{alg:1}
-  \begin{enumerate}
-  \item Define the data matrices $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} =
-    (X_{R+1},\dots,X_{T-1})$ with
-    \begin{equation*}
-      X_t = \begin{cases}
-        (y_{t+1}, x_t')' & t \leq R \\
-        (y_{t+1}, x_t', \hat{y}_{1,t+1})' & t > R.
-      \end{cases}
-    \end{equation*}
-  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
-    stationary bootstrap with expected block size $b$ and denote each
-    sample as $\X_{\p, l}^{*}$; let $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
-  \item Estimate $\bar{f}^{*}_l$ and $\hat{\sigma}_l^{*}$ as in
-    Theorem~\ref{res:1} for each bootstrap sample $\X^{*}_l$.
-  \end{enumerate}
-\end{alg}
-
-Theorem~\ref{res:2} details the final procedure.
+rate.  Theorem~\ref{res:2} shows how the \oos\ bootstrap of
+Lemma~\ref{res:3} can be used with the StepM procedure.
 
 \begin{thm}\label{res:2}
-  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
+  Suppose the conditions of Lemma~\ref{res:3} hold, with assumptions
   on the alternative model, $\hat{y}_{1t}$, holding for each of the
@@
   distribution induced by the stationary bootstrap of
-  Algorithm~\ref{alg:1}, letting $X_t = (y_{t+1}, x_t', \hat{y}_{1,t+1},
+  Lemma~\ref{res:3}, letting $X_t = (y_{t+1}, x_t', \hat{y}_{1,t+1},
   \dots, \hat{y}_{m, t+1})'$ for $t > R$ (and unchanged for $t \leq
@@
 
-  If $b \to \infty$ and $b/P \to 0$, this algorithm controls the
+  If $b \to \infty$ and $b^2/P \to 0$, this algorithm controls the
   \fwe\ at level $\alpha$ for the family of null hypotheses $H_i$
@@
 \begin{rem}
-  How we handle the first $R$ observations does not affect the
-  asymptotic properties since $R$ is finite.  I've chosen to put them
-  at the beginning of each bootstrap sample so that sample means
-  correspond to population means of the bootstrap distribution.  Note
-  that the alternative forecasts are not defined for the first $R$
-  observations, so running the stationary bootstrap over the full
-  dataset is not possible.
-\end{rem}
-
-\begin{rem}
-  See \citet{RoW:05,RoW:06} for guidance on block length
-  selection.
-\end{rem}
-
-\begin{rem}
   If the number of alternative models is large, controlling the \fwe\
@@
 
-\section{General Results for the Bootstrap}\label{sec:1b}
-The validity of the stationary boostrap in Theorem~\ref{res:2} is a
-special case of a result of independent interest---the validity in
-general of the stationary bootstrap when \oos\ statistics are
-asymptotically normal.  Existing results---\citet{Whi:00},
-\citet{Han:05}, and \citet{CoS:07}---are not appropriate here;
-\citet{Whi:00} and \citet{Han:05} require that $R$ be very large,
-while this paper requires $R$ to be finite; and \citet{CoS:07} require
-a complicated modification of the statistic of interest be used to
-create the bootstrap distribution.  Instead of using these results,
-I'll present one more general.  The proof largely follows the approach
-of \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}, using the
-arguments of \citet{Cal:11d} for asymptotic normality.
+\section{Monte Carlo Results}\label{sec:2}
+\input{mc}
+\section{Empirical Illustration}\label{sec:3}
+\input{empirics}
+\section{Conclusion}\label{sec:4}
+In this paper, we present an \oos\ test statistic similar to \poscw\
+that is asymptotically normal when comparing nested models.  We do so
+by estimating the alternative model using a fixed-length rolling
+window---as Clark and West do---but estimating the benchmark model
+with a recursive window.  We also present simulations that indicate
+the new statistic behaves similarly to Clark and West's original test,
+suggesting that the new statistic is a suitable replacement in applied
+research.
 
-In this section, let $\to^{p^{*}}$ and $\to^{d^{*}}$ refer to
+\appendix
+\section*{Appendix}
+
+This Appendix restates \citepos{Mcc:00} results (which themselves
+weaken \citepos{Wes:96} assumptions) under the dependence conditions of
+Theorem~\ref{res:1}, which is fairly trivial.  It also presents a new
+stationary bootstrap for \oos\ statistics based on the recursive
+window that uses results in \citet{GoJ:03} to weaken \citepos{CoS:07}
+assumptions.  I'll use the same notation as in the main body of the
+paper, but functional forms and definitions are different here to
+reflect the increased generality.  By and large, a variable in the
+main paper (say $f_t$) is a special case of the same variable in this
+subsection.  We'll also use array notation in this section.
+
+In this appendix, let $\to^{p^{*}}$ and $\to^{d^{*}}$ refer to
 convergence in probability or distribution conditional on the observed
@@
 
-Note that the notation in this section is more general than that of
-Section~\ref{sec:1}.  The assumptions required are generalizations of
-the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
-\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
-discussion of these conditions, as theirs are nearly identical.
+\section{General Assumptions}
 
-\begin{asmp}\label{asmp:a1} 
-  Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-1/2$ on a
-  strong mixing series $\{V_t\}$ of size $-r/(r-2)$, with $r > 2$.
+This section's lemmas depend on the following assumptions, which are
+generalizations of the conditions of Theorems~\ref{res:1}
+and~\ref{res:2}.  See \citet{Wes:96,Wes:06}, \citet{WeM:98}, and
+\citet{Mcc:00} for a discussion of these conditions, as theirs are
+nearly identical.
+
+\begin{asmp}\label{asmp:a1}  We need two versions of the weak-dependence and moment
+  conditions; the first for the asymptotic distribution of the \oos\
+  statistic, and the second for the bootstrap distribution.
+  \begin{enumerate}
+  \item[a.] Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-1/2$ on
+    a strong mixing series $\{V_t\}$ of size $-r/(r-2)$, with $r > 2$.
+  \item[b.] Let $\{y_t, z_t\}$ be an $L_{2+\delta}$-\ned\ process of
+    size $-1$ on a strong mixing series $\{V_t\}$ of size $-(2r +
+    \delta)/(r - 2)$, with $r > 2$ and $\delta > 0$.
+  \end{enumerate}
 \end{asmp}
@@
 \end{asmp}
-
-\begin{thm}\label{res:3}
-  If Assumptions~\ref{asmp:a1}--\ref{asmp:a5} hold , $P, b \to \infty$
-  and $b/P \to 0$ as $T \to \infty$, and (p.d. assumption holds) then
-  \begin{equation}
-    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
-        \leq x] - \pr[\sqrt{P}( \bar{f} - \E f(\beta_0)) \leq x] | >
-      \epsilon] \to 0
-  \end{equation}
-  for all $\epsilon > 0$.
-\end{thm}
-
-\begin{rem}
-  \citet{Whi:00}, \citet{Han:05}, and \citet{CoS:07} use the
-  distribution of $\sqrt{P}(\bar{f}^{*} - \bar{f})$ to approximate
-  that of $\sqrt{P}(\bar{f} - \E \bar{f}(\beta_0))$, while
-  Lemma~\ref{res:3} uses the distribution of $\sqrt{P}(\bar{f}^{*} -
-  \bar{f}(\hat{\beta}_{T+1}))$; $\hat{\beta}_{T+1}$ plays the same
-  role as $\beta_0$ under the bootstrap-induced probability measure.
-  Since $\hat{\beta}_t - \hat{\beta}_{T+1} = O_p(\sqrt{T-t})$, using
-  their bootstrap distribution is inconsistent unless $P/T$ vanishes
-  asymptotically, as in White and Hansen's
-  papers\footnote{\citet{Whi:00} and \citet{Han:05} actually require
-    that $P$ grow a little bit slower than $o(T)$.} or unless
-  $\hat{\beta}_t^{*}$ is further modified, as in Corradi and Swanson's
-  paper.
-\end{rem}
-
-\section{Monte Carlo Results}\label{sec:2}
-\input{mc}
-\section{Empirical Illustration}\label{sec:3}
-\input{empirics}
-\section{Conclusion}\label{sec:4}
-In this paper, we present an \oos\ test statistic similar to \poscw\
-that is asymptotically normal when comparing nested models.  We do so
-by estimating the alternative model using a fixed-length rolling
-window---as Clark and West do---but estimating the benchmark model
-with a recursive window.  We also present simulations that indicate
-the new statistic behaves similarly to Clark and West's original test,
-suggesting that the new statistic is a suitable replacement in applied
-research.
-
-\appendix
-\section*{Appendix}
-
-This Appendix restates \citepos{Mcc:00} results (which themselves
-weaken \citepos{Wes:96} assumptions) under the dependence conditions of
-Theorem~\ref{res:1}, which is fairly trivial.  It also presents a new
-stationary bootstrap for \oos\ statistics based on the recursive
-window that uses results in \citet{GoJ:03} to weaken \citepos{CoS:07}
-assumptions.  I'll use the same notation as in the main body of the
-paper, but functional forms and definitions are different here to
-reflect the increased generality.  By and large, a variable in the
-main paper (say $f_t$) is a special case of the same variable in this
-subsection.  We'll also use array notation in this section.
 
@@
 \begin{lema}\label{res:a5}
-  If Assumptions~\ref{asmp:a1}, \ref{asmp:a3}, \ref{asmp:a4}, and
-  \ref{asmp:a5} hold, and instead of \ref{asmp:a2} we have the weaker
-  condition: The estimator $\hat{\beta}_t$ of $\beta_0$ satisfies
-  $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is a
-  sequence of $k$ by $q$ matrices that converges almost surely to the
-  deterministic sequence $B_{t}$, in the sense that $\sup_{t \in
-    \{S_T,\dots,T\}} | \hat{B}_{t} - B | \to 0$ almost surely for any
-  sequence $S_T$ that diverges to $\infty$ with $T$; $H_{t}$ is a
-  sequence of $q$-vectors such that $H_{t} = (1/t) \sum_{s=1}^t
-  h_{s}(\beta_{0})$, $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E
-  h_{s}(\beta_{0}) = 0$ for all $s$.  And $P \to \infty$ as $T \to
+  If Assumptions~\ref{asmp:a1}a, \ref{asmp:a2}a, \ref{asmp:a3},
+  \ref{asmp:a4}, and \ref{asmp:a5} hold and $P \to \infty$ as $T \to
   \infty$, (add p.d. assumption too) then
@@
   proof then follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}
+\end{proof}
+
+The next Lemma presents our recursive window bootstrap scheme.
+\begin{lema}\label{res:a6}
+  If Assumptions~\ref{asmp:a1}b, \ref{asmp:a2}b, \ref{asmp:a3},
+  \ref{asmp:a4}, and \ref{asmp:a5} hold , $P \to \infty$ as $T \to
+  \infty$, and (p.d. assumption holds) then
+  \begin{equation}
+    P^{-1/2} \sum_{t=R+1}^T
+    (f_{t}^{*}(\hat{\beta}_{t}^{*}) - \E^{*} f^{*}_{t}(\beta_{0}^{*})) \to^{d^{*}} N(0, \Omega^{*})
+  \end{equation}
+  and $\Omega^{*} \to^p \Omega$, where
+  \begin{align}
+    \Omega^{*} =     
+  \end{align}
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a6}]
+  Replace $R$ and $P$ with $\tilde{R}$ and $\tilde{P}$ as in the proof
+  of Lemma~\ref{res:a5}, and expand $\E^{*}
+  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
+  \begin{equation}
+    \sqrt{P'} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
+    \frac{1}{\sqrt{P'}} \sum_{t=R'+1}^T
+    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
+    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
+  \end{equation}
+  with the proof following exactly in \citet[Theorem 2.3.1]{Mcc:00}.
+  Note that $F^{*} = \hat{F} + o_{p^{*}}$ and $B^{*} = \hat{B}_{T+1} +
+  o_{p^{*}}$.  The result then follows from Lemma~\ref{res:a3} and the
+  consistency of these estimators.
 \end{proof}
@@
 
-\begin{proof}[Proof of Theorem~\ref{res:3}]
-  Replace $R$ and $P$ with $R'$ and $P'$ as in the proof
-  of Lemma~\ref{res:a5}, and expand $\E^{*}
-  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
-  \begin{equation}
-    \sqrt{P'} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
-    \frac{1}{\sqrt{P'}} \sum_{t=R'+1}^T
-    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
-    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
-  \end{equation}
-  with the proof following exactly in \citet[Theorem 2.3.1]{Mcc:00}.
-  Note that $F^{*} = \hat{F} + o_{p}$ and $B^{*} = \hat{B}_{T+1} +
-  o_{p}$.  The result then follows from Lemma~\ref{res:a3} and the
-  consistency of these estimators.
-\end{proof}
-
 \bibliography{AllRefs}
@@
 % LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
+% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW
 % LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized fg gg GoJ
+% LocalWords:  Corradi unstudentized studentized

### 2012-03-30 empirics.Rnw
Added material for multiple tests and for empirics

\newcolumntype{C}{>{\centering\arraybackslash}X}

<<echo=F>>=
library(dbframe)
library(xtable)

printbooktabs <- function(x,...){
  tab <- gsub("\\\\begin\\{tabularx\\}", "\\\\begin\\{tabularx\\}\\{\\\\textwidth\\}",
       print(xtable(x,...), file = "/dev/null", floating=F, hline.after=NULL, 
        add.to.row=list(pos=list(-1,0, nrow(x)), 
          command=c(
            '\\toprule ',
            '\\midrule ',
            '\\bottomrule ')),...))
  cat(tab)
  invisible(tab)
}

fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))

printall <- function(mcdb,...) {
  d <- subset(select(mcdb, group.by = groups, 
                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
                               "R", "P", 
                               "100 * avg(pOld <= %f) as 'Pr[\\textsc{cw}]'",
                               "100 * avg(pNew1 <= %f) as 'Pr[new]'",
                               "100 * (avg(pOld <= %f and pNew1 > %f) + avg(pOld > %f and pNew1 <= %f)) as 'Pr[disagree]'"),
                             size, size, size, size)), select = -isPower)
  d$R <- fspace(d$R)
  d$P <- fspace(d$P)
  d[[4]] <- fspace(d[[4]])
  d[[5]] <- fspace(d[[5]])
  d[[6]] <- fspace(d[[6]])
  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
  d$type[duplicated(d$type)] <- NA
  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
                align = c("l","X","C","C","C","C","C"), 
                sanitize.text.function = function(x) x,
                tabular.environment = "tabularx")
  invisible(d)
}
@

This is the empirical section

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS
% LocalWords:  ClM

### 2012-03-30 mc.Rnw
Added material for multiple tests and for empirics

@@
-We will also conduct a brief Monte Carlo experiment to demonstrate
-that this modified statistic performs essentially the same as Clark
-and West's.  We draw observations from their \dgp\ 1:
+\newcolumntype{C}{>{\centering\arraybackslash}X}
 
-\begin{gather*}
-  y_t = 0.5 + \gamma^{*} z_{t-1} + e_t \qquad\qquad
-  z_t = 0.15 + 0.95 z_{t-1} + v_t \\
-  (e_t, v_t)' \sim iid\ N(0, \begin{pmatrix} 18 & - 0.5 \\ \cdot & 0.025 \end{pmatrix}.
-\end{gather*}
+<<echo=F>>=
+library(dbframe)
+library(xtable)
+mcdata1 <- dbframe("dgp1", "mcdata.db")
+mcdata2 <- dbframe("dgp2", "mcdata.db")
+groups <- c( "isPower", "R", "P")
+size <- .1
+
+printbooktabs <- function(x,...){
+  tab <- gsub("\\\\begin\\{tabularx\\}", "\\\\begin\\{tabularx\\}\\{\\\\textwidth\\}",
+       print(xtable(x,...), file = "/dev/null", floating=F, hline.after=NULL, 
+        add.to.row=list(pos=list(-1,0, nrow(x)), 
+          command=c(
+            '\\toprule ',
+            '\\midrule ',
+            '\\bottomrule ')),...))
+  cat(tab)
+  invisible(tab)
+}
+
+fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))
+
+printall <- function(mcdb,...) {
+  d <- subset(select(mcdb, group.by = groups, 
+                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
+                               "R", "P", 
+                               "100 * avg(pOld <= %f) as 'Pr[\\textsc{cw}]'",
+                               "100 * avg(pNew <= %f) as 'Pr[new]'",
+                               "100 * (avg(pOld <= %f and pNew > %f) + avg(pOld > %f and pNew <= %f)) as 'Pr[disagree]'"),
+                             size, size, size, size)), select = -isPower)
+  d$R <- fspace(d$R)
+  d$P <- fspace(d$P)
+  d[[4]] <- fspace(d[[4]])
+  d[[5]] <- fspace(d[[5]])
+  d[[6]] <- fspace(d[[6]])
+  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
+  d$type[duplicated(d$type)] <- NA
+  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
+                align = c("l","X","C","C","C","C","C"), 
+                sanitize.text.function = function(x) x,
+                tabular.environment = "tabularx")
+  invisible(d)
+}
+@
+
+I'll also conduct two brief Monte Carlo experiments to demonstrate
+that the modified version of \citepos{ClW:07} statistic performs
+similarly to their original test.\footnote{All of these simulations
+  were programmed in R \citep{R:2-13-0} and use the \textsc{MASS}
+  \citep[ver. 7.3-12]{VeR:02}, xtable \citep[ver. 1.5-6]{Dah:09},
+  dbframe \citep[ver. 0.1.1]{Cal:10b}, and \textsc{oos}
+  \citep[ver. 0.01]{Cal:11b} packages.}  We'll use both of the \dgp s
+they consider.  For the first, we have
+\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
+  y_t &= 0.5 + \gamma^{*} z_{t-1} + e_t &
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations} \\
+    0.35 & \text{power simulations}
+  \end{cases}\\\nonumber
+  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
+  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
+  \end{pmatrix}
+   , \begin{pmatrix} 18 & -
+    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
+\end{align}
 Both models are estimated by \ols. The benchmark model regresses $y_t$
 on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  We run the same size and power simulations as
-\citet{ClW:07}; $\gamma^{*}$ equals zero for the size simulations and
-0.35 in the power simulations.
+$z_{t-1}$.  We use both \poscw\ original statistic and our new
+statistic to test the null that the benchmark model's innovation is an
+\mds.\footnote{\citet{ClW:07} report the performance of the tests
+  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
+  based on the naive Gaussian statistic.}
+
+\begin{table}[tb]
+  \centering
+<<mc1, echo=F, results=tex>>=
+printall(mcdata1)
+@ 
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; and Pr[disagree]
+  gives the fraction of simulations in which this paper's test and
+  Clark and West's (2007) give different conclusions.}
+\label{tab:mc1}
+\end{table}
+
+The second \dgp\ is
+\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
+  y_{t} &= 2.237 + 0.261 + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
+  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
+  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
+  z_{t-4} + v_{t} \nonumber \\
+  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
+  \begin{pmatrix}
+    0 \\ 0
+  \end{pmatrix},
+  \begin{pmatrix}
+    10.505 & 1.036 \\ 1.036 & 0.366
+  \end{pmatrix}
+  \Bigg) \nonumber\\\nonumber
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations}\\
+    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
+  \end{cases}
+\end{align}
+The benchmark model for $y_{t}$ is an AR(1) and the alternative model
+includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
+120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
+first \dgp\ mimics an asset pricing application and the second mimics
+\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
+National Activity Index.
+
+\begin{table}[tb]
+  \centering
+<<mc2, echo=F, results=tex>>=
+printall(mcdata2)
+@ 
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; Pr[disagree] gives
+  the fraction of simulations in which this paper's test and Clark and
+  West's (2007) give different conclusions.}
+\label{tab:mc2}
+\end{table}
+
+Table~\ref{tab:mc1} presents the simulation results
+for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
+all of the parameter values, our proposed new statistic has slightly
+lower rejection probability than \citepos{ClW:07}.  For both \dgp s
+the statistics are slightly undersized.  In~\eqref{eq:dgp1}, this
+translates to relatively low power and the power difference between
+the two statistics may be noticeable.  In~\eqref{eq:dgp2}, though, the
+evidence against the benchmark is strong enough under the alternative
+that the tests reject almost all of the time.  In that setting, the
+lower power of our new test is essentially irrelevant.
+
+% This table presents results for an auxiliary simulation that has R
+% very low and P very high, and basically works as a check
+
+% \begin{table}[tb]
+%  \centering
+% <<mc3, echo=F, results=tex>>=
+% % mcdata3 <- dbframe("dgp3", "mcdata.db")
+
+% d <- subset(select(mcdata3, group.by = c("R", "P"), 
+%                    sprintf(c("R", "P", 
+%                              "100 * avg(pOld <= %f) as 'Pr[\\textsc{cw}]'",
+%                              "100 * avg(pNew <= %f) as 'Pr[new]'",
+%                              "100 * (avg(pOld <= %f and pNew > %f) + avg(pOld > %f and pNew <= %f)) as 'Pr[disagree]'"),
+%                            size, size, size, size)))
+% d$R <- fspace(d$R)
+% d$P <- fspace(d$P)
+% d[[3]] <- fspace(d[[3]])
+% d[[4]] <- fspace(d[[4]])
+% d[[5]] <- fspace(d[[5]])
+% printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,1,1,1), 
+%               align = c("l","C","C","C","C","C"), 
+%               sanitize.text.function = function(x) x,
+%               tabular.environment = "tabularx")
+% @ 
+% \caption{Size and power of the \oos\ tests under sanity-check \dgp\ at
+%   10\% confidence.  These percentages are calculated from 5000
+%   samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+%   and West's (2007) statistic rejects; Pr[new] shows the fraction of
+%   simulations for which this paper's test rejects; Pr[disagree] gives
+%   the fraction of simulations in which this paper's test and Clark and
+%   West's (2007) give different conclusions.}
+% \label{tab:mc3}
+% \end{table}
+% Table~\ref{tab:mc3} presents one more simulation; the alternative
+% model is $y_{t} = 0 + 0 x_{1t} + 0 x_{2t} + \varepsilon$ and the
+% benchmark model is just a constant.  This simulation is meant as a
+% sanity check on the previous results.
+
+%%% Local Variables:
+%%% TeX-master: "Paper"
+%%% End:
+% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
+% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
+% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
+% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS gsub
+% LocalWords:  ClM tabularx textwidth fspace enskip

### 2012-03-30 MakeScript.R

@@ -3,8 +3,8 @@
 # run in parallel.  Running this file will print out text for a
 # makefile, so it might be easiest to just look at its output.
 
-nsims <- 5000  # this is the number of simulations
-njobs <- 6     # I set this to equal the number of processors on my 
+nsims <- 800  # this is the number of simulations
+njobs <- 8     # I set this to equal the number of processors on my 
                # computer.  Changing its value will change the results
                # of the simulations, since they'll be seeded differently.
 

### 2012-03-30 R/empirics.R

@@ -1,0 +1,52 @@
+library(OOS)
+source("R/mcsetup.R")
+
+dfull <- ts(read.csv("data/monthlyData2009.csv")[,-1],
+            start = c(1871, 1), frequency = 12)
+stock.returns <- (dfull[,"price"] + dfull[,"dividend"]) / lag(dfull[,"price"], -1) - 1
+
+dfull <- lag(cbind(equity.premium              = lag(log1p(stock.returns)
+                 - log1p(dfull[,"risk.free.rate"]), 1),
+               default.yield.spread        = dfull[,"baa.rate"] - dfull[,"aaa.rate"],
+               inflation                   = dfull[,"inflation"],
+               stock.variance              = dfull[,"stock.variance"],
+               dividend.payout.ratio       = log(dfull[,"dividend"]) - log(dfull[,"earnings"]),
+               long.term.yield             = dfull[,"long.term.yield"],
+               term.spread                 = dfull[,"long.term.yield"] - dfull[,"t.bill"],
+               treasury.bill               = dfull[,"t.bill"],
+               default.return.spread       = dfull[,"corp.bond"] - dfull[,"long.term.rate"],
+               dividend.price.ratio        = log(dfull[,"dividend"]) - log(dfull[,"price"]),
+               dividend.yield              = log(dfull[,"dividend"]) - log(lag(dfull[,"price"], -1)),
+               long.term.rate              = dfull[,"long.term.rate"],
+               earnings.price.ratio        = log(dfull[,"earnings"]) - log(dfull[,"price"]),
+               book.to.market              = dfull[,"book.to.market"],
+               net.equity                  = dfull[,"net.equity"]),
+         k=-1)
+d <- data.frame(window(dfull, start = c(1927,1), end = c(2009,12)))
+R <- 120 ## do a ten year window?
+
+## calculate Goyal and Welch's original forecasts
+preds <- as.data.frame(lapply(setdiff(names(d), "equity.premium"), function(n) {
+  apply.oos(R, d, function(d) lm(formula(paste("equity.premium ~", n)), data = d))}))
+names(preds) <- setdiff(names(d), "equity.premium")
+
+## impose Campbell and Thompson's non-negativity requirement
+preds.CT <- as.data.frame(lapply(preds, function(x) pmax(x, 0)))
+
+## estimate aggregate forecasts
+preds$avg <- apply(as.matrix(preds), 1, mean)
[…]

### 2012-03-30 R/mcsetup.R

@@ -1,26 +1,132 @@
 calstat <- function(d, R, null, alt, xfn, yfn) {
   n <- nrow(d)
   oos <- (R+1):n
-  P <- n - R
-  
-  pnull <- apply.oos(R, d, null, "recursive", "forecast")
-  enull <- apply.oos(R, d, null, "recursive", "error")
-  palt <- apply.oos(R, d, alt, "rolling", "forecast")
-  ealt <- apply.oos(R, d, alt, "rolling", "error")
-  
-  f <- enull^2 - ealt^2 + (pnull - palt)^2
+
   X <- xfn(d)
-  Y <- yfn(d)
-  FBh <- drop(tcrossprod(solve(crossprod(X) / n,
-                               colMeans(c(2 * pnull - palt - Y[oos]) * X[oos,,drop=FALSE])),
-                         c(enull) * X[oos,,drop=FALSE]))
-  S <- var(cbind(f, FBh))
-  sd <- sqrt((S[1,1] + 2 * S[1,2] + 2 * S[2,2]) / P)
-  fbar <- mean(f)
-  
-  c(pval(fbar, sd, oneSided=TRUE), pval(fbar, sd, oneSided=FALSE))
+  pnull <- apply.oos(R, d, null, "recursive", "forecast")
+  palt <- apply.oos(R, d, alt, "rolling", "forecast")
+  r <- calmain(d, R, pnull, palt, xfn, yfn,
+               solve(crossprod(X)/n,
+                 colMeans(X[oos,,drop=FALSE] * c(pnull - palt))))
+  unname(pnorm(r[1], 0, r[2], lower.tail = FALSE))
 }
 
-pval <- function(x, sd, oneSided)
-  ifelse(oneSided, pnorm(x, 0, sd, lower.tail = FALSE),
-         2 * pnorm(abs(x), 0, sd, lower.tail = FALSE))
+calmain <- function(d, R, pnull, palt, xfn, yfn, BF) {
+  n <- nrow(d)
+  oos <- (R+1):n
+  P <- n - R
+  
+  X <- xfn(d)
+  Y <- c(yfn(d))
+
+  enull <- Y[oos] - pnull
+  ealt <- Y[oos] - palt
+  
+  f <- enull^2 - ealt^2 + (pnull - palt)^2
+  g <- enull * X[oos,,drop = FALSE] %*% BF
+
[…]

### 2012-03-30 R/montecarlo.R

@@ -63,6 +63,6 @@ for (r in rows(mcdesign)) {
       d <- with(r, rdgp(R + P, isPower))
       cals <- calstat(d, r$R, null, alt, xfn, yfn)
       c(pOld = oos.t(null, alt, d, r$R, method = "ClW:07", conf.level = .9)$p.value,
-        pNew1 = cals[1], pNew2 = cals[2])
+        pNew = cals)
     })), row.names = seq_len(nsim))
 }

### 2012-03-30 R/montecarlo2.R

@@ -56,6 +56,6 @@ for (r in rows(mcdesign)) {
       d <- with(r, rdgp(R + P, isPower))
       cals <- calstat(d, r$R, null, alt, xfn, yfn)
       c(pOld = oos.t(null, alt, d, r$R, method = "ClW:07", conf.level = .9)$p.value,
-        pNew1 = cals[1], pNew2 = cals[2])
+        pNew = cals)
     })), row.names = seq_len(nsim))
 }

### 2012-03-30 R/montecarlo3.R

@@ -38,6 +38,6 @@ for (r in rows(mcdesign)) {
       d <- with(r, rdgp(R + P))
       cals <- calstat(d, r$R, null, alt, xfn, yfn)
       c(pOld = oos.t(null, alt, d, r$R, method = "ClW:07", conf.level = .9)$p.value,
-        pNew1 = cals[1], pNew2 = cals[2])
+        pNew = cals)
     })), row.names = seq_len(nsim))
 }

### 2012-03-30 Paper.tex
Revised paper

--- 2011-11-19 Paper.tex
@@
-\documentclass[10pt,fleqn,draft]{article}
+\documentclass[12pt,fleqn]{article}
 
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate}
 \usepackage[nolists,nomarkers]{endfloat}
 \usepackage[sort,round]{natbib}
-\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
+\usepackage[margin=1.25in]{geometry}
 \usepackage[small]{caption}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
 
@@
 \frenchspacing
-\input{tex/simulationdefinitions}
-\input{tex/empiricalresults}
-
-% redfine heading styles
-\makeatletter
-\renewcommand\section{\@startsection%
-{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
-{\normalfont\normalsize\bfseries\large\raggedright}}
-\makeatother
+\onehalfspacing
 
@@
     \texttt{gcalhoun@iastate.edu}.  Web:
-    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
-    participants at the 2011 Midwest Econometrics Group meeting for
-    helpful comments.  I'd also like to thank Amit Goyal for providing
-    computer code and data for his 2008 \textsc{rfs} paper with Ivo
-    Welch \citep{GoW:08}.} \\
-  Iowa State University}
+    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  This paper
+    has benefited from my conversations with Helle Bunzel, Graham
+    Elliott, Yu-Chin Hsu, Pablo Pincheira, and Allan Timmermann; thank
+    you.  I'd also like to thank Amit Goyal for providing computer
+    code and data for his 2008 \textsc{rfs} paper with Ivo Welch
+    \citep{GoW:08}.} \\ Iowa State University}
 
@@
   paper also presents a method to compare multiple models
-  simultaneously while controlling familywise error, and
+  simultaneously while controlling family-wise error, and
   substantially improves existing block bootstrap methods for
@@
 literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.\footnote{Other papers in this literature include
+beginning with \citet{DiM:95} and \citet{Wes:96} and continuing with
 \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
-  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
-  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
-  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
-  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
-  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
-  reviews of this literature and additional references, see
-  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
-  \citet{CoD:11}, and \citet{Gia:11}}
-
-In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
-the null hypothesis that a small benchmark model is correctly
-specified.  Their test compares the forecasting performance of a pair
-of nested models, and the null hypothesis is that the innovations in
-the smaller model form a martingale difference sequence.  This test
-procedure is popular, and one assumes that this is due in part to the
-statistic's convenience.  The statistic is approximately normal after
-adjusting for the estimation error of the larger model.  Normality
-comes from a fixed-length rolling window, as in \citet{GiW:06}, and
-the adjustment centers the statistic appropriately.  This statistic is
-especially convenient because other \oos\ tests for similar hypotheses
-\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
-nonstandard limit distribution and place restrictions on the models
-under consideration, while other asymptotically normal statistics test
-a different null hypothesis \citep{GiW:06} or place assumptions on the
+\citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11}, \citet{CCS:01},
+\citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00}, \citet{InK:04,InK:06},
+\citet{Han:05}, \citet{Ros:05}, \citet{ClW:06,ClW:07}, \citet{Ana:07},
+\citet{GiR:09,GiR:10}, \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11},
+\cite{Pin:11}, \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among
+others.\footnote{For recent reviews of this literature and additional
+  references, see \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06},
+  \citet{ClM:11c}, \citet{CoD:11}, and \citet{Gia:11}}
+
+In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of the
+null hypothesis that a small benchmark model is correctly specified.
+Their test compares the forecasting performance of a pair of nested
+models, and the null hypothesis is that the innovations in the smaller
+model form a martingale difference sequence.  This test procedure is
+popular,\footnote{As of 12 September, 2011, \citet{ClW:06} has been
+  cited by 28 papers indexed by the \textsc{isi} Web of Knowledge, and
+  \citet{ClW:07} by 41. They have been cited by 132 and 172 papers
+  indexed by Google Scholar respectively.} and one assumes that this
+is due in part to the statistic's convenience.  The statistic is
+approximately normal after adjusting for the estimation error of the
+larger model.  Normality comes from a fixed-length rolling window, as
+in \citet{GiW:06}, and the adjustment centers the statistic
+appropriately.  This statistic is especially convenient because other
+\oos\ tests for similar hypotheses \citep[among
+others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a nonstandard
+limit distribution and place restrictions on the models under
+consideration, while other asymptotically normal statistics test a
+different null hypothesis \citep{GiW:06} or place assumptions on the
 models and \dgp\ that are often violated in empirical work
@@
 power advantage and is similar in spirit to using a likelihood ratio
-test instead of an \textsc{lm} or Wald test, which depend on just the
-restricted or unrestricted model respectively.  Simulations presented
-in Section~\ref{sec:2} show that mixing window strategies gives a
-substantial power advantage when there are breaks.
+test instead of an \textsc{lm} or Wald test.
 
@@
 pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
-define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
-model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
-difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
-y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
+define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model
+is correctly specified, so $\varepsilon_{t+1}$ is a martingale
+difference sequence with respect to $\mathcal{F}_t = \sigma(y_{t+1},
+x_t, v_t, y_t, x_{t-1}, v_{t-1}, \dots)$ then we can see immediately
+that
 \begin{equation}
@@
 with $R$ an arbitrary starting value\footnote{You will see momentarily
-  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
+  why the summation begins at $R+1$ instead of 1.} and $P = T - R$,
 obeys an \mds\ \clt\ (assuming that its variance is uniformly
@@
   - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
-  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
+  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big]
 \end{equation}
+almost surely.
 
@@
     $x_t$.
-  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
+  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
     $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
-    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
+    uniform mixing series of size $-\frac{r}{2r-2)}$.  Also, $y_t$,
     $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
@@
   martingale difference sequence with respect to the filtration
-  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
+  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$,
   $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
@@
 
-\begin{rem}
-  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
-  window but claim that their results hold for a fixed-length fixed
-  window as well, where the unknown coefficients are estimated only
-  once using the first $R$ observations.  This claim is true but not
-  obviously so.  The proof for the rolling window is based on the idea
-  that the forecast errors are weakly dependent because they are a
-  function of a finite number of consecutive weakly dependent
-  observations.  But using a fixed window introduces another source of
-  dependence.  All of the forecasts depend on the same coefficient
-  estimates.  One can prove that their results apply to fixed window
-  forecasts by using a coupling argument similar to \citepos{Cal:11}.
-  Interested readers should refer to \citet{Cal:11} for the argument
-  and to \citet{MeP:02} for a review of the necessary coupling
-  results.
-\end{rem}
-
 Since most empirical papers study more than one alternative model,
@@
   nominal size.}  Econometricians, e.g. \citet{Whi:00},
-\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
-statistics that test families of hypotheses that control the
-probability any hypothesis is rejected given that they all are true,
-known as \textit{weak control of familywise error}
-(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
-  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
-  control \sfwe\ for certain families of one-sided tests.}  This paper
+\citet{Han:05}, and \citet{ClM:11}, have emphasized statistics that
+test families of hypotheses that control the probability any
+hypothesis is rejected given that they all are true, known as
+\textit{weak control of family-wise error} (\wfwe).  This paper
 focuses instead on controlling the probability that at least one true
 hypothesis is rejected given any combination of true and false
-hypotheses, known as \textit{strong control of familywise error}
+hypotheses, known as \textit{strong control of family-wise error}
 (\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
@@
 control \sfwe\ if the individual null hypotheses are strengthened
-slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
-well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
-construct critical values from the asymptotic joint distribution of
-the test statistics and can control \sfwe\ as long as there is a
-consistent estimate of that distribution.
+slightly as below (see Part~\ref{it:1} of Theorem~\ref{res:2} as well as
+Remark~\ref{rem:2}).
 
@@
     $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
-    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
+    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
     $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
     procedure outlined above, but using the moving block bootstrap
-    with block length $1$, has probability at most $\alpha$ of rejecting
+    with block length 1, has probability at most $\alpha$ of rejecting
     one or more models in $I$.
   \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is an \textsl{\mds} with respect to $\mathcal{F}_{lt}$
+    \hat{y}_{0t}$ is an \mds\ with respect to $\mathcal{F}_{lt}$
     against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
@@
 \begin{rem}\label{rem:2}
-  The key difference between Parts~(\ref{it:1}) and~(\ref{it:2}) is
-  that, in Part~(\ref{it:2}), the forecast error is an \mds\ with
-  respect to several individual series, but not necessarily with
-  respect to the pooled information set generated by all of those
-  series together.\footnote{It is straightforward to construct three
-    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
-    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
+  The key difference between Parts~\ref{it:1} and~\ref{it:2} is that,
+  in Part~\ref{it:2}, the forecast error is an \mds\ with respect to
+  several individual series, but not necessarily with respect to the
+  pooled information set generated by all of those series
+  together.\footnote{It is straightforward to construct three series,
+    $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with respect
+    to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
     $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
     $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
-    This is essentially the scenario imposed in Part~(\ref{it:2}).}
-  Using $b = 1$ would consistently estimate the marginal distribution
-  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
+    This is essentially the null imposed in Part~\ref{it:2}.}  Using
+  $b = 1$ would consistently estimate the marginal distribution of
+  each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
   hypothesis, but would not necessarily estimate the joint
@@
   \citep[i.e.][]{ClM:11} achieves control of \sfwe\ only under the
-  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
-  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
-  so researchers can make use of the considerable simplifications that
-  occur in that setting.
+  stronger hypotheses of Part~\ref{it:1}.  Fortunately, Part~\ref{it:1} seems to capture
+  the goal of most empirical work, so researchers can make use of the
+  considerable simplifications that occur in that setting.
+\end{rem}
+
+\begin{rem}
+  The procedure described above is a refinement of the StepM for
+  one-sided tests along the lines of \citepos{Han:05} \spa, but with
+  better power.  Hansen's \spa\ is motivated by the observation that
+  including models $i$ for which $\E \bar f_{i}$ is strongly negative
+  reduces the test's power: the critical values are taken as the
+  maximum over a larger number of models, but the $i$th model will
+  almost never exceed the critical value.  Hansen suggests discarding
+  models for which $\bar f_i$ is below a threshold implied by the Law
+  of the Iterated Logarithm.  \citet{Cal:11e} suggests the threshold
+  used in Theorem 2 and argues that it has better size and power
+  properties.  See \citet{Cal:11e} for further motivation and
+  explanation.
 \end{rem}
@@
   models that could be used as the benchmark, researchers may want to
-  control for data snooping over the null hypotheses as well as the
+  control for data-snooping over the null hypotheses as well as the
   alternatives.  For example, one could use either \citepos{AtO:01}
@@
   Intersection-Union test, so Theorem~\ref{res:2}'s procedure
-  (Part~(\ref{it:3})) easily accommodates this extension by taking
-  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
+  (Part~\ref{it:3}) easily accommodates this extension by taking each
+  $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
   $q$-vector;\footnote{If a researcher uses multiple benchmark models,
     it would be a mistake to assume that they are all correctly
-    specified, so only the null hypothesis of Part~(\ref{it:3}) is
-    appropriate.} the first element of $\bar f_{i}$ compares the first
+    specified.} the first element of $\bar f_{i}$ compares the first
   benchmark model to the $i$th alternative and the first element of
@@
   \begin{enumerate}
-  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
+  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
     a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
@@
 \section{Monte Carlo Results}\label{sec:2}
-I'll conduct two brief Monte Carlo experiments to demonstrate that the
-modified version of \citepos{ClW:07} statistic performs similarly to
-their original test in the situations they study.\footnote{All of
-  these simulations were programmed in R \citep[version 2.14.0]{R} and
-  use the \textsc{MASS} \citep[version info]{VeR:02}, xtable
-  \citep[version info]{Dah:09}, and dbframe \citep[version
-  0.2.1]{Cal:10b} packages.  For details on the programming, please
-  see the supplemental appendices \citep{Cal:11f,Cal:11g,Cal:11h}.}
-I'll use both of the \dgp s they consider as well as a modification to
-study the performance of the statistics if there is instability.
-
-The first \dgp\ has three different parametrizations; one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
-  y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
-  \gamma^{*}_t &=
-  \begin{cases}
-    0    & \text{size simulations} \\
-    0.35 & \text{power (stable)} \\
-    0    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    0.70 & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
-  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
-\end{align}
-Both models are estimated by \ols. The benchmark model regresses $y_t$
-on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  We use both \poscw\ original statistic and the new
-statistic to test the null that the benchmark model's innovation is an
-\mds.\footnote{\citet{ClW:07} report the performance of the tests
-  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
-  based on the naive Gaussian statistic.}  \citet{ClW:06,ClW:07} only
-look at the stable case.
-
-\begin{table}[tb]
-  \centering
-  \input{floats/simulation1}
-\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
-  10\% confidence.  These percentages are calculated from 5000
-  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
-  and West's (2007) statistic rejects; Pr[new] shows the fraction of
-  simulations for which this paper's test rejects; and Pr[disagree]
-  gives the fraction of simulations in which this paper's test and
-  Clark and West's (2007) give different conclusions.}
-\label{tab:mc1}
-\end{table}
-
-The second \dgp\ is
-\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
-  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
-  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
-  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
-  z_{t-4} + v_{t} \nonumber \\
-  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
-  \begin{pmatrix}
-    0 \\ 0
-  \end{pmatrix},
-  \begin{pmatrix}
-    10.505 & 1.036 \\ 1.036 & 0.366
-  \end{pmatrix}
-  \Bigg) \nonumber\\\nonumber
-  \gamma^{*} &=
-  \begin{cases}
-    0 & \text{size simulations}\\
-    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
-  \end{cases}
-\end{align}
-The benchmark model for $y_{t}$ is an AR(1) and the alternative model
-includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
-120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
-first \dgp\ mimics an asset pricing application and the second mimics
-\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
-National Activity Index.
-
-\begin{table}[tb]
-  \centering
-  \input{floats/simulation2}
-\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
-  10\% confidence.  These percentages are calculated from 5000
-  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
-  and West's (2007) statistic rejects; Pr[new] shows the fraction of
-  simulations for which this paper's test rejects; Pr[disagree] gives
-  the fraction of simulations in which this paper's test and Clark and
-  West's (2007) give different conclusions.}
-\label{tab:mc2}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results
-for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
-all of the stable parameter values, the proposed new statistic has
-similar rejection probability to \citepos{ClW:07}.  Clark and West's
-test is slightly more undersized than the new test, but has a little
-higher power under the alternative.  Moreover, the statistics give
-different results in less than 10\% of the simulations for most
-parametrizations of the \dgp s.  In general, the statistics perform
-similarly well.
-
-For the simulations with a single break, the new statistic has about
-twice the power of \poscw\ original test.  For most parametrizations
-of \dgp\ 1, the new test rejects over 90\% of the time, while Clark
-and West's test rejects about 40\% of the time.  So mixing window
-strategies can give a substantial power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
+\input{mc}
 \section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of the statistics introduced earlier
-in the paper by revisiting \citepos{GoW:08} study of excess stock
-returns.  Goyal and Welch argue that many variables thought to predict
-excess returns (measured as the difference between the yearly log
-return of the S\&P 500 index and the T-bill interest rate) on the
-basis of in-sample evidence fail to do so out-of-sample.  To show
-this, Goyal and Welch look at the forecasting performance of models
-using a lag of the variable of interest, and show that these models do
-not significantly outperform the excess return's recursive sample mean.
-
-Here, I conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
-\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
-$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
-predictors used are listed in the ``predictor'' column of
-Table~\ref{tab:em1} \citep[see][for a detailed description of the
-variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses 10
-observations.\footnote{This statistical analysis was conducted in R
-  \citep{R} using the xtable \citep[version]{Dah:09}, Hmisc
-  \citep[version]{Har:10}, and dbframe \citep[version 0.2.1]{Cal:10b}
-  packages; please see the supplemental appendices for details on the
-  programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-``value'' gives the value of the test statistic for each model, while
-the ``naive'' and ``corrected'' columns indicate whether the statistic
-is greater than the standard size-10\% critical value (1.28) and the
-critical value estimated by the procedure of Theorem~\ref{res:2}
-(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
-  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
-  of Theorem~\ref{res:2}.}  Three predictors are significant at the
-naive critical values for both the original and bounded forecasts: the
-dividend yield, long term interest rate, and book to market ratio.
-But none are significant after accounting for data snooping, which
-highlights the importance of these methods.  The median forecast is
-significant using conventional critical values as well, but not the
-corrected values.
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the ``predictor'' column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The ``value'' column
-  lists the value of this paper's \oos\ statistic, the ``naive''
-  column indicates whether the statistic is significant at standard
-  critical values, and the ``corrected'' column indicates significance
-  using the critical values proposed in Theorem~\ref{res:2} that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
+\input{empirics}
 \section{Conclusion}\label{sec:4}
@@
 that the new statistic behaves similarly to Clark and West's original
-test when the \dgp\ is stable, but can have much higher power when the
-predictability varies over time, suggesting that the new statistic is
-a suitable replacement in applied research.  The paper also presents a
-method for comparing the benchmark model to several alternative models
-simultaneously and improves block bootstrap procedures of \oos\
-statistics.
+test, suggesting that the new statistic is a suitable replacement in
+applied research.  The paper also presents a method for comparing the
+benchmark model to several alternative models simultaneously and
+improves block bootstrap procedures of \oos\ statistics.
 
@@
   \end{equation}
-  Proving~\eqref{eq:3} uses the same argument as~\citet[Lemma
-  A.3]{Mcc:00} and~\eqref{eq:2} follows a streamlined version of the
-  argument of~\ref{res:a5}, completing the proof.  The proofs for the
-  moving and circular block bootstraps are the same.
+  Proving~\eqref{eq:3} uses essentially the same argument
+  as~\citet[Lemma A.3]{Mcc:00} and~\eqref{eq:2} essentially follows a
+  streamlined version of the argument of~\ref{res:a5}, completing the
+  proof.  The proofs for the moving and circular block bootstraps are
+  essentially the same.
 \end{proof}
@@
 % LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har
+% LocalWords:  familywise prespecified CoD Gia pointwise misspecified

### 2012-03-30 empirics.Rnw
Revised paper

@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
+\SweaveOpts{prefix.string=floats/empirics}
+\SweaveOpts{split=TRUE}
 
 <<echo=F>>=
-library(dbframe)
 library(xtable)
+library(Hmisc)
+load("empirics.RData")
+attach(results)
 
@@
 
-fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))
-
-printall <- function(mcdb,...) {
-  d <- subset(select(mcdb, group.by = groups, 
-                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
-                               "R", "P", 
-                               "100 * avg(pOld <= %f) as 'Pr[\\textsc{cw}]'",
-                               "100 * avg(pNew1 <= %f) as 'Pr[new]'",
-                               "100 * (avg(pOld <= %f and pNew1 > %f) + avg(pOld > %f and pNew1 <= %f)) as 'Pr[disagree]'"),
-                             size, size, size, size)), select = -isPower)
-  d$R <- fspace(d$R)
-  d$P <- fspace(d$P)
-  d[[4]] <- fspace(d[[4]])
-  d[[5]] <- fspace(d[[5]])
-  d[[6]] <- fspace(d[[6]])
-  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
-  d$type[duplicated(d$type)] <- NA
-  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
-                align = c("l","X","C","C","C","C","C"), 
-                sanitize.text.function = function(x) x,
-                tabular.environment = "tabularx")
-  invisible(d)
-}
+fspace <- function(x, rnd=1) gsub("-", "--", gsub(" ", "\\\\enskip", format(round(x, rnd))))
 @
 
-This is the empirical section
+This section demonstrates the use of the statistics introduced earlier
+in the paper by revisiting \citepos{GoW:08} study of excess stock
+returns.  Goyal and Welch argue that many variables thought to predict
+excess returns (measured as the difference between the yearly log
+return of the S\&P 500 index and the T-bill interest rate) on the
+basis of in-sample evidence fail to do so out-of-sample.  To show
+this, Goyal and Welch look at the forecasting performance of models
+using a lag of the variable of interest, and show that these models do
+not significantly outperform the excess return's recursive sample mean.
+
+Here, I conduct the same analysis,, but using this paper's \mds\ test.
+The benchmark model is the excess return's sample mean (as in the
+original) and the alternative models are of the form
+\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
+\text{predictor}_{t-1} + \varepsilon_{t},\]
+where $\alpha_{0}$ and $\alpha_{1}$ are estimated by \ols\ using a
+10-year window.  The predictors used are listed in the ``predictor''
+column of Table~\ref{tab:em1} \citep[see][for a detailed description
+of the variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
+correction to the models, that the forecasts be bounded below by zero
+since negative forecasts are incredible, as well as two simple
+combination forecasts, the mean and the median (over both the original
+and the non-negative forecasts).  The data set is annual data
+beginning in 1927 and ending in 2009, and the rolling window is of
+length 10.
+
+Table~\ref{tab:em1} presents the results for each model.  The column
+``value'' gives the value of the test statistic for each model, while
+the ``naive'' and ``corrected'' columns indicate whether the statistic
+is greater than the standard size-10\% critical value
+(\Sexpr{round(qnorm(.9),2)}) and the critical value estimated by the
+procedure of Theorem~\ref{res:2}
+(\Sexpr{round(sqrt(crit),2)}).\footnote{The bootstrap uses 999
+  replications, and we use the i.i.d. bootstrap proposed in
+  Part~\ref{it:1} of Theorem~\ref{res:2}.}  Three predictors are
+significant at the naive critical values for both the original and
+bounded forecasts: the dividend yield, long term interest rate, and
+book to market ratio.  But none are significant after accounting for
+data-snooping, which highlights the importance of these methods.  The
+median forecast is significant using conventional critical values as
+well, but not the corrected values.
+
+\begin{table}[tb!]
+  \centering
+<<table, echo=F, results=tex>>=
+k <- length(tstats)/2 - 1
+d <- data.frame(notes = c("Original", rep("", k-1), "CT correction", rep("", k-1), "Combination", ""),
+                predictor = names(tstats),
+                tstat = fspace(tstats, 2),
+                naive = ifelse(tstats > qnorm(.9), "sig.", ""),
+                smart  = ifelse(tstats > crit, "sig.", ""),
+                row.names = 1:(2*k + 2))
+colnames(d)[1] <- " "
+colnames(d)[3] <- "value"
+colnames(d)[4] <- "naive"
+colnames(d)[5] <- "corrected"
+
+d$predictor <- gsub("\\.mu", "", d$predictor)
+d$predictor <- gsub("\\.CT", "", d$predictor)
+d$predictor <- gsub("\\.", " ", d$predictor)
+d$predictor <- capitalize(d$predictor)
+
+printbooktabs(d, sanitize.text.function = function(x) x, include.rownames = FALSE,
+              align = c("l", "l", "l", rep("C", 3)), tabular.environment = "tabularx")
+@ 
+\caption{Results from \oos\ comparison of equity premium prediction
+  models; the benchmark is the recursive sample mean of the equity
+  premium and each alternative model is a constant and single lag of
+  the variable listed in the ``predictor'' column.  The dataset begins
+  in 1927 and ends in 2009 and is annual data. The ``value'' column
+  lists the value of this paper's \oos\ statistic, the ``naive''
+  column indicates whether the statistic is significant at standard
+  critical values, and the ``corrected'' column indicates significance
+  using the critical values proposed in Theorem~\ref{res:2} that
+  account for the number of models.  See Section~\ref{sec:3} for details.}
+\label{tab:em1}
+\end{table}
 
@@
 % LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
-% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS
-% LocalWords:  ClM
+% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS Hmisc
+% LocalWords:  ClM empirics RData gsub tabularx textwidth fspace rnd enskip GoW
+% LocalWords:  Goyal Welch return's CaT qnorm crit tstats tstat ifelse sig sqrt
+% LocalWords:  colnames

### 2012-03-30 mc.Rnw
Revised paper

@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
+\SweaveOpts{prefix.string=floats/mc}
+\SweaveOpts{split=TRUE}
 
@@
 
-I'll also conduct two brief Monte Carlo experiments to demonstrate
-that the modified version of \citepos{ClW:07} statistic performs
-similarly to their original test.\footnote{All of these simulations
-  were programmed in R \citep{R:2-13-0} and use the \textsc{MASS}
-  \citep[ver. 7.3-12]{VeR:02}, xtable \citep[ver. 1.5-6]{Dah:09},
-  dbframe \citep[ver. 0.1.1]{Cal:10b}, and \textsc{oos}
-  \citep[ver. 0.01]{Cal:11b} packages.}  We'll use both of the \dgp s
-they consider.  For the first, we have
+I'll conduct two brief Monte Carlo experiments to demonstrate that the
+modified version of \citepos{ClW:07} statistic performs similarly to
+their original test.\footnote{All of these simulations were programmed
+  in R \citep{R:2-13-0} and use the \textsc{MASS} \citep{VeR:02},
+  xtable \citep{Dah:09}, dbframe \citep{Cal:10b}, and \textsc{oos}
+  \citep{Cal:11b} packages.  Version information is listed in the
+  bibliography.}  We'll use both of the \dgp s they consider.  For the
+first, we have
 \begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
@@
 on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  We use both \poscw\ original statistic and our new
+$z_{t-1}$.  We use both \poscw\ original statistic and the new
 statistic to test the null that the benchmark model's innovation is an
@@
 for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
-all of the parameter values, our proposed new statistic has slightly
-lower rejection probability than \citepos{ClW:07}.  For both \dgp s
-the statistics are slightly undersized.  In~\eqref{eq:dgp1}, this
-translates to relatively low power and the power difference between
-the two statistics may be noticeable.  In~\eqref{eq:dgp2}, though, the
-evidence against the benchmark is strong enough under the alternative
-that the tests reject almost all of the time.  In that setting, the
-lower power of our new test is essentially irrelevant.
+all of the parameter values, the proposed new statistic has similar
+rejection probability to \citepos{ClW:07}.  Clark and West's test is
+slightly more undersized than the new test, but has a little higher
+power under the alternative.  Moreover, the statistics give different
+results in less than 10\% of the simulations for most parametrizations
+of the \dgp s.  In general, the statistics perform similarly well.
 
@@
 % LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS gsub
-% LocalWords:  ClM tabularx textwidth fspace enskip
+% LocalWords:  ClM tabularx textwidth fspace enskip VeR Dah

### 2012-03-30 R/empirics.R

@@ -1,8 +1,11 @@
 library(OOS)
 source("R/mcsetup.R")
 
-dfull <- ts(read.csv("data/monthlyData2009.csv")[,-1],
-            start = c(1871, 1), frequency = 12)
+## code to do monthly returns
+## dfull <- ts(read.csv("data/monthlyData2009.csv")[,-1],
+##             start = c(1871, 1), frequency = 12)
+dfull <- ts(read.csv("data/yearlyData2009.csv")[,-1],
+            start = 1871, frequency = 1)
 stock.returns <- (dfull[,"price"] + dfull[,"dividend"]) / lag(dfull[,"price"], -1) - 1
 
 dfull <- lag(cbind(equity.premium              = lag(log1p(stock.returns)
@@ -22,8 +25,10 @@ dfull <- lag(cbind(equity.premium              = lag(log1p(stock.returns)
                book.to.market              = dfull[,"book.to.market"],
                net.equity                  = dfull[,"net.equity"]),
          k=-1)
-d <- data.frame(window(dfull, start = c(1927,1), end = c(2009,12)))
-R <- 120 ## do a ten year window?
+## more monthly return code
+## d <- data.frame(window(dfull, start = c(1927,1), end = c(2009,12)))
+R <- 10 ## do a ten year window?
+d <- data.frame(window(dfull, start = 1927, end = c(2009)))
 
 ## calculate Goyal and Welch's original forecasts
 preds <- as.data.frame(lapply(setdiff(names(d), "equity.premium"), function(n) {
@@ -34,19 +39,28 @@ names(preds) <- setdiff(names(d), "equity.premium")
 preds.CT <- as.data.frame(lapply(preds, function(x) pmax(x, 0)))
 
 ## estimate aggregate forecasts
-preds$avg <- apply(as.matrix(preds), 1, mean)
-preds$med <- apply(as.matrix(preds), 1, median)
+## preds$Average <- apply(as.matrix(preds), 1, mean)
+## preds$Median <- apply(as.matrix(preds), 1, median)
 
-preds.CT$avg <- apply(as.matrix(preds.CT), 1, mean)
-preds.CT$med <- apply(as.matrix(preds.CT), 1, median)
+## preds.CT$Average <- apply(as.matrix(preds.CT), 1, mean)
+## preds.CT$Median <- apply(as.matrix(preds.CT), 1, median)
 
 ## combine the forecasts into a single data frame
[…]

### 2012-03-30 R/mcsetup.R

@@ -5,33 +5,35 @@ calstat <- function(d, R, null, alt, xfn, yfn) {
   X <- xfn(d)
   pnull <- apply.oos(R, d, null, "recursive", "forecast")
   palt <- apply.oos(R, d, alt, "rolling", "forecast")
-  r <- calmain(d, R, pnull, palt, xfn, yfn,
+  r <- calmain(d, R, pnull, palt, yfn, xfn,
                solve(crossprod(X)/n,
                  colMeans(X[oos,,drop=FALSE] * c(pnull - palt))))
   unname(pnorm(r[1], 0, r[2], lower.tail = FALSE))
 }
 
-calmain <- function(d, R, pnull, palt, xfn, yfn, BF) {
+calmain <- function(d, R, pnull, palt, yfn, xfn = NULL, BF = NULL) {
   n <- nrow(d)
   oos <- (R+1):n
   P <- n - R
+  Pi <- 1 - (R/P) * log(1 + P/R)
   
-  X <- xfn(d)
   Y <- c(yfn(d))
 
   enull <- Y[oos] - pnull
   ealt <- Y[oos] - palt
   
   f <- enull^2 - ealt^2 + (pnull - palt)^2
-  g <- enull * X[oos,,drop = FALSE] %*% BF
 
-  Pi <- 1 - (R/P) * log(1 + P/R)
-  
-  S <- var(cbind(f, g))
-  sd <- sqrt((S[1,1] + 2 * Pi * (S[1,2] + S[2,2])) / P)
-  fbar <- mean(f)
-  
-  c(mu = fbar, sd = sd)
+  if (is.null(xfn) | is.null(BF)) {
+    sd <- sd(f)
+  } else {
+    X <- xfn(d)
+    g <- enull * X[oos,,drop = FALSE] %*% BF
+
+    S <- var(cbind(f, g))
+    sd <- sqrt((S[1,1] + 2 * Pi * (S[1,2] + S[2,2])) / P)
+  }
+  c(mu = mean(f), sd = sd)
 }
 
 ## this is what I want rbind to do for data frames
@@ -45,11 +47,12 @@ dstack <- function(...) {
 }
 
 ## calculate the indices that give you a stationary bootstrap draw
-iboot <- function(n, p) {
+iboot <- function(n, b) {
   series <- rep(NA, n)
   bootindex <- 1
   repeat {
[…]

### 2012-03-30 Paper.tex
Drafted initial version of the paper

--- 2012-03-30 Paper.tex
@@
 \usepackage[sort,round]{natbib}
-\usepackage[margin=1.25in]{geometry}
+\usepackage[margin=1in]{geometry}
 \usepackage[small]{caption}
@@
 \bibliographystyle{abbrvnat}
-\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
+\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
 \newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
-\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
+\newcommand\citen[1]{\citeauthor{#1} \citeyear{#1}}
 \frenchspacing
@@
 \newtheorem{cor}[thm]{Corollary}
-\newtheorem{lema}{Lemma}[section]
-\newtheorem{alg}{Algorithm}
-\newtheorem{asmp}{Assumption}[section]
-
-\theoremstyle{definition}
-
+\newtheorem{asmp}{Assumption}
 \newtheorem{example}{Example}
@@
 \DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator{\cov}{cov}
-%\DeclareMathOperator{\vec}{vec}
-\DeclareMathOperator{\vech}{vech}
-
-\DeclareMathOperator{\pr}{Pr}
-
-\newcommand{\X}{\ensuremath{\mathrm{X}}}
-\newcommand{\R}{\ensuremath{\mathrm{R}}}
-\newcommand{\p}{\ensuremath{\mathrm{P}}}
-
 \newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
-\newcommand{\ned}{\textsc{ned}}
-\newcommand{\clt}{\textsc{clt}}
-\newcommand{\fclt}{\textsc{fclt}}
 \newcommand{\aic}{\textsc{aic}}
@@
 \newcommand{\hac}{\textsc{hac}}
-\newcommand{\fwe}{\textsc{fwe}}
-\newcommand{\cdf}{\textsc{cdf}}
 \newcommand{\ma}{\textsc{ma}}
-
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
 
@@
 
-\author{Gray Calhoun\thanks{Address: 467 Heady Hall, Economics
-    Department; Iowa State University; Ames, IA 50011. Telephone:
-    (515) 294-6271.  Email: \texttt{gcalhoun@iastate.edu}.} \\ Iowa
-  State University}
-
-\title{An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models} \date{\today}
+\author{Gray Calhoun} \title{An asymptotically normal out-of-sample
+  test\\ of equal predictive accuracy for nested models} 
+\date{\today}
 \maketitle
@@
 \begin{abstract} 
-  \noindent This paper proposes a modification of \citepos[J.
-  Econom.]{ClW:07} adjusted out-of-sample $t$-test.  The
-  alternative model is still estimated with a fixed-length rolling
-  window, but the benchmark is estimated with a recursive window. The
-  resulting statistic is asymptotically normal even when the models
-  are nested.  Moreover, the alternative model can be estimated using
-  popular model selection methods, such as the \aic\ or \bic.  This
-  paper also presents a new bootstrap procedure based on
-  \citet[Econometrica]{RoW:05} to compare multiple models while
-  controlling family-wise error, and demonstrates this procedure by
-  analyzing \citepos[Rev. Finan. Stud.]{GoW:08} excess returns dataset.
+  \noindent This paper proposes a modification of
+  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
+  to estimate the alternative model under a fixed-length rolling
+  window, but estimate the benchmark model under a recursive
+  window. The resulting statistic gives an asymptotically normal test
+  statistic that the benchmark model is correctly specified, even when
+  it is nested in the alternative.  Moreover, the alternative model
+  can be estimated using popular model selection methods, such as the
+  \aic\ or \bic.
 
@@
 
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Family-wise Error; Multiple Testing;
-Bootstrap; Reality Check
+\noindent Keywords: Out-of-Sample, Forecast Evaluation, Martingale
+Difference Sequence, Model Selection
 
@@
 limit distribution and place restrictions on the models under
-consideration, while other asymptotically normal statistics test a
-different null hypothesis \citep{GiW:06} or place assumptions on the
-models and \dgp\ that are rarely appropriate in empirical work
-\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.
+consideration, while other asymptotically normal statistics
+\citep{GiW:06} test a different null hypothesis.
 
@@
 \citep{ClW:06}. Estimating the parameters of the smaller model
-invalidates their proof.
+invalidates the proof.
 
-In this paper, I prove that a modified version of their statistic is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, we need a consistent estimate of the pseudo-true
-benchmark model, while maintaining an inconsistent estimate of the
-larger model so that we can ignore nesting.  We can meet both needs by
-using different window strategies for each model; the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
+In this paper, I prove that a slightly modified version of their
+statistic is asymptotically normal even when the smaller model is
+estimated.  To achieve normality, we need a consistent estimate of the
+pseudo-true benchmark model, while maintaining an inconsistent
+estimate of the larger model so that we can ignore nesting.  We can
+meet both needs by using different window strategies for each model;
+the benchmark model is estimated using a recursive window and the
+alternative with a fixed-length rolling window.
 
@@
 breaks, parameter drift, or other forms of
-instability,\footnote{Exceptions are \citepos{StW:07}
+instability,\footnote{Exceptions are \possessivecite{StW:07}
   \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
@@
 about instability is often given as a reason for doing an \oos\
-analysis, especially with a short rolling window.\footnote{This
-  motivation is discussed in \citet{StW:03}, \citet{PeT:05,PeT:07},
-  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
-  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
-stability on both models by using a recursive window or relax
-stability for both by using a rolling window; both approaches should
-not affect the test's size, but may affect power.  But the researcher
-could instead impose stability on the benchmark and relax it for the
-alternative by using a recursive window for the benchmark and a
-rolling window for the alternative model.  This approach could have a
-power advantage and is similar in spirit to using a likelihood ratio
-test instead of an \textsc{lm} or Wald test.
+analysis, especially with a short rolling window.\footnote{This is
+  discussed in \citet{StW:03}, \citet{PeT:05,PeT:07}, \cite{GiW:06},
+  \citet{GoW:08}, \citet{ClM:09c}, and \cite{GiR:09,GiR:10}, among
+  others.} A researcher could impose stability on both models by using
+a recursive window or relax stability for both by using a rolling
+window; both approaches should not affect the test's size, but may
+affect power.  But the researcher could instead impose stability on
+the benchmark and relax it for the alternative by using a recursive
+window for the benchmark and a rolling window for the alternative
+model.  This approach could have a power advantage and is similar in
+spirit to using a likelihood ratio test instead of an \textsc{lm} or
+Wald test.
 
@@
 estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
-both the alternative and the benchmark but, as mentioned earlier, they
-test a different aspect of forecasting performance.
+both the alternative and the benchmark, but they test a different
+aspect of forecasting performance.
 
@@
 statistic can be used with non-nested models as well.  This generality
-is useful, since \citepos{Wes:96} results do not apply to non-nested
-models if they both encompass the true \dgp, which is allowable under
-the null: in the limit, both models will converge to the \dgp\ and
-give identical forecasts.  Consequently, the naive \oos\ $t$-test is
-invalid, even after correcting the standard error to reflect parameter
-uncertainty.  Constructing an \oos\ test for non-nested models using
-\citepos{ClM:01} approach would be difficult.  To my knowledge, this
-paper gives the first \oos\ test of equal predictive ability for
-non-nested models that does not implicitly rule out both models
-encompassing the \dgp.\footnote{Again, \citet{GiW:06} does not make
-  this implicit assumption, but their statistic tests a different null
-  hypothesis.}
-
-Statistics for comparing two models are useful, but a researcher often
-has a set of potential models, and wants to know which of them
-significantly outperform the benchmark.  As \citet{Whi:00} shows,
-looking at the naive $p$-values is misleading, but bootstrapping the
-statistics can give a valid test (White calls this procedure the
-``bootstrap reality check'').  So I present a test for equal
-predictive ability of multiple models based on \citepos{RoW:05} StepM,
-which uses a step-down procedure that iteratively rejects models to
-achieve higher power than the reality check (see Theorem~\ref{res:2}
-for details) and will indicate which of the models improves on the
-benchmark.
-
-I also present a new result for the validity of using the stationary
-boostrap with \oos\ statistics, which is necessary to verify that the
-StepM is appropriate.  Existing results on boostrapping \oos\
-statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
-the stationary bootstrap, but require the test sample to be much
-smaller than the training sample, which is obviously inappropriate
-here.  \citet{CoS:07} relax that requirement, but only consider the
-moving block bootstrap \citep{LiS:92,Kun:89} and make the statistic
-more complicated than necessary by adjusting the objective function of
-the bootstrapped statistic to center it correctly.\footnote{Their
-  recentering is required for consistency and does not give higher
-  order accuracy.}  A parametric bootstrap, such as that used by
-\citet{ClM:11}, would be difficult to implement here since we want to
-test whether several different null hypotheses hold individually (as
-I'll discuss later, Clark and McCracken test a single null hypothesis
-that describes the behavior of all of the models under consideration).
-So this paper's result for the stationary bootstrap of \oos\ statistics
-improves on existing procedures.
+is useful, since \possessivecite{Wes:96} results do not apply to
+non-nested models if they both encompass the true \dgp, which is
+allowable under the null, and so the naive \oos\ $t$-test is not
+asymptotically normal (in the limit, both models will converge to the
+\dgp\ and give identical foreasts).  Constructing an \oos\ test for
+non-nested models using \possessivecite{ClM:01} approach would be
+difficult.  To my knowledge, this paper gives the first \oos\ test
+of equal predictive ability for non-nested models that does not
+implicitly rule out both models encompassing the
+\dgp.\footnote{Again, \citet{GiW:06} does not make this implicit
+  assumption, but their statistic tests a different null hypothesis.}
 
 The next section presents our theoretical result and
-Section~\ref{sec:2} presents two simulations that compare our pairwise
-\oos\ test to \poscw\ original statistic.  Section~\ref{sec:3}
-demonstrates the use of our statistic by reanalyzing \citepos{GoW:08}
-study of excess return predictability. Section~\ref{sec:4} concludes.
+Section~\ref{sec:2} presents two simulations that compare our
+statistic to \poscw\ original test.  Section~\ref{sec:3} concludes.
 
-\section{Theoretical Results}\label{sec:1}
-The first result modifies \citepos{ClW:07} so that it is
-asymptotically normal. The conditions are essentially the same in
-existing papers
+\section{Theoretical Result}\label{sec:1}
+We'll present our results as a single theorem.  The conditions are
+essentially the same in existing papers
 \citep[e.g.][]{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a
@@
 
-\begin{thm}\label{res:1}
-  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
+\begin{thm}\label{thm:1}
+  Suppose that we have two models $\hat{y}_{1t}$ and $\hat{y}_{2t}$ to
   forecast the variable $y_t$, and have observations for
-  $t=1,\dots,T+1$.  Assume the following hold:
+  $t=1,\dots,T$.  Assume the following hold:
   \begin{enumerate}
-  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
-    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
+  \item The benchmark forecast $\hat{y}_{1,t}$, is estimated using
+    \ols\ with a recursive window: $\hat{y}_{1,t+1} =
     x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
-    \begin{equation}
-      \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
-      \sum_{s=2}^t x_{t-1} y_t, \qquad t = R,\dots,T.
-    \end{equation}
-    Also define $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1}
-    x_{t-1}'\big)^{-1} \sum_{t=2}^T \E x_{t-1} y_t$.
-  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
-    estimated using a rolling window of fixed length $R$ (which is
-    less than $T$), so $\hat{y}_{1,t+1} =
+    \[\hat{\beta}_t = \Big(\sum_{s=1}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
+    \sum_{s=1}^t x_{t-1} y_t, \qquad t = R,\dots,T.\]
+    Also define $\beta^{*} = \big(\sum_{t=1}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
+    \sum_{t=1}^T \E x_{t-1} y_t$.
+  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
+    a rolling window of fixed length $R$ ($R < T$), so $\hat{y}_{2,t+1} =
     \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
-    function and $z_t$ is a sequence of predictors that includes
-    $x_t$.
-  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
-    $-1/2$ on a strong mixing series of size $-r/(r-2)$ for $r>2$.
-    Also, $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2
-    r+\delta$ moments for some positive $\delta$.
-  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
-    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
-    $\bar{f}(\beta) = P^{-1} \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
-    P^{-1} \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
-    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta)_0$ are
-    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
-    long run variance.
+    function and $z_t$ is a sequence of predictors that includes $x_t$.
+  \item The series $y_t$ and $z_t$ are strong mixing of size
+    $-r/(r-2)$ for $r>2$ and $y_t$, $\hat{y}_{2t}$, and $x_t$ have
+    uniformly bounded $2 r+\delta$ moments for some positive $\delta$.
+  \item Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
+    \hat{y}_{2,t+1})^2 + (x_t'\beta - \hat{y}_{2,t+1})^2\] and $\bar f
+    = P^{-1} \sum_{t=R}^{T-1} f_t(\hat{\beta}_t)$. Then $f(\beta^{*})$
+    is covariance stationary and $\bar f$ has uniformly positive long
+    run variance.
   \end{enumerate}
-  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
+  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
   martingale difference sequence with respect to the filtration
-  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$, $\sqrt{P} \bar f /
-  \hat{\sigma} \to^d N(0,1)$, where
+  $\sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$, $\sqrt{P} \bar f /
+  \hat{\sigma} \to^d N(0,1)$, where $P = T-R$ and
   \begin{align*}
-    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
-    \hat{S}_{ff} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
-    f)^2, \\
-    \hat{S}_{fg} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
-    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
-    \hat{S}_{gg} &= \frac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
-    g)(g_t(\hat{\beta}_t) - \bar g)',
+    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \hat{S}_{fh} (T^{-1}X'X)^{-1}
+    \hat{F}' +
+    2\hat{F} (T^{-1} X'X)^{-1} \hat{S}_{hh} (T^{-1}X'X)^{-1} \hat{F}'\\
+    \hat{F} &= 2 P^{-1} \sum_{t=R}^{T-1} x_t (2 x_t'\hat{\beta}_t -
+    y_{t+1} - \hat{y}_{2,t+1}) \\
+    \hat{S}_{ff} &= P^{-1}\sum_{t=R}^{T-1} (f_t(\hat{\beta}_t) - \bar
+    f)^2 \\
+    \hat{S}_{fh} &= P^{-1} \sum_{t=R}^{T-1} (f_t(\hat{\beta}_t) -
+    \bar{f})(h_t(\hat{\beta}_t) - \bar h)' \\
+    \hat{S}_{hh} &= P^{-1} \sum_{t=R}^{T-1} (h_t(\hat{\beta}_t) - \bar h)(h_t(\hat{\beta}_t) - \bar h)' \\
+    h_t(\beta) &= x_t(y_{t+1} - x_t'\beta) \\
+    \intertext{and} \bar h &= P^{-1} \sum_{t=R}^{T-1}
+    h_t(\hat{\beta}_t).
   \end{align*}
-  $\Pi = 1 - (R/P) \log(1 + P/R)$, $\bar{g} = T^{-1}
-  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
-  \begin{equation*}
-  g_t(\beta) = \Bigg\{\frac{2}{P}\sum_{t=R}^{T-1} x_t (2 x_t'\beta -
-    y_{t+1} - \hat{y}_{1,t+1}) \Bigg\} \big(\X'\X / T \big)^{-1}  x_t(y_{t+1} - x_t'\beta).
-  \end{equation*}
 \end{thm}
 
-The following remarks are relevant to Theorem~\ref{res:1}:
+\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy
+  $\tilde{R}_T \to \infty$ and $\tilde{R}_T/T \to 0$ and define
+  $\tilde{P} = T - \tilde{R}$.  Then we can replace $P$ and $R$ with
+  $\tilde{P}$ and $\tilde{R}$ in the preceding equations without
+  changing the asymptotic distributions of the statistics. Note that
+  $\tilde{P}/\tilde{R} \to \infty$. It is straightforward to verify
+  that the assumptions of Theorem 4.1 of \citet{Wes:96} are satisfied
+  (with the moment and mixing conditions weakened as in
+  \citet{Mcc:00}).  Note that \[f_t(\beta^{*})= 2 (y_{t+1} -
+  x_t'\beta^{*})(x_t'\beta^{*} - \hat{y}_{2,t+1}) \quad \text{a.s.}\]
+  under the null, as in \citet{ClW:07}, so we do not need to use a
+  \hac\ estimator of the variance.
+\end{proof}
+The following remarks are relevant to Theorem~\ref{thm:1}:
 
@@
   Forecasters will almost always be interested in the one-sided
-  alternative that $\E f_t(\beta_0) > 0$; i.e. that the alternative
+  alternative that $\E f_t(\beta^{*}) > 0$; i.e. that the alternative
   model is expected to forecast better than the benchmark.
@@
 \begin{rem}
-  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
+  The requirement that the asymptotic variance of $\bar f$ be
   uniformly positive is much less restrictive than in \cite{Wes:96}.
@@
 \begin{rem}
-  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
-  fixed.  But using West's general formula for $\Pi$ (which holds when
-  $P/R$ converges as $T \to \infty$) can improve the statistic in
-  practice, since researchers often invoke ``fixed $R$'' asymptotics
-  when $R$ is large.  Section~\ref{sec:2} shows via Monte Carlo that
-  this approximation can be accurate even when $R$ and $P$ are equal.
-\end{rem}
-
-\begin{rem}
-  If one wants to test the less restrictive null hypothesis that
-  $y_{t1} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
-  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with \hac\
-  counterparts.  Lemma~\ref{res:a5} presents a more general version of
-  the theorem that can cover this case.
-\end{rem}
-
-\begin{rem}
   The statistic we present tests the null hypothesis that the forecast
@@
   statistic can be modified to test implications of optimal forecasts
-  under other loss functions \citep[see][]{PaT:07,PaT:07b}.  Again,
-  Lemma~\ref{res:a5} can cover these other applications.
-\end{rem}
-
-Before presenting the method for testing multiple models, I'll give a
-version of \citepos{PoR:94} stationary bootstrap for the \oos\
-statistic of Theorem~\ref{res:1}.  Note that the result holds as well
-for the moving blocks bootstrap of \citet{Kun:89} and \citet{LiS:92}.
-This result will be used in Theorem~\ref{res:2} to derive the joint
-distribution of several models' \oos\ statistics.  The
-boostrap-induced probability measure is denoted $\pr^{*}$.
-
-\begin{lem}\label{res:3}
-  Suppose the conditions of Theorem~\ref{res:1} hold, but strengthen
-  condition~\ref{item:3} so that $y_t$ and $z_t$ are \ned\ of size
-  $-1$ on a strong mixing series of size $-(2r + \rho)/(r-2)$ with
-  $\rho > 0$ and $r > 2$.  Consider the following procedure:
-  \begin{enumerate}
-  \item Define the data matrices $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} =
-    (X_{R+1},\dots,X_{T-1})$ with
-    \begin{equation*}
-      X_t = \begin{cases}
-        (y_{t+1}, x_t')' & t \leq R \\
-        (y_{t+1}, x_t', \hat{y}_{1,t+1})' & t > R.
-      \end{cases}
-    \end{equation*}
-  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
-    stationary bootstrap with expected block size $b$ and denote each
-    sample as $\X_{\p, l}^{*}$; let $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
-  \item Estimate $\bar{f}^{*}_l$ and $\hat{\sigma}_l^{*}$ as in
-    Theorem~\ref{res:1} for each bootstrap sample $\X^{*}_l$.
-  \end{enumerate}
-
-  Let $(\bar{f}^{*},\hat{\sigma}^{*})$ be random variables with the
-  same (conditional) distribution as $(\bar{f}_l^{*},
-  \hat{\sigma}^{*}_l)$.  If $b \to \infty$ and $b^2/P \to 0$
-  \begin{gather}
-    \pr\big[\sup_x \big| \pr^{*}\big[\sqrt{P}(\bar{f}^{*} -
-    \bar{f}(\hat{\beta}_{T+1})) \leq x \big] - \pr\big[\sqrt{P}
-    (\bar{f} - \E \bar{f}(\beta_0)) \leq x\big] \big| > \epsilon\big]
-    \to 0 \intertext{and} \pr\Bigg[\sup_x \Bigg|
-    \pr^{*}\Bigg[\frac{\bar{f}^{*} -
-      \bar{f}(\hat{\beta}_{T+1})}{\hat{\sigma}^{*}/\sqrt{P}} \leq x
-    \Bigg] - \pr\Bigg[\frac{\bar{f} - \E
-      \bar{f}(\beta_0)}{\hat{\sigma}/\sqrt{P}} \leq x\Bigg] \Bigg| >
-    \epsilon\Bigg] \to 0
-  \end{gather}
-  for all $\epsilon>0$.
-\end{lem}
-
-\begin{rem}
-  \citet{Whi:00}, \citet{Han:05}, and \citet{CoS:07} use the
-  distribution of $\sqrt{P}(\bar{f}^{*} - \bar{f})$ to approximate
-  that of $\sqrt{P}(\bar{f} - \E \bar{f}(\beta_0))$, while
-  Lemma~\ref{res:3} uses the distribution of $\sqrt{P}(\bar{f}^{*} -
-  \bar{f}(\hat{\beta}_{T+1}))$; $\hat{\beta}_{T+1}$ plays the same
-  role as $\beta_0$ under the bootstrap-induced probability measure.
-  Since $\hat{\beta}_t - \hat{\beta}_{T+1} = O_p(\sqrt{T-t})$, using
-  their bootstrap distribution is inconsistent unless $P/T$ vanishes
-  asymptotically, as in White and Hansen's
-  papers\footnote{\citet{Whi:00} and \citet{Han:05} actually require
-    that $P$ grow a little bit slower than $o(T)$.} or unless
-  $\hat{\beta}_t^{*}$ is further modified, as in Corradi and Swanson's
-  paper.
-\end{rem}
-
-\begin{rem}
-  It is likely that Lemma~\ref{res:3} holds even if $\sqrt{P} \bar{f}$
-  is not asymptotically normal, but I leave that case to future
-  research as it's not necessary for this paper's results.
-\end{rem}
-
-\begin{rem}
-  How we handle the first $R$ observations does not affect the
-  asymptotic properties since $R$ is finite.  I've chosen to put them
-  at the beginning of each bootstrap sample so that sample means
-  correspond to population means of the bootstrap distribution.  Note
-  that the alternative forecasts are not defined for the first $R$
-  observations, so running the stationary bootstrap over the full
-  dataset is not possible.
-\end{rem}
-
-\begin{rem}
-  See \citet{RoW:05,RoW:06} for guidance on block length
-  selection.
-\end{rem}
-
-Finally, I use Lemma~\ref{res:3} to test multiple models at once.
-There are two approaches one can take.  The first is to test whether
-any of the models can improve on the benchmark; \citet{Whi:00},
-\citet{Han:05}, and \citet{ClM:11} take this approach.  This approach
-requires testing a single null hypothesis, that the best model is no
-better than the benchmark, and one wants a test statistic to control
-size as usual.  The second approach, taken by \citet{RoW:05}, is to
-try to determine which models outperform the benchmark, and to find as
-many as possible that do.  Now there are as many hypotheses as there
-are models, so we need to control a quantity similar to size, the
-family-wise error rate, which is the probability that one or more true
-hypotheses is rejected.  To appreciate the difference between these
-two approaches, suppose that there are two models and the first
-outperforms a benchmark but the second doesn't.  Under the first
-approach, finding that both models outperform the benchmark is fine:
-the null (that none of them do) is false so we want to reject.  But
-under the second approach, this finding is a failure, as we
-incorrectly believe that the second model beats the benchmark.
-
-While methods like \citepos{Whi:00} and \citepos{Han:05} control the
-family-wise error, \citepos{RoW:05} StepM procedure will typically find
-more outperforming models while still controlling the family-wise error
-rate.  Theorem~\ref{res:2} shows how the \oos\ bootstrap of
-Lemma~\ref{res:3} can be used with the StepM procedure.
-
-\begin{thm}\label{res:2}
-  Suppose the conditions of Lemma~\ref{res:3} hold, with assumptions
-  on the alternative model, $\hat{y}_{1t}$, holding for each of the
-  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$, let the subscript
-  $l$ denote the different quantities associated with $\hat{y}_{lt}$
-  (i.e. $\mathcal{F}_{lt}$, etc.), and let $H_l$ be the null
-  hypothesis that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
-  $F_{lt}$.  Also assume that the long-run variance-covariance matrix
-  of the vector $(\bar{f}_1,\dots,\bar{f}_m)'$ is uniformly positive
-  definite.
-
-  Let the $*$-superscript denote a random variable with the
-  distribution induced by the stationary bootstrap of
-  Lemma~\ref{res:3}, letting $X_t = (y_{t+1}, x_t', \hat{y}_{1,t+1},
-  \dots, \hat{y}_{m, t+1})'$ for $t > R$ (and unchanged for $t \leq
-  R$).  Define $M_j$ as follows:
-  \begin{enumerate}
-  \item define $M_0 = \emptyset$,
-  \item for $j = 1,2,\dots,m$, let $M_j = \{i : \bar{f}_{i} /
-    \hat{\sigma}_i > \hat{d}_j\}$, where $\hat{d}_j$ is the $1-\alpha$
-    quantile of $\max_{i \notin M_{j-1}} (\bar{f}_{i}^{*} -
-    \bar{f_i}(\hat{\beta}_{T+1})) / \hat{\sigma}_i^{*}$,
-  \end{enumerate}
-  and reject all of the hypotheses $H_i$ with $i \in \bigcup_{j=0}^m
-  M_j$.
-
-  If $b \to \infty$ and $b^2/P \to 0$, this algorithm controls the
-  \fwe\ at level $\alpha$ for the family of null hypotheses $H_i$
-  ($i=1,\dots,m$): the probability of rejecting any true $H_i$ is less
-  than or equal to $\alpha$.  Moreover, the probability that $H_i$ is
-  rejected converges to one if $y_{t} - \hat{y}_{0t}(\beta_0)$ and
-  $\hat{y}_{it}$ have nonzero correlation.
-\end{thm}
-
-The following remarks apply to Theorem~\ref{res:2}.
-
-\begin{rem}
-  The bootstrap does not and should not exploit the \mds\ null
-  hypotheses, even though the individual variance estimators do.
-  Imposing this null hypothesis (potentially through a parametric
-  bootstrap, as in \citen{ClM:11}) requires that $y_t - \hat{y}_{0t}$
-  be an \mds\ with respect to the filtration \[\sigma((y_t, z_{1,t-1},
-  \dots, z_{m,t-1}), (y_{t-1}, z_{1,t-2}, \dots, z_{m,t-2}), \dots)\]
-  which is stronger than even the composite null that it is an \mds\
-  with respect to all of the $m$ filtrations $\sigma(y_t, z_{i,t-1},
-  y_{t-1}, z_{i,t-2}, \dots)$ for $i = 1,\dots,m$.  Using a bootstrap
-  that imposes the null will give us a correct approximation to the
-  marginal distribution of each test statistic individual test
-  statistic, $\bar{f}_i / \hat{\sigma}_i$, but it will not necessarily
-  get their joint distribution correct.
-\end{rem}
-
-\begin{rem}
-  If calculating $\hat{\sigma}_i$ is burdensome, one can do the same
-  bootstrap without studentizing the statistics.  This procedure is
-  likely to have worse size and power properties, but may be more
-  convenient.  One could also estimate the variance with a second
-  bootstrap step, but execution might take too long to be practical
-  See \citet{Han:05} and \citet[Section~4.2]{RoW:05} for a discussion
-  of the benefits of studentization.
-\end{rem}
-
-\begin{rem}
-  Since the distribution of $\bar{f}_i$ is affected by the error in
-  estimating $\beta_0$, we need to re-estimate the benchmark model
-  in each bootstrap sample, unlike \citet{Whi:00}, \citet{Han:05}, or
-  \citet{HuW:10}.  But we do not need to re-estimate the alternative
-  models, so the additional computational burden is relatively small.
-\end{rem}
-
-\begin{rem}
-  If the number of alternative models is large, controlling the \fwe\
-  may be too strict a criterion.  \citet{RSW:08} discuss procedures to
-  control criteria other than the \fwe, and one can use their
-  generalizations of the StepM procedure here as well.
+  under other loss functions \citep[see][]{PaT:07,PaT:07b}.
 \end{rem}
@@
 \input{mc}
-\section{Empirical Illustration}\label{sec:3}
-\input{empirics}
-\section{Conclusion}\label{sec:4}
+\section{Conclusion}\label{sec:3}
 In this paper, we present an \oos\ test statistic similar to \poscw\
@@
 window---as Clark and West do---but estimating the benchmark model
-with a recursive window.  We also present simulations that indicate
+with a recurisve window.  We also present simulations that indicate
 the new statistic behaves similarly to Clark and West's original test,
@@
 research.
-
-\appendix
-\section*{Appendix}
-
-This Appendix restates \citepos{Mcc:00} results (which themselves
-weaken \citepos{Wes:96} assumptions) under the dependence conditions of
-Theorem~\ref{res:1}, which is fairly trivial.  It also presents a new
-stationary bootstrap for \oos\ statistics based on the recursive
-window that uses results in \citet{GoJ:03} to weaken \citepos{CoS:07}
-assumptions.  I'll use the same notation as in the main body of the
-paper, but functional forms and definitions are different here to
-reflect the increased generality.  By and large, a variable in the
-main paper (say $f_t$) is a special case of the same variable in this
-subsection.  We'll also use array notation in this section.
-
-In this appendix, let $\to^{p^{*}}$ and $\to^{d^{*}}$ refer to
-convergence in probability or distribution conditional on the observed
-data.  Similarly, $\E^{*}$, $\var^{*}$, and $\cov^{*}$ refer to the
-expectation, variance, and covariance with respect to the probability
-measure induced by the stationary bootstrap, and $y_t^{*}$, etc. is
-the random variable $y_t$ but under the bootstrap-induced \cdf.
-
-\section{General Assumptions}
-
-This section's lemmas depend on the following assumptions, which are
-generalizations of the conditions of Theorems~\ref{res:1}
-and~\ref{res:2}.  See \citet{Wes:96,Wes:06}, \citet{WeM:98}, and
-\citet{Mcc:00} for a discussion of these conditions, as theirs are
-nearly identical.
-
-\begin{asmp}\label{asmp:a1}  We need two versions of the weak-dependence and moment
-  conditions; the first for the asymptotic distribution of the \oos\
-  statistic, and the second for the bootstrap distribution.
-  \begin{enumerate}
-  \item[a.] Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-1/2$ on
-    a strong mixing series $\{V_t\}$ of size $-r/(r-2)$, with $r > 2$.
-  \item[b.] Let $\{y_t, z_t\}$ be an $L_{2+\delta}$-\ned\ process of
-    size $-1$ on a strong mixing series $\{V_t\}$ of size $-(2r +
-    \delta)/(r - 2)$, with $r > 2$ and $\delta > 0$.
-  \end{enumerate}
-\end{asmp}
-
-\begin{asmp}\label{asmp:a2}  This assumption defines the series of
-  estimators $\hat{\beta}_t$.  We'll use two versions of this
-  assumption; the first is identical to \citepos{Wes:96} Assumption 2.
-  The second imposes more structure so that we can work out properties
-  of the estimator under the bootstrap induced probability measure.
-  \begin{enumerate}
-  \item[a.] The estimator $\hat{\beta}_t$ of $\beta_0$ satisfies
-    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$;
-    $\hat{B}_{t}$ is a sequence of $k$ by $q$ matrices that converges
-    almost surely to the deterministic sequence $B_{t}$, in the sense
-    that $\sup_{t \in \{S_T,\dots,T\}} | \hat{B}_{t} - B | \to 0$
-    almost surely for any sequence $S_T$ that diverges to $\infty$
-    with $T$; $H_{t}$ is a sequence of $q$-vectors such that $H_{t}
-    = (1/t) \sum_{s=1}^t h_{s}(\beta_{0})$, $h_{s}(\beta) =
-    h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0}) = 0$ for all
-    $s$.
-  \item[b.] In addition to part a, $B = B(\beta_{0}) =
-    \phi((1/T) \E \sum_{t=1}^T \Psi(y_{t}, z_{t},
-    \beta_{0}))$ and $\hat{B}_{t} =
-    \hat{B}_{t}(\hat{\beta}_{t}) = \phi((1/t) \sum_{s=1}^t \Psi(y_{t},
-    z_{t}, \hat{\beta}_{t}))$ for some known function $\Psi$ and
-    a known, continuous, and invertible function $\phi$.
-  \end{enumerate}
-\end{asmp}
-
-\begin{asmp}\label{asmp:a3}
-  Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector, where
-  $y_{t}$ and $z_{t}$ are from Assumption~\ref{asmp:a1} and $\beta$ is
-  a $k$-vector.  Then $\| \sup_{\beta \in N} f_{t}(\beta)
-  \|_{r+\delta}$ and $\| \sup_{\beta \in N} h_{t}(\beta)
-  \|_{r+\delta}$ are uniformly finite in $t$, where $N$ is an open
-  neighborhood of $\beta_{0}$ and $r$ is defined in
-  Assumption~\ref{asmp:a1}.
-\end{asmp}
-
-\begin{asmp}\label{asmp:a4}
-  Each element of $\E f_{t}(\beta)$ is continuously differentiable in
-  the neighborhood $N$.  Moreover, $\sup_{\beta \in N} |
-  F_{t}(\beta) |$ is uniformly finite in $t$ with
-  $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
-\end{asmp}
-
-\begin{asmp}\label{asmp:a5}
-  There exist finite constants $C$, $\phi > 0$, and $Q \geq r$ such
-  that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
-  \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) -
-  f_{t} \|_Q \leq C \epsilon^{\phi}\]
-  and \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
-  \sup_{\beta \in N(\beta_{0}, \epsilon)} h_{t}(\beta) -
-  h_{t} \|_Q \leq C \epsilon^{\phi},\] where $N(\beta, \epsilon) =
-  \{b : |b - \beta| < \epsilon\}$.
-\end{asmp}
-
-\section{General Results}
-
-\begin{lema}\label{res:a2}
-  Suppose $a \in [0,1/2)$.
-  \begin{enumerate}
-  \item Under Assumptions~\ref{asmp:a1}a and~\ref{asmp:a2}a, $P^a
-    \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
-    \to^{p^{*}} 0$.
-  \item Under Assumptions~\ref{asmp:a1}b and~\ref{asmp:a2}b,
-    $\sup_{\beta \in N} \sup_t | \hat{B}_{t}^{*}(\beta) - B^{*}(\beta)
-    | \to^{p^{*}} 0$.
-  \item Under Assumptions~\ref{asmp:a1}a and~\ref{asmp:a2}a, $P^a
-    \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and, under
-    Assumptions~\ref{asmp:a1}b and~\ref{asmp:a2}b, $P^a \sup_t |
-    \hat{\beta}^{*}_{t} - \hat{\beta}_{T+1} | \to^{p^{*}} 0$.
-  \end{enumerate}
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a2}]
-  \begin{enumerate}
-  \item[1.] The process $h_{s} / \sqrt{T}$
-    satisfies \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
-    \begin{equation}
-      P^a \sup_t \Big| (1/t) \sum_{s=1}^t h_{s} \Big| =
-      P^a \sup_{\gamma \in [0,1]} \Bigg| \frac{1}{\lfloor \gamma
-        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Bigg| \to^{p} 0
-    \end{equation}
-    with the convergence following from the continuous mapping
-    theorem.  Now, let $U_t$ denote the number of blocks randomly
-    selected by the stationary bootstrap through period $t$, let $L_1,
-    \dots, L_{U_t}$ denote their lengths, and define $K_i =
-    \sum_{j=0}^{i-1} L_j$ (with $L_0 = 0$).  Conditional on
-    $L_1,\dots,L_{U_t}$, the sum
-    \begin{equation}
-      \frac{1}{t} \sum_{s=1}^t h_t^{*} = \frac{1}{N_t}
-      \sum_{i=1}^{N_t} \Bigg( \frac{N_t}{t} \sum_{t= K_{i-1} + 1}^{K_i}
-      h_t^{*} \Bigg)
-    \end{equation}
-    is the summation of independent random variables.  Define
-    \begin{equation}
-      \eta^{*2} = \var^{*}\Big(T^{-1/2} \sum_{t=1}^T h_t^{*} \,\Big|\,
-      L_1,\dots,L_T \Big);
-    \end{equation}
-    then $\eta^{*-1} T^{-1/2} \sum_{t=1}^{\gamma T} h_t^{*}$ converges
-    in distribution to a Brownian Motion conditional on the data and
-    the block lengths.  Since the limiting distribution does not
-    depend on the block lengths, we have unconditional convergence in
-    distribution as well, and repeating the argument for $\sup_t
-    |H_t|$ completes the proof.
-  \item As for part 1, we can break up the summation into its
-    independent blocks:
-    \begin{multline}
-      \sup_{\beta} \sup_t \Big| \sum_{s=1}^{t} \big(\Psi(y_t^{*},
-      z_t^{*},
-      \beta) - \E^{*} \Psi(y_t^{*}, z_t^{*}, \beta)\big) \Big| \leq \\
-      \sup_t \sum_{i=1}^{N_t} \sup_{\beta} \Big| \sum_{t =
-        K_{i-1}+1}^{K_i} \big(\Psi(y_t^{*}, z_t^{*}, \beta) - \E^{*}
-      \Psi(y_t^{*}, z_t^{*}, \beta)\big) \Big|
-    \end{multline}
-    And I need to finish this proof.
-  \item We have
-    \begin{multline}
-      P^a \sup_{t \in S_T} | \hat{\beta}_t - \beta_0 | = P^a \sup_{t
-        \in S_T} |\hat{B}_{t} H_{t}| \\ \leq \sup_{t,u \in S_T} \Big|
-      [ \hat{B}_u - B] (P^a/t) \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
-      B (P^a/t) \sum_{s=1}^t h_{s} \Big|
-    \end{multline}
-    and both terms converge to zero in (conditional) probability by
-    the previous argument and Assumption~\ref{asmp:a2}.  The same
-    argument holds for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ using
-    part 2.
-  \end{enumerate}
-\end{proof}
-
-\begin{lema}\label{res:a3}
-  Let $g_{t}' = (f_{t}' - \E f_{t}', a_t h_{t}')$ and $a_t =
-  \sum_{s=\max(R,t)}^T s^{-1}$.  Under Assumptions~\ref{asmp:a1}b,
-  \ref{asmp:a2}a, and~\ref{asmp:a3}
-  \begin{equation}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ T^{-1/2} \sum_t^T g_{t}^{*}
-    \leq x \Big] - \pr\Big[ T^{-1/2} \sum_{t=1}^T g_{t}
-    \leq x \Big] \Big| > \epsilon \Big] \to 0
-  \end{equation}
-  for all positive $\epsilon$.
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a3}]
-  This result is an immediate consequence of \citet[Theorem 2]{GoJ:03}.
-\end{proof}
-
-The next Lemma restates \citepos{Mcc:00} Theorem 2.3.1 under our weak
-dependence conditions.  Note that we allow $R$ to diverge to infinity
-or to remain finite.
-
-\begin{lema}\label{res:a5}
-  If Assumptions~\ref{asmp:a1}a, \ref{asmp:a2}a, \ref{asmp:a3},
-  \ref{asmp:a4}, and \ref{asmp:a5} hold and $P \to \infty$ as $T \to
-  \infty$, (add p.d. assumption too) then
-  \begin{equation}
-    P^{-1/2} \sum_{t=R+1}^T
-    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
-  \end{equation}
-  with
-  \begin{align}
-    \Omega =     
-  \end{align}
-\end{lema}
-\begin{proof}[Proof of Lemma~\ref{res:a5}]
-  Let $R'$ satisfy $R' \to \infty$ as $T \to \infty$ and $R'/T \to 0$
-  and define $P' = T - R'$.  Then we can replace $P$ and $R$ with $P'$
-  and $R'$ in the preceding equations without changing the asymptotic
-  distributions of the statistics.  Note that $P'/R' \to \infty$.  The
-  proof then follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}
-\end{proof}
-
-The next Lemma presents our recursive window bootstrap scheme.
-\begin{lema}\label{res:a6}
-  If Assumptions~\ref{asmp:a1}b, \ref{asmp:a2}b, \ref{asmp:a3},
-  \ref{asmp:a4}, and \ref{asmp:a5} hold , $P \to \infty$ as $T \to
-  \infty$, and (p.d. assumption holds) then
-  \begin{equation}
-    P^{-1/2} \sum_{t=R+1}^T
-    (f_{t}^{*}(\hat{\beta}_{t}^{*}) - \E^{*} f^{*}_{t}(\beta_{0}^{*})) \to^{d^{*}} N(0, \Omega^{*})
-  \end{equation}
-  and $\Omega^{*} \to^p \Omega$, where
-  \begin{align}
-    \Omega^{*} =     
-  \end{align}
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a6}]
-  Replace $R$ and $P$ with $\tilde{R}$ and $\tilde{P}$ as in the proof
-  of Lemma~\ref{res:a5}, and expand $\E^{*}
-  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
-  \begin{equation}
-    \sqrt{P'} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
-    \frac{1}{\sqrt{P'}} \sum_{t=R'+1}^T
-    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
-    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
-  \end{equation}
-  with the proof following exactly in \citet[Theorem 2.3.1]{Mcc:00}.
-  Note that $F^{*} = \hat{F} + o_{p^{*}}$ and $B^{*} = \hat{B}_{T+1} +
-  o_{p^{*}}$.  The result then follows from Lemma~\ref{res:a3} and the
-  consistency of these estimators.
-\end{proof}
-
-\section{Proofs of Main Theoretical Results}
-
-\begin{proof}[Proof of Theorem \ref{res:1}]
-  The theorem is an immediate consequence of Lemma~\ref{asmp:a4}.
-  Note that \[f_t(\beta_0)= 2 (y_{t+1} - x_t'\beta_0)(x_t'\beta_0 -
-  \hat{y}_{1,t+1}) \quad \text{a.s.},\] as in \citet{ClW:07}, so we do
-  not need to use a \hac\ estimator of the variance under the null.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{res:2}]
-  The result for unstudentized statistics holds from Lemma~\ref{res:3}
-  and Theorem~3.1 of \citet{RoW:05}.  For studentized statistics, note
-  that
-  \begin{equation}
-    \hat{\sigma}_i^{*} = P^{-1} \sum_{t=R+1}^T (f_{it}(\hat{\beta}_t)
-    - \bar{f}_i(\hat{\beta}_T))^2 + o_{p^{*}},
-  \end{equation}
-  which converges to the same limit as $\hat{\sigma}_i$.
-\end{proof}
 
@@
 % LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized
+% LocalWords:  PaT AllRefs

### 2012-03-30 mc.Rnw
Drafted initial version of the paper

--- 2011-04-19 mc.Rnw
@@
-We will also conduct a brief Monte Carlo experiment to demonstrate
-that this modified statistic performs essentially the same as Clark
-and West's.  We draw observations from their \dgp\ 1:
+<<echo=F>>=
+library(dbframe)
+library(xtable)
+mcdata1 <- dbframe("dgp1", "mcdata.db")
+mcdata2 <- dbframe("dgp2", "mcdata.db")
+groups <- c( "isPower", "R", "P")
+size <- .1
 
-\begin{gather*}
-  y_t = 0.5 + \gamma^{*} z_{t-1} + e_t \qquad\qquad
-  z_t = 0.15 + 0.95 z_{t-1} + v_t \\
-  (e_t, v_t)' \sim iid\ N(0, \begin{pmatrix} 18 & - 0.5 \\ \cdot & 0.025 \end{pmatrix}.
-\end{gather*}
+printbooktabs <- function(x,...){
+  print(xtable(x,...),
+        floating=F,
+        hline.after=NULL, 
+        add.to.row=list(pos=list(-1,0, nrow(x)), 
+          command=c(
+            '\\toprule ',
+            '\\midrule ',
+            '\\bottomrule ')),...)
+}
+
+fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))
+
+printall <- function(mcdb,...) {
+  d <- subset(select(mcdb, group.by = groups, 
+                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
+                               "R", "P", 
+                               "100 * avg(pOld <= %f) as 'Pr[CW]'",
+                               "100 * avg(pNew1 <= %f) as 'Pr[New]'",
+                               "100 * (avg(pOld <= %f and pNew1 > %f) + avg(pOld > %f and pNew1 <= %f)) as 'Pr[tests disagree]'"),
+                             size, size, size, size)), select = -isPower)
+  d$R <- fspace(d$R)
+  d$P <- fspace(d$P)
+  d[[4]] <- fspace(d[[4]])
+  d[[5]] <- fspace(d[[5]])
+  d[[6]] <- fspace(d[[6]])
+  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
+  d$type[duplicated(d$type)] <- NA
+  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
+                align = c("l","l","c","c","c","c","c"), 
+                sanitize.text.function = function(x) x)
+}
+@ 
+We will also conduct two brief Monte Carlo experiments to demonstrate
+that this modified statistic performs similarly to
+\possessivecite{ClW:07}.  We'll use both of the \dgp s they consider.
+For the first, we have
+\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
+  y_t &= 0.5 + \gamma^{*} z_{t-1} + e_t &
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations} \\
+    0.35 & \text{power simulations}
+  \end{cases}\\\nonumber
+  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
+  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
+  \end{pmatrix}
+   , \begin{pmatrix} 18 & -
+    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
+\end{align}
 Both models are estimated by \ols. The benchmark model regresses $y_t$
 on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  We run the same size and power simulations as
-\citet{ClW:07}; $\gamma^{*}$ equals zero for the size simulations and
-0.35 in the power simulations.
+$z_{t-1}$.  We use both \poscw\ original statistic and our new
+statistic to test the null that the benchmark model's innovation is an
+\mds.\footnote{\citet{ClW:07} report the performance of the tests
+  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
+  based on the naive Gaussian statistic.}
+
+\begin{table}[tb]
+  \centering
+<<mc1, echo=F, results=tex>>=
+printall(mcdata1)
+@ 
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[CW] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[New] shows the fraction of
+  simulations for which this paper's test rejects; and Pr[tests
+  disagree] gives the fraction of simulations in which this paper's
+  test and Clark and West's (2007) give different conclusions.}
+\label{tab:mc1}
+\end{table}
+
+The second \dgp\ is
+\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
+  y_{t} &= 2.237 + 0.261 + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
+  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
+  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
+  z_{t-4} + v_{t} \nonumber \\
+  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
+  \begin{pmatrix}
+    0 \\ 0
+  \end{pmatrix},
+  \begin{pmatrix}
+    10.505 & 1.036 \\ 1.036 & 0.366
+  \end{pmatrix}
+  \Bigg) \nonumber\\\nonumber
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations}\\
+    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
+  \end{cases}
+\end{align}
+The benchmark model for $y_{t}$ is an AR(1) and the alternative model
+includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
+120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
+first \dgp\ mimics an asset pricing application and the second mimics
+\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
+National Activity Index.
+
+\begin{table}[tb]
+  \centering
+<<mc2, echo=F, results=tex>>=
+printall(mcdata2)
+@ 
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[CW] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[New] shows the fraction of
+  simulations for which this paper's test rejects; Pr[tests disagree]
+  gives the fraction of simulations in which this paper's test and
+  Clark and West's (2007) give different conclusions.}
+\label{tab:mc2}
+\end{table}
+
+Table~\ref{tab:mc1} presents the simulation results
+for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
+all of the parameter values, our proposed new statistic has slightly
+lower rejection probability than \possessivecite{ClW:07}.  For both
+\dgp s the statistics are slightly undersized.  In~\eqref{eq:dgp1},
+this translates to relatively low power and the power difference
+between the two statistics may be noticeable.  In~\eqref{eq:dgp2},
+though, the evidence against the benchmark is strong enough under the
+alternative that the tests reject almost all of the time.  In that
+setting, the lower power of our new test is essentially irrelevant.
+
+%%% Local Variables:
+%%% TeX-master: "Paper"
+%%% End:
+% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
+% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
+% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
+% LocalWords:  possessivecite nonumber sim iid Bigg binom pmatrix ols poscw CCS
+% LocalWords:  ClM

### 2012-03-30 MakeScript.R

@@ -3,8 +3,8 @@
 # run in parallel.  Running this file will print out text for a
 # makefile, so it might be easiest to just look at its output.
 
-nsims <- 1000  # this is the number of simulations
-njobs <- 8     # I set this to equal the number of processors on my 
+nsims <- 5000  # this is the number of simulations
+njobs <- 6     # I set this to equal the number of processors on my 
                # computer.  Changing its value will change the results
                # of the simulations, since they'll be seeded differently.
 
@@ -22,7 +22,7 @@ dbfiles <- function(filename)
   paste(dbdir, "/", filename, ".db", sep = "")
 
 mkline <- function(...)
-    cat(paste("\n\t$(sqlite) $(sqliteflags) stardata.db \"",
+    cat(paste("\n\t$(sqlite) $(sqliteflags) mcdata.db \"",
               paste(...,sep = ""), ";\"", sep = ""))
 
 mergetables <- function(table) {
@@ -45,9 +45,11 @@ writeMake <- function(x, Rfile, seed) {
   cat("\n.SECONDARY: ", dbf, collapse = "", sep = " ")
   mergetables(x)
   for (job in seq.int(njobs)) {
-    cat(sprintf("\n%s: %s\n\tmkdir -p db\n\techo 'seed <- %d; jjob <- %d; nsim <- %d; dbtable <- \"%s\";' | cat - $< | $(Rscript) $(RSCRIPTFLAGS) - &> %s/%s.Rout",
+    cat(sprintf("\n%s: %s R/mcsetup.R\n\tmkdir -p db\n\techo 'seed <- %d; jjob <- %d; nsim <- %d; dbtable <- \"%s\";' | cat - $< | $(Rscript) $(RSCRIPTFLAGS) - &> %s/%s.Rout",
                 dbf[job], Rfile, seed, job, jsims[job], x, dbdir, dbn[job]))
   }
 }
 
-writeMake("dgp1", "R/montecarlo.R", 99120)
+writeMake("dgp1", "R/montecarlo.R",  1023)
+writeMake("dgp2", "R/montecarlo2.R", 1023)
+writeMake("dgp3", "R/montecarlo3.R", 1023)

### 2012-03-30 R/mcsetup.R

@@ -1,0 +1,26 @@
+calstat <- function(d, R, null, alt, xfn, yfn) {
+  n <- nrow(d)
+  oos <- (R+1):n
+  P <- n - R
+  
+  pnull <- apply.oos(R, d, null, "recursive", "forecast")
+  enull <- apply.oos(R, d, null, "recursive", "error")
+  palt <- apply.oos(R, d, alt, "rolling", "forecast")
+  ealt <- apply.oos(R, d, alt, "rolling", "error")
+  
+  f <- enull^2 - ealt^2 + (pnull - palt)^2
+  X <- xfn(d)
+  Y <- yfn(d)
+  FBh <- drop(tcrossprod(solve(crossprod(X) / n,
+                               colMeans(c(2 * pnull - palt - Y[oos]) * X[oos,,drop=FALSE])),
+                         c(enull) * X[oos,,drop=FALSE]))
+  S <- var(cbind(f, FBh))
+  sd <- sqrt((S[1,1] + 2 * S[1,2] + 2 * S[2,2]) / P)
+  fbar <- mean(f)
+  
+  c(pval(fbar, sd, oneSided=TRUE), pval(fbar, sd, oneSided=FALSE))
+}
+
+pval <- function(x, sd, oneSided)
+  ifelse(oneSided, pnorm(x, 0, sd, lower.tail = FALSE),
+         2 * pnorm(abs(x), 0, sd, lower.tail = FALSE))

### 2012-03-30 R/montecarlo2.R

@@ -1,11 +1,11 @@
-## seed, jjob, dbtable, and nsim are set in the file mc-setup.R
+## seed, jjob, dbtable, and nsim are set in the file MakeScript.R
 ## for debugging:
 ## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
 set.seed(seed)
 set.seed(sample(1:10000000, jjob)[jjob],
          kind = 'Mersenne-Twister', normal.kind = 'Inversion')
-source("R/mcsetup.R")
 
+source("R/mcsetup.R")
 library(MASS)
 library(OOS)
 library(dbframe)
@@ -14,46 +14,39 @@ mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
                   overwrite = TRUE)
 clear(mcdata)
 
-mcdesign <- expand.grid(P = c(120, 240, 360, 720), R = c(120, 240),
+mcdesign <- expand.grid(P = c(40, 80, 120, 160), R = c(80, 120),
                         isPower = c(FALSE, TRUE))
-
 
 ## really basic function to generate our data; this could be written
 ## much better.
-rdgp <- function(n, isPower) {
+rdgp <- function(n, isPower, nburn = 1600) {
   ## The processes are
-  ## y_t = a %*% c(1, z_{t-1}) + e1
-  ## z_t = b %*% c(1, z_{t-1}) + e2
+  ## y_t = a %*% c(1, y_{t-1}, z_{t-1},...,z_{t-4}) + e1
+  ## z_t = b %*% c(z_{t-1},...,z_{t-4}) + e2
   ## with 
   ## (e1, e2) ~ N(0, v)
-  gam <- 0.35 * isPower
-  a <- c(.5, gam)
-  b <- c(.15, .95)
-  v <- matrix(c(18, -.5, -.5, .025), 2)
-  
-  Ez <- b[1] / (1 - b[2])
-  Ey <- a[1] + a[2] * Ez
+  a <- c(2.237, 0.261, isPower * c(3.363, -0.633, -0.377, -0.529))
+  b <- c(0, 0, 0.804, -0.221, 0.226, -0.205)
+  v <- matrix(c(10.505, 1.036, 1.036, 0.366), 2)
 
-  ## elements of the variance-covariance matrix
-  Vz <- v[2,2] / (1 - b[2]^2)
[…]

### 2012-03-30 R/montecarlo3.R

@@ -1,0 +1,43 @@
+## seed, jjob, dbtable, and nsim are set in the file MakeScript.R
+## for debugging:
+## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
+nsim <- 100
+set.seed(seed)
+set.seed(sample(1:10000000, jjob)[jjob],
+         kind = 'Mersenne-Twister', normal.kind = 'Inversion')
+
+source("R/mcsetup.R")
+library(MASS)
+library(OOS)
+library(dbframe)
+
+mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
+                  overwrite = TRUE)
+clear(mcdata)
+
+mcdesign <- expand.grid(P = 10000, R = 20)
+
+## really basic function to generate our data; this could be written
+## much better.
+rdgp <- function(n) {
+  y  <- rnorm(n)
+  x1 <- rnorm(n)
+  x2 <- rnorm(n)
+  data.frame(y, x1, x2)
+}
+
+null <- function(d) lm(y ~ 1, data = d)
+alt <- function(d) lm(y ~ x1 + x2, data = d)
+xfn <- function(d) matrix(1, nrow(d))
+yfn <- function(d) as.matrix(d[,"y", drop = FALSE])
+  
+for (r in rows(mcdesign)) {
+  print(r)
+  insert(mcdata) <-
+    data.frame(r, t(replicate(nsim, {
+      d <- with(r, rdgp(R + P))
+      cals <- calstat(d, r$R, null, alt, xfn, yfn)
+      c(pOld = oos.t(null, alt, d, r$R, method = "ClW:07", conf.level = .9)$p.value,
+        pNew1 = cals[1], pNew2 = cals[2])
+    })), row.names = seq_len(nsim))
+}

### 2012-03-30 Paper.tex
Moved project code to Noweb

--- 2012-03-30 Paper.tex
@@
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,eco}
+\usepackage[T1]{fontenc}
 \usepackage[nolists,nomarkers]{endfloat}
@@
 \usepackage[small]{caption}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
 
@@
 \frenchspacing
-\onehalfspacing
+\input{tex/simulationdefinitions}
+\input{tex/empiricalresults}
 
@@
     \texttt{gcalhoun@iastate.edu}.  Web:
-    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  This paper
-    has benefited from my conversations with Helle Bunzel, Graham
-    Elliott, Yu-Chin Hsu, Pablo Pincheira, and Allan Timmermann; thank
-    you.  I'd also like to thank Amit Goyal for providing computer
-    code and data for his 2008 \textsc{rfs} paper with Ivo Welch
-    \citep{GoW:08}.} \\ Iowa State University}
+    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
+    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
+    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
+    participants at the 2011 Midwest Econometrics Group meeting for
+    helpful comments.  I'd also like to thank Amit Goyal for providing
+    computer code and data for his 2008 \textsc{rfs} paper with Ivo
+    Welch \citep{GoW:08}.} \\
+  Iowa State University}
 
@@
   paper also presents a method to compare multiple models
-  simultaneously while controlling family-wise error, and
+  simultaneously while controlling familywise error, and
   substantially improves existing block bootstrap methods for
@@
 literature developing the theoretical properties of these statistics,
-beginning with \citet{DiM:95} and \citet{Wes:96} and continuing with
+beginning primarily with \citet{DiM:95} and
+\citet{Wes:96}.\footnote{Other papers in this literature include
   \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-\citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11}, \citet{CCS:01},
-\citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00}, \citet{InK:04,InK:06},
-\citet{Han:05}, \citet{Ros:05}, \citet{ClW:06,ClW:07}, \citet{Ana:07},
-\citet{GiR:09,GiR:10}, \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11},
-\cite{Pin:11}, \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among
-others.\footnote{For recent reviews of this literature and additional
-  references, see \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06},
-  \citet{ClM:11c}, \citet{CoD:11}, and \citet{Gia:11}}
-
-In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of the
-null hypothesis that a small benchmark model is correctly specified.
-Their test compares the forecasting performance of a pair of nested
-models, and the null hypothesis is that the innovations in the smaller
-model form a martingale difference sequence.  This test procedure is
-popular,\footnote{As of 12 September, 2011, \citet{ClW:06} has been
-  cited by 28 papers indexed by the \textsc{isi} Web of Knowledge, and
-  \citet{ClW:07} by 41. They have been cited by 132 and 172 papers
-  indexed by Google Scholar respectively.} and one assumes that this
-is due in part to the statistic's convenience.  The statistic is
-approximately normal after adjusting for the estimation error of the
-larger model.  Normality comes from a fixed-length rolling window, as
-in \citet{GiW:06}, and the adjustment centers the statistic
-appropriately.  This statistic is especially convenient because other
-\oos\ tests for similar hypotheses \citep[among
-others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a nonstandard
-limit distribution and place restrictions on the models under
-consideration, while other asymptotically normal statistics test a
-different null hypothesis \citep{GiW:06} or place assumptions on the
+  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
+  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
+  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
+  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
+  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
+  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
+  reviews of this literature and additional references, see
+  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
+  \citet{CoD:11}, and \citet{Gia:11}}
+
+In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
+the null hypothesis that a small benchmark model is correctly
+specified.  Their test compares the forecasting performance of a pair
+of nested models, and the null hypothesis is that the innovations in
+the smaller model form a martingale difference sequence.  This test
+procedure is popular, and one assumes that this is due in part to the
+statistic's convenience.  The statistic is approximately normal after
+adjusting for the estimation error of the larger model.  Normality
+comes from a fixed-length rolling window, as in \citet{GiW:06}, and
+the adjustment centers the statistic appropriately.  This statistic is
+especially convenient because other \oos\ tests for similar hypotheses
+\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
+nonstandard limit distribution and place restrictions on the models
+under consideration, while other asymptotically normal statistics test
+a different null hypothesis \citep{GiW:06} or place assumptions on the
 models and \dgp\ that are often violated in empirical work
@@
 power advantage and is similar in spirit to using a likelihood ratio
-test instead of an \textsc{lm} or Wald test.
+test instead of an \textsc{lm} or Wald test, which depend on just the
+restricted or unrestricted model respectively.  Simulations presented
+in Section~\ref{sec:2} show that mixing window strategies gives a
+substantial power advantage when there are breaks.
 
@@
 pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
-define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model
-is correctly specified, so $\varepsilon_{t+1}$ is a martingale
-difference sequence with respect to $\mathcal{F}_t = \sigma(y_{t+1},
-x_t, v_t, y_t, x_{t-1}, v_{t-1}, \dots)$ then we can see immediately
-that
+define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
+model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
+difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
+y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
 \begin{equation}
@@
 with $R$ an arbitrary starting value\footnote{You will see momentarily
-  why the summation begins at $R+1$ instead of 1.} and $P = T - R$,
+  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
 obeys an \mds\ \clt\ (assuming that its variance is uniformly
@@
   - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
-  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big]
+  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
 \end{equation}
-almost surely.
 
@@
     $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
-    uniform mixing series of size $-\frac{r}{2r-2)}$.  Also, $y_t$,
+    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
     $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
@@
   martingale difference sequence with respect to the filtration
-  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$,
+  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
   $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
@@
 
+\begin{rem}
+  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
+  window but claim that their results hold for a fixed-length fixed
+  window as well, where the unknown coefficients are estimated only
+  once using the first $R$ observations.  This claim is true but not
+  obviously so.  The proof for the rolling window is based on the idea
+  that the forecast errors are weakly dependent because they are a
+  function of a finite number of consecutive weakly dependent
+  observations.  But using a fixed window introduces another source of
+  dependence.  All of the forecasts depend on the same coefficient
+  estimates.  One can prove that their results apply to fixed window
+  forecasts by using a coupling argument similar to \citepos{Cal:11}.
+  Interested readers should refer to \citet{Cal:11} for the argument
+  and to \citet{MeP:02} for a review of the necessary coupling
+  results.
+\end{rem}
+
 Since most empirical papers study more than one alternative model,
@@
   nominal size.}  Econometricians, e.g. \citet{Whi:00},
-\citet{Han:05}, and \citet{ClM:11}, have emphasized statistics that
-test families of hypotheses that control the probability any
-hypothesis is rejected given that they all are true, known as
-\textit{weak control of family-wise error} (\wfwe).  This paper
+\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
+statistics that test families of hypotheses that control the
+probability any hypothesis is rejected given that they all are true,
+known as \textit{weak control of familywise error}
+(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
+  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
+  control \sfwe\ for certain families of one-sided tests.}  This paper
 focuses instead on controlling the probability that at least one true
 hypothesis is rejected given any combination of true and false
-hypotheses, known as \textit{strong control of family-wise error}
+hypotheses, known as \textit{strong control of familywise error}
 (\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
@@
 control \sfwe\ if the individual null hypotheses are strengthened
-slightly as below (see Part~\ref{it:1} of Theorem~\ref{res:2} as well as
-Remark~\ref{rem:2}).
+slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
+well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
+construct critical values from the asymptotic joint distribution of
+the test statistics and can control \sfwe\ as long as there is a
+consistent estimate of that distribution.
 
@@
     procedure outlined above, but using the moving block bootstrap
-    with block length 1, has probability at most $\alpha$ of rejecting
+    with block length $1$, has probability at most $\alpha$ of rejecting
     one or more models in $I$.
@@
 \begin{rem}\label{rem:2}
-  The key difference between Parts~\ref{it:1} and~\ref{it:2} is that,
-  in Part~\ref{it:2}, the forecast error is an \mds\ with respect to
-  several individual series, but not necessarily with respect to the
-  pooled information set generated by all of those series
-  together.\footnote{It is straightforward to construct three series,
-    $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with respect
-    to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
+  The key difference between Parts~(\ref{it:1}) and~(\ref{it:2}) is
+  that, in Part~(\ref{it:2}), the forecast error is an \mds\ with
+  respect to several individual series, but not necessarily with
+  respect to the pooled information set generated by all of those
+  series together.\footnote{It is straightforward to construct three
+    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
+    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
     $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
     $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
-    This is essentially the null imposed in Part~\ref{it:2}.}  Using
-  $b = 1$ would consistently estimate the marginal distribution of
-  each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
+    This is essentially the scenario imposed in Part~(\ref{it:2}).}
+  Using $b = 1$ would consistently estimate the marginal distribution
+  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
   hypothesis, but would not necessarily estimate the joint
@@
   \citep[i.e.][]{ClM:11} achieves control of \sfwe\ only under the
-  stronger hypotheses of Part~\ref{it:1}.  Fortunately, Part~\ref{it:1} seems to capture
-  the goal of most empirical work, so researchers can make use of the
-  considerable simplifications that occur in that setting.
-\end{rem}
-
-\begin{rem}
-  The procedure described above is a refinement of the StepM for
-  one-sided tests along the lines of \citepos{Han:05} \spa, but with
-  better power.  Hansen's \spa\ is motivated by the observation that
-  including models $i$ for which $\E \bar f_{i}$ is strongly negative
-  reduces the test's power: the critical values are taken as the
-  maximum over a larger number of models, but the $i$th model will
-  almost never exceed the critical value.  Hansen suggests discarding
-  models for which $\bar f_i$ is below a threshold implied by the Law
-  of the Iterated Logarithm.  \citet{Cal:11e} suggests the threshold
-  used in Theorem 2 and argues that it has better size and power
-  properties.  See \citet{Cal:11e} for further motivation and
-  explanation.
+  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
+  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
+  so researchers can make use of the considerable simplifications that
+  occur in that setting.
 \end{rem}
@@
   models that could be used as the benchmark, researchers may want to
-  control for data-snooping over the null hypotheses as well as the
+  control for data snooping over the null hypotheses as well as the
   alternatives.  For example, one could use either \citepos{AtO:01}
@@
   Intersection-Union test, so Theorem~\ref{res:2}'s procedure
-  (Part~\ref{it:3}) easily accommodates this extension by taking each
-  $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
+  (Part~(\ref{it:3})) easily accommodates this extension by taking
+  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
   $q$-vector;\footnote{If a researcher uses multiple benchmark models,
     it would be a mistake to assume that they are all correctly
-    specified.} the first element of $\bar f_{i}$ compares the first
+    specified, so only the null hypothesis of Part~(\ref{it:3}) is
+    appropriate.} the first element of $\bar f_{i}$ compares the first
   benchmark model to the $i$th alternative and the first element of
@@
 \section{Monte Carlo Results}\label{sec:2}
-\input{mc}
+I'll conduct two brief Monte Carlo experiments to demonstrate that the
+modified version of \citepos{ClW:07} statistic performs similarly to
+their original test in the situations they study.\footnote{All of
+  these simulations were programmed in R \citep{R:2-13-0} and use the
+  \textsc{MASS} \citep{VeR:02}, xtable \citep{Dah:09}, and dbframe
+  \citep{Cal:10b} packages.  Version
+  information is listed in the bibliography.}  I'll use both of the
+\dgp s they consider as well as a modification to study the
+performance of the statistics if there is instability.
+
+The first \dgp\ has three different parametrizations; one to study the
+tests' size, one to study power under stationarity, and one to study
+power if there is a single break in the relationship between the
+target and predictors.  The \dgp\ is:
+\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
+  y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
+  \gamma^{*}_t &=
+  \begin{cases}
+    0    & \text{size simulations} \\
+    0.35 & \text{power (stable)} \\
+    0    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
+    0.70 & t > \tfrac{T}{2} \quad \text{power (break)}
+  \end{cases}\\\nonumber
+  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
+  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
+  \end{pmatrix}
+   , \begin{pmatrix} 18 & -
+    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
+\end{align}
+Both models are estimated by \ols. The benchmark model regresses $y_t$
+on a constant, and the alternative regresses $y_t$ on a constant and
+$z_{t-1}$.  We use both \poscw\ original statistic and the new
+statistic to test the null that the benchmark model's innovation is an
+\mds.\footnote{\citet{ClW:07} report the performance of the tests
+  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
+  based on the naive Gaussian statistic.}  \citet{ClW:06,ClW:07} only
+look at the stable case.
+
+\begin{table}[tb]
+  \centering
+  \input{floats/simulation1}
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; and Pr[disagree]
+  gives the fraction of simulations in which this paper's test and
+  Clark and West's (2007) give different conclusions.}
+\label{tab:mc1}
+\end{table}
+
+The second \dgp\ is
+\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
+  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
+  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
+  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
+  z_{t-4} + v_{t} \nonumber \\
+  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
+  \begin{pmatrix}
+    0 \\ 0
+  \end{pmatrix},
+  \begin{pmatrix}
+    10.505 & 1.036 \\ 1.036 & 0.366
+  \end{pmatrix}
+  \Bigg) \nonumber\\\nonumber
+  \gamma^{*} &=
+  \begin{cases}
+    0 & \text{size simulations}\\
+    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
+  \end{cases}
+\end{align}
+The benchmark model for $y_{t}$ is an AR(1) and the alternative model
+includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
+120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
+first \dgp\ mimics an asset pricing application and the second mimics
+\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
+National Activity Index.
+
+\begin{table}[tb]
+  \centering
+  \input{floats/simulation2}
+\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
+  10\% confidence.  These percentages are calculated from 5000
+  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
+  and West's (2007) statistic rejects; Pr[new] shows the fraction of
+  simulations for which this paper's test rejects; Pr[disagree] gives
+  the fraction of simulations in which this paper's test and Clark and
+  West's (2007) give different conclusions.}
+\label{tab:mc2}
+\end{table}
+
+Table~\ref{tab:mc1} presents the simulation results
+for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
+all of the stable parameter values, the proposed new statistic has
+similar rejection probability to \citepos{ClW:07}.  Clark and West's
+test is slightly more undersized than the new test, but has a little
+higher power under the alternative.  Moreover, the statistics give
+different results in less than 10\% of the simulations for most
+parametrizations of the \dgp s.  In general, the statistics perform
+similarly well.
+
+For the simulations with a single break, the new statistic has about
+twice the power of \poscw\ original test.  For most parametrizations
+of \dgp\ 1, the new test rejects over 90\% of the time, while Clark
+and West's test rejects about 40\% of the time.  So mixing window
+strategies can give a substantial power advantage when testing for
+time-varying predictability, and performs similarly to the original
+test when testing for stable outperformance.
+
 \section{Empirical Illustration}\label{sec:3}
-\input{empirics}
+
+This section demonstrates the use of the statistics introduced earlier
+in the paper by revisiting \citepos{GoW:08} study of excess stock
+returns.  Goyal and Welch argue that many variables thought to predict
+excess returns (measured as the difference between the yearly log
+return of the S\&P 500 index and the T-bill interest rate) on the
+basis of in-sample evidence fail to do so out-of-sample.  To show
+this, Goyal and Welch look at the forecasting performance of models
+using a lag of the variable of interest, and show that these models do
+not significantly outperform the excess return's recursive sample mean.
+
+Here, I conduct the same analysis, but using this paper's \mds\ test.
+The benchmark model is the excess return's sample mean (as in the
+original) and the alternative models are of the form
+\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
+\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
+$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
+predictors used are listed in the ``predictor'' column of
+Table~\ref{tab:em1} \citep[see][for a detailed description of the
+variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
+correction to the models, that the forecasts be bounded below by zero
+since negative forecasts are incredible, as well as two simple
+combination forecasts, the mean and the median (over both the original
+and the non-negative forecasts).  The data set is annual data
+beginning in 1927 and ending in 2009, and the rolling window uses 10
+observations.\footnote{This statistical analysis was conducted in R
+  \citep{R:2-13-0} using the xtable \citep{Dah:09}, Hmisc
+  \citep{Har:10}, and dbframe \citep{Cal:10b} packages; version
+  information for each package is listed in the bibliography.}
+
+Table~\ref{tab:em1} presents the results for each model.  The column
+``value'' gives the value of the test statistic for each model, while
+the ``naive'' and ``corrected'' columns indicate whether the statistic
+is greater than the standard size-10\% critical value (1.28) and the
+critical value estimated by the procedure of Theorem~\ref{res:2}
+(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
+  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
+  of Theorem~\ref{res:2}.}  Three predictors are significant at the
+naive critical values for both the original and bounded forecasts: the
+dividend yield, long term interest rate, and book to market ratio.
+But none are significant after accounting for data snooping, which
+highlights the importance of these methods.  The median forecast is
+significant using conventional critical values as well, but not the
+corrected values.
+
+\begin{table}[tb!]
+  \centering
+  \empiricaltable
+\caption{Results from \oos\ comparison of equity premium prediction
+  models; the benchmark is the recursive sample mean of the equity
+  premium and each alternative model is a constant and single lag of
+  the variable listed in the ``predictor'' column.  The dataset begins
+  in 1927 and ends in 2009 and is annual data. The ``value'' column
+  lists the value of this paper's \oos\ statistic, the ``naive''
+  column indicates whether the statistic is significant at standard
+  critical values, and the ``corrected'' column indicates significance
+  using the critical values proposed in Theorem~\ref{res:2} that
+  account for the number of models.  See Section~\ref{sec:3} for details.}
+\label{tab:em1}
+\end{table}
+
 \section{Conclusion}\label{sec:4}
@@
 that the new statistic behaves similarly to Clark and West's original
-test, suggesting that the new statistic is a suitable replacement in
-applied research.  The paper also presents a method for comparing the
-benchmark model to several alternative models simultaneously and
-improves block bootstrap procedures of \oos\ statistics.
+test when the \dgp\ is stable, but can have much higher power when the
+predictability varies over time, suggesting that the new statistic is
+a suitable replacement in applied research.  The paper also presents a
+method for comparing the benchmark model to several alternative models
+simultaneously and improves block bootstrap procedures of \oos\
+statistics.
 
@@
   \end{equation}
-  Proving~\eqref{eq:3} uses essentially the same argument
-  as~\citet[Lemma A.3]{Mcc:00} and~\eqref{eq:2} essentially follows a
-  streamlined version of the argument of~\ref{res:a5}, completing the
-  proof.  The proofs for the moving and circular block bootstraps are
-  essentially the same.
+  Proving~\eqref{eq:3} uses the same argument as~\citet[Lemma
+  A.3]{Mcc:00} and~\eqref{eq:2} follows a streamlined version of the
+  argument of~\ref{res:a5}, completing the proof.  The proofs for the
+  moving and circular block bootstraps are the same.
 \end{proof}
@@
 % LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified
+% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
+% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
+% LocalWords:  outperformance Hmisc Har

### 2012-03-30 MakeScript.R

@@ -1,55 +1,0 @@
-# The basic idea of this python script is to set up the right
-# dependencies for GNU make so that the monte carlo simulations are
-# run in parallel.  Running this file will print out text for a
-# makefile, so it might be easiest to just look at its output.
-
-nsims <- 5000  # this is the number of simulations
-njobs <- 8     # I set this to equal the number of processors on my 
-               # computer.  Changing its value will change the results
-               # of the simulations, since they'll be seeded differently.
-
-### split the simulations across the jobs
-remainder <- nsims %% njobs
-jsims = rep(nsims %/% njobs, njobs) + c(rep(1, remainder), rep(0, njobs - remainder))
-### check for dumb errors
-stopifnot(sum(jsims) == nsims)
-
-dbdir <- "db"
-
-dbnames <- function(table)
-  sapply(seq.int(njobs), function(i) paste(table, i, sep = ""))
-dbfiles <- function(filename)
-  paste(dbdir, "/", filename, ".db", sep = "")
-
-mkline <- function(...)
-    cat(paste("\n\t$(sqlite) $(sqliteflags) mcdata.db \"",
-              paste(...,sep = ""), ";\"", sep = ""))
-
-mergetables <- function(table) {
-  dbn <- dbnames(table)
-  dbf <- dbfiles(dbn)
-  cat(sprintf("\ndb/%s.done: %s", table, dbf), sep = "")
-  mkline(paste(sprintf("attach database '%s' as %s;", dbf, dbn), collapse = " "),
-         sprintf("drop table if exists main.%s; ", table),
-         sprintf("create table main.%s as %s;",
-                 table, paste(sprintf("select * from %s.%s", dbn, table),
-                              collapse = " union all ")),
-         paste(sprintf("detach database %s;", dbn), collapse = " "))
-  cat("\n\ttouch $@")
-}
-
-writeMake <- function(x, Rfile, seed) {
-  ## This is the set of make commands to create the individual databases.
-  dbn <- dbnames(x)
-  dbf <- dbfiles(dbn)
-  cat("\n.SECONDARY: ", dbf, collapse = "", sep = " ")
-  mergetables(x)
-  for (job in seq.int(njobs)) {
[…]

### 2012-03-30 R/empirics.R

@@ -1,66 +1,0 @@
-library(OOS)
-source("R/mcsetup.R")
-
-## code to do monthly returns
-## dfull <- ts(read.csv("data/monthlyData2009.csv")[,-1],
-##             start = c(1871, 1), frequency = 12)
-dfull <- ts(read.csv("data/yearlyData2009.csv")[,-1],
-            start = 1871, frequency = 1)
-stock.returns <- (dfull[,"price"] + dfull[,"dividend"]) / lag(dfull[,"price"], -1) - 1
-
-dfull <- lag(cbind(equity.premium              = lag(log1p(stock.returns)
-                 - log1p(dfull[,"risk.free.rate"]), 1),
-               default.yield.spread        = dfull[,"baa.rate"] - dfull[,"aaa.rate"],
-               inflation                   = dfull[,"inflation"],
-               stock.variance              = dfull[,"stock.variance"],
-               dividend.payout.ratio       = log(dfull[,"dividend"]) - log(dfull[,"earnings"]),
-               long.term.yield             = dfull[,"long.term.yield"],
-               term.spread                 = dfull[,"long.term.yield"] - dfull[,"t.bill"],
-               treasury.bill               = dfull[,"t.bill"],
-               default.return.spread       = dfull[,"corp.bond"] - dfull[,"long.term.rate"],
-               dividend.price.ratio        = log(dfull[,"dividend"]) - log(dfull[,"price"]),
-               dividend.yield              = log(dfull[,"dividend"]) - log(lag(dfull[,"price"], -1)),
-               long.term.rate              = dfull[,"long.term.rate"],
-               earnings.price.ratio        = log(dfull[,"earnings"]) - log(dfull[,"price"]),
-               book.to.market              = dfull[,"book.to.market"],
-               net.equity                  = dfull[,"net.equity"]),
-         k=-1)
-## more monthly return code
-## d <- data.frame(window(dfull, start = c(1927,1), end = c(2009,12)))
-R <- 10 ## do a ten year window?
-d <- data.frame(window(dfull, start = 1927, end = c(2009)))
-
-## calculate Goyal and Welch's original forecasts
-preds <- as.data.frame(lapply(setdiff(names(d), "equity.premium"), function(n) {
-  apply.oos(R, d, function(d) lm(formula(paste("equity.premium ~", n)), data = d))}))
-names(preds) <- setdiff(names(d), "equity.premium")
-
[…]

### 2012-03-30 R/mcsetup.R

@@ -1,151 +1,0 @@
-calstat <- function(d, R, null, alt, xfn, yfn) {
-  n <- nrow(d)
-  oos <- (R+1):n
-
-  X <- xfn(d)
-  pnull <- apply.oos(R, d, null, "recursive", "forecast")
-  palt <- apply.oos(R, d, alt, "rolling", "forecast")
-  r <- calmain(d, R, pnull, palt, yfn, xfn,
-               solve(crossprod(X)/n,
-                 colMeans(X[oos,,drop=FALSE] * c(pnull - palt))))
-  unname(pnorm(r[1], 0, r[2], lower.tail = FALSE))
-}
-
-calmain <- function(d, R, pnull, palt, yfn, xfn = NULL, BF = NULL) {
-  n <- nrow(d)
-  oos <- (R+1):n
-  P <- n - R
-  Pi <- 1 - (R/P) * log(1 + P/R)
-  
-  Y <- c(yfn(d))
-
-  enull <- Y[oos] - pnull
-  ealt <- Y[oos] - palt
-  
-  f <- enull^2 - ealt^2 + (pnull - palt)^2
-
-  if (is.null(xfn) | is.null(BF)) {
-    sd <- sd(f)
-  } else {
-    X <- xfn(d)
-    g <- enull * X[oos,,drop = FALSE] %*% BF
-
-    S <- var(cbind(f, g))
-    sd <- sqrt((S[1,1] + 2 * Pi * (S[1,2] + S[2,2])) / P)
-  }
-  c(mu = mean(f), sd = sd)
-}
-
-## this is what I want rbind to do for data frames
-dstack <- function(...) {
-  framelist <- list(...)
-  cols <- unique(c(lapply(framelist, colnames), recursive = TRUE))
-  do.call(rbind, lapply(framelist, function(d) {
-    for (col in setdiff(cols, colnames(d))) d[,col] <- NA
-    d[,cols]
-  }))
-}
-
-## calculate the indices that give you a stationary bootstrap draw
-iboot <- function(n, b) {
-  series <- rep(NA, n)
-  bootindex <- 1
-  repeat {
-    ##    obsindex <- 1 + (seq.int(sample(1:n, 1), length.out = rgeom(1, 1/b)) %% n)
-    obsindex <- 1 + seq.int(sample(1:n,1), length.out = b) %% n
-    if (length(obsindex) > 0) {
-      bootend <- min(bootindex + length(obsindex) - 1, n)
[…]

### 2012-03-30 R/montecarlo.R

@@ -1,68 +1,0 @@
-## seed, jjob, dbtable, and nsim are set in the file mc-setup.R
-## for debugging:
-## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
-set.seed(seed)
-set.seed(sample(1:10000000, jjob)[jjob],
-         kind = 'Mersenne-Twister', normal.kind = 'Inversion')
-source("R/mcsetup.R")
-
-library(MASS)
-library(OOS)
-library(dbframe)
-
-mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
-                  overwrite = TRUE)
-clear(mcdata)
-
-mcdesign <- expand.grid(P = c(120, 240, 360, 720), R = c(120, 240),
-                        isPower = c(FALSE, TRUE))
-
-
-## really basic function to generate our data; this could be written
-## much better.
-rdgp <- function(n, isPower) {
-  ## The processes are
-  ## y_t = a %*% c(1, z_{t-1}) + e1
-  ## z_t = b %*% c(1, z_{t-1}) + e2
-  ## with 
-  ## (e1, e2) ~ N(0, v)
-  gam <- 0.35 * isPower
-  a <- c(.5, gam)
-  b <- c(.15, .95)
-  v <- matrix(c(18, -.5, -.5, .025), 2)
-  
-  Ez <- b[1] / (1 - b[2])
-  Ey <- a[1] + a[2] * Ez
-
-  ## elements of the variance-covariance matrix
-  Vz <- v[2,2] / (1 - b[2]^2)
-  Vy <- v[1,1] + gam^2 * Vz
-  Cyz <- a[2] * b[2] * Vz + v[1,2]
-
-  ## we're going to let x_t = (y_t, z_t); draw from the stationary
-  ## distribution and then populate the rest of the matrix with the
-  ## innovations.
-  x <- rbind(mvrnorm(1, c(Ey, Ez), matrix(c(Vy, Cyz, Cyz, Vz), 2)),
-             mvrnorm(n, c(0,0), v))
-  A <- matrix(c(0, 0, a[2], b[2]), 2)
-  for (i in 1 + (1:n)) {
-    x[i,] = drop(c(a[1], b[1]) + A %*% x[i-1,] + x[i,])
-  }
-  data.frame(y = x[-1,1], zlag = x[-n,2])
-}
-
-null <- function(d) lm(y ~ 1, data = d)
[…]

### 2012-03-30 R/montecarlo2.R

@@ -1,61 +1,0 @@
-## seed, jjob, dbtable, and nsim are set in the file MakeScript.R
-## for debugging:
-## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
-set.seed(seed)
-set.seed(sample(1:10000000, jjob)[jjob],
-         kind = 'Mersenne-Twister', normal.kind = 'Inversion')
-
-source("R/mcsetup.R")
-library(MASS)
-library(OOS)
-library(dbframe)
-
-mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
-                  overwrite = TRUE)
-clear(mcdata)
-
-mcdesign <- expand.grid(P = c(40, 80, 120, 160), R = c(80, 120),
-                        isPower = c(FALSE, TRUE))
-
-## really basic function to generate our data; this could be written
-## much better.
-rdgp <- function(n, isPower, nburn = 1600) {
-  ## The processes are
-  ## y_t = a %*% c(1, y_{t-1}, z_{t-1},...,z_{t-4}) + e1
-  ## z_t = b %*% c(z_{t-1},...,z_{t-4}) + e2
-  ## with 
-  ## (e1, e2) ~ N(0, v)
-  a <- c(2.237, 0.261, isPower * c(3.363, -0.633, -0.377, -0.529))
-  b <- c(0, 0, 0.804, -0.221, 0.226, -0.205)
-  v <- matrix(c(10.505, 1.036, 1.036, 0.366), 2)
-
-  ntot <- n + nburn
-  ret <- nburn + (5:n)
-  ## we're going to let x_t = (y_t, z_t); draw from the stationary
-  ## distribution and then populate the rest of the matrix with the
-  ## innovations.
-  x <- mvrnorm(ntot, c(0,0), v)
-  A <- rbind(a, b)
-  for (i in 5:ntot) {
-    x[i,] = c(A %*% c(1, x[i-1,], x[i - (2:4),2]) + x[i,])
-  }
-  
-  data.frame(y = x[ret, 1], y1 = x[ret-1,1], z1 = x[ret-1, 2],
-             z2 = x[ret-2, 2], z3 = x[ret-3, 2], z4 = x[ret-4, 2])
-}
-
-null <- function(d) lm(y ~ y1, data = d)
-alt <- function(d) lm(y ~ y1 + z1 + z2 + z3 + z4, data = d)
[…]

### 2012-03-30 R/montecarlo3.R

@@ -1,43 +1,0 @@
-## seed, jjob, dbtable, and nsim are set in the file MakeScript.R
-## for debugging:
-## seed <- 1; jjob <- 1; dbtable <- "temp"; nsim <- 3
-nsim <- 100
-set.seed(seed)
-set.seed(sample(1:10000000, jjob)[jjob],
-         kind = 'Mersenne-Twister', normal.kind = 'Inversion')
-
-source("R/mcsetup.R")
-library(MASS)
-library(OOS)
-library(dbframe)
-
-mcdata <- dbframe(dbtable, paste("db/", dbtable, jjob, ".db", sep = ""),
-                  overwrite = TRUE)
-clear(mcdata)
-
-mcdesign <- expand.grid(P = 10000, R = 20)
-
-## really basic function to generate our data; this could be written
-## much better.
-rdgp <- function(n) {
-  y  <- rnorm(n)
-  x1 <- rnorm(n)
-  x2 <- rnorm(n)
-  data.frame(y, x1, x2)
-}
-
-null <- function(d) lm(y ~ 1, data = d)
-alt <- function(d) lm(y ~ x1 + x2, data = d)
-xfn <- function(d) matrix(1, nrow(d))
-yfn <- function(d) as.matrix(d[,"y", drop = FALSE])
-  
-for (r in rows(mcdesign)) {
-  print(r)
-  insert(mcdata) <-
-    data.frame(r, t(replicate(nsim, {
-      d <- with(r, rdgp(R + P))
-      cals <- calstat(d, r$R, null, alt, xfn, yfn)
-      c(pOld = oos.t(null, alt, d, r$R, method = "ClW:07", conf.level = .9)$p.value,
-        pNew = cals)
-    })), row.names = seq_len(nsim))
-}

### 2012-04-03 Paper.tex
Adjusted LaTeX to designate 'intermetiate' versions.
I've added a footnote to the version date that, when present, explains that
the current version of the paper is no less than the date listed, but
may be higher.

@@
-\documentclass[12pt,fleqn]{article}
+\documentclass[10pt,fleqn,draft]{article}
 
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,eco}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
 \usepackage[T1]{fontenc}
+\usepackage{lmodern}
 \usepackage[nolists,nomarkers]{endfloat}
 \usepackage[sort,round]{natbib}
-\usepackage[margin=1.25in]{geometry}
+\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
 \usepackage[small]{caption}
@@
 \input{tex/simulationdefinitions}
+\input{tex/empiricsdefinitions}
 \input{tex/empiricalresults}
+
+% redfine heading styles
+\makeatletter
+\renewcommand\section{\@startsection%
+{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
+{\normalfont\normalsize\bfseries\large\raggedright}}
+\makeatother
 
@@
 \title{An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models} \date{\today}
+  test of equal predictive accuracy for nested models}
+
+\date{\input{VERSION% <- allows VERSION to have comments
+}}
 \maketitle
@@
     $x_t$.
-  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
+  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
     $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
@@
     $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
-    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
+    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
     $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
@@
   \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is an \mds\ with respect to $\mathcal{F}_{lt}$
+    \hat{y}_{0t}$ is an \textsl{\mds} with respect to $\mathcal{F}_{lt}$
     against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
@@
   \begin{enumerate}
-  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
+  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
     a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
@@
 their original test in the situations they study.\footnote{All of
-  these simulations were programmed in R \citep{R:2-13-0} and use the
-  \textsc{MASS} \citep{VeR:02}, xtable \citep{Dah:09}, and dbframe
-  \citep{Cal:10b} packages.  Version
-  information is listed in the bibliography.}  I'll use both of the
-\dgp s they consider as well as a modification to study the
-performance of the statistics if there is instability.
+  these simulations were programmed in R \citep[version 2.14.0]{R} and
+  use the \textsc{MASS} \citep[version info]{VeR:02}, xtable
+  \citep[version info]{Dah:09}, and dbframe \citep[version
+  0.2.1]{Cal:10b} packages.  For details on the programming, please
+  see the supplemental appendices \citep{Cal:11f,Cal:11g,Cal:11h}.}
+I'll use both of the \dgp s they consider as well as a modification to
+study the performance of the statistics if there is instability.
 
@@
 and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses 10
-observations.\footnote{This statistical analysis was conducted in R
-  \citep{R:2-13-0} using the xtable \citep{Dah:09}, Hmisc
-  \citep{Har:10}, and dbframe \citep{Cal:10b} packages; version
-  information for each package is listed in the bibliography.}
+beginning in 1927 and ending in 2009, and the rolling window uses
+\windowlength\ observations.\footnote{This statistical analysis was
+  conducted in R \citep{R} using the xtable \citep[version]{Dah:09},
+  Hmisc \citep[version]{Har:10}, and dbframe \citep[version
+  0.2.1]{Cal:10b} packages; please see the supplemental appendices for
+  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
 

### 2012-05-09 Paper.tex
Corrected typos mentioned by Stephane Yen

@@
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
-    participants at the 2011 Midwest Econometrics Group meeting for
-    helpful comments.  I'd also like to thank Amit Goyal for providing
-    computer code and data for his 2008 \textsc{rfs} paper with Ivo
+    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
+    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
+    Group meeting for helpful comments.  I'd also like to thank Amit
+    Goyal for providing computer code and data for his 2008
+    \textsc{rfs} paper with Ivo
     Welch \citep{GoW:08}.} \\
@@
     g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
-    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
+    y_{t+1} - \hat{y}_{1,t+1}) \Big\}' \big(\tfrac1T \X'\X \big)^{-1}
     x_t(y_{t+1} - x_t'\beta).

### 2012-05-17 Paper.tex
Made several minor edits to the text of the main paper
- A few changes to formatting
- A few minor edits to the content

@@
-\documentclass[10pt,fleqn,draft]{article}
+\documentclass[12pt,fleqn]{article}
 
@@
 \usepackage[nolists,nomarkers]{endfloat}
-\usepackage[sort,round]{natbib}
-\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
+\usepackage[sort,round,comma]{natbib}
+\usepackage[top=1.25in,left=1.25in,right=1.25in,bottom=1.25in]{geometry}
 \usepackage[small]{caption}
@@
 \newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
-\frenchspacing
+\frenchspacing\onehalfspacing
 \input{tex/simulationdefinitions}
@@
 
-\newpage \noindent This paper proposes an out-of-sample (\oos) test
-statistic that is asymptotically normal with mean zero even when the
-models studied are nested, proves that common block bootstrap methods
-consistently estimate the statistic's distribution, and shows how the
-statistic can be used to study many models simultaneously while
-maintaining strong control of the familywise error (\fwe),
-i.e. ensuring that the probability that the hypothesis that the model
-has equal predictive ability to a benchmark is incorrectly rejected
-for any of the models is no higher than a prespecified level.  \oos\
-tests are commonly used in International Macroeconomics,
-Macroeconomics, and Finance \citep[see, for
-example,][]{MeR:83,StW:03,GoW:08} and there is a substantial
+\newpage
+
+\section{Introduction} This paper proposes an out-of-sample (\oos)
+test statistic that is asymptotically normal with mean zero even when
+the models studied are nested.  This paper also proves that common
+block bootstrap methods consistently estimate the statistic's
+distribution, and shows how the statistic can be used to study many
+models simultaneously while maintaining strong control of the
+familywise error (\fwe), i.e. ensuring that the probability that the
+hypothesis that the model has equal predictive ability to a benchmark
+is incorrectly rejected for any of the models is no higher than a
+preset level.
+
+\oos\ tests are commonly used in International Macroeconomics,
+Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
+\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
 literature developing the theoretical properties of these statistics,
@@
   \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
+  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:11,ClM:12},
   \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
@@
   \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
-  \citet{CoD:11}, and \citet{Gia:11}}
-
-In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
-the null hypothesis that a small benchmark model is correctly
-specified.  Their test compares the forecasting performance of a pair
-of nested models, and the null hypothesis is that the innovations in
-the smaller model form a martingale difference sequence.  This test
-procedure is popular, and one assumes that this is due in part to the
-statistic's convenience.  The statistic is approximately normal after
-adjusting for the estimation error of the larger model.  Normality
-comes from a fixed-length rolling window, as in \citet{GiW:06}, and
-the adjustment centers the statistic appropriately.  This statistic is
-especially convenient because other \oos\ tests for similar hypotheses
-\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
-nonstandard limit distribution and place restrictions on the models
-under consideration, while other asymptotically normal statistics test
-a different null hypothesis \citep{GiW:06} or place assumptions on the
-models and \dgp\ that are often violated in empirical work
-\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.\footnote{\citet{DiM:95} assume
-  that the models are not estimated. \citet{Wes:96,WeM:98,Mcc:00}
+  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
+\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
+that a small benchmark model is correctly specified.  Their test
+compares the forecasting performance of a pair of nested models, and
+the null hypothesis is that the innovations in the smaller model form
+a martingale difference sequence.  This test procedure is popular, and
+one assumes that this is due in part to the statistic's convenience,
+the statistic is approximately normal after adjusting for the
+estimation error of the larger model.  Normality comes from a
+fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
+centers the statistic appropriately.  This statistic is especially
+convenient because other \oos\ tests for similar hypotheses
+(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
+and \citealt{Mcc:07}; among others) have a nonstandard limit
+distribution and place restrictions on the models under consideration,
+while other asymptotically normal statistics test a different null
+hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
+that are often violated in empirical work (\citealt{DiM:95};
+\citealt{Wes:96}; \citealt{WeM:98};
+\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
+  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
   implicitly assume that the models do not converge to the same limit,
@@
 rolling window for the alternative model.  This approach could have a
-power advantage and is similar in spirit to using a likelihood ratio
-test instead of an \textsc{lm} or Wald test, which depend on just the
+power advantage and is similar in spirit to using a Likelihood Ratio
+Test instead of an \textsc{lm} or Wald test, which depend on just the
 restricted or unrestricted model respectively.  Simulations presented
-in Section~\ref{sec:2} show that mixing window strategies gives a
-substantial power advantage when there are breaks.
+in Section~\ref{sec:2} show that this approach gives a substantial
+power advantage when there are breaks.
 
 This paper's statistic has a substantial advantage over existing \oos\
-tests for nested models: the alternative can be essentially arbitrary,
-as long as it obeys the necessary moment conditions.  In particular,
+tests for nested models: the alternative can be essentially arbitrary
+as long as high level moment conditions hold.  In particular,
 researchers can use model selection techniques like the \aic\ or \bic\
@@
 know which of them significantly outperform the benchmark, procedures
-that compare a single pair of models are of limited practical use.  As
-\citet{Whi:00} demonstrates, looking at the naive $p$-values of the
+that compare a single pair of models are of limited practical value.
+As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
 individual tests is misleading, but researchers can get a valid test
@@
 individual test statistic under the null (White calls this procedure
-the ``bootstrap reality check'' or \brc).  This paper presents a test
+the \textit{Bootstrap Reality Check} or \brc).  This paper presents a test
 for equal predictive ability of multiple models based on
@@
 indicate which of the models improves on the benchmark (see
-Theorem~\ref{res:2} for details).  Since this paper is concerned with
-one-sided testing, I use the modified StepM procedure proposed by
-\citet{Cal:11e}; the original StepM procedure unnecessarily sacrifices
-power when testing one-sided hypotheses because, as \citet{Han:05}
-points out for \citepos{Whi:00} \brc, alternative models that
-substantially under-perform increase the test's critical values too
-much.\footnote{Note that the modification suggested by \citet{Cal:11e}
-  is different than \citepos{Han:05} and is explicitly designed for
-  stepwise testing.}
+Theorem~\ref{res:2} for details).
 
@@
 the stationary bootstrap, but require the test sample to be much
-smaller than the training sample, which is obviously inappropriate
-here.  \citet{CoS:07} relax that requirement, but make the statistic
-more complicated than necessary by adjusting the objective function of
-the bootstrapped statistic to center it correctly.\footnote{Their
-  recentering is required for consistency and does not give higher
+smaller than the training sample, which obviously does not hold here.
+\citet{CoS:07} relax that requirement, but make the statistic more
+complicated than necessary by adjusting the objective function of the
+bootstrapped statistic to center it correctly.\footnote{Their
+  recentering is required for consistency and does not imply higher
   order accuracy.}  A parametric bootstrap, such as that used by
@@
 This section presents the new \oos\ statistic.  I'll present the
-single-comparison statistic first and then the extension to multiple
+single-comparison statistic first and then extend it to multiple
 comparisons.  Suppose for now that a researcher is interested in
 predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$; further, let $v_t$ be another random process and suppose that
+$x_t$; also let $v_t$ be another random process and suppose that
 $(y_t, x_t, v_t)$ is stationary and weakly dependent
-(Theorem~\ref{res:1} lists the detailed assumptions required).  In
-addition, let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the
-pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
-define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
-model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
-difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
-y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
+(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
+let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
+coefficient of the regression of $y_{t+1}$ on $x_t$ and define
+$\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model is
+correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
+sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
+(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
 \begin{equation}
   \label{eq:4}
-  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
-  - v_t) 
+  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t - x_t'\beta_0)
 \end{equation}
-with $R$ an arbitrary starting value\footnote{You will see momentarily
-  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
 obeys an \mds\ \clt\ (assuming that its variance is uniformly
-positive) and is asymptotically normal as $P \to \infty$.
+positive) and is asymptotically normal as $P \to \infty$, with $R$ an
+arbitrary starting value\footnote{It will be clear momentarily why the
+  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
 Straightforward algebra \citep{ClW:07} shows that
@@
   \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
-  - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
-  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
+  \tfrac{2}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t -
+  x_t'\beta_0) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} - 
+  x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
 \end{equation}
@@
 the weak dependence properties of the variables used to estimate it.
-Moreover, keeping $R$ finite ensures that the conditional variance
-remains positive, so the \clt\ holds.  This method of ensuring
-normality was introduced by \citet{GiW:06}.  The coefficients
-$\beta_0$ are assumed to be zero so $\varepsilon_{t+1}$ is observed
-directly (under the null hypothesis) and they propose using this
-statistic to test the null that $\beta_0 = 0$.  In \citet{ClW:07},
-$\beta_0$ is unknown but is estimated with a fixed-length rolling
-window as well, so
+Keeping $R$ finite ensures that the conditional variance remains
+positive, so the sum obeys a \clt.  This method of ensuring normality
+was introduced by \citet{GiW:06}.  The coefficients $\beta_0$ are
+assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
+the null hypothesis) and Clark and West propose using this statistic
+to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
+$\mathcal{F}_t$.  In \citet{ClW:07}, $\beta_0$ is unknown but is
+estimated with a fixed-length rolling window as well, so
 \begin{equation*}
@@
 and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
-$\varepsilon_{t+1}$ in the test statistic for $\beta_0 = 0$.
-Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an \mds, so the
-statistic is no longer asymptotically mean-zero normal, even though
-this approximation performs well in the simulations reported by
-\citet{ClW:07}.
+$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
+$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
+$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
+mean-zero normal, even though this approximation performs well in the
+simulations reported by \citet{ClW:07}.
 
@@
   \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
-  x_t\hat{\beta}_t)^2 + (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
+  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
 \end{equation*}
-is asymptotically normal for fairly arbitrary processes $v_t$, as long
-as $v_t$ is weakly dependent and the \oos\ statistic has uniformly
-positive variance.  Just as in \citet{ClW:06}, these conditions are
-ensured if $v_t$ is another forecast of $y_{t+1}$ based on a fixed
-length rolling window.  Theorem~\ref{res:1} presents the details of
-this result.  The assumptions required are essentially the same in
-existing papers (e.g. \citealp{Wes:96}; \citealp{WeM:98};
-\citealp{Mcc:00}; \citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
-Please see the original papers for a discussion of these assumptions.
+is asymptotically normal with mean zero under the null for fairly
+arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
+the \oos\ statistic has uniformly positive variance.  Just as in
+\citet{ClW:06}, these conditions are ensured if $v_t$ is another
+forecast of $y_{t+1}$ based on a fixed length rolling window.
+Theorem~\ref{res:1} presents the details of this result.  The
+assumptions required are essentially the same in existing papers
+(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
+\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
+original papers for a discussion of these assumptions.
 
@@
   \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
-    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
-    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
-    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
-    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
-    \sum_{t=2}^T \E x_{t-1} y_t$.
+    estimated using \textsl{\ols} with a recursive window:
+    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
+    predictors $x_t$ with $\hat{\beta}_t$ given by
+    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
+    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that it does not depend
+    on~$t$.
   \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
@@
     \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
-    function and $z_t$ is a sequence of predictors that includes
+    function and $z_t$ is a sequence of predictors that may include
     $x_t$.
@@
     (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
-    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
-    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
-    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
-    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
-    long run variance.
+    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
+    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T -
+    R$. The processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$
+    are covariance stationary and $\bar f(\beta_0)$ has uniformly
+    positive and finite long run variance.
   \end{enumerate}
@@
   If one wants to test the less restrictive null hypothesis that
-  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
-  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with their
-  \hac\ counterparts.  Lemma~\ref{res:a5} presents a more general
-  version of the theorem that can cover this case.
+  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
+  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
+  and $\hat{S}_{gg}$ with their \hac\ counterparts.
+  Lemma~\ref{res:a5} presents a more general version of the theorem
+  that can cover this case.
 \end{rem}
@@
   observations.  But using a fixed window introduces another source of
-  dependence.  All of the forecasts depend on the same coefficient
+  dependence, all of the forecasts depend on the same coefficient
   estimates.  One can prove that their results apply to fixed window
@@
   and to \citet{MeP:02} for a review of the necessary coupling
-  results.
+  results.  Theorem~\ref{res:1} can be shown to hold when $\hat
+  y_{1t}$ is estimated with a fixed-length fixed window using the same
+  arguments.
 \end{rem}
@@
 (\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
-even though these papers only prove \wfwe, statistics based on
+even though the papers only prove \wfwe, statistics based on
 nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
@@
 the test statistics and can control \sfwe\ as long as there is a
-consistent estimate of that distribution.
-
-Only tests that have \sfwe\ can tell researchers which of the
-hypotheses are false.  To see why, imagine that there are only two
-hypotheses: $H_1$ is true and $H_2$ is false.  A test that rejects the
-true hypothesis, $H_1$, with arbitrarily high probability still can
-satisfy \wfwe: since not all of the hypotheses are true, the behavior
-of tests with weak control is essentially unconstrained.  Such a test
-would not satisfy \sfwe, though.  For \sfwe\ in this setting, a test
-must reject $H_1$ with probability at most $\alpha$ (letting $\alpha$
-be the desired level of control).  In most research, we would view
-rejection of the true hypothesis $H_1$ a mistake.
-
-This paper uses a variation of \citepos{RoW:05} StepM procedure, which
-is an iterated extension of \citepos{Whi:00} Reality Check designed to
-reject as many false hypotheses as possible while achieving \sfwe.
-This method relies on the bootstrap to estimate the joint dependence
-between the test statistic associated with each model.  The bootstrap
-used in this paper is new, and is outlined in Algorithm~\ref{alg:1}.
+consistent estimator of that distribution.
+
+Only tests with \sfwe\ can tell researchers which of the hypotheses
+are false.  To see why, imagine that there are only two hypotheses:
+$H_1$ is true and $H_2$ is false.  A test that rejects the true
+hypothesis, $H_1$, with arbitrarily high probability still can satisfy
+\wfwe: since not all of the hypotheses are true, the behavior of tests
+with weak control is essentially unconstrained.  Such a test would not
+satisfy \sfwe, though.  For \sfwe\ in this setting, a test must reject
+$H_1$ with probability at most $\alpha$ (letting $\alpha$ be the
+desired level of control).  In most research, we would view rejection
+of the true hypothesis $H_1$ as a mistake.
+
+This paper uses \citepos{RoW:05} StepM procedure, which is an iterated
+extension of \citepos{Whi:00} Reality Check designed to reject as many
+false hypotheses as possible while achieving \sfwe.  Their method
+relies on the bootstrap to estimate the joint dependence between the
+test statistic associated with each model.  The bootstrap used in this
+paper is new, and is outlined in Algorithm~\ref{alg:1}.
 Algorithm~\ref{alg:1} actually presents a more general version of the
@@
 bootstrap sample so that population means under the bootstrap-induced
-probability distribution equal sample means.  Note that the benchmark
-model needs to be reestimated in each bootstrap sample.
+probability distribution equal sample means.  The benchmark model
+still needs to be reestimated in each bootstrap sample.
 
@@
   \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
-    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
-    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
-      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
-    \bar{f_i}(\hat{\beta}_{T+1})|$.
-  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
-    and $\bar f_i > 0$.
+    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
+    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
+    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
+    \bar{f_i}(\hat{\beta}_{T+1}))$.
+  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
   \end{enumerate}
@@
     procedure outlined above, but using the moving block bootstrap
-    with block length $1$, has probability at most $\alpha$ of rejecting
-    one or more models in $I$.
+    with block length $1$, has probability at most $\alpha$ of
+    rejecting one or more models in $I$.
   \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is an \textsl{\mds} with respect to $\mathcal{F}_{lt}$
-    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
-    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
-    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
-    (for the moving or circular block bootstraps) then the procedure
-    outlined above controls \sfwe\ at level $\alpha$ for the family of
-    null hypotheses $H_1,\dots,H_m$.
+    \hat{y}_{0t}$ is an \textsl{\mds} with respect to
+    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
+    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
+    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
+    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
+    then the procedure outlined above controls \textsl{\sfwe} at level
+    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
   \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
@@
     moving or circular block bootstraps) then the procedure outlined
-    above controls \sfwe\ at level $\alpha$ for the family of null
-    hypotheses $H_1,\dots,H_m$.
+    above controls \textsl{\sfwe} at level $\alpha$ for the family of
+    null hypotheses $H_1,\dots,H_m$.
   \end{enumerate}
@@
     specified, so only the null hypothesis of Part~(\ref{it:3}) is
-    appropriate.} the first element of $\bar f_{i}$ compares the first
-  benchmark model to the $i$th alternative and the first element of
-  $\hat{\sigma}_i^2$ is the corresponding estimate of asymptotic
-  variance, the second element corresponds to the second benchmark
-  model, etc.
+    appropriate.} the first element of $\bar f_{i}$, written as $\bar
+  f_{i1}$, compares the first benchmark model to the $i$th alternative
+  and the first element of $\hat{\sigma}_i^2$ is the corresponding
+  estimate of asymptotic variance, the second element corresponds to
+  the second benchmark model, etc.
 
@@
   \item Reject all of the hypotheses $H_i$ such that $(i,k) \in
-    \bigcup_{j=1}^m M_j$ and $\bar{f}_{ik} > 0$ for all
-    $k$.\footnote{This approach is motivated by \citepos{DoH:11}
-      extension of Wolak's \citeyearpar{Wol:89b,Wol:91} tests of
-      inequality constraints.  Donald and Hsu use a threshold rule
-      based on \citepos{Han:05} \spa\ to discard nonbinding
-      inequalities.  One could, of course, use the two-sided stepdown
-      method proposed in this paper instead of the \spa\ to increase
-      the power of Donald and Hsu's test.}
+    \bigcup_{j=1}^m M_j$ for all $k$.
   \end{enumerate}
@@
 
-Note that the notation in this section is more general than that of
+The notation in this section is more general than that of
 Section~\ref{sec:1}.  The assumptions required are generalizations of
@@
 \section{Monte Carlo Results}\label{sec:2}
-I'll conduct two brief Monte Carlo experiments to demonstrate that the
-modified version of \citepos{ClW:07} statistic performs similarly to
-their original test in the situations they study.\footnote{All of
-  these simulations were programmed in R \citep[version 2.14.0]{R} and
-  use the \textsc{MASS} \citep[version info]{VeR:02}, xtable
-  \citep[version info]{Dah:09}, and dbframe \citep[version
-  0.2.1]{Cal:10b} packages.  For details on the programming, please
-  see the supplemental appendices \citep{Cal:11f,Cal:11g,Cal:11h}.}
-I'll use both of the \dgp s they consider as well as a modification to
-study the performance of the statistics if there is instability.
+I'll conduct two brief Monte Carlo experiments to demonstrate that
+this paper's modified version of \citepos{ClW:07} statistic performs
+similarly to their original test in the situations they
+study.\footnote{All of these simulations were programmed in R
+  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
+  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
+  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
+  programming, please see the supplemental appendices
+  \citep{Cal:11f,Cal:11g,Cal:11h}.}  I'll use both of the \dgp s they
+consider as well as a modification to study the performance of the
+statistics if there is instability.
 
@@
 target and predictors.  The \dgp\ is:
-\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
+\begin{align*}
   y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
@@
     0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
-\end{align}
+\end{align*}
 Both models are estimated by \ols. The benchmark model regresses $y_t$
@@
 The second \dgp\ is
-\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
+\begin{align*}
   y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
@@
   \end{cases}
-\end{align}
+\end{align*}
 The benchmark model for $y_{t}$ is an AR(1) and the alternative model
@@
 
-Table~\ref{tab:mc1} presents the simulation results
-for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
-all of the stable parameter values, the proposed new statistic has
-similar rejection probability to \citepos{ClW:07}.  Clark and West's
-test is slightly more undersized than the new test, but has a little
-higher power under the alternative.  Moreover, the statistics give
-different results in less than 10\% of the simulations for most
-parametrizations of the \dgp s.  In general, the statistics perform
-similarly well.
+Table~\ref{tab:mc1} presents the simulation results for~\textsc{dgp}~1
+and Table~\ref{tab:mc2} for~\textsc{dgp}~2.  For all of the stable
+parameter values, the proposed new statistic has similar rejection
+probability to \citepos{ClW:07}.  Clark and West's test is slightly
+more undersized than the new test, but has a little higher power under
+the alternative.  Moreover, the statistics give different results in
+less than 10\% of the simulations for most parametrizations of the
+\dgp s.  In general, the statistics perform similarly well.
 
@@
 
-This section demonstrates the use of the statistics introduced earlier
-in the paper by revisiting \citepos{GoW:08} study of excess stock
-returns.  Goyal and Welch argue that many variables thought to predict
-excess returns (measured as the difference between the yearly log
-return of the S\&P 500 index and the T-bill interest rate) on the
-basis of in-sample evidence fail to do so out-of-sample.  To show
-this, Goyal and Welch look at the forecasting performance of models
-using a lag of the variable of interest, and show that these models do
-not significantly outperform the excess return's recursive sample mean.
+This section demonstrates the use of our new statistics by revisiting
+\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
+that many variables thought to predict excess returns (measured as the
+difference between the yearly log return of the S\&P 500 index and the
+T-bill interest rate) on the basis of in-sample evidence fail to do so
+out-of-sample.  To show this, Goyal and Welch look at the forecasting
+performance of models using a lag of the variable of interest, and
+show that these models do not significantly outperform the excess
+return's recursive sample mean.
 
@@
 \windowlength\ observations.\footnote{This statistical analysis was
-  conducted in R \citep{R} using the xtable \citep[version]{Dah:09},
-  Hmisc \citep[version]{Har:10}, and dbframe \citep[version
-  0.2.1]{Cal:10b} packages; please see the supplemental appendices for
+  conducted in R \citep{R} using the xtable
+  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
+  0.2.5]{Cal:10b} packages; please see the supplemental appendices for
   details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
@@
 This Appendix restates \citepos{Mcc:00} results, which themselves
-weaken \citepos{Wes:96} assumptions, under the dependence conditions
-of Theorem~\ref{res:1}.  It also proves some of the Lemmas required
-for that result and the results in the main paper.
+weaken \citepos{Wes:96} assumptions, but under the dependence
+conditions of Theorem~\ref{res:1}.  It also proves some of the Lemmas
+required for that result and the results in the main paper.
 
@@
 \begin{lema}\label{res:a3}
-  Suppose the conditions of Theorem~\ref{res:3} hold; let $g_{t} =
-  (f_{t}' - \E f_{t}', a_t h_{t}')'$, $g_t^{*} =
+  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
+  (f_{t}' - \E f_{t}', a_t h_{t}')'$, $\psi_t^{*} =
   (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})', a_t
@@
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T g_{t}^{*}
-    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T g_{t}
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
+    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
     \leq x \Big] \Big| > \epsilon \Big] \to 0
@@
 \begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that $g_t$ satisfies the conditions of a \clt,
-  \citep[Theorem~2]{Jon:97}, and so it suffices to prove that the
-  bootstrap average obeys a \clt\ as well.
-
-  Suppose that $g_t^{**}$ is generated by the stationary bootstrap but
+  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}, and
+  so it suffices to prove that the bootstrap average obeys a \clt\ as
+  well.
+
+  Suppose that $\psi_t^{**}$ is generated by the stationary bootstrap but
   with exactly $\lfloor p P \rfloor$ full blocks of length
@@
   observations $P^{**}$ is random).  As in \citet{Cal:11d}, $\sqrt{P}
-  \bar{g}^{*}$ and $\sqrt{P^{**}} \bar{g}^{**}$ converge in
-  distribution to the same limit; moreover, $P^{**} \bar{g}^{**}$ is a
+  \bar{\psi}^{*}$ and $\sqrt{P^{**}} \bar{\psi}^{**}$ converge in
+  distribution to the same limit; moreover, $P^{**} \bar{\psi}^{**}$ is a
   sum of $\lfloor p P \rfloor$ independent blocks that obey a central
@@
     P \rfloor}$), and the result follows if $P^{**}
-  \E^{**}(\bar{g}^{**} \bar{g}^{**\prime} \mid \mathcal{M}) \to^p
-  \Sigma$ where $\Sigma = P \E(\bar{g} \bar{g}')$.
+  \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M}) \to^p
+  \Sigma$ where $\Sigma = P \E(\bar{\psi} \bar{\psi}')$.
 
@@
   \begin{multline}
-    P^{**} \E^{**}(\bar{g}^{**} \bar{g}^{**\prime} \mid \mathcal{M})
+    P^{**} \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M})
     = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor} 
-    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \hat{g}_s \hat{g}_t' 
+    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \hat{\psi}_s \hat{\psi}_t' 
     \\ = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}
-    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \big[g_s g_t' + g_s(\hat{g}_t
-    - g_{t})' + (\hat{g}_s - g_{s}) g_{t}' + (\hat{g}_s -
-    g_{s})(\hat{g}_t - g_{t}) \big],
+    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \big[\psi_s \psi_t' + \psi_s(\hat{\psi}_t
+    - \psi_{t})' + (\hat{\psi}_s - \psi_{s}) \psi_{t}' + (\hat{\psi}_s -
+    \psi_{s})(\hat{\psi}_t - \psi_{t}) \big],
   \end{multline}
-  with the first equality from \citet{Cal:11d} and $\hat{g}_s =
+  with the first equality from \citet{Cal:11d} and $\hat{\psi}_s =
   (f_t(\hat{\beta}_{T+1})' - \bar f(\hat{\beta}_{T+1})', h_t')'$.
-  Now, $\frac{1}{P^{**}} \sum_i \sum_{s,t} g_s g_t \to^p \var(\sqrt{P} \bar{g})$
+  Now, $\frac{1}{P^{**}} \sum_i \sum_{s,t} \psi_s \psi_t \to^p \var(\sqrt{P} \bar{\psi})$
   \citep[Lemma~5]{Cal:11d}, so it suffices to show that the remaining
@@
   Lemma~\ref{res:a5}.  Note that \[f_t(\beta_0)= 2 (y_{t+1} -
-  x_t'\beta_0)(x_t'\beta_0 - \hat{y}_{1,t+1}) \quad \text{a.s.},\] as
+  x_t'\beta_0)(\hat{y}_{1,t+1} - x_t'\beta_0) \quad \text{a.s.},\] as
   in \citet{ClW:07}, which is an \mds, so we do not need to use a
@@
   \end{equation}
-  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same as
-  in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
-  o_{p} = F + o_p$ and $B^{*} = B + o_{p}$.  The result then follows
-  from Lemma~\ref{res:a3}.
+  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same
+  as in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
+  o_{p}(1) = F + o_p(1)$ and $B^{*} = B + o_{p}(1)$.  The result then
+  follows from Lemma~\ref{res:a3}.
 \end{proof}
@@
   uniformly positive definite for each $k$.  Then the procedure
-  described in Remark~\ref{rem:01} achieves \sfwe.
+  described in Remark~\ref{rem:01} achieves \textsl{\sfwe}.
 \end{lem}

### 2012-05-17 Paper.tex
Updated BibTeX references so that paper would compile

@@
   \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:11,ClM:12},
+  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
   \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
@@
   order accuracy.}  A parametric bootstrap, such as that used by
-\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:11}, is an alternative
+\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
 method, but requires the benchmark model to be correctly specified.
@@
   nominal size.}  Econometricians, e.g. \citet{Whi:00},
-\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
+\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
 statistics that test families of hypotheses that control the
@@
 control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
-and those based on the parametric bootstrap \citep{ClM:11} essentially
+and those based on the parametric bootstrap \citep{ClM:12b} essentially
 control \sfwe\ if the individual null hypotheses are strengthened
@@
   The same reasoning implies that a parametric bootstrap
-  \citep[i.e.][]{ClM:11} achieves control of \sfwe\ only under the
+  \citep[i.e.][]{ClM:12b} achieves control of \sfwe\ only under the
   stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
@@
   \citep[version 0.2.1]{Cal:10b} packages.  For details on the
-  programming, please see the supplemental appendices
-  \citep{Cal:11f,Cal:11g,Cal:11h}.}  I'll use both of the \dgp s they
-consider as well as a modification to study the performance of the
-statistics if there is instability.
+  programming, please see the supplemental appendix \citep{Cal:11f}.}
+I'll use both of the \dgp s they consider as well as a modification to
+study the performance of the statistics if there is instability.
 
@@
   0.2.5]{Cal:10b} packages; please see the supplemental appendices for
-  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}
+  details on the programming \citep{Cal:11f}.}
 

### 2012-06-28 Paper.tex
Changed margins and formatting to improve editability
Minor change to 'thanks' section

@@
-\documentclass[12pt,fleqn]{article}
+\documentclass[11pt,fleqn]{article}
 
@@
 \usepackage[sort,round,comma]{natbib}
-\usepackage[top=1.25in,left=1.25in,right=1.25in,bottom=1.25in]{geometry}
+\usepackage{geometry}
 \usepackage[small]{caption}
@@
 \newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
-\frenchspacing\onehalfspacing
-\input{tex/simulationdefinitions}
-\input{tex/empiricsdefinitions}
-\input{tex/empiricalresults}
+\frenchspacing
+\input{tex/mcDef}
+\input{tex/ap}
 
@@
     Meng-Feng Yen and participants at the 2011 Midwest Econometrics
-    Group meeting for helpful comments.  I'd also like to thank Amit
+    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
     Goyal for providing computer code and data for his 2008
@@
 
-\date{\input{VERSION% <- allows VERSION to have comments
-}}
+\date{December 9, 2011}
+
 \maketitle
@@
 \newpage 
+\newgeometry{top=1.2222in,left=0.9444in,right=1.8889in,bottom=2.4444in}
 
@@
   \centering
-  \input{floats/simulation1}
+  \input{tex/mc1}
   \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
@@
   \centering
-  \input{floats/simulation2}
+  \input{tex/mc2}
   \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
@@
 
-\bibliography{AllRefs}
+\bibliography{texextra/AllRefs}
 \end{document}

### 2013-01-31 R/empirics.R
Pull code out of noweb
Breaks up the monolithic noweb file, Documentation.nw, into many smaller source
code files, mostly in R.

@@ -1,0 +1,98 @@
+# Copyright (c) 2011-2013 Gray Calhoun.
+
+# This program is free software: you can redistribute it and/or modify it under 
+# the terms of the GNU General Public License as published by the Free Software 
+# Foundation, either version 3 of the License, or (at your option) any later 
+# version.
+
+# This program is distributed in the hope that it will be useful, but WITHOUT 
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
+# details.
+
+# You should have received a copy of the GNU General Public License along with 
+# this program.  If not, see <http://www.gnu.org/licenses/>.
+
+library(oosanalysis, lib.loc = "lib")
+library(dbframe, lib.loc = "lib")
+
+gwdata <- ts(read.csv("data/yearlyData2009.csv")[,-1], start = 1871, 
+            frequency = 1)
+stock.returns <- ((gwdata[,"price"] + gwdata[,"dividend"]) / 
+                                           lag(gwdata[,"price"], -1) - 1)
+financial.data <- 
+  data.frame(window(start = 1927, end = 2009, lag(k = -1, cbind(
+    equity.premium =        lag(log1p(stock.returns)
+                                   - log1p(gwdata[,"risk.free.rate"]), 1),
+    default.yield.spread =  gwdata[,"baa.rate"] - gwdata[,"aaa.rate"],
+    inflation =             gwdata[,"inflation"],
+    stock.variance =        gwdata[,"stock.variance"],
+    dividend.payout.ratio = log(gwdata[,"dividend"])
+                                               - log(gwdata[,"earnings"]),
+    long.term.yield =       gwdata[,"long.term.yield"],
+    term.spread =           gwdata[,"long.term.yield"] - gwdata[,"t.bill"],
+    treasury.bill =         gwdata[,"t.bill"],
+    default.return.spread = gwdata[,"corp.bond"] - gwdata[,"long.term.rate"],
+    dividend.price.ratio =  log(gwdata[,"dividend"]) - log(gwdata[,"price"]),
+    dividend.yield =        log(gwdata[,"dividend"]) 
+                                         - log(lag(gwdata[,"price"], -1)),
+    long.term.rate =        gwdata[,"long.term.rate"],
[…]

### 2013-01-31 R/montecarlo.R

@@ -1,0 +1,67 @@
+# Copyright (c) 2011-2013 Gray Calhoun.
+
+# This program is free software: you can redistribute it and/or modify it under 
+# the terms of the GNU General Public License as published by the Free Software 
+# Foundation, either version 3 of the License, or (at your option) any later 
+# version.
+
+# This program is distributed in the hope that it will be useful, but WITHOUT 
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
+# details.
+
+# You should have received a copy of the GNU General Public License along with 
+# this program.  If not, see <http://www.gnu.org/licenses/>.
+
+mcdesign <- expand.grid(P = c(120, 240, 360, 720), R = c(120, 240),
+	      simulationtype = c("0.size", "1.stable", "2.breaks"),
+              stringsAsFactors = FALSE)
+
+library(dbframe, lib.loc = "lib")
+library(oosanalysis, lib.loc = "lib")
+library(rlecuyer)
+
+.lec.SetPackageSeed(c(89, 7345, 0909, 17593, 8759, 76))
+jobnames <- LETTERS[1:6]
+.lec.CreateStream(jobnames)
+.lec.CurrentStream(jobnames[jjob])
+
+null <- function(d) lm(y ~ 1, data = d)
+alt <- function(d) lm(y ~ zL1, data = d)
+
+generate.data.mc1 <- function(nobs, simulationtype, nburn = 1000) {
+  mean.gamma <- 0.35
+  innovation.vcv <- matrix(c(18, -0.5, -0.5, 0.025), 2, 2)
+  switch(simulationtype,
+    "0.size"   = rvar(nobs, list(y = c(0, 0), z = c(0, 0.95)), 
+                      c(0.5, 0.15), innovation.vcv),
+    "1.stable" = rvar(nobs, list(y = c(mean.gamma, 0), z = c(0, 0.95)), 
+                      c(0.5, 0.15), innovation.vcv),
+    "2.breaks" = {prebreak.nobs <- floor(nobs / 2)
+                  postbreak.nobs <- nobs - prebreak.nobs
+
+                  prebreak.data <- rvar(prebreak.nobs, list(y = c(0, 0), z = c(0, .95)),
+                                        c(0.5, 0.15), innovation.vcv)
+                  postbreak.data <- rvar(postbreak.nobs, 
[…]

### 2013-01-31 R/montecarlo2.R

@@ -1,0 +1,64 @@
+# Copyright (c) 2011-2013 Gray Calhoun.
+
+# This program is free software: you can redistribute it and/or modify it under 
+# the terms of the GNU General Public License as published by the Free Software 
+# Foundation, either version 3 of the License, or (at your option) any later 
+# version.
+
+# This program is distributed in the hope that it will be useful, but WITHOUT 
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
+# details.
+
+# You should have received a copy of the GNU General Public License along with 
+# this program.  If not, see <http://www.gnu.org/licenses/>.
+
+mcdesign <- expand.grid(P = c(40, 80, 120, 160), R = c(80, 120),
+			simulationtype = c("0.size", "1.power"),
+			stringsAsFactors = FALSE)
+
+library(dbframe, lib.loc = "lib")
+library(oosanalysis, lib.loc = "lib")
+library(rlecuyer)
+
+.lec.SetPackageSeed(c(819, 3475, 9090, 75139, 78599, 67))
+jobnames <- LETTERS[1:6]
+.lec.CreateStream(jobnames)
+.lec.CurrentStream(jobnames[jjob])
+
+null1 <- function(d) lm(y ~ yL1, data = d)
+null2 <- function(d) lm(y ~ yL1 + yL2 + yL3 + yL4, data = d)
+alt1 <-  function(d) lm(y ~ yL1 + zL1 + zL2 + zL3 + zL4, data = d)
+alt2 <-  function(d) lm(y ~ yL1 + yL2 + yL3 + yL4 + zL1 + zL2 + zL3 + zL4, 
+                        data = d)
+
+generate.data.mc2 <- function(nobs, simulationtype, nburn = 1000) {
+  gammastar <- switch(simulationtype,
+                      "0.size" = rep(0, 4),
+                      "1.power" = c(3.363, -0.633, -0.377, -0.529))
+  return(rvar(nobs, list(y = c(0.261, rep(0, 3), gammastar),
+                         z = c(rep(0, 4), c(0.804, -0.221, 0.226, -0.205))),
+              c(2.237, 0), matrix(c(10.505, 1.036, 1.036, 0.366), 2)))
+}
+
+mcdata <- dbframe("mc2", dbdriver = "SQLite",
[…]

### 2013-01-31 R/simulationtable1.R

@@ -1,0 +1,34 @@
+# Copyright (c) 2011-2013 Gray Calhoun.
+
+# This program is free software: you can redistribute it and/or modify it under 
+# the terms of the GNU General Public License as published by the Free Software 
+# Foundation, either version 3 of the License, or (at your option) any later 
+# version.
+
+# This program is distributed in the hope that it will be useful, but WITHOUT 
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
+# details.
+
+# You should have received a copy of the GNU General Public License along with 
+# this program.  If not, see <http://www.gnu.org/licenses/>.
+
+library(dbframe, lib.loc = "lib")
+mcdata1 <- dbframe("mc1", dbdriver = "SQLite", dbname = "data/mcdata.db",
+		   readonly = TRUE)
+displaycols <-
+  c("'Sim. type'" = "case simulationtype
+		     when '0.size' then 'size'
+		     when '1.stable' then 'power (stable)'
+		     when '2.breaks' then 'power (breaks)' end",
+    R = "R", P = "P",
+    "'Pr[\\textsc{cw}~roll.]'" = "100 * avg(clarkwestrolling <= 10.0 / 100.0)",
+    "'Pr[\\textsc{cw}~rec.]'"
+      = "100 * avg(clarkwestrecursive <= 10.0 / 100.0)",
+    "'Pr[new]'" = "100 * avg(mixed <= 10.0 / 100.0)")
+
+cat(file = "floats/simulation1.tex",
+    booktabs(select(mcdata1, displaycols, group.by = c("simulationtype", "R", "P")),
+	     purgeduplicates = c(rep(TRUE, 3), rep(FALSE, 3)),
+	     drop = "simulationtype", numberformat = c(FALSE, rep(TRUE, 5)),
+	     digits = c(0, 0, 0, 1, 1, 1), align = c("l", rep("C", 5))))

### 2013-01-31 R/simulationtable2.R

@@ -1,0 +1,36 @@
+# Copyright (c) 2011-2013 Gray Calhoun.
+
+# This program is free software: you can redistribute it and/or modify it under 
+# the terms of the GNU General Public License as published by the Free Software 
+# Foundation, either version 3 of the License, or (at your option) any later 
+# version.
+
+# This program is distributed in the hope that it will be useful, but WITHOUT 
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
+# details.
+
+# You should have received a copy of the GNU General Public License along with 
+# this program.  If not, see <http://www.gnu.org/licenses/>.
+
+library(dbframe, lib.loc = "lib")
+mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
+		   dbname = "data/mcdata.db", readonly = TRUE)
+
+colsql <- lapply(1:2, function(i) {
+  c(Model = sprintf("'Model %d'", i),
+    "'Sim. type'" = "case when simulationtype = '0.size' then 'size' else 'power' end",
+    "R", "P",
+    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling%d <= .1)", i),
+    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive%d <= .1)", i),
+    "'Pr[new]'" = sprintf("100 * avg(mixed%d <= .1)", i))
+})
+    
+summary <- lapply(colsql, function(cs)
+                  select(mcdata2, cs, group.by = c("simulationtype", "R", "P")))
+
+cat(file = "floats/simulation2.tex",
+    booktabs(do.call(rbind, summary), drop = "simulationtype",
+             digits = c(rep(0,4), rep(1,3)), align = c("l", "l", rep("C", 5)),
+             purgeduplicates = c(rep(TRUE, 4), rep(FALSE, 3)),
+	     numberformat = c(rep(FALSE, 4), rep(TRUE, 3))))

### 2013-02-01 Paper.tex
Fix typo in formula for asymptotic variance
Changes the formula for g_t so that the summation uses s, not t, as an index.
Add submodules for external libraries
Adds submodules for external libraries used in the paper and changes the source
code to use these local copies instead of installed versions.
Clean up build process
Shortens file names and simplifies build path for the paper and monte carlo.  Also sets a
few parameters to govern empirics and monte carlo (this was done through the noweb
document before).

@@
     Meng-Feng Yen and participants at the 2011 Midwest Econometrics
-    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
+    Group meeting for helpful comments.  I'd also like to thank Amit
     Goyal for providing computer code and data for his 2008

### 2013-02-01 R/ap.R

@@ -16,26 +16,27 @@
 library(oosanalysis, lib.loc = "lib")
 library(dbframe, lib.loc = "lib")
 
-gwdata <- ts(read.csv("data/yearlyData2009.csv")[,-1], start = 1871, 
-            frequency = 1)
+## These parameters are going to be reported in the paper as well.
+nboot <- 599
+bootsize <- 0.10
+windowlength <- 10
+
+gwdata <- ts(read.csv("data/yearlyData2009.csv")[,-1], start = 1871, frequency = 1)
 stock.returns <- ((gwdata[,"price"] + gwdata[,"dividend"]) / 
                                            lag(gwdata[,"price"], -1) - 1)
 financial.data <- 
   data.frame(window(start = 1927, end = 2009, lag(k = -1, cbind(
-    equity.premium =        lag(log1p(stock.returns)
-                                   - log1p(gwdata[,"risk.free.rate"]), 1),
+    equity.premium =        lag(log1p(stock.returns) - log1p(gwdata[,"risk.free.rate"]), 1),
     default.yield.spread =  gwdata[,"baa.rate"] - gwdata[,"aaa.rate"],
     inflation =             gwdata[,"inflation"],
     stock.variance =        gwdata[,"stock.variance"],
-    dividend.payout.ratio = log(gwdata[,"dividend"])
-                                               - log(gwdata[,"earnings"]),
+    dividend.payout.ratio = log(gwdata[,"dividend"]) - log(gwdata[,"earnings"]),
     long.term.yield =       gwdata[,"long.term.yield"],
     term.spread =           gwdata[,"long.term.yield"] - gwdata[,"t.bill"],
     treasury.bill =         gwdata[,"t.bill"],
     default.return.spread = gwdata[,"corp.bond"] - gwdata[,"long.term.rate"],
     dividend.price.ratio =  log(gwdata[,"dividend"]) - log(gwdata[,"price"]),
-    dividend.yield =        log(gwdata[,"dividend"]) 
-                                         - log(lag(gwdata[,"price"], -1)),
+    dividend.yield =        log(gwdata[,"dividend"]) - log(lag(gwdata[,"price"], -1)),
     long.term.rate =        gwdata[,"long.term.rate"],
     earnings.price.ratio =  log(gwdata[,"earnings"]) - log(gwdata[,"price"]),
     book.to.market =        gwdata[,"book.to.market"],
@@ -69,29 +70,27 @@ alternatives <- c(alternatives_gw, alternatives_ct,
[…]

### 2013-02-01 R/mc1.R

@@ -13,9 +13,10 @@
 # You should have received a copy of the GNU General Public License along with 
 # this program.  If not, see <http://www.gnu.org/licenses/>.
 
+source("R/mcSetup.R")
 mcdesign <- expand.grid(P = c(120, 240, 360, 720), R = c(120, 240),
-	      simulationtype = c("0.size", "1.stable", "2.breaks"),
-              stringsAsFactors = FALSE)
+                        simulationtype = c("0.size", "1.stable", "2.breaks"),
+                        stringsAsFactors = FALSE)
 
 library(dbframe, lib.loc = "lib")
 library(oosanalysis, lib.loc = "lib")
@@ -52,16 +53,12 @@ generate.data.mc1 <- function(nobs, simulationtype, nburn = 1000) {
 mcdata <- dbframe("mc1", dbdriver = "SQLite", clear = TRUE,
 		  dbname = sprintf("db/mc1db%d.db", jjob))
 
-nsims <- 12
 for (r in rows(mcdesign)) {
   print(r)
   insert(mcdata) <- data.frame(r, row.names = NULL,
     t(replicate((nsims %/% 6 + (jjob <= nsims %% 6)), {
       randomdata <- with(r, generate.data.mc1(R + P, simulationtype))
-      c(clarkwestrolling = clarkwest(null, alt, randomdata, r$R,
-				     window = "rolling")$pvalue,
-	clarkwestrecursive = clarkwest(null, alt, randomdata, r$R,
-				       window = "recursive")$pvalue,
-	mixed = mixedwindow(null, alt, randomdata, r$R,
-			    window = "rolling")$pvalue)})))
+      c(clarkwestrolling = clarkwest(null, alt, randomdata, r$R, window = "rolling")$pvalue,
+	clarkwestrecursive = clarkwest(null, alt, randomdata, r$R, window = "recursive")$pvalue,
+	mixed = mixedwindow(null, alt, randomdata, r$R, window = "rolling")$pvalue)})))
 }

### 2013-02-01 R/mc1Table.R

@@ -13,6 +13,7 @@
 # You should have received a copy of the GNU General Public License along with 
 # this program.  If not, see <http://www.gnu.org/licenses/>.
 
+source("R/mcSetup.R")
 library(dbframe, lib.loc = "lib")
 mcdata1 <- dbframe("mc1", dbdriver = "SQLite", dbname = "data/mcdata.db",
 		   readonly = TRUE)
@@ -22,12 +23,11 @@ displaycols <-
 		     when '1.stable' then 'power (stable)'
 		     when '2.breaks' then 'power (breaks)' end",
     R = "R", P = "P",
-    "'Pr[\\textsc{cw}~roll.]'" = "100 * avg(clarkwestrolling <= 10.0 / 100.0)",
-    "'Pr[\\textsc{cw}~rec.]'"
-      = "100 * avg(clarkwestrecursive <= 10.0 / 100.0)",
-    "'Pr[new]'" = "100 * avg(mixed <= 10.0 / 100.0)")
+    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling <= %f)", testsize),
+    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive <= %f)", testsize),
+    "'Pr[new]'" = sprintf("100 * avg(mixed <= %f)", testsize))
 
-cat(file = "floats/simulation1.tex",
+cat(file = "tex/mc1.tex",
     booktabs(select(mcdata1, displaycols, group.by = c("simulationtype", "R", "P")),
 	     purgeduplicates = c(rep(TRUE, 3), rep(FALSE, 3)),
 	     drop = "simulationtype", numberformat = c(FALSE, rep(TRUE, 5)),

### 2013-02-01 R/mc2.R

@@ -13,6 +13,7 @@
 # You should have received a copy of the GNU General Public License along with 
 # this program.  If not, see <http://www.gnu.org/licenses/>.
 
+source("R/mcSetup.R")
 mcdesign <- expand.grid(P = c(40, 80, 120, 160), R = c(80, 120),
 			simulationtype = c("0.size", "1.power"),
 			stringsAsFactors = FALSE)
@@ -43,22 +44,16 @@ generate.data.mc2 <- function(nobs, simulationtype, nburn = 1000) {
 
 mcdata <- dbframe("mc2", dbdriver = "SQLite",
 		  dbname = sprintf("db/mc2db%d.db", jjob), clear = TRUE)
-nsims <- 12
+
 for (r in rows(mcdesign)) {
   print(r)
   insert(mcdata) <- data.frame(r, row.names = NULL,
     t(replicate((nsims %/% 6 + (jjob <= nsims %% 6)), {
       randomdata <- with(r, generate.data.mc2(R + P, simulationtype))
-      c(clarkwestrolling1 = clarkwest(null1, alt1, randomdata,
-				      r$R, window = "rolling")$pvalue,
-	clarkwestrecursive1 = clarkwest(null1, alt1, randomdata, r$R,
-					window = "recursive")$pvalue,
-	mixed1 = mixedwindow(null1, alt1, randomdata, r$R,
-			     window = "rolling")$pvalue,
-	clarkwestrolling2 = clarkwest(null2, alt2, randomdata, r$R,
-				      window = "rolling")$pvalue,
-	clarkwestrecursive2 = clarkwest(null2, alt2, randomdata, r$R,
-					window = "recursive")$pvalue,
-	mixed2 = mixedwindow(null2, alt2, randomdata, r$R,
-			     window = "rolling")$pvalue)})))
+      c(clarkwestrolling1 = clarkwest(null1, alt1, randomdata, r$R, window = "rolling")$pvalue,
+	clarkwestrecursive1 = clarkwest(null1, alt1, randomdata, r$R, window = "recursive")$pvalue,
+	mixed1 = mixedwindow(null1, alt1, randomdata, r$R, window = "rolling")$pvalue,
+	clarkwestrolling2 = clarkwest(null2, alt2, randomdata, r$R, window = "rolling")$pvalue,
+	clarkwestrecursive2 = clarkwest(null2, alt2, randomdata, r$R, window = "recursive")$pvalue,
[…]

### 2013-02-01 R/mc2Table.R

@@ -13,6 +13,7 @@
 # You should have received a copy of the GNU General Public License along with 
 # this program.  If not, see <http://www.gnu.org/licenses/>.
 
+source("R/mcSetup.R")
 library(dbframe, lib.loc = "lib")
 mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
 		   dbname = "data/mcdata.db", readonly = TRUE)
@@ -21,15 +22,15 @@ colsql <- lapply(1:2, function(i) {
   c(Model = sprintf("'Model %d'", i),
     "'Sim. type'" = "case when simulationtype = '0.size' then 'size' else 'power' end",
     "R", "P",
-    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling%d <= .1)", i),
-    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive%d <= .1)", i),
-    "'Pr[new]'" = sprintf("100 * avg(mixed%d <= .1)", i))
+    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling%d <= %f)", i, testsize),
+    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive%d <= %f)", i, testsize),
+    "'Pr[new]'" = sprintf("100 * avg(mixed%d <= %f)", i, testsize))
 })
     
 summary <- lapply(colsql, function(cs)
                   select(mcdata2, cs, group.by = c("simulationtype", "R", "P")))
 
-cat(file = "floats/simulation2.tex",
+cat(file = "tex/mc2.tex",
     booktabs(do.call(rbind, summary), drop = "simulationtype",
              digits = c(rep(0,4), rep(1,3)), align = c("l", "l", rep("C", 5)),
              purgeduplicates = c(rep(TRUE, 4), rep(FALSE, 3)),

### 2013-02-01 R/mcSetup.R

@@ -1,0 +1,2 @@
+nsims <- 2000
+testsize <- 0.1

### 2013-02-01 R/mcTex.R

@@ -1,0 +1,4 @@
+source("R/mcSetup.R")
+cat(file = "tex/mcDef.tex",
+    sprintf("\\newcommand{\\%s}{%d}", c("totalsims", "testsize"),
+            c(nsims, 100 * testsize)))

### 2013-02-03 Paper.tex
Tweak formula of asymptotic variance
Changes the formula of the asymptotic variance of the oos statistic to
use the fact that x_s (y_{s+1} - x_s'\beta) is an MDS.
Ongoing tweaks to main text

--- 2012-06-28 Paper.tex
@@
 \section{Out-of-Sample Model Comparisons}\label{sec:1}
-This section presents the new \oos\ statistic.  I'll present the
+This section presents the new \oos\ statistic.  I will present the
 single-comparison statistic first and then extend it to multiple
@@
   \begin{equation*}
-    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
-    y_{t+1} - \hat{y}_{1,t+1}) \Big\}' \big(\tfrac1T \X'\X \big)^{-1}
-    x_t(y_{t+1} - x_t'\beta).
+    g_t(\beta) =
+    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
+    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
   \end{equation*}
@@
 \begin{rem}
-  Forecasters will be interested in the one-sided alternative that $\E
-  f_t(\beta_0) > 0$; i.e. that the alternative model is expected to
-  forecast better than the benchmark.
+  Forecasters are usually interested in the one-sided alternative that
+  $\E f_t(\beta_0) > 0$; i.e. that the alternative model is expected
+  to forecast better than the benchmark.
 \end{rem}
@@
 \begin{rem}
-  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
-  window but claim that their results hold for a fixed-length fixed
-  window as well, where the unknown coefficients are estimated only
-  once using the first $R$ observations.  This claim is true but not
-  obviously so.  The proof for the rolling window is based on the idea
-  that the forecast errors are weakly dependent because they are a
-  function of a finite number of consecutive weakly dependent
-  observations.  But using a fixed window introduces another source of
-  dependence, all of the forecasts depend on the same coefficient
-  estimates.  One can prove that their results apply to fixed window
-  forecasts by using a coupling argument similar to \citepos{Cal:11}.
-  Interested readers should refer to \citet{Cal:11} for the argument
-  and to \citet{MeP:02} for a review of the necessary coupling
-  results.  Theorem~\ref{res:1} can be shown to hold when $\hat
-  y_{1t}$ is estimated with a fixed-length fixed window using the same
-  arguments.
+  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize model comparison
+  using a rolling window but claim in passing that their results hold
+  for a fixed-length fixed window as well, where the unknown
+  coefficients are estimated only once using the first $R$
+  observations.  This claim is true but not obvious.  The proof for
+  the rolling window is based on weak dependence that arises because
+  the forecast errors are a function of a finite number of consecutive
+  weakly dependent observations.  But using a fixed window introduces
+  another source of dependence: all of the forecasts depend on the
+  same coefficient estimates and the estimation uncertainty introduced
+  by those estimates does not vanish when $R$ is bounded.  One can
+  prove that their results apply to fixed window forecasts by using a
+  coupling argument similar to \citepos{Cal:11}.  Interested readers
+  should refer to \citet{Cal:11} for the argument and to
+  \citet{MeP:02} for a review of the necessary coupling results.
+  Theorem~\ref{res:1} can be shown to hold when $\hat y_{1t}$ is
+  estimated with a fixed-length fixed window using the same arguments.
 \end{rem}

### 2013-02-03 Paper.tex
Minor changes to wording in theorems 1 and 3
Changes the phrasing slightly, but should not change the content or meaning
of any statements in the paper.
Remove weak-stationarity requirement in theorem 1
Under the null, the mean is zero; so assuming covariance stationarity is
just a restriction on the variances.  That restriction isn't necessary for
the CLT to hold, so I'm removing it.

--- 2012-06-28 Paper.tex
@@
 \usepackage[sort,round,comma]{natbib}
-\usepackage{geometry}
+\usepackage[margin=1.25in]{geometry}
 \usepackage[small]{caption}
@@
 \input{tex/ap}
-
-% redfine heading styles
-\makeatletter
-\renewcommand\section{\@startsection%
-{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
-{\normalfont\normalsize\bfseries\large\raggedright}}
-\makeatother
 
@@
 \newpage
-\newgeometry{top=1.2222in,left=0.9444in,right=1.8889in,bottom=2.4444in}
 
@@
     Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
-    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that it does not depend
+    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
     on~$t$.
@@
     $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
-    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T -
-    R$. The processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$
-    are covariance stationary and $\bar f(\beta_0)$ has uniformly
-    positive and finite long run variance.
+    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
+    $\bar f(\beta_0)$ has uniformly positive and finite long run
+    variance.
   \end{enumerate}
@@
       H_{t} = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s}(\beta_{0}) & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_{0}) & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s}(\beta_{0}) & \text{fixed window} \\
+        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
       \end{cases}
     \end{equation}
-    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0})
-    = 0$ for all $s$.
-  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector.
-    Then $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
+    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
+    $\E h_{s} = 0$ for all $s$.
+  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
+    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
     \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly

### 2013-02-03 Paper.tex
Add requirement of constant mean to theorem 3
Without a constant mean, the OOS bootstrap used in Theorem 3 is not valid.
So I'm adding the assumption.
Remove unsubstantiated power claim from conclusion.

--- 2013-02-03 Paper.tex
@@
 that the new statistic behaves similarly to Clark and West's original
-test when the \dgp\ is stable, but can have much higher power when the
-predictability varies over time, suggesting that the new statistic is
+test when the \dgp\ is stable, suggesting that the new statistic is
 a suitable replacement in applied research.  The paper also presents a

### 2013-02-04 Paper.tex
Removed separate reference to tech. appendix
Since I'm not using literate programming anymore, citing the software you
used in the paper seems tacky.  I'm taking it out.

--- 2013-02-03 Paper.tex
@@
   \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
-    uniformly positive definite.
+    uniformly positive definite and $\E f_t(\beta_0) = \E
+    f_s(\beta_0)$ for all $s$ and $t$.
   \end{enumerate}
@@
   info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
-  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
-  programming, please see the supplemental appendix \citep{Cal:11f}.}
-I'll use both of the \dgp s they consider as well as a modification to
-study the performance of the statistics if there is instability.
+  \citep[version 0.2.1]{Cal:10b} packages.}  I'll use both of the \dgp
+s they consider as well as a modification to study the performance of
+the statistics if there is instability.
 

### 2013-02-04 Paper.tex
Edit Lemma A.1
Tweaks proof and adds additional conditions.

@@
     > 2$.
+  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
+    generated by the moving blocks, circular blocks, or stationary
+    bootstrap with block lengths drawn from the geometric
+    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
+    \to 0$; $b$ is the block length of the moving or circular blocks
+    bootstraps and is the expected block length of the stationary
+    bootstrap.
   \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
@@
     $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
-    $\E h_{s} = 0$ for all $s$.
+    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
+    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
+    \begin{equation}
+      H_{t}^* = \begin{cases} 
+        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
+      \end{cases}
+    \end{equation}
   \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
@@
   \item $R, P \to \infty$ as $T \to \infty$.
-  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
-    circular blocks, or stationary bootstrap with block lengths drawn
-    from the geometric distribution, and $b$ satisfies $b \to \infty$
-    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
-    circular blocks bootstraps and is the expected block length of the
-    stationary bootstrap.
   \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
@@
   \begin{equation}
-    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
+    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
         \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
@@
   \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
-    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_{T+1} |
+    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
     \to^{p^{*}} 0$.
@@
     with the convergence following from the continuous mapping
-    theorem.  \citepos{Cal:11d} Theorem~1 ensures the same argument
+    theorem.  \citepos{Cal:11d} Theorem~2 ensures the same argument
     holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
@@
     \begin{multline}
-      P^a \sup_{t \in S_T} | \hat{\beta}_t - \beta_0 | = P^a \sup_{t
-        \in S_T} |\hat{B}_{t} H_{t}| \\ \leq \sup_{t,u \in S_T} \Big|
-      [ \hat{B}_u - B] \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
+      P^a \sup_t | \hat{\beta}_t - \beta_0 | = P^a \sup_t |\hat{B}_{t}
+      H_{t}| \\ \leq \sup_{t,u \in S_T} \Big| [ \hat{B}_u - B]
+      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
       B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|

### 2013-02-05 Paper.tex
Minor changes to the wording
Changed paper margins to more standard 1.25in

--- 2013-02-04 Paper.tex
@@
 \input{tex/ap}
+
+% redfine heading styles
+\makeatletter
+\renewcommand\section{\@startsection%
+{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
+{\normalfont\normalsize\bfseries\large\raggedright}}
+\makeatother
 
@@
     Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
-    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
+    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that it does not depend
     on~$t$.
@@
     $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
-    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
-    $\bar f(\beta_0)$ has uniformly positive and finite long run
-    variance.
+    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T -
+    R$. The processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$
+    are covariance stationary and $\bar f(\beta_0)$ has uniformly
+    positive and finite long run variance.
   \end{enumerate}
@@
       H_{t} = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
+        \tfrac1t \sum_{s=1}^t h_{s}(\beta_{0}) & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_{0}) & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}(\beta_{0}) & \text{fixed window} \\
       \end{cases}
     \end{equation}
-    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
-    $\E h_{s} = 0$ for all $s$.
-  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
-    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
+    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, and $\E h_{s}(\beta_{0})
+    = 0$ for all $s$.
+  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector.
+    Then $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
     \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
@@
   \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
-    uniformly positive definite and $\E f_t(\beta_0) = \E
-    f_s(\beta_0)$ for all $s$ and $t$.
+    uniformly positive definite.
   \end{enumerate}
@@
   info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
-  \citep[version 0.2.1]{Cal:10b} packages.}  I'll use both of the \dgp
-s they consider as well as a modification to study the performance of
-the statistics if there is instability.
+  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
+  programming, please see the supplemental appendix \citep{Cal:11f}.}
+I'll use both of the \dgp s they consider as well as a modification to
+study the performance of the statistics if there is instability.
 

### 2013-02-06 Paper.tex
Remove custom section-header style
This commit changes the styling of the section labels back to the default style.
Correct and edit proof of normality for oos bootstrap components
Updates Lemma A2, a proof that the individual components of the OOS average
obey a CLT under the bootstrap-induced distribution.  This change corrects some
errors in the original proof and updates the proof strategy to be consistent
with the method proposed in the underlying stationary bootstrap paper (Calhoun
2011).

--- 2013-02-04 Paper.tex
@@
   Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
-  (f_{t}' - \E f_{t}', a_t h_{t}')'$, $\psi_t^{*} =
-  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})', a_t
-  h_t^{*\prime})'$, and $a_t = \sum_{s=\max(R,t)}^T \tfrac{1}{s}$.  Then
+  (f_{t}' - \E f_{t}', a_t h_{t}')'$ and $\psi_t^{*} =
+  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})',
+  h_t^{*\prime})'$.  Then
   \begin{equation}\label{eq:1}
@@
 \begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}, and
-  so it suffices to prove that the bootstrap average obeys a \clt\ as
-  well.
-
-  Suppose that $\psi_t^{**}$ is generated by the stationary bootstrap but
-  with exactly $\lfloor p P \rfloor$ full blocks of length
-  $M_1,\dots,M_{\lfloor p P \rfloor}$ (so that the number of
-  observations $P^{**}$ is random).  As in \citet{Cal:11d}, $\sqrt{P}
-  \bar{\psi}^{*}$ and $\sqrt{P^{**}} \bar{\psi}^{**}$ converge in
-  distribution to the same limit; moreover, $P^{**} \bar{\psi}^{**}$ is a
-  sum of $\lfloor p P \rfloor$ independent blocks that obey a central
-  limit theorem conditional on $\mathcal{M} = (M_1,\dots,M_{\lfloor p
-    P \rfloor}$), and the result follows if $P^{**}
-  \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M}) \to^p
-  \Sigma$ where $\Sigma = P \E(\bar{\psi} \bar{\psi}')$.
-
-  For $\tau = 1,\dots,P^{**}$, let $\kappa$ denote the block
-  containing $\tau$, so $\sum_{i=1}^{\kappa-1} M_i < \tau \leq
-  \sum_{i=1}^{\kappa} M_i$, and let $K_{\tau,i} = \sum_{j=\kappa+1}^i
-  M_{(j \mod \lfloor p P \rfloor) + 1}$, $K_{\tau,0} = 0$.  Then we have
-  \begin{multline}
-    P^{**} \E^{**}(\bar{\psi}^{**} \bar{\psi}^{**\prime} \mid \mathcal{M})
-    = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor} 
-    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \hat{\psi}_s \hat{\psi}_t' 
-    \\ = \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}
-    \sum_{s,t=K_{\tau,i-1}}^{K_{\tau,i}} \big[\psi_s \psi_t' + \psi_s(\hat{\psi}_t
-    - \psi_{t})' + (\hat{\psi}_s - \psi_{s}) \psi_{t}' + (\hat{\psi}_s -
-    \psi_{s})(\hat{\psi}_t - \psi_{t}) \big],
-  \end{multline}
-  with the first equality from \citet{Cal:11d} and $\hat{\psi}_s =
-  (f_t(\hat{\beta}_{T+1})' - \bar f(\hat{\beta}_{T+1})', h_t')'$.
-  Now, $\frac{1}{P^{**}} \sum_i \sum_{s,t} \psi_s \psi_t \to^p \var(\sqrt{P} \bar{\psi})$
-  \citep[Lemma~5]{Cal:11d}, so it suffices to show that the remaining
-  terms vanish, which is equivalent to showing
-  \begin{equation}\label{eq:3}
-    \tfrac{1}{P^{**}} \sum_{i=1}^{\lfloor p P \rfloor}\sum_{s,t =
-      K_{\tau,i-1}}^{K_{\tau,i}} (f_s(\hat{\beta}_{T+1}) -
-    f_s(\beta_0)) (f_t(\hat{\beta}_{T+1}) - f_t(\beta_0))
-    \to^p 0
-  \end{equation}
-  and
-  \begin{equation}\label{eq:2}
-    (\bar{f}(\hat{\beta}_{T+1}) - \E
-    \bar{f}(\beta_0)) (\bar{f}(\hat{\beta}_{T+1}) - \E
-    \bar{f}(\beta_0))' \to^p 0.
-  \end{equation}
-  Proving~\eqref{eq:3} uses the same argument as~\citet[Lemma
-  A.3]{Mcc:00} and~\eqref{eq:2} follows a streamlined version of the
-  argument of~\ref{res:a5}, completing the proof.  The proofs for the
-  moving and circular block bootstraps are the same.
+  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}; the
+  bootstrap average obeys a \clt\ as well from
+  \citet[Theorem~2]{Cal:11d} and is asymptotically normal, so it
+  suffices to prove that
+  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big) -
+  \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t \Big) \to^p 0. \]
+  I will prove this result for the Moving Blocks Bootstrap---the proof
+  for other block bootstraps is similar and follows as in
+  \cite{Cal:11d}.
+
+  \newcommand{\su}{\tfrac{ 1 }{ T - b } \sum_{ \tau = 0 }^{ T - b - 1
+    } \tfrac{ 1 }{ b }\sum_{ s, t = \tau + 1 }^{ \tau + b }}
+
+  Note that
+  \begin{equation*}
+  \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big)
+  = \su \hat\psi_s \hat\psi_t'
+     - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
+  \end{equation*}
+  where
+  \begin{equation*}
+    \tilde \psi( \hat \beta_T
+    = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
+       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b \tfrac{ t }{ b }
+         \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big)
+  \end{equation*}
+  Since $\bar \psi( \hat \beta_T ) = 0$ by construction and (finish explanation), we have
+  \begin{align*}
+    \tilde \psi( \hat \beta_T )
+    &= \tfrac{ b }{ T } \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
+       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b 
+       \Big( \tfrac{ t - b }{ b } - \tfrac{ b }{ T } \Big)
+       \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big) \\
+    &= o_p(1).
+  \end{align*}
+  Moreover,
+  \begin{equation*}
+    \su \hat\psi_s \hat\psi_t' \to^p \var \Big( \sum_{t=R+1}^T \psi_t \Big)
+  \end{equation*}
+  by (de Jong and Davidson reference), completing the proof.
 \end{proof}

### 2013-02-06 Paper.tex
Tweak wording in reference to McCracken (2000)
One of the results for the supplemental appendix claims that the proof procedes
pretty much exactly as in McCracken.  I tweaked the wording.

@@
 \begin{proof}[Proof of Lemma~\ref{res:a5}]
-  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}.
+  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}, using
+  the previous results in this appendix as substitutes where the
+  original proof requires stronger moment or weak dependence
+  conditions.
 \end{proof}

### 2013-02-06 Paper.tex
Change order of main and supplemental appendix
I plan to eventually have the supplemental appendix as a separate document, so
I put it after the main appendix to encourage that thought process while I write.

--- 2013-02-05 Paper.tex
@@
 weaken \citepos{Wes:96} assumptions, but under the dependence
-conditions of Theorem~\ref{res:1}.  It also proves some of the Lemmas
-required for that result and the results in the main paper.
+conditions of Theorem~\ref{res:1}.  It also proves Lemmas required for
+that result and the results in the main paper.
 

### 2013-02-06 Paper.tex

--- 2013-02-06 Paper.tex
@@
 \appendix
+\section{Proofs of Main Theoretical Results}\label{sec:B}
+
+\begin{proof}[Proof of Theorem \ref{res:1}]
+  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
+  statistic; this substitution does not affect its asymptotic
+  distribution; the theorem is now an immediate consequence of
+  Lemma~\ref{res:a5}.  Note that \[f_t(\beta_0)= 2 (y_{t+1} -
+  x_t'\beta_0)(\hat{y}_{1,t+1} - x_t'\beta_0) \quad \text{a.s.},\] as
+  in \citet{ClW:07}, which is an \mds, so we do not need to use a
+  \hac\ estimator of the variance under the null.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{res:2}]
+  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
+  Theorem~\ref{res:3} of this paper, Theorem~3.1 and~4.1 of
+  \citet{RoW:05}, and Theorem~1 of \citet{Cal:11e} complete the proof.
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{res:3}] Expand $\E^{*}
+  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
+  \begin{equation}
+    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
+    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
+    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
+  \end{equation}
+  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same
+  as in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
+  o_{p}(1) = F + o_p(1)$ and $B^{*} = B + o_{p}(1)$.  The result then
+  follows from Lemma~\ref{res:a3}.
+\end{proof}
+
+\begin{lem}[Formalization of Remark~\ref{rem:01}]
+  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
+  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
+  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
+  uniformly positive definite for each $k$.  Then the procedure
+  described in Remark~\ref{rem:01} achieves \textsl{\sfwe}.
+\end{lem}
+
+The proof is similar to that of Theorem~\ref{res:2}. Note that we
+allow $\sqrt{P}(\bar{f}_{i1}(\beta_1),\dots,\bar{f}_{iq}(\beta_q))$ to
+converge to a normal with singular variance-covariance matrix as long
+as each element has positive variance.
+
 \section{Supporting Results}
@@
 
-\section{Proofs of Main Theoretical Results}\label{sec:B}
-
-\begin{proof}[Proof of Theorem \ref{res:1}]
-  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
-  statistic; this substitution does not affect its asymptotic
-  distribution; the theorem is now an immediate consequence of
-  Lemma~\ref{res:a5}.  Note that \[f_t(\beta_0)= 2 (y_{t+1} -
-  x_t'\beta_0)(\hat{y}_{1,t+1} - x_t'\beta_0) \quad \text{a.s.},\] as
-  in \citet{ClW:07}, which is an \mds, so we do not need to use a
-  \hac\ estimator of the variance under the null.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{res:2}]
-  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper, Theorem~3.1 and~4.1 of
-  \citet{RoW:05}, and Theorem~1 of \citet{Cal:11e} complete the proof.
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{res:3}] Expand $\E^{*}
-  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
-  \begin{equation}
-    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
-    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
-    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
-    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
-  \end{equation}
-  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same
-  as in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
-  o_{p}(1) = F + o_p(1)$ and $B^{*} = B + o_{p}(1)$.  The result then
-  follows from Lemma~\ref{res:a3}.
-\end{proof}
-
-\begin{lem}[Formalization of Remark~\ref{rem:01}]
-  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
-  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
-  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
-  uniformly positive definite for each $k$.  Then the procedure
-  described in Remark~\ref{rem:01} achieves \textsl{\sfwe}.
-\end{lem}
-
-The proof is similar to that of Theorem~\ref{res:2}. Note that we
-allow $\sqrt{P}(\bar{f}_{i1}(\beta_1),\dots,\bar{f}_{iq}(\beta_q))$ to
-converge to a normal with singular variance-covariance matrix as long
-as each element has positive variance.
-
 \bibliography{texextra/AllRefs}

### 2013-02-11 R/mc1Table.R
Debug R code to generate MC tables
Formatting in the MC tables was broken, this commit makes some minor changes
to the code that seem to fix the formatting problems.

@@ -18,17 +18,21 @@ library(dbframe, lib.loc = "lib")
 mcdata1 <- dbframe("mc1", dbdriver = "SQLite", dbname = "data/mcdata.db",
 		   readonly = TRUE)
 displaycols <-
-  c("'Sim. type'" = "case simulationtype
-		     when '0.size' then 'size'
-		     when '1.stable' then 'power (stable)'
-		     when '2.breaks' then 'power (breaks)' end",
-    R = "R", P = "P",
-    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling <= %f)", testsize),
-    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive <= %f)", testsize),
-    "'Pr[new]'" = sprintf("100 * avg(mixed <= %f)", testsize))
+  
+
+d <- select(mcdata1, c("'Sim. type'" = "case simulationtype
+	                                when '0.size' then 'size'
+		                        when '1.stable' then 'power (stable)'
+		                        when '2.breaks' then 'power (breaks)' end",
+                       R = "R", P = "P",
+                       "'Pr[\\textsc{cw}~roll.]'" =
+                       sprintf("100 * avg(clarkwestrolling <= %f)", testsize),
+                       "'Pr[\\textsc{cw}~rec.]'" =
+                       sprintf("100 * avg(clarkwestrecursive <= %f)", testsize),
+                       "'Pr[new]'" = sprintf("100 * avg(mixed <= %f)", testsize)),
+            group.by = c("simulationtype", R = "R", P = "P"))[,-1]
 
 cat(file = "tex/mc1.tex",
-    booktabs(select(mcdata1, displaycols, group.by = c("simulationtype", "R", "P")),
-	     purgeduplicates = c(rep(TRUE, 3), rep(FALSE, 3)),
-	     drop = "simulationtype", numberformat = c(FALSE, rep(TRUE, 5)),
+    booktabs(d, purgeduplicates = c(rep(TRUE, 3), rep(FALSE, 3)),
+	     numberformat = c(FALSE, rep(TRUE, 5)),
 	     digits = c(0, 0, 0, 1, 1, 1), align = c("l", rep("C", 5))))

### 2013-02-11 R/mc2Table.R

@@ -19,19 +19,23 @@ mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
 		   dbname = "data/mcdata.db", readonly = TRUE)
 
 colsql <- lapply(1:2, function(i) {
-  c(Model = sprintf("'Model %d'", i),
-    "'Sim. type'" = "case when simulationtype = '0.size' then 'size' else 'power' end",
-    "R", "P",
-    "'Pr[\\textsc{cw}~roll.]'" = sprintf("100 * avg(clarkwestrolling%d <= %f)", i, testsize),
-    "'Pr[\\textsc{cw}~rec.]'" = sprintf("100 * avg(clarkwestrecursive%d <= %f)", i, testsize),
+  c("'Sim. type'" =
+      sprintf("case when simulationtype = '0.size' then 'size %d'
+                    else 'power %d' end", i, i),
+    R = "R", P = "P",
+    "'Pr[\\textsc{cw}~roll.]'" =
+      sprintf("100 * avg(clarkwestrolling%d <= %f)", i, testsize),
+    "'Pr[\\textsc{cw}~rec.]'" =
+      sprintf("100 * avg(clarkwestrecursive%d <= %f)", i, testsize),
     "'Pr[new]'" = sprintf("100 * avg(mixed%d <= %f)", i, testsize))
 })
     
 summary <- lapply(colsql, function(cs)
-                  select(mcdata2, cs, group.by = c("simulationtype", "R", "P")))
+                  select(mcdata2, cs,
+                         group.by = c("simulationtype", R = "R", P = "P"))[,-1])
 
 cat(file = "tex/mc2.tex",
-    booktabs(do.call(rbind, summary), drop = "simulationtype",
-             digits = c(rep(0,4), rep(1,3)), align = c("l", "l", rep("C", 5)),
-             purgeduplicates = c(rep(TRUE, 4), rep(FALSE, 3)),
-	     numberformat = c(rep(FALSE, 4), rep(TRUE, 3))))
+    booktabs(do.call(rbind, summary),
+             digits = c(rep(0,3), rep(1,3)), align = c("l", rep("C", 5)),
+             purgeduplicates = c(rep(TRUE, 3), rep(FALSE, 3)),
+	     numberformat = c(FALSE, rep(TRUE, 5))))

### 2013-02-12 Paper.tex
Removed special reference to software appendix
Update website address
I'm using <http://gray.clhn.co> for everything now, not xyz.iastate.edu.

@@
     \texttt{gcalhoun@iastate.edu}.  Web:
-    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
+    \texttt{http://gray.clhn.co}.  I'd like to
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
@@
   \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
-  0.2.5]{Cal:10b} packages; please see the supplemental appendices for
-  details on the programming \citep{Cal:11f}.}
+  0.2.5]{Cal:10b} packages.}
 

### 2013-02-12 Paper.tex
Fix slanted small-caps
The 'lmodern' package overrides slanted small caps, so I removed it.  Somehow I
also started explicitly wrapping acronyms in '\textsl', so I removed those as
well.

@@
 \usepackage[T1]{fontenc}
-\usepackage{lmodern}
 \usepackage[nolists,nomarkers]{endfloat}
@@
   \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
-    estimated using \textsl{\ols} with a recursive window:
+    estimated using \ols\ with a recursive window:
     $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
@@
     $x_t$.
-  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
+  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
     $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
@@
     $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
-    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
+    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
     $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
@@
   \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is an \textsl{\mds} with respect to
+    \hat{y}_{0t}$ is an \mds\ with respect to
     $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
@@
     $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
-    then the procedure outlined above controls \textsl{\sfwe} at level
+    then the procedure outlined above controls \sfwe\ at level
     $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
@@
     moving or circular block bootstraps) then the procedure outlined
-    above controls \textsl{\sfwe} at level $\alpha$ for the family of
+    above controls \sfwe\ at level $\alpha$ for the family of
     null hypotheses $H_1,\dots,H_m$.
@@
   uniformly positive definite for each $k$.  Then the procedure
-  described in Remark~\ref{rem:01} achieves \textsl{\sfwe}.
+  described in Remark~\ref{rem:01} achieves \sfwe.
 \end{lem}

### 2013-02-12 Paper.tex
Start corrections to bootstrap result for vcv convergence
The initial 'proof' of theorem 3--convergence of the bootstrap distribution
to the limiting distribution of the statistic--is pretty wrong.  I'm
fixing it by explicitly invoking de Jong and Davidson's vcv result for the
convergence of the bootstrap variance.  This commit adds part of it, but
the LLN for the deriviatives and stochastic equicontinuity still need to be
established.

--- 2013-02-12 Paper.tex
@@
 \newcommand{\hac}{\textsc{hac}}
+\newcommand{\lln}{\textsc{lln}}
 \newcommand{\ma}{\textsc{ma}}
@@
     \texttt{gcalhoun@iastate.edu}.  Web:
-    \texttt{http://gray.clhn.co}.  I'd like to
+    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
@@
   \begin{enumerate}
-  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
-    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
-    > 2$.
+  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size
+    $-\frac12$ on the series $V_t$; $V_t$ is strong mixing of size
+    $-\frac{r}{r-2}$ or uniform mixing of size $-\frac{r}{2r-2}$ with
+    $r > 2$.\footnote{For uniform mixing processes, $r = 2$ is also
+      allowed as long as $\sup_{\beta \in N} \psi_t(\beta)^2$ and
+      $\sup_{\beta \in N} (\partial \psi_t(\beta) / \partial \beta)^2$
+      are uniformly integrable; these terms are defined later in these
+      assumptions.}  Moreover, the \ned-coefficients are uniformly
+    bounded.
   \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
@@
     bootstrap with block lengths drawn from the geometric
-    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
-    \to 0$; $b$ is the block length of the moving or circular blocks
-    bootstraps and is the expected block length of the stationary
-    bootstrap.
+    distribution.  The (expected) block length $b$ satisfies $b \to
+    \infty$ and $\frac{b}{P} \to 0$.
   \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
@@
   \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
-    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
-    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
-    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
-  \item Each element of $\E f_{t}(\beta)$ is continuously
-    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
-      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
-    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
-  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
-    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
-    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
-    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
-      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
-    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
-    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
+    the asymptotic variance matrix of $\bar{f}(\beta_0)$ is uniformly
+    positive definite.
+  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
+    $\psi_t(\beta)$ is covariance stationary and is continuously
+    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
+    $\E( \sup_{\beta \in N} |\psi_t(\beta)|)^r$ and $\E\sup_{\beta \in
+      N} |\frac{\partial \psi_t(\beta)}{\partial \beta}|^2$ are
+    uniformly bounded.
   \item $R, P \to \infty$ as $T \to \infty$.
-  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
-    uniformly positive definite and $\E f_t(\beta_0) = \E
-    f_s(\beta_0)$ for all $s$ and $t$.
   \end{enumerate}
@@
 \begin{rem}
+  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
+  condtions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
+  must be continuously differentiable.  It may be possible to extend
+  Theorem~\ref{res:3} to those weaker conditions, but the current
+  proof relies on a theorem of \citepos{JoD:00} establishing the
+  consistency of \hac\ estimators which requires differentiability of
+  the observations.  Extending \citepos{JoD:00} result to
+  nondifferentiable functions should be possible, but is beyond the
+  scope of this paper.
+\end{rem}
+
+\begin{rem}
   \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
@@
   \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
-  \bar{f}(\beta_0))$.  But it is clear that
-  $\bar{f}(\hat{\beta}_{T+1})$ is the bootstrap analogue of $\E
-  \bar{f}(\beta_0)$, the parameter of interest.  Because their
-  bootstrap is miscentered, \citet{CoS:07} must redefine
-  $\hat{\beta}_t^{*}$ to achieve consistency.  In this paper, though,
-  consistency arises naturally.
+  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\hat{\beta}_T)$
+  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
+  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
+  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
+  paper, though, consistency arises naturally.
 \end{rem}
@@
 \begin{lema}\label{res:a3}
-  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
-  (f_{t}' - \E f_{t}', a_t h_{t}')'$ and $\psi_t^{*} =
-  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})',
-  h_t^{*\prime})'$.  Then
+  Suppose the conditions of Theorem~\ref{res:3} hold and let
+  \[\psi_t^{*}(\beta) = 
+  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
+  Then
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
-    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}(\hat\beta_T)
+    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}(\beta_0)
     \leq x \Big] \Big| > \epsilon \Big] \to 0
@@
   bootstrap average obeys a \clt\ as well from
-  \citet[Theorem~2]{Cal:11d} and is asymptotically normal, so it
-  suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big) -
-  \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t \Big) \to^p 0. \]
-  I will prove this result for the Moving Blocks Bootstrap---the proof
-  for other block bootstraps is similar and follows as in
-  \cite{Cal:11d}.
+  \citet[Theorem~2]{Cal:11d}, so it suffices to prove that
+  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
+  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
+  \beta_0 ) \Big) \to^p 0. \] I will prove this result for the Moving
+  Blocks Bootstrap---the proof for other block bootstraps is similar
+  and follows as in \cite{Cal:11d}.
 
@@
   \begin{equation*}
-  \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big)
-  = \su \hat\psi_s \hat\psi_t'
+  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_T ) \Big)
+  = \su \hat \psi_s( \hat \beta_T ) \hat \psi_t( \hat \beta_T )'
      - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
@@
   \begin{equation*}
-    \tilde \psi( \hat \beta_T
+    \tilde \psi( \hat \beta_T )
     = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
@@
   \end{equation*}
-  by (de Jong and Davidson reference), completing the proof.
+  by \citet[Theorem 2.2]{JoD:00}.  To see this, observe that 
+  \begin{equation*}
+    \su \hat\psi_s \hat\psi_t' 
+    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
+      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ + term.
+  \end{equation*}
+  The first term satisfies most of \citepos{JoD:00} Assumptions by
+  construction and it suffices to prove their condition (2.9) holds,
+  namely that
+  \begin{equation}\label{eq:2}
+    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
+    \Bigg\rVert_2 \to 0
+  \end{equation}
+  for all $i$, $j$, and $\xi$.  I will show that \eqref{eq:2} holds
+  for the real part of the expression; the proof for the complex part
+  is similar.
+
+  For any fixed $\beta \in N$,
+  \begin{equation*}
+    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
+  \end{equation*}
+  obeys an \lln\ (give reference and explanation -- you need to show
+  that the derivatives are \ned\ as well.) and convergence in $L_2$
+  follows from uniform integrability.
+
+  TODO: add stochastic equicontinuity conditions.
 \end{proof}

### 2013-02-14 Paper.tex
Finish edits to bootstrap normality
Makes additional changes to the statement of Theorem 3 and to the proof of
asymptotic normality for the bootstrap process, so that I can invoke de Jong
and Davidson's proof for the convergence of the second moment.

@@
   \begin{enumerate}
-  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size
-    $-\frac12$ on the series $V_t$; $V_t$ is strong mixing of size
-    $-\frac{r}{r-2}$ or uniform mixing of size $-\frac{r}{2r-2}$ with
-    $r > 2$.\footnote{For uniform mixing processes, $r = 2$ is also
-      allowed as long as $\sup_{\beta \in N} \psi_t(\beta)^2$ and
-      $\sup_{\beta \in N} (\partial \psi_t(\beta) / \partial \beta)^2$
-      are uniformly integrable; these terms are defined later in these
-      assumptions.}  Moreover, the \ned-coefficients are uniformly
-    bounded.
-  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
-    generated by the moving blocks, circular blocks, or stationary
-    bootstrap with block lengths drawn from the geometric
-    distribution.  The (expected) block length $b$ satisfies $b \to
-    \infty$ and $\frac{b}{P} \to 0$.
   \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
@@
     $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
-    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
-    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
-    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
+    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
+    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
     \begin{equation}
       H_{t} = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
+        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
       \end{cases}
     \end{equation}
-    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
-    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
-    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
-    \begin{equation}
-      H_{t}^* = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
-      \end{cases}
-    \end{equation}
-  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
-    the asymptotic variance matrix of $\bar{f}(\beta_0)$ is uniformly
-    positive definite.
+    and $\E h_{s}(\beta_0) = 0$ for all $s$.
   \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
-    $\psi_t(\beta)$ is covariance stationary and is continuously
-    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
-    $\E( \sup_{\beta \in N} |\psi_t(\beta)|)^r$ and $\E\sup_{\beta \in
-      N} |\frac{\partial \psi_t(\beta)}{\partial \beta}|^2$ are
-    uniformly bounded.
+    $\psi_t(\beta)$ is covariance stationary and twice continuously
+    differentiable with bounded second derivative in an open
+    neighborhood $N$ of $\beta_0$.  Also, $\E \sup_{\beta \in N}
+    |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in N} |\frac{\partial
+      \psi_t(\beta)}{\partial \beta'}|^r$ are uniformly bounded ($r$ is
+    defined below).
+  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
+    \psi_t(\beta)$ are $L_2$-\textsl{\ned} of size $-\frac12$ on the
+    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
+    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
+    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
+      uniform mixing processes, $r = 2$ is also allowed as long as
+      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
+      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
+      integrable.}
+  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
+    moving blocks, circular blocks, or stationary bootstrap with block
+    lengths drawn from the geometric distribution.  The (expected)
+    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
+  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
+    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
+  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
+    uniformly positive definite.
   \item $R, P \to \infty$ as $T \to \infty$.
@@
 \begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}; the
-  bootstrap average obeys a \clt\ as well from
-  \citet[Theorem~2]{Cal:11d}, so it suffices to prove that
+  Note that both $\psi_t(\beta_0)$ and $\psi_t^*(\hat\beta_T)$ satisfy
+  \clt s, (\citealp[Theorem~2]{Jon:97} and
+  \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
   \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
   \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
-  \beta_0 ) \Big) \to^p 0. \] I will prove this result for the Moving
-  Blocks Bootstrap---the proof for other block bootstraps is similar
-  and follows as in \cite{Cal:11d}.
-
-  \newcommand{\su}{\tfrac{ 1 }{ T - b } \sum_{ \tau = 0 }^{ T - b - 1
-    } \tfrac{ 1 }{ b }\sum_{ s, t = \tau + 1 }^{ \tau + b }}
-
-  Note that
-  \begin{equation*}
+  \beta_0 ) \Big) \to^p 0. \]
+  I will prove this result for the Circular Block Bootstrap
+  \citep{PoR:92}---the proof for other block bootstraps is similar and
+  follows as in \cite{Cal:11d}.
+
+  \newcommand{\su}{\tfrac{ 1 }{ b T } \sum_{ \tau = 1 }^{ T }%
+  \sum_{ s, t \in I( \tau ) }}
+
+  Since $\E^* \psi_t^*( \hat \beta_T ) = 0$ by construction, we have
+  \begin{equation}\label{eq:3}
   \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_T ) \Big)
   = \su \hat \psi_s( \hat \beta_T ) \hat \psi_t( \hat \beta_T )'
-     - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
+  \end{equation}
+  almost surely, with
+  \begin{equation*}
+    I(\tau) =
+    \begin{cases}
+      \{ \tau, \dots, \tau + b - 1 \} & \text{if } \tau \leq T - b + 1 \\
+      \{ \tau, \dots, T \} \cup \{ 1, \dots, \tau - ( T - b + 1 ) \}
+      & \text{if } \tau > T - b + 1.
+    \end{cases}
   \end{equation*}
-  where
-  \begin{equation*}
-    \tilde \psi( \hat \beta_T )
-    = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
-       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b \tfrac{ t }{ b }
-         \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big)
-  \end{equation*}
-  Since $\bar \psi( \hat \beta_T ) = 0$ by construction and (finish explanation), we have
-  \begin{align*}
-    \tilde \psi( \hat \beta_T )
-    &= \tfrac{ b }{ T } \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
-       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b 
-       \Big( \tfrac{ t - b }{ b } - \tfrac{ b }{ T } \Big)
-       \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big) \\
-    &= o_p(1).
-  \end{align*}
-  Moreover,
-  \begin{equation*}
-    \su \hat\psi_s \hat\psi_t' \to^p \var \Big( \sum_{t=R+1}^T \psi_t \Big)
-  \end{equation*}
-  by \citet[Theorem 2.2]{JoD:00}.  To see this, observe that 
-  \begin{equation*}
-    \su \hat\psi_s \hat\psi_t' 
-    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
-      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ + term.
-  \end{equation*}
-  The first term satisfies most of \citepos{JoD:00} Assumptions by
-  construction and it suffices to prove their condition (2.9) holds,
-  namely that
+  We can rewrite the right side of \eqref{eq:3} as
+  \begin{multline}\label{eq:6}
+    \su \psi_s(\hat\beta_T) \psi_t(\hat\beta_T)'
+    = \tfrac{1}{T} \sum_{s,t=1}^T \psi_s(\hat\beta_T) \psi_t(\hat\beta_T)' \;
+      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ \\
+      + \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
+        (\psi_s(\hat\beta_T) \psi_t(\hat\beta_T)' +
+         \psi_t(\hat\beta_T) \psi_s(\hat\beta_T)') \;
+        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+.
+  \end{multline}
+
+  The first term of \eqref{eq:6} can be shown to converge in
+  probability to $(1/P) \var \sum_{t=R+1}^T \psi_t( \beta_0 )$
+  by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
+  hold by assumption and it suffices to prove their condition (2.9)
+  holds, namely that
   \begin{equation}\label{eq:2}
@@
   \end{equation}
-  for all $i$, $j$, and $\xi$.  I will show that \eqref{eq:2} holds
-  for the real part of the expression; the proof for the complex part
-  is similar.
-
-  For any fixed $\beta \in N$,
+  for all $i$, $j$, and $\xi$.  Now, for any fixed $\beta \in N$,
   \begin{equation*}
@@
           \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
+    \to^p 0
   \end{equation*}
-  obeys an \lln\ (give reference and explanation -- you need to show
-  that the derivatives are \ned\ as well.) and convergence in $L_2$
-  follows from uniform integrability.
-
-  TODO: add stochastic equicontinuity conditions.
+  and
+  \begin{equation*}
+    \tfrac{1}{T} \sum_{t=1}^T \sin( \xi t / b )
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
+    \to^p 0
+  \end{equation*}
+  by a mixingale \lln\ \citep{Dav:93}.\footnote{Remember that \ned\
+    processes are also mixingales.  See, for example, \citet[Section
+    17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
+  follows from the existence of the $r$th moment and uniform
+  convergence is a consequence of the bounded second derivative of
+  $\psi_t$.
+
+  The conclusion then holds if the second term of~\eqref{eq:6} is
+  $o_p(1)$.  We have, for each element of that matrix,
+  \begin{multline}
+    \Big| \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
+        \psi_{is}(\hat\beta_T) \psi_{jt}(\hat\beta_T)
+        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+ \Big| \leq\\
+     \tfrac{1}{T} \sum_{s = 1}^{b - 1} |\psi_{is}(\hat\beta_T)|
+         \times\tfrac{1}{b} \sum_{t = T - b + 1}^{T} | \psi_{jt}(\hat\beta_T) |
+  \end{multline}
+  almost surely.  Now, for any positive $\delta$,
+  \begin{equation*}
+    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \psi_{is}( \hat \beta_T ) |
+              > \delta \Bigg] \leq 
+    \pr \Bigg[\tfrac{1}{T} \sum_{s = 1}^{b - 1} \sup_{ \beta \in N } | \psi_{is}( \beta ) |
+              > \delta \Bigg] +
+    \pr \big[ \hat \beta_T \notin N \big].
+  \end{equation*}
+  Both terms converge to zero by assumption, so $\tfrac{1}{T} \sum_{s
+    = 1}^{b - 1} |\psi_{is}(\hat\beta_T)| = o_p(1)$.  A similar
+  argument shows that $\tfrac{1}{b} \sum_{t = T - b + 1}^{T} |
+  \psi_{jt}(\hat\beta_T) | = O_p(1)$, completing the proof.
 \end{proof}

### 2013-02-14 Paper.tex
Remove reference to stepm paper
Earlier versions of this paper reference my (sort of) in-progress stepm paper,
but it is not necessary.

@@
   \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
-    \psi_t(\beta)$ are $L_2$-\textsl{\ned} of size $-\frac12$ on the
+    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
     series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
@@
   Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper, Theorem~3.1 and~4.1 of
-  \citet{RoW:05}, and Theorem~1 of \citet{Cal:11e} complete the proof.
+  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
+  \citet{RoW:05} complete the proof.
 \end{proof}

### 2013-02-14 Paper.tex
Remove extra patter from the supporting results appendix

--- 2013-02-12 Paper.tex
@@
 \newcommand{\hac}{\textsc{hac}}
-\newcommand{\lln}{\textsc{lln}}
 \newcommand{\ma}{\textsc{ma}}
@@
   \begin{enumerate}
-  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size
-    $-\frac12$ on the series $V_t$; $V_t$ is strong mixing of size
-    $-\frac{r}{r-2}$ or uniform mixing of size $-\frac{r}{2r-2}$ with
-    $r > 2$.\footnote{For uniform mixing processes, $r = 2$ is also
-      allowed as long as $\sup_{\beta \in N} \psi_t(\beta)^2$ and
-      $\sup_{\beta \in N} (\partial \psi_t(\beta) / \partial \beta)^2$
-      are uniformly integrable; these terms are defined later in these
-      assumptions.}  Moreover, the \ned-coefficients are uniformly
-    bounded.
+  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
+    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
+    > 2$.
   \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
@@
     bootstrap with block lengths drawn from the geometric
-    distribution.  The (expected) block length $b$ satisfies $b \to
-    \infty$ and $\frac{b}{P} \to 0$.
+    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
+    \to 0$; $b$ is the block length of the moving or circular blocks
+    bootstraps and is the expected block length of the stationary
+    bootstrap.
   \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
@@
   \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
-    the asymptotic variance matrix of $\bar{f}(\beta_0)$ is uniformly
-    positive definite.
-  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
-    $\psi_t(\beta)$ is covariance stationary and is continuously
-    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
-    $\E( \sup_{\beta \in N} |\psi_t(\beta)|)^r$ and $\E\sup_{\beta \in
-      N} |\frac{\partial \psi_t(\beta)}{\partial \beta}|^2$ are
-    uniformly bounded.
+    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
+    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
+    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
+  \item Each element of $\E f_{t}(\beta)$ is continuously
+    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
+      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
+    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
+  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
+    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
+    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
+    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
+      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
+    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
+    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
   \item $R, P \to \infty$ as $T \to \infty$.
+  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
+    uniformly positive definite and $\E f_t(\beta_0) = \E
+    f_s(\beta_0)$ for all $s$ and $t$.
   \end{enumerate}
@@
 \begin{rem}
-  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
-  condtions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
-  must be continuously differentiable.  It may be possible to extend
-  Theorem~\ref{res:3} to those weaker conditions, but the current
-  proof relies on a theorem of \citepos{JoD:00} establishing the
-  consistency of \hac\ estimators which requires differentiability of
-  the observations.  Extending \citepos{JoD:00} result to
-  nondifferentiable functions should be possible, but is beyond the
-  scope of this paper.
-\end{rem}
-
-\begin{rem}
   \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
@@
   \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
-  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\hat{\beta}_T)$
-  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
-  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
-  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
-  paper, though, consistency arises naturally.
+  \bar{f}(\beta_0))$.  But it is clear that
+  $\bar{f}(\hat{\beta}_{T+1})$ is the bootstrap analogue of $\E
+  \bar{f}(\beta_0)$, the parameter of interest.  Because their
+  bootstrap is miscentered, \citet{CoS:07} must redefine
+  $\hat{\beta}_t^{*}$ to achieve consistency.  In this paper, though,
+  consistency arises naturally.
 \end{rem}
@@
 \section{Supporting Results}
-This Appendix restates \citepos{Mcc:00} results, which themselves
-weaken \citepos{Wes:96} assumptions, but under the dependence
-conditions of Theorem~\ref{res:1}.  It also proves Lemmas required for
-that result and the results in the main paper.
 
@@
 \begin{lema}\label{res:a3}
-  Suppose the conditions of Theorem~\ref{res:3} hold and let
-  \[\psi_t^{*}(\beta) = 
-  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
-  Then
+  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
+  (f_{t}' - \E f_{t}', a_t h_{t}')'$ and $\psi_t^{*} =
+  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})',
+  h_t^{*\prime})'$.  Then
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}(\hat\beta_T)
-    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}(\beta_0)
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
+    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
     \leq x \Big] \Big| > \epsilon \Big] \to 0
@@
   bootstrap average obeys a \clt\ as well from
-  \citet[Theorem~2]{Cal:11d}, so it suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
-  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
-  \beta_0 ) \Big) \to^p 0. \] I will prove this result for the Moving
-  Blocks Bootstrap---the proof for other block bootstraps is similar
-  and follows as in \cite{Cal:11d}.
+  \citet[Theorem~2]{Cal:11d} and is asymptotically normal, so it
+  suffices to prove that
+  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big) -
+  \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t \Big) \to^p 0. \]
+  I will prove this result for the Moving Blocks Bootstrap---the proof
+  for other block bootstraps is similar and follows as in
+  \cite{Cal:11d}.
 
@@
   \begin{equation*}
-  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_T ) \Big)
-  = \su \hat \psi_s( \hat \beta_T ) \hat \psi_t( \hat \beta_T )'
+  \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big)
+  = \su \hat\psi_s \hat\psi_t'
      - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
@@
   \begin{equation*}
-    \tilde \psi( \hat \beta_T )
+    \tilde \psi( \hat \beta_T
     = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
@@
   \end{equation*}
-  by \citet[Theorem 2.2]{JoD:00}.  To see this, observe that 
-  \begin{equation*}
-    \su \hat\psi_s \hat\psi_t' 
-    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
-      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ + term.
-  \end{equation*}
-  The first term satisfies most of \citepos{JoD:00} Assumptions by
-  construction and it suffices to prove their condition (2.9) holds,
-  namely that
-  \begin{equation}\label{eq:2}
-    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
-    \Bigg\rVert_2 \to 0
-  \end{equation}
-  for all $i$, $j$, and $\xi$.  I will show that \eqref{eq:2} holds
-  for the real part of the expression; the proof for the complex part
-  is similar.
-
-  For any fixed $\beta \in N$,
-  \begin{equation*}
-    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
-  \end{equation*}
-  obeys an \lln\ (give reference and explanation -- you need to show
-  that the derivatives are \ned\ as well.) and convergence in $L_2$
-  follows from uniform integrability.
-
-  TODO: add stochastic equicontinuity conditions.
+  by (de Jong and Davidson reference), completing the proof.
 \end{proof}

### 2013-02-19 Paper.tex
Edit proof of oos bootstrap normality
This commit makes some extensive changes to the oos bootstrap normality
result; I change the conditions to better match West's argument, and I
spell out most of the details of the proof.

--- 2013-02-14 Paper.tex
@@
 \newcommand{\p}{\ensuremath{\mathrm{P}}}
+
+\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
+\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
+\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
 
@@
   \label{eq:4}
-  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t - x_t'\beta_0)
+  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\beta_0)
 \end{equation}
@@
   \label{eq:5}
-  \tfrac{2}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t -
-  x_t'\beta_0) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} - 
+  \tfrac{2}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
+  x_t'\beta_0) = \oclt{t} \Big[(y_{t+1} - 
   x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
@@
 \begin{equation*}
-  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
+  \oclt{t} \Big[(y_{t+1} -
   x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
@@
     (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
-    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
+    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
     = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
@@
     \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
-    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
+    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
     f)^2, \\
-    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
+    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
     \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
-    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
+    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
     g)(g_t(\hat{\beta}_t) - \bar g)',
@@
   $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
-  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
+  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
   \begin{equation*}
@@
     $\psi_t(\beta)$ is covariance stationary and twice continuously
-    differentiable with bounded second derivative in an open
-    neighborhood $N$ of $\beta_0$.  Also, $\E \sup_{\beta \in N}
-    |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in N} |\frac{\partial
-      \psi_t(\beta)}{\partial \beta'}|^r$ are uniformly bounded ($r$ is
-    defined below).
+    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
+    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
+      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
+    uniformly bounded ($r$ is defined below), and there exists a
+    sequence of random variables $m_t$ such that $\sup_{i,\beta \in N}
+    |\tfrac{\partial^2}{\partial \beta \partial \beta'}
+    \psi_{it}(\beta)| \leq m_t$ almost surely and $\E m_t^2$ is
+    uniformly finite.
   \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
@@
   \citet{Mcc:00} proves asymptotic normality under weaker smoothness
-  condtions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
+  conditions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
   must be continuously differentiable.  It may be possible to extend
@@
 
-\begin{proof}[Proof of Theorem~\ref{res:3}] Expand $\E^{*}
-  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
-  \begin{equation}
-    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
-    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
-    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
-    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
-  \end{equation}
-  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same
-  as in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
-  o_{p}(1) = F + o_p(1)$ and $B^{*} = B + o_{p}(1)$.  The result then
-  follows from Lemma~\ref{res:a3}.
+\newcommand{\WesA}{\oclt{t} (\nabla
+  f_t^*(\hat\beta_{T}) - F^*) B^* H_t^*}
+\newcommand{\WesB}{\tfrac{1}{\sqrt{P}} F^* \osum{t} (B_t^* -
+  B^*) H_t^*}
+\newcommand{\WesC}{\oclt{t} (\nabla
+  f_t^*(\hat\beta_{T}) - F^*) (B_t^* - B^*) H_t^*}
+\begin{proof}[Proof of Theorem~\ref{res:3}]
+  Expand $\E^{*} f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T}$
+  to get
+  \begin{align*}
+    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T})) &= \oclt{t}
+    f_t^{*}(\hat{\beta}_{T}) - \bar{f}(\hat{\beta}_{T}) +
+    F^{*} B^{*} \oclt{t} H_t^* \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t^*
+  \end{align*}
+  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
+  \begin{equation*}
+    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_T)'
+    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
+    f_{it}^*(\tilde\beta_{it}^*) \Big]
+    (\hat\beta_t^* - \hat\beta_T)
+  \end{equation*}
+  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
+  $\hat\beta_T$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
+  identical to West's, using our Lemma~\ref{res:a2} in place of his
+  Lemma A3.  Then
+  \begin{gather}
+    \WesA \to^{p^*} 0 \label{eq:7} \\
+    \WesB \to^{p^*} 0 \label{eq:9} \\
+  \intertext{and}
+    \WesC \to^{p^*} 0 \label{eq:10}
+  \end{gather}
+  from Lemma~\ref{res:a4} and the result follows from Lemma~\ref{res:a3}.
 \end{proof}
@@
 
+\begin{lema}\label{res:a4}
+  Under the conditions of Theorem~\ref{res:3}, \eqref{eq:7},
+  \eqref{eq:9}, and \eqref{eq:10} hold.
+\end{lema}
+\noindent For each of these results, I will present the proof for the
+recursive window and the circular block bootstrap only; extensions to
+the fixed and rolling window follow exactly as in \citet{WeM:98}.
+
+\begin{proof}[Proof of Lemma~\ref{res:a4}]
+We can write
+\begin{equation*}
+  \Big\lvert \WesA \Big\rvert \leq 
+  \Big\lvert \oclt{t} (\nabla f_t^*(\hat\beta_T) - F^*) B^* \Big\rvert
+  \sup_t | H_t^* |.
+\end{equation*}
+From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$; $\oclt{t} (\nabla
+f_t^*(\hat\beta_T) - F^*)$ obeys a \clt\ \citep{Cal:11d} and is
+$O_{p^*}(1)$, establishing~\eqref{eq:7}.  The proofs of~\eqref{eq:9}
+and~\eqref{eq:10} are similar.
+\end{proof}
+
 \begin{lema}\label{res:a3}
@@
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}(\hat\beta_T)
-    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}(\beta_0)
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}(\hat\beta_T)
+    \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}(\beta_0)
     \leq x \Big] \Big| > \epsilon \Big] \to 0
@@
   \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
-  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
+  \[ \tfrac{ 1 }{ P } \var^* \Big( \osum{t} \psi_t^*( \hat
+  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \osum{t} \psi_t(
   \beta_0 ) \Big) \to^p 0. \]
@@
   The first term of \eqref{eq:6} can be shown to converge in
-  probability to $(1/P) \var \sum_{t=R+1}^T \psi_t( \beta_0 )$
+  probability to $(1/P) \var \osum{t} \psi_t( \beta_0 )$
   by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
@@
   \begin{equation}
-    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \oclt{t}
     (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
@@
 % LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har
+% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt
+%  LocalWords:  stationarity mixingale mixingales texextra

### 2013-03-05 Paper.tex
Minor edits
Edit mathematical appendix
This commit tightens up the mathematical reasoning and corrects some errors
and omissions.

@@
 \DeclareMathOperator{\pr}{Pr}
+
+\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
 
@@
 \begin{equation*}
-  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{t-1} x_{t-1}'\Big)^{-1}
-  \sum_{s=t-R+1}^t x_{t-1} y_t
+  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
+  \sum_{s=t-R+1}^t x_{s-1} y_s
 \end{equation*}
@@
     $x_t$.
-  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
-    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
-    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
-    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
-    moments for some positive $\delta$.
+  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
+    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
+    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
+    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
+    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
+    series of size $-\frac{r}{2r-2}$.
   \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
@@
 \begin{thm}\label{res:2}
-  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
+  Suppose the conditions of Theorem~\ref{res:1} hold, with assumptions
   on the alternative model, $\hat{y}_{1t}$, holding for each of the
@@
     \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
-    \bar{f_i}(\hat{\beta}_{T+1}))$.
+    \bar{f_i}(\btrue[*]))$.
   \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
@@
       N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
-    uniformly bounded ($r$ is defined below), and there exists a
-    sequence of random variables $m_t$ such that $\sup_{i,\beta \in N}
-    |\tfrac{\partial^2}{\partial \beta \partial \beta'}
-    \psi_{it}(\beta)| \leq m_t$ almost surely and $\E m_t^2$ is
-    uniformly finite.
+    uniformly bounded, and there exists a sequence of random variables
+    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
+      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
+    and $\E m_t^2$ is uniformly finite.
   \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
@@
   \begin{equation}
-    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
+    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
         \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
@@
   \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
-  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\hat{\beta}_T)$
+  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\btrue[*])$
   is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
@@
 
-\newcommand{\WesA}{\oclt{t} (\nabla
-  f_t^*(\hat\beta_{T}) - F^*) B^* H_t^*}
-\newcommand{\WesB}{\tfrac{1}{\sqrt{P}} F^* \osum{t} (B_t^* -
-  B^*) H_t^*}
-\newcommand{\WesC}{\oclt{t} (\nabla
-  f_t^*(\hat\beta_{T}) - F^*) (B_t^* - B^*) H_t^*}
+\newcommand{\WesA}[1][]{\oclt{t} (\nabla
+  f_t^{#1}(\btrue[#1]) - F^{#1}) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} F^{#1} \osum{t} (B_t^{#1} -
+  B^{#1}) H_t^{#1}}
+\newcommand{\WesC}[1][]{\oclt{t} (\nabla
+  f_t^{#1}(\btrue[#1]) - F^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
 \begin{proof}[Proof of Theorem~\ref{res:3}]
-  Expand $\E^{*} f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T}$
+  Expand $f_t^{*}(\hat{\beta}_t^{*})$ around $\btrue[*]$
   to get
   \begin{align*}
-    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T})) &= \oclt{t}
-    f_t^{*}(\hat{\beta}_{T}) - \bar{f}(\hat{\beta}_{T}) +
+    \sqrt{P} \big(\bar{f}^{*} - \bar{f}(\btrue[*])\big) &= \oclt{t}
+    \big(f_t^{*}(\btrue[*]) - \bar{f}(\btrue[*])\big) +
     F^{*} B^{*} \oclt{t} H_t^* \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t^*
+    & \quad + \WesA[*] + \WesB[*] \\ & \quad + \WesC[*] + \oclt{t} w_t^*
   \end{align*}
@@
   \begin{equation*}
-    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_T)'
+    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_{T+1})'
     \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
     f_{it}^*(\tilde\beta_{it}^*) \Big]
-    (\hat\beta_t^* - \hat\beta_T)
+    (\hat\beta_t^* - \hat\beta_{T+1})
   \end{equation*}
   and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
-  $\hat\beta_T$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
+  $\hat\beta_{T+1}$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
   identical to West's, using our Lemma~\ref{res:a2} in place of his
@@
   \begin{gather}
-    \WesA \to^{p^*} 0 \label{eq:7} \\
-    \WesB \to^{p^*} 0 \label{eq:9} \\
+    \WesA[*] \to^{p^*} 0 \label{eq:7} \\
+    \WesB[*] \to^{p^*} 0 \label{eq:9} \\
   \intertext{and}
-    \WesC \to^{p^*} 0 \label{eq:10}
+    \WesC[*] \to^{p^*} 0 \label{eq:10}
   \end{gather}
-  from Lemma~\ref{res:a4} and the result follows from Lemma~\ref{res:a3}.
+  from Lemma~\ref{res:a4} and the result follows from
+  Lemma~\ref{res:a3}, with the form of the asymptotic variance
+  following directly from \citet{Wes:96} and \citet{WeM:98}.
 \end{proof}
@@
     \to^{p^{*}} 0$.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \big(\tfrac{\partial}{\partial \beta} f_t(\beta_0) - F\big) =
+    O_{p}(1)$ and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \big(\tfrac{\partial}{\partial \beta} f_t^*(\hat\beta_{T+1}) -
+    F^*\big) = O_{p^*}(1)$.
   \end{enumerate}
@@
 
-\begin{proof}[Proof of Lemma~\ref{res:a2}] \quad
+\begin{proof}[Proof of Lemma~\ref{res:a2}]
   \begin{enumerate}
-  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies \citepos[Theorem
-    3.1]{JoD:00b} functional \clt.  So
+  \item The process $\tfrac{1}{\sqrt{T}} h_{s}(\beta_0)$ satisfies
+    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
     \begin{equation}
-      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
+      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) \Big| =
       P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
-        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
+        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}(\beta_0) \Big| \to^{p} 0
     \end{equation}
     with the convergence following from the continuous mapping
-    theorem.  \citepos{Cal:11d} Theorem~2 ensures the same argument
-    holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
+    theorem.  For the bootstrapped average, \citepos{Cal:11d}
+    Theorem~2 ensures that
+    \begin{equation}
+      \tfrac{1}{\sqrt{\gamma
+          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*(\hat\beta_{T+1}) 
+      = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2})
+    \end{equation}
+    where $\Omega^*(\beta) = \var^* h_t^*(\beta)$.  Since
+    $\hat\beta_{T+1} \to^p \beta_0$, it suffices to show that
+    $\sup_{\beta \in N} | \Omega^*(\beta) - \var h_t(\beta) | \to^p
+    0$.  But this convergence holds for any fixed $\beta$ and our
+    assumptions guarantee stochastic equicontinuity as in
+    \citet{JoD:00} \citep[also see][]{Dav:94}, completing the proof.
+
   \item We have
@@
       P^a \sup_t | \hat{\beta}_t - \beta_0 | = P^a \sup_t |\hat{B}_{t}
-      H_{t}| \\ \leq \sup_{t,u \in S_T} \Big| [ \hat{B}_u - B]
-      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
-      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
+      H_{t}| \\ \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
+      \tfrac{P^a}{t} \sum_{s=1}^t h_{s}(\beta_0) \Big| + \sup_{t} \Big|
+      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s}(\beta_0) \Big|
     \end{multline}
@@
     the previous argument and by assumption.  The same argument holds
-    for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ as well.
+    for $\hat{\beta}_t^{*} - \btrue[*]$ as well.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
+    \big(\tfrac{\partial}{\partial \beta} f_t(\beta_0) - F\big)$ obeys
+    \citepos{Jon:97} \clt, so the result is trivial.  Also,
+   \begin{equation}
+     \Big\{\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T 
+     \big(\tfrac{\partial}{\partial \beta} f_t^*(\hat\beta_{T+1}) -
+     F^*\big)\Big\} = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2}) = O_p(1)
+    \end{equation}
+    as in the proof of part 1, where now $\Omega^*(\beta) = \var^*
+    \tfrac{\partial}{\partial \beta} f_t^*(\beta)$.
   \end{enumerate}
@@
 \begin{lema}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:3}, \eqref{eq:7},
-  \eqref{eq:9}, and \eqref{eq:10} hold.
+  Under the conditions of Theorem~\ref{res:3}, Equations
+  \eqref{eq:7}--\eqref{eq:10} and \eqref{eq:11}--\eqref{eq:13} hold.
 \end{lema}
-\noindent For each of these results, I will present the proof for the
-recursive window and the circular block bootstrap only; extensions to
-the fixed and rolling window follow exactly as in \citet{WeM:98}.
 
@@
 \begin{equation*}
-  \Big\lvert \WesA \Big\rvert \leq 
-  \Big\lvert \oclt{t} (\nabla f_t^*(\hat\beta_T) - F^*) B^* \Big\rvert
+  \Big\lvert \WesA[*] \Big\rvert \leq 
+  \Big\lvert \oclt{t} (\nabla f_t^*(\hat\beta_{T+1}) - F^*) B^* \Big\rvert
   \sup_t | H_t^* |.
 \end{equation*}
-From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$; $\oclt{t} (\nabla
-f_t^*(\hat\beta_T) - F^*)$ obeys a \clt\ \citep{Cal:11d} and is
-$O_{p^*}(1)$, establishing~\eqref{eq:7}.  The proofs of~\eqref{eq:9}
-and~\eqref{eq:10} are similar.
+From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$ and $\oclt{t}
+(\nabla f_t^*(\hat\beta_{T+1}) - F^*) = O_p(1)$,
+establishing~\eqref{eq:7}.  The proofs of~\eqref{eq:9}, \eqref{eq:10},
+and \eqref{eq:11}--\eqref{eq:13} are similar.
 \end{proof}
@@
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}(\hat\beta_T)
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}(\hat\beta_{T+1})
     \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}(\beta_0)
@@
   \end{equation}
-  for all positive $\epsilon$.
+  for all positive $\epsilon$, where the inequality holds element-by-element.
 \end{lema}
@@
 \begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that both $\psi_t(\beta_0)$ and $\psi_t^*(\hat\beta_T)$ satisfy
+  Note that both $\psi_t(\btrue)$ and $\psi_t^*(\btrue[*])$ satisfy
   \clt s, (\citealp[Theorem~2]{Jon:97} and
   \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \Big( \osum{t} \psi_t^*( \hat
-  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \osum{t} \psi_t(
-  \beta_0 ) \Big) \to^p 0. \]
-  I will prove this result for the Circular Block Bootstrap
+  \[ \tfrac{ 1 }{ P } \var^* \Big( \osum{t} \psi_t^*(\btrue[*])) \Big)
+  - \tfrac{ 1 }{ P } \var \Big( \osum{t} \psi_t(\btrue) \Big) \to^p
+  0. \] I will prove this result for the Circular Block Bootstrap
   \citep{PoR:92}---the proof for other block bootstraps is similar and
@@
 
-  Since $\E^* \psi_t^*( \hat \beta_T ) = 0$ by construction, we have
+  Since $\E^* \psi_t^*( \hat \beta_{T+1} ) = 0$ by construction, we have
   \begin{equation}\label{eq:3}
-  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_T ) \Big)
-  = \su \hat \psi_s( \hat \beta_T ) \hat \psi_t( \hat \beta_T )'
+  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_{T+1} ) \Big)
+  = \su \hat \psi_s( \hat \beta_{T+1} ) \hat \psi_t( \hat \beta_{T+1} )'
   \end{equation}
@@
   \begin{multline}\label{eq:6}
-    \su \psi_s(\hat\beta_T) \psi_t(\hat\beta_T)'
-    = \tfrac{1}{T} \sum_{s,t=1}^T \psi_s(\hat\beta_T) \psi_t(\hat\beta_T)' \;
+    \su \psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})'
+    = \tfrac{1}{T} \sum_{s,t=1}^T \psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})' \;
       \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ \\
       + \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        (\psi_s(\hat\beta_T) \psi_t(\hat\beta_T)' +
-         \psi_t(\hat\beta_T) \psi_s(\hat\beta_T)') \;
+        (\psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})' +
+         \psi_t(\hat\beta_{T+1}) \psi_s(\hat\beta_{T+1})') \;
         \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+.
@@
   The first term of \eqref{eq:6} can be shown to converge in
-  probability to $(1/P) \var \osum{t} \psi_t( \beta_0 )$
+  probability to $(1/P) \var \osum{t} \psi_t(\btrue)$
   by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
-  hold by assumption and it suffices to prove their condition (2.9)
+  hold by assumption and it remains to prove their condition (2.9)
   holds, namely that
@@
     \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} -
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg) 
     \Bigg\rVert_2 \to 0
   \end{equation}
-  for all $i$, $j$, and $\xi$.  Now, for any fixed $\beta \in N$,
+  for all $j$, $k$, and $\xi$.  For any fixed $\beta \in N$,
   \begin{equation*}
     \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg)
     \to^p 0
@@
     \tfrac{1}{T} \sum_{t=1}^T \sin( \xi t / b )
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
+    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
+          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg)
     \to^p 0
@@
     17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
-  follows from the existence of the $r$th moment and uniform
-  convergence is a consequence of the bounded second derivative of
-  $\psi_t$.
+  follows from the existence of the $r$th moment ($r > 2$) and uniform
+  convergence is a consequence of our bound on the second derivative
+  of $\psi_t$.
 
@@
   $o_p(1)$.  We have, for each element of that matrix,
-  \begin{multline}
+  \begin{multline*}
     \Big| \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        \psi_{is}(\hat\beta_T) \psi_{jt}(\hat\beta_T)
+        \psi_{ks}(\hat\beta_{T+1}) \psi_{jt}(\hat\beta_{T+1})
         \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+ \Big| \leq\\
-     \tfrac{1}{T} \sum_{s = 1}^{b - 1} |\psi_{is}(\hat\beta_T)|
-         \times\tfrac{1}{b} \sum_{t = T - b + 1}^{T} | \psi_{jt}(\hat\beta_T) |
-  \end{multline}
-  almost surely.  Now, for any positive $\delta$,
+     \tfrac{1}{b T} \sum_{s = 1}^{b - 1} |\psi_{ks}(\hat\beta_{T+1})|
+         \sum_{t = T - b + 1}^{T} | \psi_{jt}(\hat\beta_{T+1}) |
+  \end{multline*}
+  almost surely.  For any positive $\delta$,
   \begin{equation*}
-    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \psi_{is}( \hat \beta_T ) |
+    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \psi_{is}( \hat \beta_{T+1} ) |
               > \delta \Bigg] \leq 
@@
               > \delta \Bigg] +
-    \pr \big[ \hat \beta_T \notin N \big].
+    \pr \big[ \hat \beta_{T+1} \notin N \big].
   \end{equation*}
   Both terms converge to zero by assumption, so $\tfrac{1}{T} \sum_{s
-    = 1}^{b - 1} |\psi_{is}(\hat\beta_T)| = o_p(1)$.  A similar
+    = 1}^{b - 1} |\psi_{is}(\hat\beta_{T+1})| = o_p(1)$.  A similar
   argument shows that $\tfrac{1}{b} \sum_{t = T - b + 1}^{T} |
-  \psi_{jt}(\hat\beta_T) | = O_p(1)$, completing the proof.
+  \psi_{jt}(\hat\beta_{T+1}) | = O_p(1)$, completing the proof.
 \end{proof}
@@
     \oclt{t}
-    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
+    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\btrue)) \to^d N(0, \sigma^2),
   \end{equation}
-  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
+  with 
+  \begin{align}
+  \sigma^2 &= S_{ff} + \lambda_{fh} (F B S_{fh}' + S_{fh} B' F') + 2 \lambda_{hh} F V_\beta F' \\
+  (\lambda_{fh}, \lambda_{hh}) &= 
+  \begin{cases}
+    (1, 2) \times \big(1 - \tfrac{1}{\pi} \ln(1 + \pi)\big) 
+      & \text{recursive window} \\
+    \big(\tfrac{\pi}{2}, \pi - \tfrac{\pi^2}{3}\big)
+      & \text{rolling window with $\pi \leq 1$} \\
+    \big(1 - \tfrac{1}{2\pi}, 1 - \tfrac{1}{3\pi}\big)
+      & \text{rolling window with $\pi > 1$} \\
+    (0, \pi) & \text{fixed window},
+  \end{cases}
+  \end{align}
+  $\Big(\begin{smallmatrix}S_{ff} & S_{fh} \\ S_{fh}' &
+    S_{hh} \end{smallmatrix} \Big)$ the asymptotic variance of $(\bar
+  f(\btrue)', \bar h(\btrue)')'$, and $V_\beta$ the asymptotic
+  variance of~$\hat\beta_{T+1}$.
 \end{lema}
-\begin{proof}[Proof of Lemma~\ref{res:a5}]
-  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}, using
-  the previous results in this appendix as substitutes where the
-  original proof requires stronger moment or weak dependence
-  conditions.
+
+\begin{proof}[Proof of Theorem~\ref{res:3}]
+  As in \citet{Wes:96} and \citet{WeM:98} (and as in the proof of
+  Theorem~\ref{res:3}), expand $f_t(\hat{\beta}_t^{*})$ around
+  $\btrue$ to get
+  \begin{align*}
+    \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
+    \big(f_t(\btrue) - \E f_t(\btrue)\big) +
+    F B \oclt{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
+  \end{align*}
+  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
+  \begin{equation*}
+    w_{it} = \tfrac12 (\hat\beta_t - \btrue)'
+    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
+    f_{it}(\tilde\beta_{it}) \Big]
+    (\hat\beta_t - \btrue)
+  \end{equation*}
+  and each $\tilde\beta_{it}$ lies between $\hat\beta_t$ and
+  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
+  Then, again,
+  \begin{gather}
+    \WesA \to^{p} 0 \label{eq:11} \\
+    \WesB \to^{p} 0 \label{eq:12}\\
+  \intertext{and}
+    \WesC \to^{p} 0 \label{eq:13}
+  \end{gather}
+  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
+  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}. Since
+  $f_t(\btrue)$ and $H_t$ both satistfy \clt s, this completes the
+  proof.
 \end{proof}
@@
 % LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt
-%  LocalWords:  stationarity mixingale mixingales texextra
+% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
+% LocalWords:  stationarity mixingale mixingales texextra Timmermann

### 2013-03-12 R/ap.R
Fix LaTeX macros for variables in empirics design
The code to write the (for example) number of bootstrap simulations as a
LaTeX macro was imposing two decimal points, which looked moronic.  So
I've changed it to write integers as integers.

@@ -87,10 +87,14 @@ results.data$predictor <- gsub(" \\.CT", "(\\\\textsc{ct})", results.data$predic
 results.data$predictor <- gsub("\\.", " ", results.data$predictor)
 names(results.data)[1] <- " "
 
+
+integer.macros <- c(nboot = nboot, bootsize = 100 * bootsize,
+                       windowlength = windowlength)
+real.macros <- c(empiricalcriticalvalue = stepm.results$rightcrit)
+
 cat(file = "tex/ap.tex", sep = "\n",
-    sprintf("\\newcommand{\\%s}{%.2f}",
-            c("empiricalcriticalvalue", "nboot", "bootsize", "windowlength"),
-            c(stepm.results$rightcrit, nboot, 100 * bootsize, windowlength)),
+    sprintf("\\newcommand{\\%s}{%.2f}", names(real.macros), real.macros),
+    sprintf("\\newcommand{\\%s}{%d}", names(integer.macros), integer.macros),
     sprintf("\\newcommand{\\empiricaltable}{%s}",
             booktabs(results.data, align = c("l", rep("C", 3)), 
                      numberformat = c(FALSE, TRUE, FALSE, FALSE),

### 2013-03-12 R/mc2Table.R
Remove design 2 of second monte carlo from paper
I've changed the code that generates the LaTeX table for MC 2 so that it only displays
the first set of results; the second set of parameters gave basically the same results
as the first.

@@ -1,41 +1,57 @@
-# Copyright (c) 2011-2013 Gray Calhoun.
+## Copyright (c) 2011-2013 Gray Calhoun.
 
-# This program is free software: you can redistribute it and/or modify it under 
-# the terms of the GNU General Public License as published by the Free Software 
-# Foundation, either version 3 of the License, or (at your option) any later 
-# version.
+## This program is free software: you can redistribute it and/or
+## modify it under the terms of the GNU General Public License as
+## published by the Free Software Foundation, either version 3 of the
+## License, or (at your option) any later version.
 
-# This program is distributed in the hope that it will be useful, but WITHOUT 
-# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS 
-# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more 
-# details.
+## This program is distributed in the hope that it will be useful, but
+## WITHOUT ANY WARRANTY; without even the implied warranty of
+## MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+## General Public License for more details.
 
-# You should have received a copy of the GNU General Public License along with 
-# this program.  If not, see <http://www.gnu.org/licenses/>.
+## You should have received a copy of the GNU General Public License
+## along with this program.  If not, see
+## <http://www.gnu.org/licenses/>.
 
 source("R/mcSetup.R")
 library(dbframe, lib.loc = "lib")
 mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
 		   dbname = "data/mcdata.db", readonly = TRUE)
 
-colsql <- lapply(1:2, function(i) {
-  c("'Sim. type'" =
-      sprintf("case when simulationtype = '0.size' then 'size %d'
-                    else 'power %d' end", i, i),
-    R = "R", P = "P",
-    "'Pr[\\textsc{cw}~roll.]'" =
-      sprintf("100 * avg(clarkwestrolling%d <= %f)", i, testsize),
-    "'Pr[\\textsc{cw}~rec.]'" =
-      sprintf("100 * avg(clarkwestrecursive%d <= %f)", i, testsize),
-    "'Pr[new]'" = sprintf("100 * avg(mixed%d <= %f)", i, testsize))
-})
[…]

### 2013-03-14 Paper.tex
Edit text of paper
This commit makes a lot of minor edits to the text of the paper and the math.

@@
 Test instead of an \textsc{lm} or Wald test, which depend on just the
-restricted or unrestricted model respectively.  Simulations presented
-in Section~\ref{sec:2} show that this approach gives a substantial
-power advantage when there are breaks.
+restricted or unrestricted model respectively.
 
@@
 As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
-individual tests is misleading, but researchers can get a valid test
+individual tests is misleading, but researchers can obtain a valid test
 by using the bootstrap to approximate the distribution of the largest
@@
 (Theorem~\ref{res:1} lists the assumptions formally).  In addition,
-let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
+let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
 coefficient of the regression of $y_{t+1}$ on $x_t$ and define
-$\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model is
+$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
 correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
@@
   \label{eq:4}
-  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\beta_0)
+  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
 \end{equation}
@@
   \label{eq:5}
-  \tfrac{2}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
-  x_t'\beta_0) = \oclt{t} \Big[(y_{t+1} - 
-  x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
+  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
+  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
+  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
 \end{equation}
@@
 positive, so the sum obeys a \clt.  This method of ensuring normality
-was introduced by \citet{GiW:06}.  The coefficients $\beta_0$ are
+was introduced by \citet{GiW:06}.  In \citet{ClW:06}, the coefficients $\btrue$ are
 assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
@@
 to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
-$\mathcal{F}_t$.  In \citet{ClW:07}, $\beta_0$ is unknown but is
+$\mathcal{F}_t$.  In \citet{ClW:07}, $\btrue$ is unknown but is
 estimated with a fixed-length rolling window as well, so
@@
 This paper proposes using the same basic \oos\ statistic, 
-but using a recursive window to estimate $\beta_0$ and produce
+but using a recursive window to estimate $\btrue$ and produce
 $\hat{\varepsilon}_{t+1}$; i.e.
@@
     predictors $x_t$ with $\hat{\beta}_t$ given by
-    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
-    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
+    Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
+    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not depend
     on~$t$.
@@
     (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
+    $f_t = f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$,
     $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
-    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
-    $\bar f(\beta_0)$ has uniformly positive and finite long run
+    = \tfrac1P \sum_{t=R+1}^{T} \hat f_t$, with $P = T - R$;
+    $\bar f(\btrue)$ has uniformly positive and finite long run
     variance.
   \end{enumerate}
-  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
+  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
   martingale difference sequence with respect to the filtration
@@
     \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
-    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
-    f)^2, \\
-    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
-    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
-    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
-    g)(g_t(\hat{\beta}_t) - \bar g)',
+    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
+    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
+    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
   \end{align*}
-  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
-  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
+  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
+  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
   \begin{equation*}
@@
     \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
-    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
+    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
   \end{equation*}
+  and $\hat g_t = g_t(\hat\beta_t)$.
 \end{thm}
@@
   Forecasters are usually interested in the one-sided alternative that
-  $\E f_t(\beta_0) > 0$; i.e. that the alternative model is expected
+  $\E f_t > 0$; i.e. that the alternative model is expected
   to forecast better than the benchmark.
@@
 \begin{rem}
-  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
+  The requirement that the asymptotic variance of $\bar f(\btrue)$ is
   uniformly positive is much less restrictive than in \cite{Wes:96}.
@@
   serves to rule out pathological cases---for example, letting both
-  the benchmark and the alternative model be white noise. In
+  the benchmark and the alternative model be perfectly correlated white noise. In
   \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
@@
 \begin{rem}
-  If one wants to test the less restrictive null hypothesis that
-  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
-  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
-  and $\hat{S}_{gg}$ with their \hac\ counterparts.
-  Lemma~\ref{res:a5} presents a more general version of the theorem
-  that can cover this case.
-\end{rem}
-
-\begin{rem}
   The statistic we present tests the null hypothesis that the forecast
@@
   appropriate, depending on the loss function or utility function of
-  interest.  Our statistic can be modified to test implications of
+  interest.  If one wants to test the less restrictive null hypothesis that
+  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
+  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
+  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
+  Our statistic can also be modified to test implications of
   optimal forecasts under other loss functions
@@
   same coefficient estimates and the estimation uncertainty introduced
-  by those estimates does not vanish when $R$ is bounded.  One can
+  by those estimates does not vanish asymptotically when $R$ is bounded.  One can
   prove that their results apply to fixed window forecasts by using a
@@
   we would need to account for the existence of multiple models even if
-each paper considers a single model, since there are many papers
+each paper only considered a single model, since there are many papers
 studying the same data.}  It can, however, be
 used as the basis for a procedure that allows researchers to make
-multiple comparisons.  Before presenting a theoretical result, I'll
+multiple comparisons.  Before presenting a theoretical result, I will
 discuss some issues related to multiple hypothesis testing.
@@
 (\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
-even though the papers only prove \wfwe, statistics based on
+even though these papers only prove \wfwe, statistics based on
 nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
@@
 control \sfwe\ if the individual null hypotheses are strengthened
-slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
+slightly as below (see conclusion~\ref{it:1} of Theorem~\ref{res:2} as
 well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
 construct critical values from the asymptotic joint distribution of
-the test statistics and can control \sfwe\ as long as there is a
+the test statistics and this procedure can control \sfwe\ as long as there is a
 consistent estimator of that distribution.
@@
 bootstrap sample so that population means under the bootstrap-induced
-probability distribution equal sample means.  The benchmark model
-still needs to be reestimated in each bootstrap sample.
+probability distribution equal sample means.\footnote{This equality is
+  strictly true only for the stationary and circular block
+  bootstraps.}  The benchmark model still needs to be reestimated in
+each bootstrap sample.
 
@@
   variance-covariance matrix of the vector
-  $(\bar{f}_1(\beta_0),\dots,\bar{f}_m(\beta_0))'$ is uniformly
+  $(\bar{f}_1(\btrue),\dots,\bar{f}_m(\btrue))'$ is uniformly
   positive definite.
@@
   \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
-    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
+    \{l : \tfrac1{\hat\sigma_l} \bar{f}_{l} > \hat{d}_j\}$, where
     $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
@@
     \bar{f_i}(\btrue[*]))$.
-  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
+  \item Reject all of the models $l$ with $l \in \bigcup_{j=1}^m M_j$.
   \end{enumerate}
   The following conclusions hold:
-  \begin{enumerate}[i.]
+  \begin{enumerate}
   \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
@@
     $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
-    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
+    f_i(\btrue) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
     \infty$ (for the stationary bootstrap) or $b \to \infty$ and
@@
     \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
-    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
+    one-sided alternative $\E \bar f_i(\btrue) > 0$.  If $p \to 0$
     and $P p \to \infty$ as $T \to \infty$ (for the stationary
@@
 \begin{rem}
+  The next section will discuss the block bootstrap procedures for
+  \oos\ comparisons in detail.  Note that $\bar f(\btrue[*])$ is the
+  bootstrap equivalent of $\E f_t(\btrue)$, hence its role as the
+  centering term in step 1 of the procedure.
+\end{rem}
+
+\begin{rem}
 It is worth emphasizing that this procedure is very easy to use under
-the null hypothesis of correct specification (Part~\ref{it:1}).  The
+the null hypothesis of correct specification (conclusion~\ref{it:1}).  The
 researcher can use a standard estimate of the statistic's asymptotic
@@
 \begin{rem}\label{rem:2}
-  The key difference between Parts~(\ref{it:1}) and~(\ref{it:2}) is
-  that, in Part~(\ref{it:2}), the forecast error is an \mds\ with
+  The key difference between conclusions~\ref{it:1} and~\ref{it:2} is
+  that, in conclusion~\ref{it:2}, the forecast error is an \mds\ with
   respect to several individual series, but not necessarily with
@@
     $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
-    This is essentially the scenario imposed in Part~(\ref{it:2}).}
+    This is essentially the scenario imposed in conclusion~\ref{it:2}.}
   Using $b = 1$ would consistently estimate the marginal distribution
@@
   the covariance could be wrong).  The stronger null hypothesis
-  imposed in Part~\ref{it:1} ensures that resampling with $b = 1$
+  imposed in conclusion~\ref{it:1} ensures that resampling with $b = 1$
   estimates the joint distribution correctly as well.
@@
   \citep[i.e.][]{ClM:12b} achieves control of \sfwe\ only under the
-  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
-  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
+  stronger hypotheses of conclusion~\ref{it:1}.  Fortunately,
+  conclusion~\ref{it:1} seems to capture the goals of most empirical work,
   so researchers can make use of the considerable simplifications that
@@
   or use a convenient but inconsistent approximation of the variance.
-  The estimator of the variance in Part~\ref{it:3} should have the
+  The estimator of the variance in conclusion~\ref{it:3} should have the
   best performance if it is \hac\ \cite[the results of][may be
@@
   If the number of alternative models is large, controlling the \fwe\
-  may be too strict a criterion.  \citet{RSW:08} discuss procedures to
+  may be too strict a criterion to be useful.  \citet{RSW:08} discuss procedures to
   control criteria other than the \fwe, and one can use their
@@
   Intersection-Union test, so Theorem~\ref{res:2}'s procedure
-  (Part~(\ref{it:3})) easily accommodates this extension by taking
+  (conclusion~\ref{it:3}) easily accommodates this extension by taking
   each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
@@
     it would be a mistake to assume that they are all correctly
-    specified, so only the null hypothesis of Part~(\ref{it:3}) is
+    specified, so only the null hypothesis of conclusion~\ref{it:3} is
     appropriate.} the first element of $\bar f_{i}$, written as $\bar
@@
   \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
-    \{(i,k): \tfrac1{\hat\sigma_{ik}} |\bar{f}_{ik}| > \hat{d}_j\}$,
-    where $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{(i,k)
-      \notin M_{j-1}} \tfrac1{\hat\sigma_{ik}^*} |\bar{f}_{ik}^{*} -
-    \bar{f}_{ik}(\hat{\beta}_{k,T+1})|$.
+    \{(i,k): \tfrac1{\hat\sigma_{ik}} \bar{f}_{ik} > \hat{d}_j\}$,
+    where $\hat{d}_j$ is the $1 - \alpha$ quantile of $\max_{(i,k)
+      \notin M_{j-1}} \tfrac1{\hat\sigma_{ik}^*} \big(\bar{f}_{ik}^{*} -
+    \bar{f}_{ik}(\hat{\beta}_{k,T+1})\big)$.
   \item Reject all of the hypotheses $H_i$ such that $(i,k) \in
@@
   \begin{enumerate}
-  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
+  \item The estimator $\hat{\beta}_t$ of $\btrue$ is estimated with a
     recursive, rolling, or fixed estimation window and satisfies
@@
       H_{t} = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
+        \tfrac1t \sum_{s=1}^t h_{s}(\btrue) & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\btrue) & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}(\btrue) & \text{fixed window} \\
       \end{cases}
     \end{equation}
-    and $\E h_{s}(\beta_0) = 0$ for all $s$.
+    and $\E h_{s}(\btrue) = 0$ for all $s$.
   \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
     $\psi_t(\beta)$ is covariance stationary and twice continuously
-    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
+    differentiable in an open neighborhood $N$ of $\btrue$.  Also,
     $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
@@
       integrable.}
-  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
+  \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
+    using the same procedure as the original \oos\ analysis over the
+    bootstrap sample, where the bootstrap sample is generated by
     moving blocks, circular blocks, or stationary bootstrap with block
@@
   \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
-    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
-  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
+    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T
+    h_t^*(\btrue[*]) = 0$ a.s.
+  \item The asymptotic variance matrix of $\bar{f}(\btrue)$ is
     uniformly positive definite.
@@
     \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
-        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
+        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
       \epsilon] \to 0
@@
   proof relies on a theorem of \citepos{JoD:00} establishing the
-  consistency of \hac\ estimators which requires differentiability of
+  consistency of \hac\ estimators and their theorem requires differentiability of
   the observations.  Extending \citepos{JoD:00} result to
@@
   \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
-  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\btrue[*])$
-  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
+  \bar{f}(\btrue))$.  But it is clear that $\bar{f}(\btrue[*])$
+  is the bootstrap analogue of $\E \bar{f}(\btrue)$, the parameter of
   interest.  Because their bootstrap is miscentered, \citet{CoS:07}
@@
 \begin{rem}
-  It may be unnecessary to assume that $\bar{f}(\beta_0)$ has positive
+  It may be unnecessary to assume that $\bar{f}(\btrue)$ has positive
   definite asymptotic variance; if so, the bootstrap would work in the
@@
 \section{Monte Carlo Results}\label{sec:2}
-I'll conduct two brief Monte Carlo experiments to demonstrate that
+I will conduct two brief Monte Carlo experiments to demonstrate that
 this paper's modified version of \citepos{ClW:07} statistic performs
@@
 study.\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
-  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
-  \citep[version 0.2.1]{Cal:10b} packages.}  I'll use both of the \dgp
-s they consider as well as a modification to study the performance of
-the statistics if there is instability.
+  \citep[version 2.14.0]{R} and use the \textsc{MASS}
+  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
+  dbframe \citep[version 0.2.7]{Cal:10b} packages.}
 
@@
   proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
-  based on the naive Gaussian statistic.}  \citet{ClW:06,ClW:07} only
-look at the stable case.
+  based on the naive Gaussian statistic.}
 
@@
 \begin{align*}
-  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
-  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
+  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma_{1} z_{t-1} + \gamma_{2}
+  z_{t-2} + \gamma_{3} z_{t-3} + \gamma_{4} z_{t-4} + e_{t} \\
   z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
@@
   \Bigg) \nonumber\\\nonumber
-  \gamma^{*} &=
+  \gamma &=
   \begin{cases}
@@
 more undersized than the new test, but has a little higher power under
-the alternative.  Moreover, the statistics give different results in
-less than 10\% of the simulations for most parametrizations of the
-\dgp s.  In general, the statistics perform similarly well.
-
-For the simulations with a single break, the new statistic has about
-twice the power of \poscw\ original test.  For most parametrizations
-of \dgp\ 1, the new test rejects over 90\% of the time, while Clark
-and West's test rejects about 40\% of the time.  So mixing window
-strategies can give a substantial power advantage when testing for
+the alternative.  In general, the statistics perform similarly well.
+
+For the simulations with a single break, the new statistic modestly
+higher power than \poscw\ original test.  For most parametrizations of
+\dgp\ 1, the new test rejects over 90\% of the time, while Clark and
+West's test rejects about 40\% of the time.  So mixing window
+strategies can give a small power advantage when testing for
 time-varying predictability, and performs similarly to the original
@@
   \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
-  0.2.5]{Cal:10b} packages.}
+  0.2.7]{Cal:10b} packages.}
 
@@
   uses \nboot\ replications with i.i.d. sampling, as proposed in
-  Part~(\ref{it:1}) of Theorem~\ref{res:2}.}  Three predictors are
+  conclusion~\ref{it:1} of Theorem~\ref{res:2}.}  Three predictors are
 significant at the naive critical values for both the original and
@@
 
+Define the additional notation 
+$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
+$F_t = F_t(\btrue)$,
+$\hat f_t^* = f_t^*(\hat\beta_t^*)$,
+$F_t^*(\beta) = \tfrac{\partial}{\partial \beta} f_t^*(\beta)$,
+$F_t^* = F_t^*(\btrue[*])$,
+$h_t = h_t(\btrue)$,
+$h_t^* = h_t^*(\btrue[*])$, 
+and
+\begin{equation*}
+      H_{t}^* = \begin{cases} 
+        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
+        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
+        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
+      \end{cases}
+\end{equation*}
+
 \begin{proof}[Proof of Theorem \ref{res:1}]
@@
   distribution; the theorem is now an immediate consequence of
-  Lemma~\ref{res:a5}.  Note that \[f_t(\beta_0)= 2 (y_{t+1} -
-  x_t'\beta_0)(\hat{y}_{1,t+1} - x_t'\beta_0) \quad \text{a.s.},\] as
+  Lemma~\ref{res:a5} with $h_t(\beta) = x_t (y_{t+1} - x_t'\beta)$.
+  Note that \[f_t(\btrue)= 2 (y_{t+1} -
+  x_t'\btrue)(\hat{y}_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
   in \citet{ClW:07}, which is an \mds, so we do not need to use a
-  \hac\ estimator of the variance under the null.
+  \hac\ estimator of the variance under the null.  Also observe that
+  \[F_t(\beta) = 2 x_t(x_t'\beta - \hat y_{1,t+1}) + 2 x_t(x_t'\beta -
+  y_{t+1})\] and the second term is an \mds\ under the null,
+  explaining the particular form of $g_t(\beta)$.
 \end{proof}
@@
 
-\newcommand{\WesA}[1][]{\oclt{t} (\nabla
-  f_t^{#1}(\btrue[#1]) - F^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} F^{#1} \osum{t} (B_t^{#1} -
+\newcommand{\WesA}[1][]{\oclt{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
   B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\oclt{t} (\nabla
-  f_t^{#1}(\btrue[#1]) - F^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
+\newcommand{\WesC}[1][]{\oclt{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
 \begin{proof}[Proof of Theorem~\ref{res:3}]
@@
     \sqrt{P} \big(\bar{f}^{*} - \bar{f}(\btrue[*])\big) &= \oclt{t}
-    \big(f_t^{*}(\btrue[*]) - \bar{f}(\btrue[*])\big) +
-    F^{*} B^{*} \oclt{t} H_t^* \\
+    \big(f_t^{*} - \bar{f}(\btrue[*])\big) +
+    \E^* F_t^{*} B^{*} \oclt{t} H_t^* \\
     & \quad + \WesA[*] + \WesB[*] \\ & \quad + \WesC[*] + \oclt{t} w_t^*
@@
 \begin{lem}[Formalization of Remark~\ref{rem:01}]
-  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
+  Suppose that the conditions of Theorem~\ref{res:2} conclusion~\ref{it:3}
   hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
@@
     \to^{p^{*}} 0$.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
-    \big(\tfrac{\partial}{\partial \beta} f_t(\beta_0) - F\big) =
-    O_{p}(1)$ and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
-    \big(\tfrac{\partial}{\partial \beta} f_t^*(\hat\beta_{T+1}) -
-    F^*\big) = O_{p^*}(1)$.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$
+    and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t^* - \E F_t^*) =
+    O_{p^*}(1)$.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item The process $\tfrac{1}{\sqrt{T}} h_{s}(\beta_0)$ satisfies
+  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
     \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
     \begin{equation}
-      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) \Big| =
+      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
       P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
-        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}(\beta_0) \Big| \to^{p} 0
+        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
     \end{equation}
     with the convergence following from the continuous mapping
-    theorem.  For the bootstrapped average, \citepos{Cal:11d}
+    theorem.  For the bootstrapped average, \citepos{Cal:13}
     Theorem~2 ensures that
@@
       \tfrac{1}{\sqrt{\gamma
-          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*(\hat\beta_{T+1}) 
+          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*
       = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2})
@@
     where $\Omega^*(\beta) = \var^* h_t^*(\beta)$.  Since
-    $\hat\beta_{T+1} \to^p \beta_0$, it suffices to show that
+    $\hat\beta_{T+1} \to^p \btrue$, it suffices to show that
     $\sup_{\beta \in N} | \Omega^*(\beta) - \var h_t(\beta) | \to^p
@@
     \begin{multline}
-      P^a \sup_t | \hat{\beta}_t - \beta_0 | = P^a \sup_t |\hat{B}_{t}
+      P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
       H_{t}| \\ \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
-      \tfrac{P^a}{t} \sum_{s=1}^t h_{s}(\beta_0) \Big| + \sup_{t} \Big|
-      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s}(\beta_0) \Big|
+      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
+      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
     \end{multline}
@@
     for $\hat{\beta}_t^{*} - \btrue[*]$ as well.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
-    \big(\tfrac{\partial}{\partial \beta} f_t(\beta_0) - F\big)$ obeys
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
     \citepos{Jon:97} \clt, so the result is trivial.  Also,
    \begin{equation}
-     \Big\{\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T 
-     \big(\tfrac{\partial}{\partial \beta} f_t^*(\hat\beta_{T+1}) -
-     F^*\big)\Big\} = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2}) = O_p(1)
+     \Big\lvert\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T 
+     ( F_t^* - \E^* F^*)\Big\rvert = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2}) = O_p(1)
     \end{equation}
-    as in the proof of part 1, where now $\Omega^*(\beta) = \var^*
-    \tfrac{\partial}{\partial \beta} f_t^*(\beta)$.
+    as in the proof of part 1, where now $\Omega^*(\beta) = \var^* F_t^*(\beta)$.
   \end{enumerate}
@@
   \Big\lvert \WesA[*] \Big\rvert \leq 
-  \Big\lvert \oclt{t} (\nabla f_t^*(\hat\beta_{T+1}) - F^*) B^* \Big\rvert
+  \Big\lvert \oclt{t} (F_t^* - \E^* F^*_t) B^* \Big\rvert
   \sup_t | H_t^* |.
@@
 From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$ and $\oclt{t}
-(\nabla f_t^*(\hat\beta_{T+1}) - F^*) = O_p(1)$,
-establishing~\eqref{eq:7}.  The proofs of~\eqref{eq:9}, \eqref{eq:10},
-and \eqref{eq:11}--\eqref{eq:13} are similar.
+(F_t^* - \E^* F_t^*) = O_p(1)$, establishing~\eqref{eq:7}.  The proofs
+of~\eqref{eq:9}, \eqref{eq:10}, and \eqref{eq:11}--\eqref{eq:13} are
+similar.
 \end{proof}
@@
 \begin{lema}\label{res:a3}
-  Suppose the conditions of Theorem~\ref{res:3} hold and let
+  Suppose the conditions of Theorem~\ref{res:3} hold, let
   \[\psi_t^{*}(\beta) = 
-  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
-  Then
+  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)},\]
+  and define $\psi_t = \psi_t(\btrue)$, $\hat\psi_t = \psi_t(\btrue[*])$, and 
+  $\psi_t^* = \psi_t^*(\btrue[*])$.  Then
   \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}(\hat\beta_{T+1})
-    \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}(\beta_0)
+    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}
+    \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}
     \leq x \Big] \Big| > \epsilon \Big] \to 0
   \end{equation}
-  for all positive $\epsilon$, where the inequality holds element-by-element.
+  for all positive $\epsilon$, where the inequalities hold element-by-element.
 \end{lema}
@@
 \begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that both $\psi_t(\btrue)$ and $\psi_t^*(\btrue[*])$ satisfy
+  Note that both $\psi_t$ and $\psi_t^*$ satisfy
   \clt s, (\citealp[Theorem~2]{Jon:97} and
-  \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \Big( \osum{t} \psi_t^*(\btrue[*])) \Big)
-  - \tfrac{ 1 }{ P } \var \Big( \osum{t} \psi_t(\btrue) \Big) \to^p
+  \citealp[Theorem~1]{Cal:13}) so it suffices to prove that
+  \[ \tfrac{ 1 }{ P } \var^* \osum{t} \psi_t^* 
+  - \tfrac{ 1 }{ P } \var \osum{t} \psi_t \to^p
   0. \] I will prove this result for the Circular Block Bootstrap
   \citep{PoR:92}---the proof for other block bootstraps is similar and
-  follows as in \cite{Cal:11d}.
+  follows as in \cite{Cal:13}.
 
@@
 
-  Since $\E^* \psi_t^*( \hat \beta_{T+1} ) = 0$ by construction, we have
+  Since $\E^* \psi_t^* = 0$ by construction, we have
   \begin{equation}\label{eq:3}
-  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_{T+1} ) \Big)
-  = \su \hat \psi_s( \hat \beta_{T+1} ) \hat \psi_t( \hat \beta_{T+1} )'
+  \tfrac{ 1 }{ P } \var^* \sum_{ t = R + 1 }^T \psi_t^*
+  = \su \hat \psi_s \hat \psi_t'
   \end{equation}
@@
   \begin{multline}\label{eq:6}
-    \su \psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})'
-    = \tfrac{1}{T} \sum_{s,t=1}^T \psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})' \;
+    \su \hat\psi_s \hat\psi_t'
+    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
       \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ \\
       + \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        (\psi_s(\hat\beta_{T+1}) \psi_t(\hat\beta_{T+1})' +
-         \psi_t(\hat\beta_{T+1}) \psi_s(\hat\beta_{T+1})') \;
+        (\hat\psi_s \hat\psi_t' +
+         \hat\psi_t \hat\psi_s') \;
         \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+.
@@
   The first term of \eqref{eq:6} can be shown to converge in
-  probability to $(1/P) \var \osum{t} \psi_t(\btrue)$
-  by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
+  probability to $\tfrac{1}{P} \var \osum{t} \psi_t$ by Theorem 2.2 of
+  \citet{JoD:00}.  Most of the necessary conditions of their theorem
   hold by assumption and it remains to prove their condition (2.9)
@@
   $o_p(1)$.  We have, for each element of that matrix,
-  \begin{multline*}
+  \begin{equation*}
     \Big| \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        \psi_{ks}(\hat\beta_{T+1}) \psi_{jt}(\hat\beta_{T+1})
-        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+ \Big| \leq\\
-     \tfrac{1}{b T} \sum_{s = 1}^{b - 1} |\psi_{ks}(\hat\beta_{T+1})|
-         \sum_{t = T - b + 1}^{T} | \psi_{jt}(\hat\beta_{T+1}) |
-  \end{multline*}
+        \hat\psi_{ks} \hat\psi_{jt}
+        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+ \Big| \leq
+     \tfrac{1}{b T} \sum_{s = 1}^{b - 1} |\hat\psi_{ks}|
+         \sum_{t = T - b + 1}^{T} | \hat\psi_{jt} |
+  \end{equation*}
   almost surely.  For any positive $\delta$,
   \begin{equation*}
-    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \psi_{is}( \hat \beta_{T+1} ) |
+    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \hat\psi_{is} |
               > \delta \Bigg] \leq 
@@
   Both terms converge to zero by assumption, so $\tfrac{1}{T} \sum_{s
-    = 1}^{b - 1} |\psi_{is}(\hat\beta_{T+1})| = o_p(1)$.  A similar
+    = 1}^{b - 1} |\hat\psi_{is}| = o_p(1)$.  A similar
   argument shows that $\tfrac{1}{b} \sum_{t = T - b + 1}^{T} |
-  \psi_{jt}(\hat\beta_{T+1}) | = O_p(1)$, completing the proof.
+  \hat\psi_{jt} | = O_p(1)$, completing the proof.
 \end{proof}
@@
 \begin{lema}\label{res:a5}
-  If the conditions of Theorem~\ref{res:3} hold\footnote{The
-    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
+  If the conditions of Theorem~\ref{res:3}, except for those governing
+  the bootstrap process, hold then
   \begin{equation}
     \oclt{t}
-    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\btrue)) \to^d N(0, \sigma^2),
+    (\hat f_t - \E f_t) \to^d N(0, \sigma^2),
   \end{equation}
@@
   f(\btrue)', \bar h(\btrue)')'$, and $V_\beta$ the asymptotic
-  variance of~$\hat\beta_{T+1}$.
+  variance of~$\btrue[*]$.
 \end{lema}
@@
   As in \citet{Wes:96} and \citet{WeM:98} (and as in the proof of
-  Theorem~\ref{res:3}), expand $f_t(\hat{\beta}_t^{*})$ around
+  Theorem~\ref{res:3}), expand $\hat f_t$ around
   $\btrue$ to get
@@
     \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
-    \big(f_t(\btrue) - \E f_t(\btrue)\big) +
-    F B \oclt{t} H_t \\
+    \big(f_t - \E f_t\big) +
+    \E F_t B \oclt{t} H_t \\
     & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
@@
   $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
-  Then, again,
+  Then, as before,
   \begin{gather}
@@
   be derived exactly as in \citet{Wes:96} and \citet{WeM:98}. Since
-  $f_t(\btrue)$ and $H_t$ both satistfy \clt s, this completes the
+  $f_t$ and $H_t$ both satisfy \clt s, this completes the
   proof.

### 2013-03-14 Paper.tex
Add structural break to MC
Change the first monte carlo to add a structural break set of simulation; they
reflect really well on my statistic.  I also removed the second set of simulations
from the paper (the code is still there, but it's off the dependency path for the
pdf paper) since the first sims are so awesome.

@@
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-
+\onehalfspacing
 \bibliographystyle{abbrvnat}
@@
 The next section presents our new statistics and Section~\ref{sec:1b}
-our block bootstrap result.  Section~\ref{sec:2} presents two
+our block bootstrap result.  Section~\ref{sec:2} presents
 simulations that compare our pairwise \oos\ test to \poscw\ original
-statistic.  Section~\ref{sec:3} demonstrates the use of our statistic
+statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
 by reanalyzing \citepos{GoW:08} study of excess return
@@
 \section{Monte Carlo Results}\label{sec:2}
-I will conduct two brief Monte Carlo experiments to demonstrate that
+This section presents Monte Carlo experiments demonstrating that
 this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they
-study.\footnote{All of these simulations were programmed in R
+similarly to their original test in the situations they study, but can
+have substantially higher power when the \dgp\ has a structural
+break.\footnote{All of these simulations were programmed in R
   \citep[version 2.14.0]{R} and use the \textsc{MASS}
@@
 
-The first \dgp\ has three different parametrizations; one to study the
+The \dgp\ has three different parametrizations: one to study the
 tests' size, one to study power under stationarity, and one to study
@@
 \begin{align*}
-  y_t &= 0.5 + \gamma^{*}_t z_{t-1} + e_t &
-  \gamma^{*}_t &=
+  y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t &
+  \gamma_t &=
   \begin{cases}
-    0    & \text{size simulations} \\
-    0.35 & \text{power (stable)} \\
-    0    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    0.70 & t > \tfrac{T}{2} \quad \text{power (break)}
+    (0.5, 0)    & \text{size simulations} \\
+    (0.5, 0.35) & \text{power (stable)} \\
+    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
+    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
   \end{cases}\\\nonumber
@@
    , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg).
+    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
+  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
 \end{align*}
@@
 on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  We use both \poscw\ original statistic and the new
-statistic to test the null that the benchmark model's innovation is an
-\mds.\footnote{\citet{ClW:07} report the performance of the tests
-  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
-  based on the naive Gaussian statistic.}
+$z_{t-1}$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
+pricing application similar to \citepos{GoW:08} which we study in
+Section~\ref{sec:3}.
+
+For comparison, we study this paper's new statistic as well as \poscw
+rolling-window and recursive-window test statistics.  Clark and West
+only prove that their rolling-window statistic is asymptotically
+normal, and only then if the benchmark model is not estimated, but
+their recursive-window statistic is popular in practice and in
+simulations tends to perform similarly to their rolling window test.
+We use all three of these statistics to test the null that the
+benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
+  report the performance of the tests proposed by \citet{CCS:01} and
+  \citet{ClM:05} as well, and of tests based on the naive Gaussian
+  statistic.}
 
@@
   \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
+  \caption{Size and power of the \oos\ tests in the simulations 
+    described by Section~\ref{sec:2}, at
     \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
-    and West's (2007) statistic rejects; Pr[new] shows the fraction of
-    simulations for which this paper's test rejects; and Pr[disagree]
-    gives the fraction of simulations in which this paper's test and
-    Clark and West's (2007) give different conclusions.}
+    samples.  Pr[\textsc{cw} roll.] shows the fraction of simulations for
+    which Clark and West's (2007) rolling-window statistic rejects; 
+    Pr[\textsc{cw} rec.] shows the fraction of simulations for which 
+    their recursive-window statistic rejects; and Pr[new] shows the fraction of
+    simulations for which this paper's test rejects.}
 \label{tab:mc1}
@@
 
-The second \dgp\ is
-\begin{align*}
-  y_{t} &= 2.237 + 0.261 y_{t-1} + \gamma_{1} z_{t-1} + \gamma_{2}
-  z_{t-2} + \gamma_{3} z_{t-3} + \gamma_{4} z_{t-4} + e_{t} \\
-  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
-  z_{t-4} + v_{t} \nonumber \\
-  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
-  \begin{pmatrix}
-    0 \\ 0
-  \end{pmatrix},
-  \begin{pmatrix}
-    10.505 & 1.036 \\ 1.036 & 0.366
-  \end{pmatrix}
-  \Bigg) \nonumber\\\nonumber
-  \gamma &=
-  \begin{cases}
-    0 & \text{size simulations}\\
-    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
-  \end{cases}
-\end{align*}
-The benchmark model for $y_{t}$ is an AR(1) and the alternative model
-includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
-120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
-first \dgp\ mimics an asset pricing application and the second mimics
-\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
-National Activity Index.
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc2}
-  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
-    and West's (2007) statistic rejects; Pr[new] shows the fraction of
-    simulations for which this paper's test rejects; Pr[disagree] gives
-    the fraction of simulations in which this paper's test and Clark and
-    West's (2007) give different conclusions.}
-\label{tab:mc2}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results for~\textsc{dgp}~1
-and Table~\ref{tab:mc2} for~\textsc{dgp}~2.  For all of the stable
-parameter values, the proposed new statistic has similar rejection
-probability to \citepos{ClW:07}.  Clark and West's test is slightly
-more undersized than the new test, but has a little higher power under
-the alternative.  In general, the statistics perform similarly well.
-
-For the simulations with a single break, the new statistic modestly
-higher power than \poscw\ original test.  For most parametrizations of
-\dgp\ 1, the new test rejects over 90\% of the time, while Clark and
-West's test rejects about 40\% of the time.  So mixing window
-strategies can give a small power advantage when testing for
+Table~\ref{tab:mc1} presents the simulation results.  For all of the
+stable parameter values, the proposed new statistic has similar
+rejection probability to \citepos{ClW:07}.  Both of Clark and West's
+tests are generally slightly undersized relative to our new test,
+which is itself slightly undersized: when $R$ is 120 and $P$ is 360
+our test statistic has size 7.6\% and Clark and West's rolling and
+recursive window tests have size 7.5\% and 6.2\% respectively, at a
+nominal size of 10\%.  For the stable alternative, our new statistic
+typically has slightly higher power than Clark and West's rolling
+window and lower power than their recursive window.  For example, when
+$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
+our statistic at 73.0\%, and the recrusive window statistic at 82.3\%,
+again for a nominal size of 10\%.  In general, the statistics perform
+similarly under stability.
+
+For the simulations with a single break, the new statistic has
+considerably higher power than \poscw\ original tests across all of
+the choices of $R$ and $P$; the rejection probability is more than
+twice as large for most parametrizations.  When $R$ is 120 and $P$ is
+360 with a nominal size of 10\%, for example, the new statistic
+rejects at 96.4\% while the rolling and recursive window statistics
+reject at 35.5\% and 32.9\% respectively.  Results for other choices
+of nominal size and sample split give similar results.  So mixing
+window strategies can give a large power advantage when testing for
 time-varying predictability, and performs similarly to the original
@@
 
-This section demonstrates the use of our new statistics by revisiting
+This section demonstrates the use of our new statistic by revisiting
 \citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
@@
 that the new statistic behaves similarly to Clark and West's original
-test when the \dgp\ is stable, suggesting that the new statistic is
-a suitable replacement in applied research.  The paper also presents a
+test when the \dgp\ is stable but can have much higher power when the 
+\dgp\ has structural breaks.  The paper also presents a
 method for comparing the benchmark model to several alternative models

### 2013-03-14 R/mc1.R

@@ -42,10 +42,10 @@ generate.data.mc1 <- function(nobs, simulationtype, nburn = 1000) {
                   postbreak.nobs <- nobs - prebreak.nobs
 
                   prebreak.data <- rvar(prebreak.nobs, list(y = c(0, 0), z = c(0, .95)),
-                                        c(0.5, 0.15), innovation.vcv)
+                                        c(-0.5, 0.15), innovation.vcv)
                   postbreak.data <- rvar(postbreak.nobs, 
-                                         list(y = c(2 * mean.gamma, 0), z = c(0, .95)),
-                                         c(0.5, 0.15), innovation.vcv, nburn = 0,
+                                         list(y = c(mean.gamma, 0), z = c(0, .95)),
+                                         c(1.0, 0.15), innovation.vcv, nburn = 0,
                                          y0 = prebreak.data[prebreak.nobs,c("y", "z")])
                   rbind(prebreak.data, postbreak.data)})
 }

### 2014-04-01 mixedwindow.tex
Rename file with main paper
Remove bootstrap material from paper
This commit is the first real step towards submitting this paper as a note to
Econometrica. It removes the bootstrap material to focus on just the mixed-window
ideas.

--- 2013-03-14 Paper.tex
@@
 \input{tex/ap}
+
+% These commands are generated when the monte carlo and applied
+% sections are run; I'm giving them definitions now so that LaTeX will
+% run.
+\providecommand\bootsize{[missing]}
+\providecommand\empiricalcriticalvalue{[missing]}
+\providecommand\nboot{[missing]}
+\providecommand\testsize{[missing]}
+\providecommand\totalsims{[missing]}
+\providecommand\windowlength{[missing]}
+\providecommand\empiricaltable{[missing]}
 
@@
 
-\date{December 9, 2011}
+% \date{March 14, 2013}
 
@@
   are nested.  Moreover, the alternative model can be estimated using
-  common model selection methods, such as the \aic\ or \bic.  This
-  paper also presents a method to compare multiple models
-  simultaneously while controlling familywise error, and
-  substantially improves existing block bootstrap methods for
-  out-of-sample statistics.  This procedure is then used to analyze
+  common model selection methods, such as the \aic\ or \bic.
+  This procedure is then used to analyze
   \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.
@@
 test statistic that is asymptotically normal with mean zero even when
-the models studied are nested.  This paper also proves that common
-block bootstrap methods consistently estimate the statistic's
-distribution, and shows how the statistic can be used to study many
-models simultaneously while maintaining strong control of the
-familywise error (\fwe), i.e. ensuring that the probability that the
-hypothesis that the model has equal predictive ability to a benchmark
-is incorrectly rejected for any of the models is no higher than a
-preset level.
-
+the models studied are nested.
 \oos\ tests are commonly used in International Macroeconomics,
@@
 
-Since researchers often have a set of potential models and want to
-know which of them significantly outperform the benchmark, procedures
-that compare a single pair of models are of limited practical value.
-As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
-individual tests is misleading, but researchers can obtain a valid test
-by using the bootstrap to approximate the distribution of the largest
-individual test statistic under the null (White calls this procedure
-the \textit{Bootstrap Reality Check} or \brc).  This paper presents a test
-for equal predictive ability of multiple models based on
-\citepos{RoW:05} StepM, which uses a step-down procedure that
-iteratively rejects models to achieve higher power than the \brc\ and
-indicate which of the models improves on the benchmark (see
-Theorem~\ref{res:2} for details).
-
-This paper also presents a new result for the validity of block
-bootstraps with \oos\ statistics, which is necessary to verify that
-the StepM is valid.  Existing results on bootstrapping \oos\
-statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
-the stationary bootstrap, but require the test sample to be much
-smaller than the training sample, which obviously does not hold here.
-\citet{CoS:07} relax that requirement, but make the statistic more
-complicated than necessary by adjusting the objective function of the
-bootstrapped statistic to center it correctly.\footnote{Their
-  recentering is required for consistency and does not imply higher
-  order accuracy.}  A parametric bootstrap, such as that used by
-\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
-method, but requires the benchmark model to be correctly specified.
-Although I focus on the null hypothesis that the benchmark is
-correctly specified, this paper's block bootstrap methods remain valid
-when the benchmark is misspecified and are relatively easy to
-implement.  So this paper's result for bootstrapping \oos\ statistics
-considerably improves on existing procedures.
-
-The next section presents our new statistics and Section~\ref{sec:1b}
-our block bootstrap result.  Section~\ref{sec:2} presents
-simulations that compare our pairwise \oos\ test to \poscw\ original
+The next section presents our new statistics and Section~\ref{sec:2} presents
+simulations that compare our test to \poscw\ original
 statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
@@
 
-This paper uses \citepos{RoW:05} StepM procedure, which is an iterated
-extension of \citepos{Whi:00} Reality Check designed to reject as many
-false hypotheses as possible while achieving \sfwe.  Their method
-relies on the bootstrap to estimate the joint dependence between the
-test statistic associated with each model.  The bootstrap used in this
-paper is new, and is outlined in Algorithm~\ref{alg:1}.
-Algorithm~\ref{alg:1} actually presents a more general version of the
-bootstrap that remains valid with a misspecified benchmark model.
-Imposing the null hypothesis of \mds\ leads to simpler version that
-will be discussed later.
-\begin{alg}\label{alg:1}
-  Suppose that there are $m$ alternative forecasting models,
-  $\hat{y}_{1t},\dots, \hat{y}_{mt}$, and define the data matrices
-  $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} = (X_{R+1},\dots,X_{T-1})$
-  with
-  \begin{equation*}
-    X_t = \begin{cases}
-      (y_{t+1}, x_t')' & t \leq R \\
-      (y_{t+1}, x_t', \hat{y}_{1,t+1}, \dots, \hat{y}_{m,t+1})' & t > R.
-    \end{cases}
-  \end{equation*}
-  \begin{enumerate}
-  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
-    moving or circular blocks bootstrap with block length $b$ or the
-    stationary bootstrap with geometric block lengths with success
-    probability $p$.  Denote each sample as $\X_{\p, l}^{*}$ and let
-    $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
-  \item Estimate $\bar{f}^{*}_{li}$ and $\hat{\sigma}_{li}^{*}$ as in
-    Theorem~\ref{res:1} for each bootstrap sample, $\X^{*}_l$, and each
-    alternative model, $\hat{y}_{it}$.
-  \end{enumerate}
-\end{alg}
-
-This procedure exploits the fact that $R$ is finite in
-Theorem~\ref{res:1} and that the expected block length will grow with
-$T$.  Under these asymptotics, a growing proportion of the
-rolling-window forecasts are the same if we bootstrap the forecasts as
-if we bootstrap the empirical data and reestimate the models.
-Bootstrapping the forecasts makes the computations faster and easier,
-but requires us to drop the first $R$ observations from the bootstrap
-(the alternative forecasts are not defined for the first $R$
-observations).  I add those observations to the beginning of each
-bootstrap sample so that population means under the bootstrap-induced
-probability distribution equal sample means.\footnote{This equality is
-  strictly true only for the stationary and circular block
-  bootstraps.}  The benchmark model still needs to be reestimated in
-each bootstrap sample.
+[Need to fill in joint normality corollary and StepM procedure.]
 
@@
 
-\begin{rem}\label{rem:01}
-  \citet{Pin:11} raises the issue that, since there are often several
-  models that could be used as the benchmark, researchers may want to
-  control for data snooping over the null hypotheses as well as the
-  alternatives.  For example, one could use either \citepos{AtO:01}
-  random walk or \citepos{StW:07} \textsc{ima}(1,1) as benchmark
-  inflation models, so it might make sense to require an alternative
-  model to outperform them both.\footnote{\citet{Pin:11} studies tests
-    that reject if the alternative model outperforms either of the
-    models, so the details are somewhat different in our papers.}
-  Allowing multiple benchmark models can be expressed as an
-  Intersection-Union test, so Theorem~\ref{res:2}'s procedure
-  (conclusion~\ref{it:3}) easily accommodates this extension by taking
-  each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
-  $q$-vector;\footnote{If a researcher uses multiple benchmark models,
-    it would be a mistake to assume that they are all correctly
-    specified, so only the null hypothesis of conclusion~\ref{it:3} is
-    appropriate.} the first element of $\bar f_{i}$, written as $\bar
-  f_{i1}$, compares the first benchmark model to the $i$th alternative
-  and the first element of $\hat{\sigma}_i^2$ is the corresponding
-  estimate of asymptotic variance, the second element corresponds to
-  the second benchmark model, etc.
-
-  Steps 1 and 2 of Theorem~\ref{res:2}'s procedure now become:
-  \begin{enumerate}
-  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
-    \{(i,k): \tfrac1{\hat\sigma_{ik}} \bar{f}_{ik} > \hat{d}_j\}$,
-    where $\hat{d}_j$ is the $1 - \alpha$ quantile of $\max_{(i,k)
-      \notin M_{j-1}} \tfrac1{\hat\sigma_{ik}^*} \big(\bar{f}_{ik}^{*} -
-    \bar{f}_{ik}(\hat{\beta}_{k,T+1})\big)$.
-  \item Reject all of the hypotheses $H_i$ such that $(i,k) \in
-    \bigcup_{j=1}^m M_j$ for all $k$.
-  \end{enumerate}
-  Also note that the asymptotic variance-covariance matrix of each
-  $\bar f_i$ does not need to be positive definite as long as the
-  variance of each of its elements is positive.  A formal statement of
-  this result is given in Appendix~\ref{sec:B}.
-\end{rem}
-
-\section{The Bootstrap for Out-of-Sample Statistics}\label{sec:1b}
-The validity of the bootstrap in Theorem~\ref{res:2} is a special case
-of a result of independent interest---the validity in general of block
-bootstraps for asymptotically normal \oos\ statistics.  This section
-presents the general result.  In this section, let $\to^{p^{*}}$ and
-$\to^{d^{*}}$ refer to convergence in probability or distribution
-conditional on the observed data.  Similarly, $\E^{*}$, $\var^{*}$,
-and $\cov^{*}$ refer to the expectation, variance, and covariance with
-respect to the probability measure induced by the bootstrap, and
-$y_t^{*}$, etc. is the random variable $y_t$ but under the
-bootstrap-induced \cdf.
-
-The notation in this section is more general than that of
-Section~\ref{sec:1}.  The assumptions required are generalizations of
-the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
-\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
-discussion of these conditions, as theirs are nearly identical.
-Theorem~\ref{res:3} gives the result.
-
-\begin{thm}\label{res:3}
-  Suppose the following conditions hold:
-  \begin{enumerate}
-  \item The estimator $\hat{\beta}_t$ of $\btrue$ is estimated with a
-    recursive, rolling, or fixed estimation window and satisfies
-    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
-    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
-    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
-    \begin{equation}
-      H_{t} = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s}(\btrue) & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\btrue) & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s}(\btrue) & \text{fixed window} \\
-      \end{cases}
-    \end{equation}
-    and $\E h_{s}(\btrue) = 0$ for all $s$.
-  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
-    $\psi_t(\beta)$ is covariance stationary and twice continuously
-    differentiable in an open neighborhood $N$ of $\btrue$.  Also,
-    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
-      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
-    uniformly bounded, and there exists a sequence of random variables
-    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
-      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
-    and $\E m_t^2$ is uniformly finite.
-  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
-    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
-    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
-    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
-    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
-      uniform mixing processes, $r = 2$ is also allowed as long as
-      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
-      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
-      integrable.}
-  \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
-    using the same procedure as the original \oos\ analysis over the
-    bootstrap sample, where the bootstrap sample is generated by
-    moving blocks, circular blocks, or stationary bootstrap with block
-    lengths drawn from the geometric distribution.  The (expected)
-    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
-  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
-    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T
-    h_t^*(\btrue[*]) = 0$ a.s.
-  \item The asymptotic variance matrix of $\bar{f}(\btrue)$ is
-    uniformly positive definite.
-  \item $R, P \to \infty$ as $T \to \infty$.
-  \end{enumerate}
-  Then
-  \begin{equation}
-    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
-        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
-      \epsilon] \to 0
-  \end{equation}
-  for all $\epsilon > 0$.
-\end{thm}
-
-\begin{rem}
-  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
-  conditions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
-  must be continuously differentiable.  It may be possible to extend
-  Theorem~\ref{res:3} to those weaker conditions, but the current
-  proof relies on a theorem of \citepos{JoD:00} establishing the
-  consistency of \hac\ estimators and their theorem requires differentiability of
-  the observations.  Extending \citepos{JoD:00} result to
-  nondifferentiable functions should be possible, but is beyond the
-  scope of this paper.
-\end{rem}
-
-\begin{rem}
-  \citet{Whi:00} and \citet{Han:05} resample the forecasts but do not
-  reestimate any of them which requires the additional assumption that
-  $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
-  have no estimated parameters.\footnote{\citet{Whi:00} lists several
-    different sets of assumptions that give the same result, but these
-    seem to be the most general.}
-\end{rem}
-
-\begin{rem}
-  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
-  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
-  \bar{f}(\btrue))$.  But it is clear that $\bar{f}(\btrue[*])$
-  is the bootstrap analogue of $\E \bar{f}(\btrue)$, the parameter of
-  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
-  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
-  paper, though, consistency arises naturally.
-\end{rem}
-
-\begin{rem}
-  It may be unnecessary to assume that $\bar{f}(\btrue)$ has positive
-  definite asymptotic variance; if so, the bootstrap would work in the
-  setup of \citet{ClM:05,ClM:01} and \citet{Mcc:07}.  That question is
-  left to future research.
-\end{rem}
-
 \section{Monte Carlo Results}\label{sec:2}
@@
 
-For comparison, we study this paper's new statistic as well as \poscw
+For comparison, we study this paper's new statistic as well as \poscw\
 rolling-window and recursive-window test statistics.  Clark and West
@@
 test when the \dgp\ is stable but can have much higher power when the 
-\dgp\ has structural breaks.  The paper also presents a
-method for comparing the benchmark model to several alternative models
-simultaneously and improves block bootstrap procedures of \oos\
-statistics.
+\dgp\ has structural breaks.
 
@@
 $F_t = F_t(\btrue)$,
-$\hat f_t^* = f_t^*(\hat\beta_t^*)$,
-$F_t^*(\beta) = \tfrac{\partial}{\partial \beta} f_t^*(\beta)$,
-$F_t^* = F_t^*(\btrue[*])$,
-$h_t = h_t(\btrue)$,
-$h_t^* = h_t^*(\btrue[*])$, 
 and
-\begin{equation*}
-      H_{t}^* = \begin{cases} 
-        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
-        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
-        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
-      \end{cases}
-\end{equation*}
+$h_t = h_t(\btrue)$.
 
@@
   (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
-\begin{proof}[Proof of Theorem~\ref{res:3}]
-  Expand $f_t^{*}(\hat{\beta}_t^{*})$ around $\btrue[*]$
-  to get
-  \begin{align*}
-    \sqrt{P} \big(\bar{f}^{*} - \bar{f}(\btrue[*])\big) &= \oclt{t}
-    \big(f_t^{*} - \bar{f}(\btrue[*])\big) +
-    \E^* F_t^{*} B^{*} \oclt{t} H_t^* \\
-    & \quad + \WesA[*] + \WesB[*] \\ & \quad + \WesC[*] + \oclt{t} w_t^*
-  \end{align*}
-  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
-  \begin{equation*}
-    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_{T+1})'
-    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
-    f_{it}^*(\tilde\beta_{it}^*) \Big]
-    (\hat\beta_t^* - \hat\beta_{T+1})
-  \end{equation*}
-  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
-  $\hat\beta_{T+1}$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
-  identical to West's, using our Lemma~\ref{res:a2} in place of his
-  Lemma A3.  Then
-  \begin{gather}
-    \WesA[*] \to^{p^*} 0 \label{eq:7} \\
-    \WesB[*] \to^{p^*} 0 \label{eq:9} \\
-  \intertext{and}
-    \WesC[*] \to^{p^*} 0 \label{eq:10}
-  \end{gather}
-  from Lemma~\ref{res:a4} and the result follows from
-  Lemma~\ref{res:a3}, with the form of the asymptotic variance
-  following directly from \citet{Wes:96} and \citet{WeM:98}.
-\end{proof}
-
-\begin{lem}[Formalization of Remark~\ref{rem:01}]
-  Suppose that the conditions of Theorem~\ref{res:2} conclusion~\ref{it:3}
-  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
-  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
-  uniformly positive definite for each $k$.  Then the procedure
-  described in Remark~\ref{rem:01} achieves \sfwe.
-\end{lem}
-
-The proof is similar to that of Theorem~\ref{res:2}. Note that we
-allow $\sqrt{P}(\bar{f}_{i1}(\beta_1),\dots,\bar{f}_{iq}(\beta_q))$ to
-converge to a normal with singular variance-covariance matrix as long
-as each element has positive variance.
 
@@
   \begin{enumerate}
-  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
-    \to^{p^{*}} 0$.
-  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
-    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
-    \to^{p^{*}} 0$.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$
-    and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t^* - \E F_t^*) =
-    O_{p^*}(1)$.
+  \item $P^a \sup_t | H_{t} | \to^p 0$.
+  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
   \end{enumerate}
@@
     with the convergence following from the continuous mapping
-    theorem.  For the bootstrapped average, \citepos{Cal:13}
-    Theorem~2 ensures that
+    theorem.
+  \item We have
     \begin{equation}
-      \tfrac{1}{\sqrt{\gamma
-          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*
-      = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2})
-    \end{equation}
-    where $\Omega^*(\beta) = \var^* h_t^*(\beta)$.  Since
-    $\hat\beta_{T+1} \to^p \btrue$, it suffices to show that
-    $\sup_{\beta \in N} | \Omega^*(\beta) - \var h_t(\beta) | \to^p
-    0$.  But this convergence holds for any fixed $\beta$ and our
-    assumptions guarantee stochastic equicontinuity as in
-    \citet{JoD:00} \citep[also see][]{Dav:94}, completing the proof.
-
-  \item We have
-    \begin{multline}
       P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
-      H_{t}| \\ \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
+      H_{t}| \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
       \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
       B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
-    \end{multline}
+    \end{equation}
     and both terms converge to zero in (conditional) probability by
-    the previous argument and by assumption.  The same argument holds
-    for $\hat{\beta}_t^{*} - \btrue[*]$ as well.
+    the previous argument and by assumption.
   \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
-    \citepos{Jon:97} \clt, so the result is trivial.  Also,
-   \begin{equation}
-     \Big\lvert\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T 
-     ( F_t^* - \E^* F^*)\Big\rvert = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2}) = O_p(1)
-    \end{equation}
-    as in the proof of part 1, where now $\Omega^*(\beta) = \var^* F_t^*(\beta)$.
+    \citepos{Jon:97} \clt, so the result is trivial.
   \end{enumerate}
@@
 \begin{lema}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:3}, Equations
-  \eqref{eq:7}--\eqref{eq:10} and \eqref{eq:11}--\eqref{eq:13} hold.
+  Under the conditions of Theorem~\ref{res:1}, Equations
+  \eqref{eq:11}--\eqref{eq:13} hold.
 \end{lema}
@@
 \begin{equation*}
-  \Big\lvert \WesA[*] \Big\rvert \leq 
-  \Big\lvert \oclt{t} (F_t^* - \E^* F^*_t) B^* \Big\rvert
-  \sup_t | H_t^* |.
+  \Big\lvert \WesA \Big\rvert \leq 
+  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
+  \sup_t | H_t |.
 \end{equation*}
-From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$ and $\oclt{t}
-(F_t^* - \E^* F_t^*) = O_p(1)$, establishing~\eqref{eq:7}.  The proofs
-of~\eqref{eq:9}, \eqref{eq:10}, and \eqref{eq:11}--\eqref{eq:13} are
-similar.
+From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
+(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
+of \eqref{eq:12} and \eqref{eq:13} are similar.
 \end{proof}
 
-\begin{lema}\label{res:a3}
-  Suppose the conditions of Theorem~\ref{res:3} hold, let
-  \[\psi_t^{*}(\beta) = 
-  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)},\]
-  and define $\psi_t = \psi_t(\btrue)$, $\hat\psi_t = \psi_t(\btrue[*])$, and 
-  $\psi_t^* = \psi_t^*(\btrue[*])$.  Then
-  \begin{equation}\label{eq:1}
-    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}
-    \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}
-    \leq x \Big] \Big| > \epsilon \Big] \to 0
-  \end{equation}
-  for all positive $\epsilon$, where the inequalities hold element-by-element.
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a3}]
-  Note that both $\psi_t$ and $\psi_t^*$ satisfy
-  \clt s, (\citealp[Theorem~2]{Jon:97} and
-  \citealp[Theorem~1]{Cal:13}) so it suffices to prove that
-  \[ \tfrac{ 1 }{ P } \var^* \osum{t} \psi_t^* 
-  - \tfrac{ 1 }{ P } \var \osum{t} \psi_t \to^p
-  0. \] I will prove this result for the Circular Block Bootstrap
-  \citep{PoR:92}---the proof for other block bootstraps is similar and
-  follows as in \cite{Cal:13}.
-
-  \newcommand{\su}{\tfrac{ 1 }{ b T } \sum_{ \tau = 1 }^{ T }%
-  \sum_{ s, t \in I( \tau ) }}
-
-  Since $\E^* \psi_t^* = 0$ by construction, we have
-  \begin{equation}\label{eq:3}
-  \tfrac{ 1 }{ P } \var^* \sum_{ t = R + 1 }^T \psi_t^*
-  = \su \hat \psi_s \hat \psi_t'
-  \end{equation}
-  almost surely, with
-  \begin{equation*}
-    I(\tau) =
-    \begin{cases}
-      \{ \tau, \dots, \tau + b - 1 \} & \text{if } \tau \leq T - b + 1 \\
-      \{ \tau, \dots, T \} \cup \{ 1, \dots, \tau - ( T - b + 1 ) \}
-      & \text{if } \tau > T - b + 1.
-    \end{cases}
-  \end{equation*}
-  We can rewrite the right side of \eqref{eq:3} as
-  \begin{multline}\label{eq:6}
-    \su \hat\psi_s \hat\psi_t'
-    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
-      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ \\
-      + \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        (\hat\psi_s \hat\psi_t' +
-         \hat\psi_t \hat\psi_s') \;
-        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+.
-  \end{multline}
-
-  The first term of \eqref{eq:6} can be shown to converge in
-  probability to $\tfrac{1}{P} \var \osum{t} \psi_t$ by Theorem 2.2 of
-  \citet{JoD:00}.  Most of the necessary conditions of their theorem
-  hold by assumption and it remains to prove their condition (2.9)
-  holds, namely that
-  \begin{equation}\label{eq:2}
-    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg) 
-    \Bigg\rVert_2 \to 0
-  \end{equation}
-  for all $j$, $k$, and $\xi$.  For any fixed $\beta \in N$,
-  \begin{equation*}
-    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg)
-    \to^p 0
-  \end{equation*}
-  and
-  \begin{equation*}
-    \tfrac{1}{T} \sum_{t=1}^T \sin( \xi t / b )
-    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} -
-          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_k} \Bigg)
-    \to^p 0
-  \end{equation*}
-  by a mixingale \lln\ \citep{Dav:93}.\footnote{Remember that \ned\
-    processes are also mixingales.  See, for example, \citet[Section
-    17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
-  follows from the existence of the $r$th moment ($r > 2$) and uniform
-  convergence is a consequence of our bound on the second derivative
-  of $\psi_t$.
-
-  The conclusion then holds if the second term of~\eqref{eq:6} is
-  $o_p(1)$.  We have, for each element of that matrix,
-  \begin{equation*}
-    \Big| \tfrac{1}{bT} \sum_{s = 1}^{b - 1} \sum_{t = T - b + s}^{T}
-        \hat\psi_{ks} \hat\psi_{jt}
-        \big(1 - \tfrac{\lvert s - t + T\rvert}{b}\big)^+ \Big| \leq
-     \tfrac{1}{b T} \sum_{s = 1}^{b - 1} |\hat\psi_{ks}|
-         \sum_{t = T - b + 1}^{T} | \hat\psi_{jt} |
-  \end{equation*}
-  almost surely.  For any positive $\delta$,
-  \begin{equation*}
-    \pr \Bigg[ \tfrac{1}{T} \sum_{s = 1}^{b - 1} | \hat\psi_{is} |
-              > \delta \Bigg] \leq 
-    \pr \Bigg[\tfrac{1}{T} \sum_{s = 1}^{b - 1} \sup_{ \beta \in N } | \psi_{is}( \beta ) |
-              > \delta \Bigg] +
-    \pr \big[ \hat \beta_{T+1} \notin N \big].
-  \end{equation*}
-  Both terms converge to zero by assumption, so $\tfrac{1}{T} \sum_{s
-    = 1}^{b - 1} |\hat\psi_{is}| = o_p(1)$.  A similar
-  argument shows that $\tfrac{1}{b} \sum_{t = T - b + 1}^{T} |
-  \hat\psi_{jt} | = O_p(1)$, completing the proof.
-\end{proof}
-
 \begin{lema}\label{res:a5}
-  If the conditions of Theorem~\ref{res:3}, except for those governing
-  the bootstrap process, hold then
+  If the conditions of Theorem~\ref{res:1} hold then
   \begin{equation}
@@
 
-\begin{proof}[Proof of Theorem~\ref{res:3}]
-  As in \citet{Wes:96} and \citet{WeM:98} (and as in the proof of
-  Theorem~\ref{res:3}), expand $\hat f_t$ around
+\begin{proof}[Proof of Theorem~\ref{res:a5}]
+  As in \citet{Wes:96} and \citet{WeM:98}, expand $\hat f_t$ around
   $\btrue$ to get

### 2014-04-01 Paper.tex
Updated date
Change footnote representation
This commit tweaks the source code for footnotes. It starts them on a
new line (with a comment eating the previous newline) and adds a space
and comment to close them. This representation makes line-wrapping work
better and makes the footnote self-contained in git.

@@
 
-\date{December 9, 2011}
+\date{March 14, 2013}
 
@@
 beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.\footnote{Other papers in this literature include
+\citet{Wes:96}.%
+\footnote{Other papers in this literature include
   \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
@@
   \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
-  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
+  \citet{CoD:11}, and \citet{Gia:11}} %
+In a pair of papers,
 \citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
@@
 \citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
+\citealt{Mcc:00}).%
+\footnote{\citet{DiM:95} assume that the models are
   not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
   implicitly assume that the models do not converge to the same limit,
-  which rules out nesting.}
+  which rules out nesting.} %
 
@@
 for breaks, parameter drift, or other forms of
-instability,\footnote{Exceptions are \citepos{StW:07}
-  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
+instability,%
+\footnote{Exceptions are \citepos{StW:07}
+  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} %
+but the
 researcher is typically concerned about instability.  Indeed, concern
 about instability is often given as a reason for doing an \oos\
-analysis, especially with a short rolling window.\footnote{This
+analysis, especially with a short rolling window.%
+\footnote{This
   motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
   \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
-  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
+  \cite{GiR:09,GiR:10}, among others.} %
+A researcher could impose
 stability on both models by using a recursive window or relax
@@
 is useful, since \citepos{Wes:96} results do not apply to non-nested
-models if they both encompass the true \dgp,\footnote{\citet{ClM:11b}
-  call this scenario, ``overlapping models.''} which is allowable
+models if they both encompass the true \dgp,%
+\footnote{\citet{ClM:11b}
+  call this scenario, ``overlapping models.''} %
+which is allowable
 under the null: in the limit, both models will converge to the \dgp\
@@
 complicated than necessary by adjusting the objective function of the
-bootstrapped statistic to center it correctly.\footnote{Their
+bootstrapped statistic to center it correctly.%
+\footnote{Their
   recentering is required for consistency and does not imply higher
-  order accuracy.}  A parametric bootstrap, such as that used by
+  order accuracy.} %
+A parametric bootstrap, such as that used by
 \cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
@@
 positive) and is asymptotically normal as $P \to \infty$, with $R$ an
-arbitrary starting value\footnote{It will be clear momentarily why the
-  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
+arbitrary starting value%
+\footnote{It will be clear momentarily why the
+  summation begins at $R+1$ instead of $1$.} %
+and $P = T - R$.
 Straightforward algebra \citep{ClW:07} shows that
@@
   a forecast encompassing test using the models' generalized forecast
-  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
+  errors.%
+\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
   Again, Lemma~\ref{res:a5} can cover these other applications.
@@
 Since most empirical papers study more than one alternative model,
-Theorem~\ref{sec:1} is of limited use on its own.\footnote{Moreover,
+Theorem~\ref{sec:1} is of limited use on its own.%
+\footnote{Moreover,
   we would need to account for the existence of multiple models even if
 each paper only considered a single model, since there are many papers
-studying the same data.}  It can, however, be
+studying the same data.} %
+It can, however, be
 used as the basis for a procedure that allows researchers to make
@@
 probability greater than the tests' nominal size of rejecting at least
-once.\footnote{Unless the statistics used for each test are completely
+once.%
+\footnote{Unless the statistics used for each test are completely
   interdependent, the probability will be strictly greater than the
-  nominal size.}  Econometricians, e.g. \citet{Whi:00},
+  nominal size.} %
+Econometricians, e.g. \citet{Whi:00},
 \citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
@@
 known as \textit{weak control of familywise error}
-(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
+(\wfwe).%
+\footnote{An exception is \citet{HHK:10} who combine
   \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
-  control \sfwe\ for certain families of one-sided tests.}  This paper
+  control \sfwe\ for certain families of one-sided tests.} %
+This paper
 focuses instead on controlling the probability that at least one true
@@
 bootstrap sample so that population means under the bootstrap-induced
-probability distribution equal sample means.\footnote{This equality is
+probability distribution equal sample means.%
+\footnote{This equality is
   strictly true only for the stationary and circular block
-  bootstraps.}  The benchmark model still needs to be reestimated in
+  bootstraps.} %
+The benchmark model still needs to be reestimated in
 each bootstrap sample.
@@
   respect to the pooled information set generated by all of those
-  series together.\footnote{It is straightforward to construct three
+  series together.%
+\footnote{It is straightforward to construct three
     series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
@@
     $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
-    This is essentially the scenario imposed in conclusion~\ref{it:2}.}
+    This is essentially the scenario imposed in conclusion~\ref{it:2}.} %
   Using $b = 1$ would consistently estimate the marginal distribution
@@
   inflation models, so it might make sense to require an alternative
-  model to outperform them both.\footnote{\citet{Pin:11} studies tests
+  model to outperform them both.%
+\footnote{\citet{Pin:11} studies tests
     that reject if the alternative model outperforms either of the
-    models, so the details are somewhat different in our papers.}
+    models, so the details are somewhat different in our papers.} %
   Allowing multiple benchmark models can be expressed as an
@@
   each $\bar f_i$ and $\hat{\sigma}_{i}^{2}$ to be a random
-  $q$-vector;\footnote{If a researcher uses multiple benchmark models,
+  $q$-vector;%
+\footnote{If a researcher uses multiple benchmark models,
     it would be a mistake to assume that they are all correctly
     specified, so only the null hypothesis of conclusion~\ref{it:3} is
-    appropriate.} the first element of $\bar f_{i}$, written as $\bar
+    appropriate.} %
+  the first element of $\bar f_{i}$, written as $\bar
   f_{i1}$, compares the first benchmark model to the $i$th alternative
@@
     in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
-    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
+    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.%
+\footnote{For
       uniform mixing processes, $r = 2$ is also allowed as long as
@@
       (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
-      integrable.}
+      integrable.} %
   \item The sequence $\hat f_1^{*},\dots,\hat f_T^{*}$ is constructed
@@
   $\tfrac{P}{R} \log \log R \to 0$ or that the forecasts themselves
-  have no estimated parameters.\footnote{\citet{Whi:00} lists several
+  have no estimated parameters.%
+\footnote{\citet{Whi:00} lists several
     different sets of assumptions that give the same result, but these
-    seem to be the most general.}
+    seem to be the most general.} %
 \end{rem}
@@
 have substantially higher power when the \dgp\ has a structural
-break.\footnote{All of these simulations were programmed in R
+break.%
+\footnote{All of these simulations were programmed in R
   \citep[version 2.14.0]{R} and use the \textsc{MASS}
   \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
-  dbframe \citep[version 0.2.7]{Cal:10b} packages.}
+  dbframe \citep[version 0.2.7]{Cal:10b} packages.} %
 
@@
 We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.\footnote{\citet{ClW:07}
+benchmark model's innovation is an \mds.%
+\footnote{\citet{ClW:07}
   report the performance of the tests proposed by \citet{CCS:01} and
   \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.}
+  statistic.} %
 
@@
 beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.\footnote{This statistical analysis was
+\windowlength\ observations.%
+\footnote{This statistical analysis was
   conducted in R \citep{R} using the xtable
   \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
-  0.2.7]{Cal:10b} packages.}
+  0.2.7]{Cal:10b} packages.} %
 
@@
 and the critical value estimated by the procedure of
-Theorem~\ref{res:2} (\empiricalcriticalvalue).\footnote{The bootstrap
+Theorem~\ref{res:2} (\empiricalcriticalvalue).%
+\footnote{The bootstrap
   uses \nboot\ replications with i.i.d. sampling, as proposed in
-  conclusion~\ref{it:1} of Theorem~\ref{res:2}.}  Three predictors are
+  conclusion~\ref{it:1} of Theorem~\ref{res:2}.} %
+Three predictors are
 significant at the naive critical values for both the original and
@@
   \end{equation*}
-  by a mixingale \lln\ \citep{Dav:93}.\footnote{Remember that \ned\
+  by a mixingale \lln\ \citep{Dav:93}.%
+\footnote{Remember that \ned\
     processes are also mixingales.  See, for example, \citet[Section
-    17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
+    17.2]{Dav:94}.} %
+  Convergence in $L_2$ for each $\beta \in N$ then
   follows from the existence of the $r$th moment ($r > 2$) and uniform

### 2014-04-01 mixedwindow.tex
Move some theoretical results in the appendix

@@
 \appendix
-\section{Proofs of Main Theoretical Results}\label{sec:B}
+\section{Proofs of Main Theoretical Results}
+\label{sec:B}
+
+\newcommand{\WesA}[1][]{\oclt{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
+  B^{#1}) H_t^{#1}}
+\newcommand{\WesC}[1][]{\oclt{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
 
@@
   statistic; this substitution does not affect its asymptotic
-  distribution; the theorem is now an immediate consequence of
-  Lemma~\ref{res:a5} with $h_t(\beta) = x_t (y_{t+1} - x_t'\beta)$.
+  distribution.
+  As in \citet{Wes:96} and \citet{WeM:98}, expand $\hat f_t$ around
+  $\btrue$ to get
+  \begin{align*}
+    \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
+    \big(f_t - \E f_t\big) +
+    \E F_t B \oclt{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
+  \end{align*}
+  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
+  \begin{equation*}
+    w_{it} = \tfrac12 (\hat\beta_t - \btrue)'
+    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
+    f_{it}(\tilde\beta_{it}) \Big]
+    (\hat\beta_t - \btrue)
+  \end{equation*}
+  and each $\tilde\beta_{it}$ lies between $\hat\beta_t$ and
+  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
+  Then, as before,
+  \begin{gather}
+    \WesA \to^{p} 0 \label{eq:11} \\
+    \WesB \to^{p} 0 \label{eq:12}\\
+  \intertext{and}
+    \WesC \to^{p} 0 \label{eq:13}
+  \end{gather}
+  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
+  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.
+
   Note that \[f_t(\btrue)= 2 (y_{t+1} -
@@
 \end{proof}
-
-\newcommand{\WesA}[1][]{\oclt{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\oclt{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
 
@@
 
-\begin{lema}\label{res:a5}
-  If the conditions of Theorem~\ref{res:1} hold then
-  \begin{equation}
-    \oclt{t}
-    (\hat f_t - \E f_t) \to^d N(0, \sigma^2),
-  \end{equation}
-  with 
-  \begin{align}
-  \sigma^2 &= S_{ff} + \lambda_{fh} (F B S_{fh}' + S_{fh} B' F') + 2 \lambda_{hh} F V_\beta F' \\
-  (\lambda_{fh}, \lambda_{hh}) &= 
-  \begin{cases}
-    (1, 2) \times \big(1 - \tfrac{1}{\pi} \ln(1 + \pi)\big) 
-      & \text{recursive window} \\
-    \big(\tfrac{\pi}{2}, \pi - \tfrac{\pi^2}{3}\big)
-      & \text{rolling window with $\pi \leq 1$} \\
-    \big(1 - \tfrac{1}{2\pi}, 1 - \tfrac{1}{3\pi}\big)
-      & \text{rolling window with $\pi > 1$} \\
-    (0, \pi) & \text{fixed window},
-  \end{cases}
-  \end{align}
-  $\Big(\begin{smallmatrix}S_{ff} & S_{fh} \\ S_{fh}' &
-    S_{hh} \end{smallmatrix} \Big)$ the asymptotic variance of $(\bar
-  f(\btrue)', \bar h(\btrue)')'$, and $V_\beta$ the asymptotic
-  variance of~$\btrue[*]$.
-\end{lema}
-
-\begin{proof}[Proof of Theorem~\ref{res:a5}]
-  As in \citet{Wes:96} and \citet{WeM:98}, expand $\hat f_t$ around
-  $\btrue$ to get
-  \begin{align*}
-    \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
-    \big(f_t - \E f_t\big) +
-    \E F_t B \oclt{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
-  \end{align*}
-  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
-  \begin{equation*}
-    w_{it} = \tfrac12 (\hat\beta_t - \btrue)'
-    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
-    f_{it}(\tilde\beta_{it}) \Big]
-    (\hat\beta_t - \btrue)
-  \end{equation*}
-  and each $\tilde\beta_{it}$ lies between $\hat\beta_t$ and
-  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
-  Then, as before,
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12}\\
-  \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
-  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}. Since
-  $f_t$ and $H_t$ both satisfy \clt s, this completes the
-  proof.
-\end{proof}
-
 \bibliography{texextra/AllRefs}

### 2014-04-01 mixedwindow.tex
Move assumptions from theorem to stand alone

@@
 \newtheorem{alg}{Algorithm}
-\newtheorem{asmp}{Assumption}[section]
+\newtheorem{asmp}{Assumption}
 
@@
 
+\begin{asmp}\label{a1}%
+  The benchmark forecast $\hat{y}_{0,t+1}$, is estimated using \ols\
+  with a recursive window: $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for
+  some vector of predictors $x_t$ with $\hat{\beta}_t$ given by
+  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
+  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
+  depend on~$t$.
+\end{asmp}
+
+\begin{asmp}\label{a2}%
+  The alternative forecast, $\hat{y}_{1t}$, is estimated using a
+  rolling window of fixed length $R$ (which is less than $T$), so
+  $\hat{y}_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
+  $\psi$ is a known function and $z_t$ is a sequence of predictors
+  that may include $x_t$.
+\end{asmp}
+
+\begin{asmp}\label{a3}%
+  The series $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded
+  $2 r$ moments for some $r > 2$, and $\hat y_t y_t$ $\hat y_t
+  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
+  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
+  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
+\end{asmp}
+
+\begin{asmp}\label{a4}%
+  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
+  \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\] $f_t =
+  f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$, $\bar{f}(\beta) =
+  \oavg{t} f_t(\beta)$, and $\bar f = \tfrac1P \sum_{t=R+1}^{T} \hat
+  f_t$, with $P = T - R$; $\bar f(\btrue)$ has uniformly positive and
+  finite long run variance.
+\end{asmp}
+
 \begin{thm}\label{res:1}
@@
   forecast the variable $y_t$, and have observations for
-  $t=1,\dots,T+1$.  Assume the following hold:
-  \begin{enumerate}
-  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
-    estimated using \ols\ with a recursive window:
-    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
-    predictors $x_t$ with $\hat{\beta}_t$ given by
-    Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
-    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not depend
-    on~$t$.
-  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
-    estimated using a rolling window of fixed length $R$ (which is
-    less than $T$), so $\hat{y}_{1,t+1} =
-    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
-    function and $z_t$ is a sequence of predictors that may include
-    $x_t$.
-  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
-    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
-    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
-    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
-    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
-    series of size $-\frac{r}{2r-2}$.
-  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
-    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
-    $f_t = f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$,
-    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
-    = \tfrac1P \sum_{t=R+1}^{T} \hat f_t$, with $P = T - R$;
-    $\bar f(\btrue)$ has uniformly positive and finite long run
-    variance.
-  \end{enumerate}
+  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
   Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a

### 2014-04-08 mixedwindow.tex
Minor changes to appearence
- increase the font size to 12pt
- switch to single spacing
- move monte carlo and empirical tables into the body of the text
Use guillemets to differentiate URLs from rest of text
Replace small caps with capitalized letters
This commit finishes converting small caps to uppercase letters; the
free version of Charter uses faked small caps that are ugly.

@@
-\documentclass[11pt,fleqn]{article}
+\documentclass[12pt,fleqn]{article}
 
@@
 \usepackage[T1]{fontenc}
-\usepackage[nolists,nomarkers]{endfloat}
 \usepackage[sort,round,comma]{natbib}
@@
 \usepackage[small]{caption}
+\usepackage[charter]{mathdesign}
+\urlstyle{same}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\onehalfspacing
 \bibliographystyle{abbrvnat}
@@
 
-\newcommand{\aic}{\textsc{aic}}
-\newcommand{\bic}{\textsc{bic}}
-\newcommand{\brc}{\textsc{brc}}
-\newcommand{\cdf}{\textsc{cdf}}
-\newcommand{\clt}{\textsc{clt}}
+\newcommand{\aic}{AIC}
+\newcommand{\bic}{BIC}
+\newcommand{\brc}{BRC}
+\newcommand{\cdf}{CDF}
+\newcommand{\clt}{CLT}
 \newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
-\newcommand{\dgp}{\textsc{dgp}}
-\newcommand{\fclt}{\textsc{fclt}}
-\newcommand{\fwe}{\textsc{fwe}}
-\newcommand{\gdp}{\textsc{gdp}}
-\newcommand{\hac}{\textsc{hac}}
-\newcommand{\lln}{\textsc{lln}}
-\newcommand{\ma}{\textsc{ma}}
-\newcommand{\mds}{\textsc{mds}}
-\newcommand{\ned}{\textsc{ned}}
-\newcommand{\ols}{\textsc{ols}}
-\newcommand{\oos}{\textsc{oos}}
-\newcommand{\sfwe}{\textsc{sfwe}}
-\newcommand{\spa}{\textsc{spa}}
-\newcommand{\wfwe}{\textsc{wfwe}}
+\newcommand{\dgp}{DGP}
+\newcommand{\fclt}{FCLT}
+\newcommand{\fwe}{FWE}
+\newcommand{\gdp}{GDP}
+\newcommand{\hac}{HAC}
+\newcommand{\lln}{LLN}
+\newcommand{\ma}{MA}
+\newcommand{\mds}{MDS}
+\newcommand{\ned}{NED}
+\newcommand{\ols}{OLS}
+\newcommand{\oos}{OOS}
+\newcommand{\sfwe}{SFWE}
+\newcommand{\spa}{SPA}
+\newcommand{\wfwe}{WFWE}
 
@@
     University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \texttt{gcalhoun@iastate.edu}.  Web:
-    \texttt{http://gray.clhn.co}.  I'd like to
+    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
+    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
+    I'd like to
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
@@
     Goyal for providing computer code and data for his 2008
-    \textsc{rfs} paper with Ivo
-    Welch \citep{GoW:08}.} \\
+    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
   Iowa State University}
@@
 \footnote{Exceptions are \citepos{StW:07}
-  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} %
+  IMA(1,1) and UC-SV models of inflation.} %
 but the
@@
 power advantage and is similar in spirit to using a Likelihood Ratio
-Test instead of an \textsc{lm} or Wald test, which depend on just the
+Test instead of an LM or Wald test, which depend on just the
 restricted or unrestricted model respectively.
@@
 \footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \textsc{MASS}
+  \citep[version 2.14.0]{R} and use the MASS
   \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
@@
     \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\textsc{cw} roll.] shows the fraction of simulations for
+    samples.  Pr[CW roll.] shows the fraction of simulations for
     which Clark and West's (2007) rolling-window statistic rejects; 
-    Pr[\textsc{cw} rec.] shows the fraction of simulations for which 
+    Pr[CW rec.] shows the fraction of simulations for which
     their recursive-window statistic rejects; and Pr[new] shows the fraction of

### 2014-04-08 R/mc1Table.R

@@ -25,9 +25,9 @@ d <- select(mcdata1, c("'Sim. type'" = "case simulationtype
 		                        when '1.stable' then 'power (stable)'
 		                        when '2.breaks' then 'power (breaks)' end",
                        R = "R", P = "P",
-                       "'Pr[\\textsc{cw}~roll.]'" =
+                       "'Pr[CW~roll.]'" =
                        sprintf("100 * avg(clarkwestrolling <= %f)", testsize),
-                       "'Pr[\\textsc{cw}~rec.]'" =
+                       "'Pr[CW~rec.]'" =
                        sprintf("100 * avg(clarkwestrecursive <= %f)", testsize),
                        "'Pr[new]'" = sprintf("100 * avg(mixed <= %f)", testsize)),
             group.by = c("simulationtype", R = "R", P = "P"))[,-1]

### 2014-04-08 R/mc2Table.R

@@ -27,9 +27,9 @@ mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
 ##       sprintf("case when simulationtype = '0.size' then 'size %d'
 ##                     else 'power %d' end", i, i),
 ##     R = "R", P = "P",
-##     "'Pr[\\textsc{cw}~roll.]'" =
+##     "'Pr[CW~roll.]'" =
 ##       sprintf("100 * avg(clarkwestrolling%d <= %f)", i, testsize),
-##     "'Pr[\\textsc{cw}~rec.]'" =
+##     "'Pr[CW~rec.]'" =
 ##       sprintf("100 * avg(clarkwestrecursive%d <= %f)", i, testsize),
 ##     "'Pr[new]'" = sprintf("100 * avg(mixed%d <= %f)", i, testsize))
 ## })
@@ -42,9 +42,9 @@ mcdata2 <- dbframe("mc2", dbdriver = "SQLite",
 colsql <- c("'Sim. type'" =
             "case when simulationtype = '0.size' then 'size' else 'power' end",
             R = "R", P = "P",
-            "'Pr[\\textsc{cw}~roll.]'" =
+            "'Pr[CW~roll.]'" =
             sprintf("100 * avg(clarkwestrolling1 <= %f)", testsize),
-            "'Pr[\\textsc{cw}~rec.]'" =
+            "'Pr[CW~rec.]'" =
             sprintf("100 * avg(clarkwestrecursive1 <= %f)", testsize),
             "'Pr[new]'" = sprintf("100 * avg(mixed1 <= %f)", testsize))
 

### 2014-04-08 mixedwindow.tex
Remove hyphen in pseudo-true

@@
 asymptotically normal even when the smaller model is estimated.  To
-achieve normality, we need a consistent estimate of the pseudo-true
+achieve normality, we need a consistent estimate of the pseudotrue
 benchmark model, while maintaining an inconsistent estimate of the
@@
 (Theorem~\ref{res:1} lists the assumptions formally).  In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
+let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
 coefficient of the regression of $y_{t+1}$ on $x_t$ and define

### 2014-04-08 mixedwindow.tex
Small changes to wording in introduction

@@
   \noindent This paper proposes a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
-  alternative model is still estimated with a fixed-length rolling
-  window, but the benchmark is estimated with a recursive window. The
+    Econom.}]{ClW:07} adjusted out-of-sample $t$-test: using a
+  fixed-length rolling window to estimate the alternative model but a
+  recursive window to estimate the benchmark. The
   resulting statistic is asymptotically normal even when the models
@@
 \noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Family-Wise Error Rate; Multiple Testing;
-Bootstrap; Reality Check
+Sequence, Model Selection
 
@@
 asymptotically normal even when the smaller model is estimated.  To
-achieve normality, we need a consistent estimate of the pseudotrue
-benchmark model, while maintaining an inconsistent estimate of the
-larger model so that we can ignore nesting.  We can meet both needs by
+achieve normality, the pseudotrue benchmark model must be estimated
+consistently, but the larger alternative model must continue to be
+estimated inconsistently so that the test statistic is not degenerate
+when the models are nested. We can meet both needs by
 using different window strategies for each model: the benchmark model
@@
 
-\section{Out-of-Sample Model Comparisons}\label{sec:1}
+\section{Theoretical results supporting the asympotically normal OOS statistic}
+\label{sec:1}
+
 This section presents the new \oos\ statistic.  I will present the

### 2014-04-08 mixedwindow.tex
Add NBER-NSF conference to acknowledgements

@@
     Meng-Feng Yen and participants at the 2011 Midwest Econometrics
-    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
+    Group meeting and the 2013 NBER-NSF Time Series conference
+    for helpful comments and discussions.  I'd also like to thank Amit
     Goyal for providing computer code and data for his 2008

### 2014-04-08 mixedwindow.tex
Define MDS acronym in introduction

@@
 the null hypothesis is that the innovations in the smaller model form
-a martingale difference sequence.  This test procedure is popular, and
+a Martingale Difference Sequence (\mds).  This test procedure is popular, and
 one assumes that this is due in part to the statistic's convenience,

### 2014-04-08 mixedwindow.tex
Start to rewrite theory section
This commit splits up the assumptions and theorems into separate subsections.
It also makes small tweaks to the wording in the intro to their section and
removes an unnecessarily negative remark about the GW and CW approaches
for fixed window strategies

@@
 
-This section presents the new \oos\ statistic.  I will present the
-single-comparison statistic first and then extend it to multiple
-comparisons.  Suppose for now that a researcher is interested in
+This section presents the new \oos\ statistic.
+Suppose for now that a researcher is interested in
 predicting the target variable $y_{t+1}$ with a vector of regressors
@@
 $\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
-correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
-sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
-(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
+correctly specified, so $\varepsilon_{t+1}$ is an \mds\ with respect to
+$\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
+y_{t-1}),\dots)$,%
+\footnote{Section~\ref{sec:1b} discusses conditions under which the
+  \mds\ condition holds. We also present results that allow
+  $\varepsilon_{t+1}$ to be serially correlated.} %
+then we can see immediately that
 \begin{equation}
@@
 \end{equation}
-obeys an \mds\ \clt\ (assuming that its variance is uniformly
-positive) and is asymptotically normal as $P \to \infty$, with $R$ an
+obeys an \mds\ \clt%
+\footnote{This claim assumes that the asymptotic variance of the
+  sample average is uniformly positive, a requirement that we will
+  address in Section~\ref{sec:1b}.} %
+and is asymptotically normal as $P \to \infty$, with $R$ an
 arbitrary starting value%
@@
 
-\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
-of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
+\citet{ClW:06,ClW:07} base their \oos\ statistic on the RHS of
+Equation~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
 the size of the test sample used to evaluate the forecasting models.
 \citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
-use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
+use a rolling window of length $R$ (making $\hat{y}_{t+1}$ a
 function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
@@
 and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
-$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
+$\varepsilon_{t+1}$ in \oos\ test statistic.  Unfortunately,
 $\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
@@
 forecast of $y_{t+1}$ based on a fixed length rolling window.
-Theorem~\ref{res:1} presents the details of this result.  The
-assumptions required are essentially the same in existing papers
+
+Section~\ref{sec:1a} lays out the necessary assumptions for our
+results and Section~\ref{sec:1b} presents the details.
+
+\subsection{Assumptions}
+\label{sec:1a}
+
+The assumptions required are essentially the same in existing papers
 (e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
-\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
-original papers for a discussion of these assumptions.
+\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
 
@@
   depend on~$t$.
-\end{asmp}
 
-\begin{asmp}\label{a2}%
   The alternative forecast, $\hat{y}_{1t}$, is estimated using a
@@
 \end{asmp}
+
+\subsection{Theoretical results}
+\label{sec:1b}
 
@@
   Again, Lemma~\ref{res:a5} can cover these other applications.
-\end{rem}
-
-\begin{rem}
-  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize model comparison
-  using a rolling window but claim in passing that their results hold
-  for a fixed-length fixed window as well, where the unknown
-  coefficients are estimated only once using the first $R$
-  observations.  This claim is true but not obvious.  The proof for
-  the rolling window is based on weak dependence that arises because
-  the forecast errors are a function of a finite number of consecutive
-  weakly dependent observations.  But using a fixed window introduces
-  another source of dependence: all of the forecasts depend on the
-  same coefficient estimates and the estimation uncertainty introduced
-  by those estimates does not vanish asymptotically when $R$ is bounded.  One can
-  prove that their results apply to fixed window forecasts by using a
-  coupling argument similar to \citepos{Cal:11}.  Interested readers
-  should refer to \citet{Cal:11} for the argument and to
-  \citet{MeP:02} for a review of the necessary coupling results.
-  Theorem~\ref{res:1} can be shown to hold when $\hat y_{1t}$ is
-  estimated with a fixed-length fixed window using the same arguments.
 \end{rem}

### 2014-04-08 mixedwindow.tex
Remove theoretical results on multiple testing
I'm going to present radically simplified multiple testing results
for this paper (no stepdown; just present asymptotic normality in a
way that allows for multiple alternatives, then invoke CMT and explain
why Hansen's criticisms don't matter); this commit removes that
part of the theory.

@@
 
-Since most empirical papers study more than one alternative model,
-Theorem~\ref{sec:1} is of limited use on its own.%
-\footnote{Moreover,
-  we would need to account for the existence of multiple models even if
-each paper only considered a single model, since there are many papers
-studying the same data.} %
-It can, however, be
-used as the basis for a procedure that allows researchers to make
-multiple comparisons.  Before presenting a theoretical result, I will
-discuss some issues related to multiple hypothesis testing.
-
-Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
-clear that testing each hypothesis individually will often have a
-probability greater than the tests' nominal size of rejecting at least
-once.%
-\footnote{Unless the statistics used for each test are completely
-  interdependent, the probability will be strictly greater than the
-  nominal size.} %
-Econometricians, e.g. \citet{Whi:00},
-\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
-statistics that test families of hypotheses that control the
-probability any hypothesis is rejected given that they all are true,
-known as \textit{weak control of familywise error}
-(\wfwe).%
-\footnote{An exception is \citet{HHK:10} who combine
-  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
-  control \sfwe\ for certain families of one-sided tests.} %
-This paper
-focuses instead on controlling the probability that at least one true
-hypothesis is rejected given any combination of true and false
-hypotheses, known as \textit{strong control of familywise error}
-(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
-even though these papers only prove \wfwe, statistics based on
-nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
-control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
-and those based on the parametric bootstrap \citep{ClM:12b} essentially
-control \sfwe\ if the individual null hypotheses are strengthened
-slightly as below (see conclusion~\ref{it:1} of Theorem~\ref{res:2} as
-well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
-construct critical values from the asymptotic joint distribution of
-the test statistics and this procedure can control \sfwe\ as long as there is a
-consistent estimator of that distribution.
-
-Only tests with \sfwe\ can tell researchers which of the hypotheses
-are false.  To see why, imagine that there are only two hypotheses:
-$H_1$ is true and $H_2$ is false.  A test that rejects the true
-hypothesis, $H_1$, with arbitrarily high probability still can satisfy
-\wfwe: since not all of the hypotheses are true, the behavior of tests
-with weak control is essentially unconstrained.  Such a test would not
-satisfy \sfwe, though.  For \sfwe\ in this setting, a test must reject
-$H_1$ with probability at most $\alpha$ (letting $\alpha$ be the
-desired level of control).  In most research, we would view rejection
-of the true hypothesis $H_1$ as a mistake.
-
-[Need to fill in joint normality corollary and StepM procedure.]
-
-Theorem~\ref{res:2} presents the final procedure.
-
-\begin{thm}\label{res:2}
-  Suppose the conditions of Theorem~\ref{res:1} hold, with assumptions
-  on the alternative model, $\hat{y}_{1t}$, holding for each of the
-  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
-  $l$ denote the different quantities associated with $\hat{y}_{lt}$
-  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
-  variance-covariance matrix of the vector
-  $(\bar{f}_1(\btrue),\dots,\bar{f}_m(\btrue))'$ is uniformly
-  positive definite.
-
-  Let the $*$-superscript denote a random variable with the
-  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
-  consider the following procedure:
-  \begin{enumerate}
-  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
-    \{l : \tfrac1{\hat\sigma_l} \bar{f}_{l} > \hat{d}_j\}$, where
-    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
-    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
-    \bar{f_i}(\btrue[*]))$.
-  \item Reject all of the models $l$ with $l \in \bigcup_{j=1}^m M_j$.
-  \end{enumerate}
-  The following conclusions hold:
-  \begin{enumerate}
-  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
-    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
-    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
-    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
-    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
-    procedure outlined above, but using the moving block bootstrap
-    with block length $1$, has probability at most $\alpha$ of
-    rejecting one or more models in $I$.
-  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is an \mds\ with respect to
-    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
-    f_i(\btrue) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
-    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
-    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
-    then the procedure outlined above controls \sfwe\ at level
-    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
-  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
-    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
-    one-sided alternative $\E \bar f_i(\btrue) > 0$.  If $p \to 0$
-    and $P p \to \infty$ as $T \to \infty$ (for the stationary
-    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
-    moving or circular block bootstraps) then the procedure outlined
-    above controls \sfwe\ at level $\alpha$ for the family of
-    null hypotheses $H_1,\dots,H_m$.
-  \end{enumerate}
-\end{thm}
-
-The following remarks apply to Theorem~\ref{res:2}.
-
-\begin{rem}
-  The next section will discuss the block bootstrap procedures for
-  \oos\ comparisons in detail.  Note that $\bar f(\btrue[*])$ is the
-  bootstrap equivalent of $\E f_t(\btrue)$, hence its role as the
-  centering term in step 1 of the procedure.
-\end{rem}
-
-\begin{rem}
-It is worth emphasizing that this procedure is very easy to use under
-the null hypothesis of correct specification (conclusion~\ref{it:1}).  The
-researcher can use a standard estimate of the statistic's asymptotic
-variance (not a \hac\ estimator) and an i.i.d. bootstrap.  Even
-better, the alternative forecasts only need to be estimated once,
-before the bootstrap.
-\end{rem}
-
-\begin{rem}\label{rem:2}
-  The key difference between conclusions~\ref{it:1} and~\ref{it:2} is
-  that, in conclusion~\ref{it:2}, the forecast error is an \mds\ with
-  respect to several individual series, but not necessarily with
-  respect to the pooled information set generated by all of those
-  series together.%
-\footnote{It is straightforward to construct three
-    series, $u_t$, $v_t$, and $w_t$, such that $w_t$ is an \mds\ with
-    respect to $\sigma((u_t, w_t), (u_{t-1}, w_{t-1}),\dots)$ and
-    $\sigma((v_t, w_t), (v_{t-1}, w_{t-1}),\dots)$ but not
-    $\sigma((u_t, v_t, w_t), (u_{t-1}, v_{t-1}, w_{t-1}),\dots)$.
-    This is essentially the scenario imposed in conclusion~\ref{it:2}.} %
-  Using $b = 1$ would consistently estimate the marginal distribution
-  of each $\tfrac1{\sigma_i} \bar{f}_i$ under this weaker null
-  hypothesis, but would not necessarily estimate the joint
-  distribution of two or more of those terms correctly (in particular,
-  the covariance could be wrong).  The stronger null hypothesis
-  imposed in conclusion~\ref{it:1} ensures that resampling with $b = 1$
-  estimates the joint distribution correctly as well.
-
-  The same reasoning implies that a parametric bootstrap
-  \citep[i.e.][]{ClM:12b} achieves control of \sfwe\ only under the
-  stronger hypotheses of conclusion~\ref{it:1}.  Fortunately,
-  conclusion~\ref{it:1} seems to capture the goals of most empirical work,
-  so researchers can make use of the considerable simplifications that
-  occur in that setting.
-\end{rem}
-
-\begin{rem}
-  If calculating $\hat{\sigma}_i$ is burdensome, one can do the same
-  bootstrap without studentizing the statistics.  This procedure is
-  likely to have worse size and power properties, but may be more
-  convenient.  One could also estimate the variance with a second
-  bootstrap step, but execution might take too long to be practical,
-  or use a convenient but inconsistent approximation of the variance.
-  The estimator of the variance in conclusion~\ref{it:3} should have the
-  best performance if it is \hac\ \cite[the results of][may be
-  relevant]{GoK:96}, but that is not necessary for validity.
-  See \citet{Han:05} and \citet[Section~4.2]{RoW:05} for a discussion
-  of the benefits of studentization.
-\end{rem}
-
-\begin{rem}
-  If the number of alternative models is large, controlling the \fwe\
-  may be too strict a criterion to be useful.  \citet{RSW:08} discuss procedures to
-  control criteria other than the \fwe, and one can use their
-  generalizations of the StepM procedure here as well.
-\end{rem}
-
 \section{Monte Carlo Results}\label{sec:2}

### 2014-04-08 mixedwindow.tex
Remove references to presentation-only R packages
i.e. booktabs and xtable. The rationale is that there is a ton of
software that goes into formatting the paper, so singling out the
R packages doesn't make much sense.

@@
   \citep[version 2.14.0]{R} and use the MASS
-  \citep[7.3-22]{VeR:02}, xtable \citep[version 1.6-0]{Dah:09}, and
-  dbframe \citep[version 0.2.7]{Cal:10b} packages.} %
+  \citep[7.3-22]{VeR:02} package.} %
 
@@
 \footnote{This statistical analysis was
-  conducted in R \citep{R} using the xtable
-  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
-  0.2.7]{Cal:10b} packages.} %
+  conducted in R \citep{R}.} %
 

### 2014-04-08 mixedwindow.tex
Set Pi = 1 in theory and simulations
Setting Pi = 1 should give essentially the same performance, but makes
the expression for the OOS statistic marginally simpler.

@@
   \begin{align*}
-    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
+    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 (\hat{S}_{fg} + \hat{S}_{gg}), &
     \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
@@
   \end{align*}
-  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
+  $\bar{g} = \oavg{t}
   \hat g_t$, $\X' = [x_1,\dots,x_T]$,
@@
   restriction only on the models.
-\end{rem}
-
-\begin{rem}
-  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
-  fixed.  But using West's general formula for $\Pi$ (which holds when
-  $\lim \tfrac{P}{R} \in [0,\infty]$) can improve the statistic in practice,
-  since researchers often invoke ``fixed $R$'' asymptotics when $R$ is
-  large.  Section~\ref{sec:2} shows via Monte Carlo that this
-  approximation can be accurate even when $R$ and $P$ are equal.
 \end{rem}

### 2014-04-08 R/ap.R

@@ -71,7 +71,7 @@ alternatives <- c(alternatives_gw, alternatives_ct,
   
 oos.bootstrap <- mixedbootstrap(benchmark, alternatives, financial.data,
 				R = windowlength, nboot = nboot, blocklength = 1,
-				window = "rolling", bootstrap = "circular")
+				window = "rolling", bootstrap = "circular", pimethod = "theory")
 
 stepm.results <- stepm(oos.bootstrap$statistics, oos.bootstrap$replications, 
                        NA, bootsize)

### 2014-04-08 R/mc1.R

@@ -60,5 +60,6 @@ for (r in rows(mcdesign)) {
       randomdata <- with(r, generate.data.mc1(R + P, simulationtype))
       c(clarkwestrolling = clarkwest(null, alt, randomdata, r$R, window = "rolling")$pvalue,
 	clarkwestrecursive = clarkwest(null, alt, randomdata, r$R, window = "recursive")$pvalue,
-	mixed = mixedwindow(null, alt, randomdata, r$R, window = "rolling")$pvalue)})))
+	mixed = mixedwindow(null, alt, randomdata, r$R,
+                            window = "rolling", pimethod = "theory")$pvalue)})))
 }

### 2014-04-09 mixedwindow.tex
Update multiple testing in empirical section
This commit changes the empirical section to use a much simpler
method of correcting for multiple comparisons. Instead of the
bootstrap we used before, we just simulate from the asymptotic
distribution and take the 1-alpha quantile of the largest
t-statistic. This correction makes the math and the presentation
a lot simpler, and complies with the editor's suggestion to
remove the bootstrap from the paper :).

@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator{\diag}{diag}
 \DeclareMathOperator{\E}{E}
@@
 \windowlength\ observations.%
-\footnote{This statistical analysis was
-  conducted in R \citep{R}.} %
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-``value'' gives the value of the test statistic for each model, while
-the ``naive'' and ``corrected'' columns indicate whether the statistic
-is greater than the standard size-\bootsize\% critical value (1.28)
-and the critical value estimated by the procedure of
-Theorem~\ref{res:2} (\empiricalcriticalvalue).%
-\footnote{The bootstrap
-  uses \nboot\ replications with i.i.d. sampling, as proposed in
-  conclusion~\ref{it:1} of Theorem~\ref{res:2}.} %
-Three predictors are
-significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio.  But none are significant after accounting for
-data snooping, which highlights the importance of these methods.  The
-median forecast is significant using conventional critical values as
-well, but not the corrected values.
+\footnote{This statistical analysis was conducted in R \citep{R} and
+  uses the MASS \citep[7.3-22]{VeR:02} package.} %
 
@@
 \end{table}
+
+Table~\ref{tab:em1} presents the results for each model.  The column
+``value'' gives the value of the test statistic for each model, while
+the ``naive'' indicates whether the statistic is greater than the
+standard \bootsize\% critical value (\naivecriticalvalue) Three
+predictors are
+significant at the naive critical values for both the original and
+bounded forecasts: the dividend yield, long term interest rate, and
+book to market ratio.
+
+However, we know that this is an extremely optimistic assessment of
+the models' performance. We are conducting \nmod\ simultaneous
+hypothesis tests, so it is likely that some will reject by chance. A
+full treatment of this issue is beyond the scope of this paper,
+however, it is straightforward to use Theorem~\ref{res:1} and
+Lemma~\ref{lem:2} to derive an appropriate critical value as
+in~\citet{Whi:00}. Since $\sqrt{P} \bar f \to^d N(0, \Sigma)$ under
+the MDS null hypothesis, the continuous mapping theorem implies that
+$\max_i \sqrt{P} \bar f_i/\hat\sigma_i \to^d \max_i W_i$, where $Z_i
+\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
+\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \hat\Sigma
+\hat D^{-1/2})$ distribution to generate a critical value for the
+\emph{largest} individual test statistic under the null ---
+\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
+this critical value, none of the predictors are siginificant at
+\bootsize\%.%
+\footnote{\citet{Han:05} makes the point that multiple one-sided
+  comparisons can have poor power if irrelevant predictors are
+  included in these tests and proposes a threshold for discarding very
+  poor forecasts. His threshold is well below our worst performing
+  model, so this issue is not a concern here. Moreover, I need to
+  explain why it's not a concern for these statistics in general.} %
 

### 2014-04-09 R/ap.R

@@ -17,9 +17,9 @@ library(oosanalysis, lib.loc = "lib")
 library(dbframe, lib.loc = "lib")
 
 ## These parameters are going to be reported in the paper as well.
-nboot <- 599
-bootsize <- 0.10
+size <- 0.10
 windowlength <- 10
+ndraw <- 1999
 
 gwdata <- ts(read.csv("data/yearlyData2009.csv")[,-1], start = 1871, frequency = 1)
 stock.returns <- ((gwdata[,"price"] + gwdata[,"dividend"]) / 
@@ -68,29 +68,28 @@ alternatives_median <-
 
 alternatives <- c(alternatives_gw, alternatives_ct,
                   average = alternatives_mean, median = alternatives_median)
-  
-oos.bootstrap <- mixedbootstrap(benchmark, alternatives, financial.data,
-				R = windowlength, nboot = nboot, blocklength = 1,
-				window = "rolling", bootstrap = "circular", pimethod = "theory")
+nmod <- length(alternatives)
 
-stepm.results <- stepm(oos.bootstrap$statistics, oos.bootstrap$replications, 
-                       NA, bootsize)
+oosstats <- mixedwindow(benchmark, alternatives, financial.data,
+                        windowlength, window = "rolling", pimethod = "theory")
+Sigma <- makecorr(oosstats$avar)
+critval <- quantile(replicate(ndraw, max(mvrnorm(1, rep(0, nmod), Sigma))), 1 - size)
 
 results.data <- data.frame(stringsAsFactors = FALSE,
-                           predictor = names(oos.bootstrap$statistics),
-                           value = oos.bootstrap$statistics,
-                           naive = ifelse(oos.bootstrap$statistics > qnorm(1 - bootsize), "sig.", ""),
-                           corrected = ifelse(stepm.results$rejected, "sig.", ""))
+                           predictor = names(oosstats$tstat),
+                           value = oosstats$tstat,
+                           naive = ifelse(oosstats$tstat > qnorm(1 - size), "sig.", ""),
+                           corrected = ifelse(oosstats$tstat > critval, "sig.", ""))
 
 results.data <- results.data[order(results.data$value, decreasing = TRUE),]
 results.data$predictor <- gsub(" \\.CT", "(\\\\textsc{ct})", results.data$predictor)
 results.data$predictor <- gsub("\\.", " ", results.data$predictor)
 names(results.data)[1] <- " "
 
-
[…]

### 2014-04-09 R/mc1Table.R

@@ -17,8 +17,6 @@ source("R/mcSetup.R")
 library(dbframe, lib.loc = "lib")
 mcdata1 <- dbframe("mc1", dbdriver = "SQLite", dbname = "data/mcdata.db",
 		   readonly = TRUE)
-displaycols <-
-  
 
 d <- select(mcdata1, c("'Sim. type'" = "case simulationtype
 	                                when '0.size' then 'size'

### 2014-04-10 mixedwindow.tex
Tweak wording of abstract
This commit fleshes out the abstract a bit more.

@@
 \begin{abstract} 
-  \noindent This paper proposes a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test: using a
-  fixed-length rolling window to estimate the alternative model but a
-  recursive window to estimate the benchmark. The
+  \noindent This paper develops a modification of \citepos[\textit{J.
+    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
+  using a recursive window to estimate the benchmark model but a
+  fixed-length rolling window to estimate the alternative. The
   resulting statistic is asymptotically normal even when the models
   are nested.  Moreover, the alternative model can be estimated using
-  common model selection methods, such as the \aic\ or \bic.
+  common model selection methods, such as the \aic\ or \bic, without
+  affecting the asymptotic distribution of this test statistic.  The
+  paper also presents Monte Carlo evidence that this statistic has
+  much higher power than existing out-of-sample statistics in a common
+  use-case for these tests: when the DGP is subject to instability.
   This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.
+  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
+  and supports their finding that the equity premium is unpredictable
+  out-of-sample.
 

### 2014-04-10 mixedwindow.tex
Rewrite introduction to theory section
This commit rewords parts of the introduction to the theory section,
and hopefully makes it work better as a stand alone subsection.

@@
 
-This section presents the new \oos\ statistic.
+This section presents the new \oos\ statistic; first we give an
+informal motivation of the statistc, then section~\ref{sec:1a}
+presents the paper's key assumptions and section~\ref{sec:1b} presents
+our formal theoretical results.
+
 Suppose for now that a researcher is interested in
 predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$; also let $v_t$ be another random process and suppose that
+$x_t$; also let $v_t$ be another random process that may contain information about
+$y_{t+1}$ and suppose that
 $(y_t, x_t, v_t)$ is stationary and weakly dependent
-(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
+In addition,
 let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
 coefficient of the regression of $y_{t+1}$ on $x_t$ and define
-$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
-correctly specified, so $\varepsilon_{t+1}$ is an \mds\ with respect to
-$\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
-y_{t-1}),\dots)$,%
-\footnote{Section~\ref{sec:1b} discusses conditions under which the
-  \mds\ condition holds. We also present results that allow
-  $\varepsilon_{t+1}$ to be serially correlated.} %
-then we can see immediately that
+$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
+correctly specified, then $\varepsilon_{t+1}$ is an \mds\ with respect
+to the information set
+\begin{equation*}
+\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
+y_{t-1}),\dots),
+\end{equation*}
+and we can see immediately that
 \begin{equation}
@@
   summation begins at $R+1$ instead of $1$.} %
-and $P = T - R$.
+and $P = T - R$.%
+\footnote{Section~\ref{sec:1b} discusses conditions under which the
+  \mds\ condition holds. We will also present results that allow
+  $\varepsilon_{t+1}$ to be serially correlated.} %
 Straightforward algebra \citep{ClW:07} shows that
@@
 
-\citet{ClW:06,ClW:07} base their \oos\ statistic on the RHS of
-Equation~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
-the size of the test sample used to evaluate the forecasting models.
-\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
-use a rolling window of length $R$ (making $\hat{y}_{t+1}$ a
-function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
-$z_{t-R}$ where $z_t$ is another weakly dependent random process),
-which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
-the weak dependence properties of the variables used to estimate it.
-Keeping $R$ finite ensures that the conditional variance remains
-positive, so the sum obeys a \clt.  This method of ensuring normality
-was introduced by \citet{GiW:06}.  In \citet{ClW:06}, the coefficients $\btrue$ are
-assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
-the null hypothesis) and Clark and West propose using this statistic
-to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
-$\mathcal{F}_t$.  In \citet{ClW:07}, $\btrue$ is unknown but is
-estimated with a fixed-length rolling window as well, so
-\begin{equation*}
-  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
-  \sum_{s=t-R+1}^t x_{s-1} y_s
-\end{equation*}
-and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
-$\varepsilon_{t+1}$ in \oos\ test statistic.  Unfortunately,
-$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
-$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
-mean-zero normal, even though this approximation performs well in the
-simulations reported by \citet{ClW:07}.
+\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
+Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
+$v_t$. (Call it $\hat{y}_{t+1}$.) They use a rolling window of length
+$R$ to estimate $\hat{y}_{t+1}$;%
+\footnote{Making $\hat{y}_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
+\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
+dependent random process} %
+$R$ is kept finite as $T \to \infty$, so
+$\hat{y}_{t+1}$ inherits the weak dependence properties of the
+variables used to estimate it. Using a finite window length $R$ avoids
+the degeneracy that often arises in OOS test statistics (see
+\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
+of the OOS average remains positive and the average obeys a \clt, an
+approach introduced by \citet{GiW:06}.
+
+\citet{ClW:06,ClW:07} develop a test of whether $\varepsilon_{t+1}$ is
+an \mds. In the 2006 paper, Clark and West assume that the
+coefficients $\btrue$ are zero under the null, making
+$\varepsilon_{t+1}$ observed directly. This restriction is relaxed in
+the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
+rolling window. Now the estimated linear model's prediction errors,
+$\hat{\varepsilon}_{t+1}$, replace $\varepsilon_{t+1}$ in the \oos\
+test statistic. Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an
+\mds\ even when $\varepsilon_{t+1}$ is, so the statistic is no longer
+asymptotically mean-zero normal, even though this approximation
+performs well in simulations.
 
@@
 but using a recursive window to estimate $\btrue$ and produce
-$\hat{\varepsilon}_{t+1}$; i.e.
+$\hat{\varepsilon}_{t+1}$; so
 \begin{equation}
@@
 the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06}, these conditions are ensured if $v_t$ is another
-forecast of $y_{t+1}$ based on a fixed length rolling window.
+\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
+another forecast of $y_{t+1}$ based on a fixed-length rolling window.
 
-Section~\ref{sec:1a} lays out the necessary assumptions for our
-results and Section~\ref{sec:1b} presents the details.
+This overview has presented an especially simple version of the result
+to make the intuition as clear as possible. The next section lists the
+specific assumptions that need to hold.
 

### 2014-04-11 mixedwindow.tex
Convert estimators and decorations to shorthand

@@
 
+\newcommand{\Bh}{\hat{B}}
 \newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
+\newcommand{\bh}{\hat{\beta}}
+\newcommand{\bt}{\tilde{\beta}}
+\newcommand{\ep}{\varepsilon}
+\newcommand{\eph}{\hat{\varepsilon}}
+\newcommand{\Fh}{\hat{F}}
+\newcommand{\Fs}{\mathcal{F}}
+\newcommand{\fb}{\bar{f}}
+\newcommand{\fh}{\hat{f}}
+\newcommand{\gb}{\bar{g}}
+\newcommand{\gh}{\hat{g}}
+\newcommand{\Sh}{\hat{S}}
+\newcommand{\Sigmah}{\hat\Sigma}
+\newcommand{\sh}{\hat\sigma}
+\newcommand{\yh}{\hat{y}}
 
@@
 coefficient of the regression of $y_{t+1}$ on $x_t$ and define
-$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\varepsilon_{t+1}$ is an \mds\ with respect
+$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
+correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
 to the information set
@@
   \label{eq:4}
-  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
+  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
 \end{equation}
@@
   \mds\ condition holds. We will also present results that allow
-  $\varepsilon_{t+1}$ to be serially correlated.} %
+  $\ep_{t+1}$ to be serially correlated.} %
 Straightforward algebra \citep{ClW:07} shows that
@@
   \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
+  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
   x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
@@
 Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\hat{y}_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\hat{y}_{t+1}$;%
-\footnote{Making $\hat{y}_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
+$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
+$R$ to estimate $\yh_{t+1}$;%
+\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
 \dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
@@
 $R$ is kept finite as $T \to \infty$, so
-$\hat{y}_{t+1}$ inherits the weak dependence properties of the
+$\yh_{t+1}$ inherits the weak dependence properties of the
 variables used to estimate it. Using a finite window length $R$ avoids
@@
 
-\citet{ClW:06,ClW:07} develop a test of whether $\varepsilon_{t+1}$ is
+\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
 an \mds. In the 2006 paper, Clark and West assume that the
 coefficients $\btrue$ are zero under the null, making
-$\varepsilon_{t+1}$ observed directly. This restriction is relaxed in
+$\ep_{t+1}$ observed directly. This restriction is relaxed in
 the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
 rolling window. Now the estimated linear model's prediction errors,
-$\hat{\varepsilon}_{t+1}$, replace $\varepsilon_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an
-\mds\ even when $\varepsilon_{t+1}$ is, so the statistic is no longer
+$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
+test statistic. Unfortunately, $\eph_{t+1}$ is not an
+\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
 asymptotically mean-zero normal, even though this approximation
@@
 but using a recursive window to estimate $\btrue$ and produce
-$\hat{\varepsilon}_{t+1}$; so
+$\eph_{t+1}$; so
 \begin{equation}
   \label{eq:8}
-  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
+  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
   \sum_{s=2}^t x_{t-1} y_t.
@@
   \oclt{t} \Big[(y_{t+1} -
-  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
+  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
 \end{equation*}
@@
 \begin{asmp}\label{a1}%
-  The benchmark forecast $\hat{y}_{0,t+1}$, is estimated using \ols\
-  with a recursive window: $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for
-  some vector of predictors $x_t$ with $\hat{\beta}_t$ given by
+  The benchmark forecast $\yh_{0,t+1}$, is estimated using \ols\
+  with a recursive window: $\yh_{0,t+1} = x_t'\bh_t$ for
+  some vector of predictors $x_t$ with $\bh_t$ given by
   Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
@@
 
-  The alternative forecast, $\hat{y}_{1t}$, is estimated using a
+  The alternative forecast, $\yh_{1t}$, is estimated using a
   rolling window of fixed length $R$ (which is less than $T$), so
-  $\hat{y}_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
+  $\yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
   $\psi$ is a known function and $z_t$ is a sequence of predictors
@@
 \begin{asmp}\label{a3}%
-  The series $y_t$, $\hat{y}_{1t}$, and $x_t$ have uniformly bounded
-  $2 r$ moments for some $r > 2$, and $\hat y_t y_t$ $\hat y_t
+  The series $y_t$, $\yh_{1t}$, and $x_t$ have uniformly bounded
+  $2 r$ moments for some $r > 2$, and $\yh_t y_t$ $\yh_t
   x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
@@
   Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
-  \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\] $f_t =
-  f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$, $\bar{f}(\beta) =
-  \oavg{t} f_t(\beta)$, and $\bar f = \tfrac1P \sum_{t=R+1}^{T} \hat
-  f_t$, with $P = T - R$; $\bar f(\btrue)$ has uniformly positive and
+  \yh_{1,t+1})^2 + (x_t'\beta - \yh_{1,t+1})^2,\] $f_t =
+  f_t(\btrue)$, $\fh_t = f_t(\bh_t)$, $\fb(\beta) =
+  \oavg{t} f_t(\beta)$, and $\fb = \tfrac1P \sum_{t=R+1}^{T} \fh_t$
+  with $P = T - R$; $\fb(\btrue)$ has uniformly positive and
   finite long run variance.
@@
 \begin{thm}\label{res:1}
-  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
+  Suppose that we have two models $\yh_{0t}$ and $\yh_{1t}$ to
   forecast the variable $y_t$, and have observations for
   $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
-  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
+  Under the null hypothesis that $y_t - \yh_{0t}(\btrue)$ is a
   martingale difference sequence with respect to the filtration
   $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
-  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
+  $\tfrac{\sqrt{P}}{\sh} \fb \to^d N(0,1)$, where
   \begin{align*}
-    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 (\hat{S}_{fg} + \hat{S}_{gg}), &
-    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
-    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
-    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
+    \sh^2 &= \Sh_{ff} + 2 (\Sh_{fg} + \Sh_{gg}), &
+    \Sh_{ff} &= \oavg{t} (\fh_t - \fb)^2, \\
+    \Sh_{fg} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
+    \Sh_{gg} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
   \end{align*}
-  $\bar{g} = \oavg{t}
-  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
+  $\gb = \oavg{t}
+  \gh_t$, $\X' = [x_1,\dots,x_T]$,
   \begin{equation*}
     g_t(\beta) =
-    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
+    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}'
     \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
   \end{equation*}
-  and $\hat g_t = g_t(\hat\beta_t)$.
+  and $\gh_t = g_t(\bh_t)$.
 \end{thm}
@@
 \begin{rem}
-  The requirement that the asymptotic variance of $\bar f(\btrue)$ is
+  The requirement that the asymptotic variance of $\fb(\btrue)$ is
   uniformly positive is much less restrictive than in \cite{Wes:96}.
@@
 
+Define $\X' = [x_1,\dots,x_T]$
+
+\begin{align*}
+  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
+  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
+\end{align*}
+
+Define the variables
+$g_t(\beta) = \Fh \Bh x_t(y_{t+1} - x_t'\beta)$,
+$\gh_t = g_t(\bh_t)$, and $\gb = \oavg{t} \gh_t$.
+
+\newcommand{\K}[1]{K(\tfrac{#1}{w})}
+
+Define the general covariance estimator:
+\begin{align*}
+  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
+  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
+  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
+  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
+\end{align*}
+
+Define the MDS covariance estimator:
+\begin{align*}
+  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
+  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
+  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
+  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
+\end{align*}
+
+\begin{lem}\label{lem:2}
+  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
+  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
+  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
+\end{lem}
+
 \begin{rem}
@@
   interest.  If one wants to test the less restrictive null hypothesis that
-  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
-  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
-  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
+  $y_{t} - \yh_{0t}$ is uncorrelated with $\yh_{1t}$ but not
+  necessarily an \mds, one can replace $\Sh_{21}$, $\Sh_{22}$
+  and $\Sh_{23}$ with their \hac\ counterparts.
   Our statistic can also be modified to test implications of
@@
 \[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
-\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
+\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
 $\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
@@
 Lemma~\ref{lem:2} to derive an appropriate critical value as
-in~\citet{Whi:00}. Since $\sqrt{P} \bar f \to^d N(0, \Sigma)$ under
+in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
 the MDS null hypothesis, the continuous mapping theorem implies that
-$\max_i \sqrt{P} \bar f_i/\hat\sigma_i \to^d \max_i W_i$, where $Z_i
+$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
 \sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
-\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \hat\Sigma
+\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
 \hat D^{-1/2})$ distribution to generate a critical value for the
@@
   distribution.
-  As in \citet{Wes:96} and \citet{WeM:98}, expand $\hat f_t$ around
+  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
   $\btrue$ to get
   \begin{align*}
-    \sqrt{P} \big(\bar{f} - \bar{f}(\btrue)\big) &= \oclt{t}
+    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
     \big(f_t - \E f_t\big) +
@@
   \begin{equation*}
-    w_{it} = \tfrac12 (\hat\beta_t - \btrue)'
+    w_{it} = \tfrac12 (\bh_t - \btrue)'
     \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
-    f_{it}(\tilde\beta_{it}) \Big]
-    (\hat\beta_t - \btrue)
+    f_{it}(\bt_{it}) \Big]
+    (\bh_t - \btrue)
   \end{equation*}
-  and each $\tilde\beta_{it}$ lies between $\hat\beta_t$ and
+  and each $\bt_{it}$ lies between $\bh_t$ and
   $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
@@
   Note that \[f_t(\btrue)= 2 (y_{t+1} -
-  x_t'\btrue)(\hat{y}_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
+  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
   in \citet{ClW:07}, which is an \mds, so we do not need to use a
   \hac\ estimator of the variance under the null.  Also observe that
-  \[F_t(\beta) = 2 x_t(x_t'\beta - \hat y_{1,t+1}) + 2 x_t(x_t'\beta -
+  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
   y_{t+1})\] and the second term is an \mds\ under the null,
@@
   \item $P^a \sup_t | H_{t} | \to^p 0$.
-  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$.
+  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
   \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
@@
     \begin{equation}
-      P^a \sup_t | \hat{\beta}_t - \btrue | = P^a \sup_t |\hat{B}_{t}
-      H_{t}| \leq \sup_{t,u} \Big| [ \hat{B}_u - B]
+      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
+      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
       \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
@@
 % LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized fg gg GoJ gcalhoun HLN li PoW
+% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
 % LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle

### 2014-04-15 mixedwindow.tex
Update assumptions and draft a discussion of their importance
This commit fleshes out the 'assumptions' subsection by adding real
text and discussion. It also simplifies some of the assumptions
themselves and adds positive-definiteness as a condition.

@@
 \DeclareMathOperator{\cov}{cov}
+\DeclareMathOperator*{\plim}{plim}
 %\DeclareMathOperator{\vec}{vec}
@@
 \DeclareMathOperator{\pr}{Pr}
+
+\newcommand{\iid}{\ensuremath\mathit{i.i.d.}}
+\newcommand{\bernoulli}{\ensuremath\mathit{bernoulli}}
 
@@
 This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistc, then section~\ref{sec:1a}
-presents the paper's key assumptions and section~\ref{sec:1b} presents
-our formal theoretical results.
+informal motivation of the statistc, then present the paper's key
+assumptions in section~\ref{sec:1a} and present our formal theoretical
+results in section~\ref{sec:1b}.
 
@@
 predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$; also let $v_t$ be another random process that may contain information about
-$y_{t+1}$ and suppose that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent
+$x_t$; also let $v_t$ be another random process that is believed to
+potentially contain information about $y_{t+1}$ and suppose that
+$(y_t, x_t, v_t)$ is stationary and weakly dependent.
 In addition,
 let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient of the regression of $y_{t+1}$ on $x_t$ and define
+coefficient for the regression of $y_{t+1}$ on $x_t$ and define
 $\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
@@
 \end{equation}
-obeys an \mds\ \clt%
+obeys an \mds\ \clt and is asymptotically normal as $P \to \infty$,%
 \footnote{This claim assumes that the asymptotic variance of the
@@
   address in Section~\ref{sec:1b}.} %
-and is asymptotically normal as $P \to \infty$, with $R$ an
-arbitrary starting value%
-\footnote{It will be clear momentarily why the
-  summation begins at $R+1$ instead of $1$.} %
+with $R$ an arbitrary starting value%
+\footnote{It will be clear momentarily why the summation begins at
+  $R+1$ instead of $1$.} %
 and $P = T - R$.%
@@
 \citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
-Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$;%
+Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
+$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
+$R$ to estimate $\yh_{t+1}$%
 \footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
@@
 dependent random process} %
-$R$ is kept finite as $T \to \infty$, so
+and $R$ is kept finite as $T \to \infty$ so that
 $\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window length $R$ avoids
-the degeneracy that often arises in OOS test statistics (see
+variables used to estimate it. Using a finite window length $R$ prevents
+the degeneracy that can arise when comparing nested models out-of-sample (see
 \citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the OOS average remains positive and the average obeys a \clt, an
-approach introduced by \citet{GiW:06}.
+of the OOS average remains positive and the average obeys a \clt.%
+\footnote{This approach was first introduced by \citet{GiW:06}.} %
 
@@
 an \mds. In the 2006 paper, Clark and West assume that the
-coefficients $\btrue$ are zero under the null, making
+coefficients on the benchmark model, $\btrue$, are zero under the null, making
 $\ep_{t+1}$ observed directly. This restriction is relaxed in
-the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
+the 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
 rolling window. Now the estimated linear model's prediction errors,
@@
 asymptotically mean-zero normal, even though this approximation
-performs well in simulations.
+performs well in simulations. Since the window length is finite,
+the estimators of $\beta_0$ do not converge to $\beta_0$.
 
@@
 but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$; so
+$\eph_{t+1}$; i.e.
 \begin{equation}
@@
 \end{equation*}
-is asymptotically normal with mean zero under the null for fairly
+is asymptotically normal with mean zero under Clark and West's MDS
+null for fairly
 arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
@@
 to make the intuition as clear as possible. The next section lists the
-specific assumptions that need to hold.
+specific assumptions for a more general case.
 
-\subsection{Assumptions}
+\subsection{Theoretical assumptions}
 \label{sec:1a}
 
-The assumptions required are essentially the same in existing papers
-(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
-\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
+Consider the following environment. There is a single linear
+benchmark model of the target variable, $y_{t+1}$:
+\begin{equation}\label{eq:1}
+  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
+\end{equation}
+where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
+observed vector of predictors. The parameter $\beta$ is
+estimated with OLS using a recursive window as described by
+Equation~\eqref{eq:8}
+and the period-$t$ forecast is given by
+\begin{equation}\label{eq:3}
+  \yh_{0,t+1} = x_t'\bh_t.
+\end{equation}
+
+We deviate slightly from the previous section's introduction by
+allowing for multiple alternative models, as in \cite{HuW:10}. This
+allowance is crucial if we want the statistic to be empirically
+useful, since almost every empirical analysis considers several
+alternative models at once.  Each of these alternative models is
+denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estiatmed with a
+rolling window of length $R$.
+
+These conditions are summarized in the first assumption.
 
 \begin{asmp}\label{a1}%
-  The benchmark forecast $\yh_{0,t+1}$, is estimated using \ols\
-  with a recursive window: $\yh_{0,t+1} = x_t'\bh_t$ for
-  some vector of predictors $x_t$ with $\bh_t$ given by
-  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
-  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
-  depend on~$t$.
-
-  The alternative forecast, $\yh_{1t}$, is estimated using a
-  rolling window of fixed length $R$ (which is less than $T$), so
-  $\yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
-  $\psi$ is a known function and $z_t$ is a sequence of predictors
-  that may include $x_t$.
+  The benchmark forecast, $\yh_{0,t+1}$, is generated by
+  Equation~\eqref{eq:3}, where $\bh_t$ is constructed with a recursive
+  window and satisfies~\eqref{eq:8}. The alternative forecasts are
+  estimated using a rolling window of length $R$, so $\yh_{j,t+1} =
+  \psi_j(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi_j$ is a
+  known function and $z_t$ is a sequence of predictors that may
+  include $x_t$. The window length, $R$, remains finite as $T \to
+  \infty$.
 \end{asmp}
 
+Assumption~\ref{a3} describes the DGP. The weak dependence and moment
+conditions are standard. These assumptions are slightly weaker than
+similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
+because we make use of more recent developments in limit theory, in
+particular the CLT for Near-Epoch Dependent (NED) processes proven by
+\cite{Jon:97}.
+
 \begin{asmp}\label{a3}%
-  The series $y_t$, $\yh_{1t}$, and $x_t$ have uniformly bounded
-  $2 r$ moments for some $r > 2$, and $\yh_t y_t$ $\yh_t
-  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
-  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
-  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
+  The series $y_t$, $x_t$, and $z_t$ are NED of size $-1/2$ on either a
+  strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
+  mixing process of size $-\frac{r}{2r-2}$ for $r \geq 2$. Moreover,
+  $y_t$ and $\yh_{j,t+1}$, $j = 1,\dots,J$, have uniformly bounded $2 r$
+  moments.
 \end{asmp}
 
+The requirement that the alternative forecasts satisfy a moment
+condition, rather than the underlying predictors $z_t$, is somewhat
+unappealing but necessary. The functions $\psi_j$ that generate these
+forecasts is essentially unrestricted, so even well-behaved predictors
+could produce arbitrarily badly-behaved forecasts. For example, if
+\begin{equation*}
+  z_t \sim \iid~\bernoulli(1/2),
+\end{equation*}
+setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a CLT from holding
+since the forecast equals positive infinity with probability $1/2$. It
+is easy to construct less obvious examples of problematic functions as
+well. Assumption~\ref{a3} implicitly rules out these functional forms
+by imposing moment conditions on the alternative models' forecasts.
+
+Finally, we define some notation for the \oos\ statistic. The
+adjusted OOS loss for each alternative model and a hypothetical value
+of $\beta$ is denoted by
+\begin{equation}
+  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
+  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
+\end{equation}
+and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
+Also define
+\begin{align*}
+  \fh_t &= f_t(\bh),
+  &\fb(\beta) &= \oavg{t} f_t(\beta),
+  &\text{and}&
+  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
+\end{align*}
+with $P = T - R$. Also define $\beta_0$ to be the pseudotrue value of
+$\beta$ that minimizes the MSE of the benchmark model,
+\begin{equation*}
+  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
+\end{equation*}
+and let $\Sigma$ be the asymptotic variance of $\fb$, $\Sigma
+= \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
+The next assumption ensures that $\Sigma$ is positive definite.
 \begin{asmp}\label{a4}%
-  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
-  \yh_{1,t+1})^2 + (x_t'\beta - \yh_{1,t+1})^2,\] $f_t =
-  f_t(\btrue)$, $\fh_t = f_t(\bh_t)$, $\fb(\beta) =
-  \oavg{t} f_t(\beta)$, and $\fb = \tfrac1P \sum_{t=R+1}^{T} \fh_t$
-  with $P = T - R$; $\fb(\btrue)$ has uniformly positive and
-  finite long run variance.
+  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
 \end{asmp}
+
+This assumption is much less restrictive than in \cite{Wes:96}.  As in
+\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
+rule out pathological cases---for example, letting both the benchmark
+and the alternative models be perfectly correlated white noise. In
+\citet{Wes:96}, this assumption is a restriction on the \dgp\ as well
+as the forecasting models, but in this paper it is a restriction only
+on the models.
 
@@
 \begin{thm}\label{res:1}
-  Suppose that we have two models $\yh_{0t}$ and $\yh_{1t}$ to
-  forecast the variable $y_t$, and have observations for
-  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
-  Under the null hypothesis that $y_t - \yh_{0t}(\btrue)$ is a
-  martingale difference sequence with respect to the filtration
-  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
-  $\tfrac{\sqrt{P}}{\sh} \fb \to^d N(0,1)$, where
-  \begin{align*}
-    \sh^2 &= \Sh_{ff} + 2 (\Sh_{fg} + \Sh_{gg}), &
-    \Sh_{ff} &= \oavg{t} (\fh_t - \fb)^2, \\
-    \Sh_{fg} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
-    \Sh_{gg} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
-  \end{align*}
-  $\gb = \oavg{t}
-  \gh_t$, $\X' = [x_1,\dots,x_T]$,
-  \begin{equation*}
-    g_t(\beta) =
-    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}'
-    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
-  \end{equation*}
-  and $\gh_t = g_t(\bh_t)$.
+  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
+  (\fb - \E f_t) \to^d N(0, \Sigma)$.
 \end{thm}
@@
   $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
-\end{rem}
-
-\begin{rem}
-  The requirement that the asymptotic variance of $\fb(\btrue)$ is
-  uniformly positive is much less restrictive than in \cite{Wes:96}.
-  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
-  serves to rule out pathological cases---for example, letting both
-  the benchmark and the alternative model be perfectly correlated white noise. In
-  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
-  well as the forecasting models, but in this paper it is a
-  restriction only on the models.
 \end{rem}

### 2014-04-15 mixedwindow.tex
Edit the motivation subsection that introduces the statistic
This commit makes some minor changes to the motivation section
to try to improve exposition, etc.

--- 2014-04-11 mixedwindow.tex
@@
 to make the intuition as clear as possible. The next section lists the
-specific assumptions that need to hold.
+specific assumptions for a more general case.
 

### 2014-10-29 appendix.tex
Move appendix and proofs to a separate document

--- 2014-04-11 mixedwindow.tex
@@
 \documentclass[12pt,fleqn]{article}
-
-\usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
-\usepackage[T1]{fontenc}
-\usepackage[sort,round,comma]{natbib}
-\usepackage[margin=1.25in]{geometry}
-\usepackage[small]{caption}
-\usepackage[charter]{mathdesign}
-\urlstyle{same}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\bibliographystyle{abbrvnat}
-\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
-\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
-\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
-\frenchspacing
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the monte carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% run.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lema}{Lemma}[section]
-\newtheorem{alg}{Algorithm}
-\newtheorem{asmp}{Assumption}
-
-\theoremstyle{definition}
-
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-\newtheorem{rem}{Remark}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator{\cov}{cov}
-%\DeclareMathOperator{\vec}{vec}
-\DeclareMathOperator{\vech}{vech}
-
-\DeclareMathOperator{\pr}{Pr}
-
-\newcommand{\Bh}{\hat{B}}
-\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
-\newcommand{\bh}{\hat{\beta}}
-\newcommand{\bt}{\tilde{\beta}}
-\newcommand{\ep}{\varepsilon}
-\newcommand{\eph}{\hat{\varepsilon}}
-\newcommand{\Fh}{\hat{F}}
-\newcommand{\Fs}{\mathcal{F}}
-\newcommand{\fb}{\bar{f}}
-\newcommand{\fh}{\hat{f}}
-\newcommand{\gb}{\bar{g}}
-\newcommand{\gh}{\hat{g}}
-\newcommand{\Sh}{\hat{S}}
-\newcommand{\Sigmah}{\hat\Sigma}
-\newcommand{\sh}{\hat\sigma}
-\newcommand{\yh}{\hat{y}}
-
-\newcommand{\X}{\ensuremath{\mathrm{X}}}
-\newcommand{\R}{\ensuremath{\mathrm{R}}}
-\newcommand{\p}{\ensuremath{\mathrm{P}}}
-
-\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
-\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
-\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
-
-\newcommand{\aic}{AIC}
-\newcommand{\bic}{BIC}
-\newcommand{\brc}{BRC}
-\newcommand{\cdf}{CDF}
-\newcommand{\clt}{CLT}
-\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
-\newcommand{\dgp}{DGP}
-\newcommand{\fclt}{FCLT}
-\newcommand{\fwe}{FWE}
-\newcommand{\gdp}{GDP}
-\newcommand{\hac}{HAC}
-\newcommand{\lln}{LLN}
-\newcommand{\ma}{MA}
-\newcommand{\mds}{MDS}
-\newcommand{\ned}{NED}
-\newcommand{\ols}{OLS}
-\newcommand{\oos}{OOS}
-\newcommand{\sfwe}{SFWE}
-\newcommand{\spa}{SPA}
-\newcommand{\wfwe}{WFWE}
-
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
-
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\renewcommand{\dbltopfraction}{.66}
-\renewcommand{\dblfloatpagefraction}{.66}
-\setcounter{topnumber}{9}
-\setcounter{bottomnumber}{9}
-\setcounter{totalnumber}{20}
-\setcounter{dbltopnumber}{9}
-
-\begin{document}
+\input{tex/setup}
+\usepackage{xr}
+\externaldocument{mixedwindow}
 
@@
     \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
-    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 NBER-NSF Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
+    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.}\\%
   Iowa State University}
 
-\title{An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models}
-
-% \date{March 14, 2013}
-
-\maketitle
-
-\begin{abstract} 
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested.  Moreover, the alternative model can be estimated using
-  common model selection methods, such as the \aic\ or \bic, without
-  affecting the asymptotic distribution of this test statistic.  The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the DGP is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection
-
-\strut
-
-\noindent JEL Classification Numbers: C22, C53
-
-\end{abstract}
-
-\newpage
-
-\section{Introduction} This paper proposes an out-of-sample (\oos)
-test statistic that is asymptotically normal with mean zero even when
-the models studied are nested.
-\oos\ tests are commonly used in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.%
-\footnote{Other papers in this literature include
-  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
-  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
-  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
-  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
-  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
-  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
-  reviews of this literature and additional references, see
-  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
-  \citet{CoD:11}, and \citet{Gia:11}} %
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic appropriately.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  implicitly assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is a
-random walk \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-In this paper, I show that a modified version of their statistic is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-
-Mixing window strategies is uncommon but needn't be. In most
-applications, the null hypothesis imposes stability as well as equal
-accuracy between the two models.  The benchmark model rarely allows
-for breaks, parameter drift, or other forms of
-instability,%
-\footnote{Exceptions are \citepos{StW:07}
-  IMA(1,1) and UC-SV models of inflation.} %
-but the
-researcher is typically concerned about instability.  Indeed, concern
-about instability is often given as a reason for doing an \oos\
-analysis, especially with a short rolling window.%
-\footnote{This
-  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
-  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
-  \cite{GiR:09,GiR:10}, among others.} %
-A researcher could impose
-stability on both models by using a recursive window or relax
-stability for both by using a rolling window; either approach should
-not affect the test's size, but may affect power.  But the researcher
-could instead impose stability on the benchmark and relax it for the
-alternative by using a recursive window for the benchmark and a
-rolling window for the alternative model.  This approach could have a
-power advantage and is similar in spirit to using a Likelihood Ratio
-Test instead of an LM or Wald test, which depend on just the
-restricted or unrestricted model respectively.
-
-This paper's statistic has a substantial advantage over existing \oos\
-tests for nested models: the alternative can be essentially arbitrary
-as long as high level moment conditions hold.  In particular,
-researchers can use model selection techniques like the \aic\ or \bic\
-to determine the number of lags to include, the particular exogenous
-variables to include, etc.  Other methods that test a similar
-hypothesis are unable to handle these models \citep[except][which does
-not allow the benchmark to be estimated]{ClW:06}; \citet{GiW:06} are
-able to handle such models for both the alternative and the benchmark
-but, as mentioned earlier, they test a different aspect of forecasting
-performance.
-
-This paper focuses on nested models, as they have received the most
-attention in the empirical and theoretical literature, but the
-statistic can be used with non-nested models as well.  This generality
-is useful, since \citepos{Wes:96} results do not apply to non-nested
-models if they both encompass the true \dgp,%
-\footnote{\citet{ClM:11b}
-  call this scenario, ``overlapping models.''} %
-which is allowable
-under the null: in the limit, both models will converge to the \dgp\
-and give identical forecasts.  Consequently, the naive \oos\ $t$-test
-is invalid, even after correcting the standard error if necessary to
-reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
-window \oos\ $t$-test remains normal for these models but the
-recursive and rolling windows (with the window size increasing to
-$\infty$) do not, and provide a procedure for pointwise (but not
-uniformly) valid tests for the recursive and rolling windows and
-uniformly valid tests for the fixed window.  The test proposed in this
-paper is uniformly valid and places fewer assumptions on the models
-under study and the true \dgp.
-
-The next section presents our new statistics and Section~\ref{sec:2} presents
-simulations that compare our test to \poscw\ original
-statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
-by reanalyzing \citepos{GoW:08} study of excess return
-predictability. Section~\ref{sec:4} concludes.
-
-\section{Theoretical results supporting the asympotically normal OOS statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistc, then section~\ref{sec:1a}
-presents the paper's key assumptions and section~\ref{sec:1b} presents
-our formal theoretical results.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$; also let $v_t$ be another random process that may contain information about
-$y_{t+1}$ and suppose that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient of the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to the information set
-\begin{equation*}
-\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
-y_{t-1}),\dots),
-\end{equation*}
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-and is asymptotically normal as $P \to \infty$, with $R$ an
-arbitrary starting value%
-\footnote{It will be clear momentarily why the
-  summation begins at $R+1$ instead of $1$.} %
-and $P = T - R$.%
-\footnote{Section~\ref{sec:1b} discusses conditions under which the
-  \mds\ condition holds. We will also present results that allow
-  $\ep_{t+1}$ to be serially correlated.} %
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
-\end{equation}
-
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
-Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$;%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-$R$ is kept finite as $T \to \infty$, so
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window length $R$ avoids
-the degeneracy that often arises in OOS test statistics (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the OOS average remains positive and the average obeys a \clt, an
-approach introduced by \citet{GiW:06}.
-
-\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
-an \mds. In the 2006 paper, Clark and West assume that the
-coefficients $\btrue$ are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
-rolling window. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations.
-
-This paper proposes using the same basic \oos\ statistic, 
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$; so
-\begin{equation}
-  \label{eq:8}
-  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
-  \sum_{s=2}^t x_{t-1} y_t.
-\end{equation}
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under the null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-This overview has presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions that need to hold.
-
-\subsection{Assumptions}
-\label{sec:1a}
-
-The assumptions required are essentially the same in existing papers
-(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
-\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
-
-\begin{asmp}\label{a1}%
-  The benchmark forecast $\yh_{0,t+1}$, is estimated using \ols\
-  with a recursive window: $\yh_{0,t+1} = x_t'\bh_t$ for
-  some vector of predictors $x_t$ with $\bh_t$ given by
-  Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
-  x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not
-  depend on~$t$.
-
-  The alternative forecast, $\yh_{1t}$, is estimated using a
-  rolling window of fixed length $R$ (which is less than $T$), so
-  $\yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where
-  $\psi$ is a known function and $z_t$ is a sequence of predictors
-  that may include $x_t$.
-\end{asmp}
-
-\begin{asmp}\label{a3}%
-  The series $y_t$, $\yh_{1t}$, and $x_t$ have uniformly bounded
-  $2 r$ moments for some $r > 2$, and $\yh_t y_t$ $\yh_t
-  x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1}, x_{t-1}'$ are $L_2$-\ned\ of
-  size $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$
-  for $r>2$ or a uniform mixing series of size $-\frac{r}{2r-2}$.
-\end{asmp}
-
-\begin{asmp}\label{a4}%
-  Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} -
-  \yh_{1,t+1})^2 + (x_t'\beta - \yh_{1,t+1})^2,\] $f_t =
-  f_t(\btrue)$, $\fh_t = f_t(\bh_t)$, $\fb(\beta) =
-  \oavg{t} f_t(\beta)$, and $\fb = \tfrac1P \sum_{t=R+1}^{T} \fh_t$
-  with $P = T - R$; $\fb(\btrue)$ has uniformly positive and
-  finite long run variance.
-\end{asmp}
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-\begin{thm}\label{res:1}
-  Suppose that we have two models $\yh_{0t}$ and $\yh_{1t}$ to
-  forecast the variable $y_t$, and have observations for
-  $t=1,\dots,T+1$. Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.
-  Under the null hypothesis that $y_t - \yh_{0t}(\btrue)$ is a
-  martingale difference sequence with respect to the filtration
-  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
-  $\tfrac{\sqrt{P}}{\sh} \fb \to^d N(0,1)$, where
-  \begin{align*}
-    \sh^2 &= \Sh_{ff} + 2 (\Sh_{fg} + \Sh_{gg}), &
-    \Sh_{ff} &= \oavg{t} (\fh_t - \fb)^2, \\
-    \Sh_{fg} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
-    \Sh_{gg} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
-  \end{align*}
-  $\gb = \oavg{t}
-  \gh_t$, $\X' = [x_1,\dots,x_T]$,
-  \begin{equation*}
-    g_t(\beta) =
-    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}'
-    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
-  \end{equation*}
-  and $\gh_t = g_t(\bh_t)$.
-\end{thm}
-
-The following remarks are relevant to Theorem~\ref{res:1}:
-
-\begin{rem}
-  Forecasters are usually interested in the one-sided alternative that
-  $\E f_t > 0$; i.e. that the alternative model is expected
-  to forecast better than the benchmark.
-\end{rem}
-
-\begin{rem}
-  These results are presented for one-period-ahead forecasting for
-  simplicity.  They can be extended to forecasting at a longer horizon
-  by appropriately modifying the variance-covariance matrix to account
-  for the correlation structure of the forecast errors. (i.e. for
-  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
-\end{rem}
-
-\begin{rem}
-  The requirement that the asymptotic variance of $\fb(\btrue)$ is
-  uniformly positive is much less restrictive than in \cite{Wes:96}.
-  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
-  serves to rule out pathological cases---for example, letting both
-  the benchmark and the alternative model be perfectly correlated white noise. In
-  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
-  well as the forecasting models, but in this paper it is a
-  restriction only on the models.
-\end{rem}
-
-Define $\X' = [x_1,\dots,x_T]$
-
-\begin{align*}
-  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
-  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
-\end{align*}
-
-Define the variables
-$g_t(\beta) = \Fh \Bh x_t(y_{t+1} - x_t'\beta)$,
-$\gh_t = g_t(\bh_t)$, and $\gb = \oavg{t} \gh_t$.
-
-\newcommand{\K}[1]{K(\tfrac{#1}{w})}
-
-Define the general covariance estimator:
-\begin{align*}
-  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
-  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
-  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
-\end{align*}
-
-Define the MDS covariance estimator:
-\begin{align*}
-  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
-  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
-  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
-\end{align*}
-
-\begin{lem}\label{lem:2}
-  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
-  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
-  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
-\end{lem}
-
-\begin{rem}
-  The statistic we present tests the null hypothesis that the forecast
-  errors from the population version of the benchmark model are a
-  martingale difference sequence.  This hypothesis may not be
-  appropriate, depending on the loss function or utility function of
-  interest.  If one wants to test the less restrictive null hypothesis that
-  $y_{t} - \yh_{0t}$ is uncorrelated with $\yh_{1t}$ but not
-  necessarily an \mds, one can replace $\Sh_{21}$, $\Sh_{22}$
-  and $\Sh_{23}$ with their \hac\ counterparts.
-  Our statistic can also be modified to test implications of
-  optimal forecasts under other loss functions
-  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
-  a forecast encompassing test using the models' generalized forecast
-  errors.%
-\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
-  Again, Lemma~\ref{res:a5} can cover these other applications.
-\end{rem}
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the MASS
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
-  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_t$
-on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as \poscw\
-rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations 
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[CW roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects; 
-    Pr[CW rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recrusive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, I conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
-\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
-$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the ``predictor'' column of
-Table~\ref{tab:em1} \citep[see][for a detailed description of the
-variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the ``predictor'' column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The ``value'' column
-  lists the value of this paper's \oos\ statistic, the ``naive''
-  column indicates whether the statistic is significant at standard
-  critical values, and the ``corrected'' column indicates significance
-  using the critical values proposed in Theorem~\ref{res:2} that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-``value'' gives the value of the test statistic for each model, while
-the ``naive'' indicates whether the statistic is greater than the
-standard \bootsize\% critical value (\naivecriticalvalue) Three
-predictors are
-significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance. A
-full treatment of this issue is beyond the scope of this paper,
-however, it is straightforward to use Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to derive an appropriate critical value as
-in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
-the MDS null hypothesis, the continuous mapping theorem implies that
-$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
-\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
-\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
-\hat D^{-1/2})$ distribution to generate a critical value for the
-\emph{largest} individual test statistic under the null ---
-\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
-this critical value, none of the predictors are siginificant at
-\bootsize\%.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here. Moreover, I need to
-  explain why it's not a concern for these statistics in general.} %
-
-\section{Conclusion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window---as do Clark and West---but estimating
-the benchmark model with a recursive window.  Simulations indicate
-that the new statistic behaves similarly to Clark and West's original
-test when the \dgp\ is stable but can have much higher power when the 
-\dgp\ has structural breaks.
-
-\appendix
-\section{Proofs of Main Theoretical Results}
-\label{sec:B}
+\title{Supplemental Appendix for ``An asymptotically normal out-of-sample
+  test of equal predictive accuracy for nested models''}
 
@@
 
+\begin{document}
+\maketitle
+
+\noindent%
+This appendix contains mathematical proofs and some supporting Lemmas
+for the paper, ``An asymptotically normal out-of-sample test of equal
+predictive accuracy for nested models.''
 Define the additional notation
@@
 
-\begin{proof}[Proof of Theorem \ref{res:1}]
+\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
+\begin{proof}
   Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
@@
 
-\begin{proof}[Proof of Theorem \ref{res:2}]
+\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
+\begin{proof}
   Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
@@
 
-\section{Supporting Results}
+\section*{Supporting Results}
+\stepcounter{section}
+\renewcommand\thesection{\Alph{section}}
 
-\begin{lema}\label{res:a2}
+\begin{alem}\label{res:a2}
   Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
@@
   \end{enumerate}
-\end{lema}
+\end{alem}
 
-\begin{proof}[Proof of Lemma~\ref{res:a2}]
+\begin{proof}
   \begin{enumerate}
@@
 
-\begin{lema}\label{res:a4}
+\begin{alem}\label{res:a4}
   Under the conditions of Theorem~\ref{res:1}, Equations
   \eqref{eq:11}--\eqref{eq:13} hold.
-\end{lema}
+\end{alem}
 
@@
 \end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann

### 2014-10-29 mixedwindow.tex
Change empirical variables to italic
Move appendix and proofs to a separate document

--- 2014-04-15 mixedwindow.tex
@@
 \documentclass[12pt,fleqn]{article}
-
-\usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
-\usepackage[T1]{fontenc}
-\usepackage[sort,round,comma]{natbib}
-\usepackage[margin=1.25in]{geometry}
-\usepackage[small]{caption}
-\usepackage[charter]{mathdesign}
-\urlstyle{same}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\bibliographystyle{abbrvnat}
-\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
-\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
-\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
-\frenchspacing
+\input{tex/setup}
 \input{tex/mcDef}
@@
 
-% These commands are generated when the monte carlo and applied
+% These commands are generated when the Monte Carlo and applied
 % sections are run; I'm giving them definitions now so that LaTeX will
-% run.
+% compile the document even if that code hasn't been run yet.
 \providecommand\bootsize{[missing]}
@@
 \providecommand\empiricaltable{[missing]}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lema}{Lemma}[section]
-\newtheorem{alg}{Algorithm}
-\newtheorem{asmp}{Assumption}
-
-\theoremstyle{definition}
-
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-\newtheorem{rem}{Remark}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator{\cov}{cov}
-\DeclareMathOperator*{\plim}{plim}
-%\DeclareMathOperator{\vec}{vec}
-\DeclareMathOperator{\vech}{vech}
-
-\DeclareMathOperator{\pr}{Pr}
-
-\newcommand{\iid}{\ensuremath\mathit{i.i.d.}}
-\newcommand{\bernoulli}{\ensuremath\mathit{bernoulli}}
-
-\newcommand{\Bh}{\hat{B}}
-\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
-\newcommand{\bh}{\hat{\beta}}
-\newcommand{\bt}{\tilde{\beta}}
-\newcommand{\ep}{\varepsilon}
-\newcommand{\eph}{\hat{\varepsilon}}
-\newcommand{\Fh}{\hat{F}}
-\newcommand{\Fs}{\mathcal{F}}
-\newcommand{\fb}{\bar{f}}
-\newcommand{\fh}{\hat{f}}
-\newcommand{\gb}{\bar{g}}
-\newcommand{\gh}{\hat{g}}
-\newcommand{\Sh}{\hat{S}}
-\newcommand{\Sigmah}{\hat\Sigma}
-\newcommand{\sh}{\hat\sigma}
-\newcommand{\yh}{\hat{y}}
-
-\newcommand{\X}{\ensuremath{\mathrm{X}}}
-\newcommand{\R}{\ensuremath{\mathrm{R}}}
-\newcommand{\p}{\ensuremath{\mathrm{P}}}
-
-\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
-\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
-\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
-
-\newcommand{\aic}{AIC}
-\newcommand{\bic}{BIC}
-\newcommand{\brc}{BRC}
-\newcommand{\cdf}{CDF}
-\newcommand{\clt}{CLT}
-\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
-\newcommand{\dgp}{DGP}
-\newcommand{\fclt}{FCLT}
-\newcommand{\fwe}{FWE}
-\newcommand{\gdp}{GDP}
-\newcommand{\hac}{HAC}
-\newcommand{\lln}{LLN}
-\newcommand{\ma}{MA}
-\newcommand{\mds}{MDS}
-\newcommand{\ned}{NED}
-\newcommand{\ols}{OLS}
-\newcommand{\oos}{OOS}
-\newcommand{\sfwe}{SFWE}
-\newcommand{\spa}{SPA}
-\newcommand{\wfwe}{WFWE}
-
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
-
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\renewcommand{\dbltopfraction}{.66}
-\renewcommand{\dblfloatpagefraction}{.66}
-\setcounter{topnumber}{9}
-\setcounter{bottomnumber}{9}
-\setcounter{totalnumber}{20}
-\setcounter{dbltopnumber}{9}
-
-\begin{document}
 
@@
 
+\begin{document}
 \maketitle
@@
 by reanalyzing \citepos{GoW:08} study of excess return
-predictability. Section~\ref{sec:4} concludes.
+predictability and Section~\ref{sec:4} concludes. Proofs of
+our results have been put in a separate Appendix along with
+some minor supporting arguments \citep{Cal:14}.
 
@@
 
-\begin{thm}\label{res:1}
-  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
-  (\fb - \E f_t) \to^d N(0, \Sigma)$.
-\end{thm}
+\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
 
@@
 
-\begin{lem}\label{lem:2}
-  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
-  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
-  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
-\end{lem}
+\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
 
@@
 original) and the alternative models are of the form
-\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
-\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
+\begin{equation*}
+  \mathit{excess~return}_{t} = \alpha_{0} + \alpha_{1}\
+  \mathit{predictor}_{t-1} + \ep_{t},
+\end{equation*}
+where $\alpha_{0}$ and
 $\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
@@
 
-\appendix
-\section{Proofs of Main Theoretical Results}
-\label{sec:B}
-
-\newcommand{\WesA}[1][]{\oclt{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\oclt{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-Define the additional notation 
-$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
-$F_t = F_t(\btrue)$,
-and
-$h_t = h_t(\btrue)$.
-
-\begin{proof}[Proof of Theorem \ref{res:1}]
-  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
-  statistic; this substitution does not affect its asymptotic
-  distribution.
-  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
-  $\btrue$ to get
-  \begin{align*}
-    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
-    \big(f_t - \E f_t\big) +
-    \E F_t B \oclt{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
-  \end{align*}
-  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
-  \begin{equation*}
-    w_{it} = \tfrac12 (\bh_t - \btrue)'
-    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
-    f_{it}(\bt_{it}) \Big]
-    (\bh_t - \btrue)
-  \end{equation*}
-  and each $\bt_{it}$ lies between $\bh_t$ and
-  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
-  Then, as before,
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12}\\
-  \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
-  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.
-
-  Note that \[f_t(\btrue)= 2 (y_{t+1} -
-  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
-  in \citet{ClW:07}, which is an \mds, so we do not need to use a
-  \hac\ estimator of the variance under the null.  Also observe that
-  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
-  y_{t+1})\] and the second term is an \mds\ under the null,
-  explaining the particular form of $g_t(\beta)$.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{res:2}]
-  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
-  \citet{RoW:05} complete the proof.
-\end{proof}
-
-\section{Supporting Results}
-
-\begin{lema}\label{res:a2}
-  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
-  hold.
-  \begin{enumerate}
-  \item $P^a \sup_t | H_{t} | \to^p 0$.
-  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
-  \end{enumerate}
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a2}]
-  \begin{enumerate}
-  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
-    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
-    \begin{equation}
-      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
-      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
-        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
-    \end{equation}
-    with the convergence following from the continuous mapping
-    theorem.
-  \item We have
-    \begin{equation}
-      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
-      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
-      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
-      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
-    \end{equation}
-    and both terms converge to zero in (conditional) probability by
-    the previous argument and by assumption.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
-    \citepos{Jon:97} \clt, so the result is trivial.
-  \end{enumerate}
-\end{proof}
-
-\begin{lema}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a4}]
-We can write
-\begin{equation*}
-  \Big\lvert \WesA \Big\rvert \leq 
-  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
-  \sup_t | H_t |.
-\end{equation*}
-From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
-(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
-of \eqref{eq:12} and \eqref{eq:13} are similar.
-\end{proof}
-
 \bibliography{texextra/AllRefs}

### 2014-10-29 appendix.tex
Update homepage listed on paper and appendix

@@
     \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.}\\%
+    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
+    gcalhoun\guillemotright.}\\%
   Iowa State University}

### 2014-10-29 mixedwindow.tex
Update homepage listed on paper and appendix
Remove trailing whitespace characters
Swap some acronyms for predefined macros

@@
     \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
+    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
+    gcalhoun\guillemotright.
     I'd like to
@@
   much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the DGP is subject to instability.
+  use-case for these tests: when the \dgp\ is subject to instability.
   This procedure is then used to analyze
@@
 
-Assumption~\ref{a3} describes the DGP. The weak dependence and moment
+Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
 conditions are standard. These assumptions are slightly weaker than
@@
 because we make use of more recent developments in limit theory, in
-particular the CLT for Near-Epoch Dependent (NED) processes proven by
+particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
 \cite{Jon:97}.
@@
 \begin{asmp}\label{a3}%
-  The series $y_t$, $x_t$, and $z_t$ are NED of size $-1/2$ on either a
+  The series $y_t$, $x_t$, and $z_t$ are \ned\ of size $-1/2$ on either a
   strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
@@
 \end{equation*}
-setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a CLT from holding
+setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
 since the forecast equals positive infinity with probability $1/2$. It

### 2014-10-29 mixedwindow.tex
Extensive rewrite of supporting results
- Fix the proofs
- Add results over R+1,...,R'

--- 2014-10-29 mixedwindow.tex
@@
 \documentclass[12pt,fleqn]{article}
-\input{tex/setup}
+
+\usepackage{amsfonts}
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
+\usepackage[T1]{fontenc}
+\usepackage[sort,round,comma]{natbib}
+\usepackage[margin=1.25in]{geometry}
+\usepackage[small]{caption}
+\usepackage[charter]{mathdesign}
+\urlstyle{same}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\bibliographystyle{abbrvnat}
+\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
+\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
+\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
+\frenchspacing
 \input{tex/mcDef}
@@
 
-% These commands are generated when the Monte Carlo and applied
+% These commands are generated when the monte carlo and applied
 % sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
+% run.
 \providecommand\bootsize{[missing]}
@@
 \providecommand\nboot{[missing]}
+\providecommand\nmod{[missing]}
 \providecommand\testsize{[missing]}
@@
 \providecommand\empiricaltable{[missing]}
+\providecommand\empiricaldraws{[missing]}
+\providecommand\naivecriticalvalue{[missing]}
+
+\newtheorem{thm}{Theorem}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{claim}[thm]{Claim}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{lema}{Lemma}[section]
+\newtheorem{alg}{Algorithm}
+\newtheorem{asmp}{Assumption}
+
+\theoremstyle{definition}
+
+\newtheorem{example}{Example}
+\newtheorem{defn}{Definition}
+\newtheorem{rem}{Remark}
+
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator{\diag}{diag}
+\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\var}{var}
+\DeclareMathOperator{\cov}{cov}
+\DeclareMathOperator*{\plim}{plim}
+%\DeclareMathOperator{\vec}{vec}
+\DeclareMathOperator{\vech}{vech}
+
+\DeclareMathOperator{\pr}{Pr}
+
+\newcommand{\iid}{\ensuremath\mathit{i.i.d.}}
+\newcommand{\bernoulli}{\ensuremath\mathit{bernoulli}}
+
+\newcommand{\Bh}{\hat{B}}
+\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
+\newcommand{\bh}{\hat{\beta}}
+\newcommand{\bt}{\tilde{\beta}}
+\newcommand{\ep}{\varepsilon}
+\newcommand{\eph}{\hat{\varepsilon}}
+\newcommand{\Fh}{\hat{F}}
+\newcommand{\Fs}{\mathcal{F}}
+\newcommand{\fb}{\bar{f}}
+\newcommand{\fh}{\hat{f}}
+\newcommand{\gb}{\bar{g}}
+\newcommand{\gh}{\hat{g}}
+\newcommand{\Sh}{\hat{S}}
+\newcommand{\Sigmah}{\hat\Sigma}
+\newcommand{\sh}{\hat\sigma}
+\newcommand{\yh}{\hat{y}}
+
+\newcommand{\X}{\ensuremath{\mathrm{X}}}
+\newcommand{\R}{\ensuremath{\mathrm{R}}}
+\newcommand{\p}{\ensuremath{\mathrm{P}}}
+
+\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
+\newcommand{\osumb}[1]{\sum_{#1=R'+1}^T}
+\newcommand{\osumc}[1]{\sum_{#1=R+1}^{R'}}
+\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
+\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
+\newcommand{\ocltb}[1]{\tfrac{1}{\sqrt{P}} \osumb{#1}}
+\newcommand{\ocltc}[1]{\tfrac{1}{\sqrt{P}} \osumc{#1}}
+
+\newcommand{\aic}{AIC}
+\newcommand{\bic}{BIC}
+\newcommand{\brc}{BRC}
+\newcommand{\cdf}{CDF}
+\newcommand{\clt}{CLT}
+\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
+\newcommand{\dgp}{DGP}
+\newcommand{\fclt}{FCLT}
+\newcommand{\fwe}{FWE}
+\newcommand{\gdp}{GDP}
+\newcommand{\hac}{HAC}
+\newcommand{\lln}{LLN}
+\newcommand{\ma}{MA}
+\newcommand{\mds}{MDS}
+\newcommand{\ned}{NED}
+\newcommand{\ols}{OLS}
+\newcommand{\oos}{OOS}
+\newcommand{\sfwe}{SFWE}
+\newcommand{\spa}{SPA}
+\newcommand{\wfwe}{WFWE}
+
+\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
+
+\renewcommand{\topfraction}{.85}
+\renewcommand{\bottomfraction}{.7}
+\renewcommand{\textfraction}{.15}
+\renewcommand{\floatpagefraction}{.66}
+\renewcommand{\dbltopfraction}{.66}
+\renewcommand{\dblfloatpagefraction}{.66}
+\setcounter{topnumber}{9}
+\setcounter{bottomnumber}{9}
+\setcounter{totalnumber}{20}
+\setcounter{dbltopnumber}{9}
+
+\begin{document}
 
@@
 
-\begin{document}
 \maketitle
@@
 by reanalyzing \citepos{GoW:08} study of excess return
-predictability and Section~\ref{sec:4} concludes. Proofs of
-our results have been put in a separate Appendix along with
-some minor supporting arguments \citep{Cal:14}.
+predictability. Section~\ref{sec:4} concludes.
 
@@
 
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
+\begin{thm}\label{res:1}
+  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
+  (\fb - \E f_t) \to^d N(0, \Sigma)$.
+\end{thm}
 
@@
 
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
+\begin{lem}\label{lem:2}
+  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
+  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
+  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
+\end{lem}
 
@@
 original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t} = \alpha_{0} + \alpha_{1}\
-  \mathit{predictor}_{t-1} + \ep_{t},
-\end{equation*}
-where $\alpha_{0}$ and
+\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
+\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
 $\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
@@
 
+\appendix
+\section{Main theoretical results}
+\label{sec:B}
+
+\newcommand{\WesA}[1][]{\ocltb{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
+  B^{#1}) H_t^{#1}}
+\newcommand{\WesC}[1][]{\ocltb{t}
+  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
+
+Define the additional notation 
+$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
+$F_t = F_t(\btrue)$,
+and
+$h_t = h_t(\btrue)$.
+
+\begin{proof}[Proof of Theorem \ref{res:1}]
+  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
+  statistic; this substitution does not affect its asymptotic
+  distribution.
+  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
+  $\btrue$ to get
+  \begin{align*}
+    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
+    \big(f_t - \E f_t\big) +
+    \E F_t B \oclt{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
+  \end{align*}
+  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
+  \begin{equation*}
+    w_{it} = \tfrac12 (\bh_t - \btrue)'
+    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
+    f_{it}(\bt_{it}) \Big]
+    (\bh_t - \btrue)
+  \end{equation*}
+  and each $\bt_{it}$ lies between $\bh_t$ and
+  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
+  Then, as before,
+  \begin{gather}
+    \WesA \to^{p} 0 \label{eq:11} \\
+    \WesB \to^{p} 0 \label{eq:12}\\
+  \intertext{and}
+    \WesC \to^{p} 0 \label{eq:13}
+  \end{gather}
+  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
+  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.
+
+  Note that \[f_t(\btrue)= 2 (y_{t+1} -
+  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
+  in \citet{ClW:07}, which is an \mds, so we do not need to use a
+  \hac\ estimator of the variance under the null.  Also observe that
+  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
+  y_{t+1})\] and the second term is an \mds\ under the null,
+  explaining the particular form of $g_t(\beta)$.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{res:2}]
+  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
+  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
+  \citet{RoW:05} complete the proof.
+\end{proof}
+
+\begin{thm}
+  If the conditions of Theorem~\ref{res:1} and that $y_{t+1} -
+  x_t'\btrue$ is an MDS with respect to $\Fs_t$ then $\Sigmah_2 \to^p
+  \Sigma$, where $\Sigmah_2 = \Sh_{ff} + \Sh_{2,fg} + \Sh_{2,fg}' +
+  \Sh_{2,gg}$, with $\Sh_{ff}$ defined earlier and
+  \begin{align}
+    \Sh_{fg,2} &= \oavg{t} (\fh_t - \fb) (\gh_t - \gb_2)' \\
+    \Sh_{gg,2} &= \oavg{t} (\gh_{2t} - \gb_2) (\gh_{2t} - \gb_2)' \\
+    \gh_{2t} &= \Bigg\{\sum_{s=\max(t, R+1)}^T \tfrac1s \Fh_s \Bh_s\Bigg\} x_{t-1} \ep_t
+    \intertext{and}
+    \gb_2 &= \oavg{t} \gh_{2t}.
+  \end{align}
+\end{thm}
+
+\section{Supporting results}
+
+\begin{lema}\label{res:a1}
+  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
+  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$. Then
+  \begin{equation*}
+    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
+  \end{equation*}
+\end{lema}
+
+\begin{proof}
+  We can rewrite this summation as
+  \begin{multline*}
+    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
+    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
+    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
+  \end{multline*}
+  Each of these individual summations can be shown to converge to
+  zero in probability. First,
+  \begin{equation*}
+    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
+    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
+    = O(R'/\sqrt{P}).
+  \end{equation*}
+  Also,
+  \begin{align*}
+    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
+    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
+    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
+    & = O_p(R'/\sqrt{P})
+  \end{align*}
+  and
+  \begin{equation*}
+    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
+    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
+    = O_p(R'/\sqrt{P}).
+  \end{equation*}
+  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
+  construction, this completes the proof.
+\end{proof}
+
+\begin{lema}\label{res:a2}
+  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
+  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
+  \infty$ and $R' = o(\sqrt{P})$. Then
+  \begin{enumerate}
+  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
+  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
+  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
+  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
+  \end{enumerate}
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a2}]
+  We will prove each part in order.
+  \begin{enumerate}
+  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
+    the same mixing process as the original variables) by
+    Assumption~\ref{a3}, and the moment and size conditions in that
+    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
+    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
+    \begin{equation}\label{eq:2}
+      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
+    \end{equation}
+    where $W(\cdot)$ is a multivariate Gaussian process.
+
+    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
+    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
+    \begin{equation*}
+      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
+    \end{equation*}
+    and the limit in~\eqref{eq:2} is again almost surely 0. The
+    Continuous Mapping Theorem then implies that
+    \begin{equation*}
+      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
+    \end{equation*}
+  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
+    $-1/2$. As a result, we can use a maximal inequality of
+    \cite{Mcl:75} (also available as Corollary 16.10 in
+    \citealp{Dav:94}), giving
+    \begin{align*}
+      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
+      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
+      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
+    \end{align*}
+    which converges to a finite limit.
+  \item We have
+    \begin{multline*}
+      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
+      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
+      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
+      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
+    \end{multline*}
+    and both terms converge to zero in probability by Part 1 and by
+    assumption.
+  \item Similar to the previous argument, we have
+    \begin{multline*}
+      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
+      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
+      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
+      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
+    \end{multline*}
+    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
+  \end{enumerate}
+\end{proof}
+
+\begin{lema}\label{res:a4}
+  Under the conditions of Theorem~\ref{res:1}, Equations
+  \eqref{eq:11}--\eqref{eq:13} hold.
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a4}]
+We can write
+\begin{equation*}
+  \Big\lvert \WesA \Big\rvert \leq
+  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
+  \sup_{t = R'+1,\dots,T} | H_t |.
+\end{equation*}
+From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
+that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
+establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
+and~\eqref{eq:13} are similar.
+\end{proof}
+
 \bibliography{texextra/AllRefs}

### 2014-10-30 mixedwindow.tex
Add new dummy macros for empirics
The empirics code defines some LaTeX macros that convey design
choices, etc. This commit provides default definitions for them
so that the LaTeX compiles whether or not the simulations have
been run. I've done this before, but must have missed these
macros.

@@
 \newcommand{\osum}[1]{\sum_{#1=R+1}^T}
-\newcommand{\osumb}[1]{\sum_{#1=R'+1}^T}
-\newcommand{\osumc}[1]{\sum_{#1=R+1}^{R'}}
 \newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
 \newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
-\newcommand{\ocltb}[1]{\tfrac{1}{\sqrt{P}} \osumb{#1}}
-\newcommand{\ocltc}[1]{\tfrac{1}{\sqrt{P}} \osumc{#1}}
 
@@
 \appendix
-\section{Main theoretical results}
+\section{Proofs of Main Theoretical Results}
 \label{sec:B}
 
-\newcommand{\WesA}[1][]{\ocltb{t}
+\newcommand{\WesA}[1][]{\oclt{t}
   (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
   B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
+\newcommand{\WesC}[1][]{\oclt{t}
   (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
@@
 
-\begin{thm}
-  If the conditions of Theorem~\ref{res:1} and that $y_{t+1} -
-  x_t'\btrue$ is an MDS with respect to $\Fs_t$ then $\Sigmah_2 \to^p
-  \Sigma$, where $\Sigmah_2 = \Sh_{ff} + \Sh_{2,fg} + \Sh_{2,fg}' +
-  \Sh_{2,gg}$, with $\Sh_{ff}$ defined earlier and
-  \begin{align}
-    \Sh_{fg,2} &= \oavg{t} (\fh_t - \fb) (\gh_t - \gb_2)' \\
-    \Sh_{gg,2} &= \oavg{t} (\gh_{2t} - \gb_2) (\gh_{2t} - \gb_2)' \\
-    \gh_{2t} &= \Bigg\{\sum_{s=\max(t, R+1)}^T \tfrac1s \Fh_s \Bh_s\Bigg\} x_{t-1} \ep_t
-    \intertext{and}
-    \gb_2 &= \oavg{t} \gh_{2t}.
-  \end{align}
-\end{thm}
-
-\section{Supporting results}
-
-\begin{lema}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{lema}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
-    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
+\section{Supporting Results}
 
 \begin{lema}\label{res:a2}
-  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
+  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
+  hold.
   \begin{enumerate}
-  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
-  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
-  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
-  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
+  \item $P^a \sup_t | H_{t} | \to^p 0$.
+  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
   \end{enumerate}
@@
 \begin{proof}[Proof of Lemma~\ref{res:a2}]
-  We will prove each part in order.
   \begin{enumerate}
-  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
-    the same mixing process as the original variables) by
-    Assumption~\ref{a3}, and the moment and size conditions in that
-    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
-    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
-    \begin{equation}\label{eq:2}
-      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
+  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
+    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
+    \begin{equation}
+      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
+      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
+        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
     \end{equation}
-    where $W(\cdot)$ is a multivariate Gaussian process.
-
-    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
-    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
-    \begin{equation*}
-      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
-    \end{equation*}
-    and the limit in~\eqref{eq:2} is again almost surely 0. The
-    Continuous Mapping Theorem then implies that
-    \begin{equation*}
-      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
-    \end{equation*}
-  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
-    $-1/2$. As a result, we can use a maximal inequality of
-    \cite{Mcl:75} (also available as Corollary 16.10 in
-    \citealp{Dav:94}), giving
-    \begin{align*}
-      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
+    with the convergence following from the continuous mapping
+    theorem.
   \item We have
-    \begin{multline*}
-      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
-    \end{multline*}
-    and both terms converge to zero in probability by Part 1 and by
-    assumption.
-  \item Similar to the previous argument, we have
-    \begin{multline*}
-      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
-    \end{multline*}
-    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
+    \begin{equation}
+      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
+      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
+      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
+      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
+    \end{equation}
+    and both terms converge to zero in (conditional) probability by
+    the previous argument and by assumption.
+  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
+    \citepos{Jon:97} \clt, so the result is trivial.
   \end{enumerate}
@@
   \Big\lvert \WesA \Big\rvert \leq 
-  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
-  \sup_{t = R'+1,\dots,T} | H_t |.
+  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
+  \sup_t | H_t |.
 \end{equation*}
-From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
-that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
-establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
-and~\eqref{eq:13} are similar.
+From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
+(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
+of \eqref{eq:12} and \eqref{eq:13} are similar.
 \end{proof}

### 2014-10-30 mixedwindow.tex
Add notation and clarification to beginning of appendix
- Defines a few terms that had been accidentally deleted at the beginning
  of the appendix
- Add text specifying that the proofs are for scalars.
Rephrase parts of proof of Theorem 1

--- 2014-10-29 mixedwindow.tex
@@
 Define the additional notation 
+$f_t = f_t(\btrue)$,
 $F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
 $F_t = F_t(\btrue)$,
+$h_t = h_t(\btrue)$,
 and
-$h_t = h_t(\btrue)$.
+\begin{equation*}
+  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
+\end{equation*}
+All of the proofs in this section will be presented for the case where
+there is a single alternative model. The Cram\'er-Wold device ensures
+that the corresponding multivariate results follow trivially.
 
 \begin{proof}[Proof of Theorem \ref{res:1}]
-  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
-  statistic; this substitution does not affect its asymptotic
-  distribution.
-  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
-  $\btrue$ to get
+  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
+  \begin{equation*}
+    \sqrt{P} (\fb - \E \fb(\btrue))
+    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
+      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
+  \end{equation*}
+  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
+  we can rewrite this summation as
   \begin{align*}
-    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
-    \big(f_t - \E f_t\big) +
-    \E F_t B \oclt{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
+    \sqrt{P} (\fb - \E \fb(\btrue))
+    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
   \end{align*}
-  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
-  \begin{equation*}
-    w_{it} = \tfrac12 (\bh_t - \btrue)'
-    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
-    f_{it}(\bt_{it}) \Big]
-    (\bh_t - \btrue)
-  \end{equation*}
-  and each $\bt_{it}$ lies between $\bh_t$ and
-  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
-  Then, as before,
+  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
+
+  Lemma~\ref{res:a4} shows that
   \begin{gather}
     \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12}\\
+    \WesB \to^{p} 0 \label{eq:12} \\
     \intertext{and}
@@
   \end{gather}
-  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
-  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.
-
-  Note that \[f_t(\btrue)= 2 (y_{t+1} -
-  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
-  in \citet{ClW:07}, which is an \mds, so we do not need to use a
-  \hac\ estimator of the variance under the null.  Also observe that
-  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
-  y_{t+1})\] and the second term is an \mds\ under the null,
-  explaining the particular form of $g_t(\beta)$.
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{res:2}]
-  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
-  \citet{RoW:05} complete the proof.
+  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
+  w_t = o_{p}(1)$. Finally,
+  \begin{equation*}
+    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
+  \end{equation*}
+  using the same argument as \citet{Wes:96}.
 \end{proof}

### 2014-10-31 mixedwindow.tex
Remove redundant theorem from appendix
Tweak wording in introduction to paper

@@
 test statistic that is asymptotically normal with mean zero even when
-the models studied are nested.
+the models studied are nested.  This paper also proves that common
+block bootstrap methods consistently estimate the statistic's
+distribution, and shows how the statistic can be used to study many
+models simultaneously while maintaining strong control of the
+familywise error (\fwe), i.e. ensuring that the probability that the
+hypothesis that the model has equal predictive ability to a benchmark
+is incorrectly rejected for any of the models is no higher than a
+preset level.
+
 \oos\ tests are commonly used in International Macroeconomics,
@@
 
-The next section presents our new statistics and Section~\ref{sec:2} presents
-simulations that compare our test to \poscw\ original
+The next section presents our new statistic. Section~\ref{sec:2} presents
+simulations that compare our pairwise \oos\ test to \poscw\ original
 statistics. Section~\ref{sec:3} demonstrates the use of our statistic
@@
 
-For comparison, we study this paper's new statistic as well as \poscw\
-rolling-window and recursive-window test statistics.  Clark and West
+For comparison, we study this paper's new statistic as well as
+\poscw\ rolling-window and recursive-window test statistics.  Clark and West
 only prove that their rolling-window statistic is asymptotically
@@
 
-\begin{thm}
-  If the conditions of Theorem~\ref{res:1} and that $y_{t+1} -
-  x_t'\btrue$ is an MDS with respect to $\Fs_t$ then $\Sigmah_2 \to^p
-  \Sigma$, where $\Sigmah_2 = \Sh_{ff} + \Sh_{2,fg} + \Sh_{2,fg}' +
-  \Sh_{2,gg}$, with $\Sh_{ff}$ defined earlier and
-  \begin{align}
-    \Sh_{fg,2} &= \oavg{t} (\fh_t - \fb) (\gh_t - \gb_2)' \\
-    \Sh_{gg,2} &= \oavg{t} (\gh_{2t} - \gb_2) (\gh_{2t} - \gb_2)' \\
-    \gh_{2t} &= \Bigg\{\sum_{s=\max(t, R+1)}^T \tfrac1s \Fh_s \Bh_s\Bigg\} x_{t-1} \ep_t
-    \intertext{and}
-    \gb_2 &= \oavg{t} \gh_{2t}.
-  \end{align}
-\end{thm}
-
 \section{Supporting results}

### 2014-10-31 mixedwindow.tex
Change Assumption 3 on NED size
The NED size conditions were incorrect; this commit changes them to
the right ones.

@@
 \begin{asmp}\label{a3}%
-  The series $y_t$, $x_t$, and $z_t$ are NED of size $-1/2$ on either a
-  strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
-  mixing process of size $-\frac{r}{2r-2}$ for $r \geq 2$. Moreover,
-  $y_t$ and $\yh_{j,t+1}$, $j = 1,\dots,J$, have uniformly bounded $2 r$
-  moments.
+  The series $y_t$, $x_t$, and $z_t$ are $L_2$-NED of size
+  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
+  $-r/(r-2)$ or a uniform mixing process of size
+  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
+  1,\dots,J$, have uniformly bounded $2 r$ moments.
 \end{asmp}

### 2014-10-31 mixedwindow.tex
Add variance-covariance matrix to Theorem 1

@@
 
+Asymptotic normality of the OOS average follows directly from the
+previous three assumptions without any other conditions. The proof is
+presented in the Appendix and follows \citet{Wes:96} directly.
+
 \begin{thm}\label{res:1}
-  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
-  (\fb - \E f_t) \to^d N(0, \Sigma)$.
+  If Assumptions~\ref{a1} -- \ref{a4} hold then $\sqrt{P} (\fb - \E
+  \fb(\btrue)) \to^d N(0, \Sigma)$, with
+  \begin{align*}
+    \Sigma &= S_{ff} + S_{fg} + S_{fg}' + 2 \, S_{gg}, &
+    S_{ff}  &= \lim P \var(\fb(\btrue)), \\
+    S_{fg}  &= \lim P \cov(\fb(\btrue), \gb(\btrue)), &
+    S_{gg}  &= \lim P \var(\gb(\btrue)).
+  \end{align*}
 \end{thm}
+
+Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
+\begin{equation*}
+  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
+\end{equation*}
+
+Clearly, the main use of this theorem is to test the null hypothesis
+$\E f_t = 0$.
 

### 2014-10-31 mixedwindow.tex
Very minor tweaks to wording of paper

--- 2014-10-31 mixedwindow.tex
@@
 \providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
 \providecommand\testsize{[missing]}
@@
 \providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{claim}[thm]{Claim}
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lema}{Lemma}[section]
-\newtheorem{alg}{Algorithm}
-\newtheorem{asmp}{Assumption}
-
-\theoremstyle{definition}
-
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-\newtheorem{rem}{Remark}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator{\cov}{cov}
-\DeclareMathOperator*{\plim}{plim}
-%\DeclareMathOperator{\vec}{vec}
-\DeclareMathOperator{\vech}{vech}
-
-\DeclareMathOperator{\pr}{Pr}
-
-\newcommand{\iid}{\ensuremath\mathit{i.i.d.}}
-\newcommand{\bernoulli}{\ensuremath\mathit{bernoulli}}
-
-\newcommand{\Bh}{\hat{B}}
-\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
-\newcommand{\bh}{\hat{\beta}}
-\newcommand{\bt}{\tilde{\beta}}
-\newcommand{\ep}{\varepsilon}
-\newcommand{\eph}{\hat{\varepsilon}}
-\newcommand{\Fh}{\hat{F}}
-\newcommand{\Fs}{\mathcal{F}}
-\newcommand{\fb}{\bar{f}}
-\newcommand{\fh}{\hat{f}}
-\newcommand{\gb}{\bar{g}}
-\newcommand{\gh}{\hat{g}}
-\newcommand{\Sh}{\hat{S}}
-\newcommand{\Sigmah}{\hat\Sigma}
-\newcommand{\sh}{\hat\sigma}
-\newcommand{\yh}{\hat{y}}
-
-\newcommand{\X}{\ensuremath{\mathrm{X}}}
-\newcommand{\R}{\ensuremath{\mathrm{R}}}
-\newcommand{\p}{\ensuremath{\mathrm{P}}}
-
-\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
-\newcommand{\osumb}[1]{\sum_{#1=R'+1}^T}
-\newcommand{\osumc}[1]{\sum_{#1=R+1}^{R'}}
-\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
-\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
-\newcommand{\ocltb}[1]{\tfrac{1}{\sqrt{P}} \osumb{#1}}
-\newcommand{\ocltc}[1]{\tfrac{1}{\sqrt{P}} \osumc{#1}}
-
-\newcommand{\aic}{AIC}
-\newcommand{\bic}{BIC}
-\newcommand{\brc}{BRC}
-\newcommand{\cdf}{CDF}
-\newcommand{\clt}{CLT}
-\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
-\newcommand{\dgp}{DGP}
-\newcommand{\fclt}{FCLT}
-\newcommand{\fwe}{FWE}
-\newcommand{\gdp}{GDP}
-\newcommand{\hac}{HAC}
-\newcommand{\lln}{LLN}
-\newcommand{\ma}{MA}
-\newcommand{\mds}{MDS}
-\newcommand{\ned}{NED}
-\newcommand{\ols}{OLS}
-\newcommand{\oos}{OOS}
-\newcommand{\sfwe}{SFWE}
-\newcommand{\spa}{SPA}
-\newcommand{\wfwe}{WFWE}
-
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
-
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\renewcommand{\dbltopfraction}{.66}
-\renewcommand{\dblfloatpagefraction}{.66}
-\setcounter{topnumber}{9}
-\setcounter{bottomnumber}{9}
-\setcounter{totalnumber}{20}
-\setcounter{dbltopnumber}{9}
-
-\begin{document}
 
@@
 
-The next section presents our new statistic. Section~\ref{sec:2} presents
-simulations that compare our pairwise \oos\ test to \poscw\ original
+The next section presents our new statistics and Section~\ref{sec:2} presents
+simulations that compare our test to \poscw\ original
 statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
 by reanalyzing \citepos{GoW:08} study of excess return
-predictability. Section~\ref{sec:4} concludes.
+predictability and Section~\ref{sec:4} concludes. Proofs of
+our results have been put in a separate Appendix along with
+some minor supporting arguments \citep{Cal:14}.
 
@@
 \footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
-  Again, Lemma~\ref{res:a5} can cover these other applications.
 \end{rem}
@@
 
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
+For comparison, we study this paper's new statistic as well as \poscw\
+rolling-window and recursive-window test statistics.  Clark and West
 only prove that their rolling-window statistic is asymptotically
@@
   critical values, and the ``corrected'' column indicates significance
-  using the critical values proposed in Theorem~\ref{res:2} that
+  using critical values that
   account for the number of models.  See Section~\ref{sec:3} for details.}
@@
 
-\appendix
-\section{Main theoretical results}
-\label{sec:B}
-
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-Define the additional notation 
-$f_t = f_t(\btrue)$,
-$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
-$F_t = F_t(\btrue)$,
-$h_t = h_t(\btrue)$,
-and
-\begin{equation*}
-  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
-\end{equation*}
-All of the proofs in this section will be presented for the case where
-there is a single alternative model. The Cram\'er-Wold device ensures
-that the corresponding multivariate results follow trivially.
-
-\begin{proof}[Proof of Theorem \ref{res:1}]
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
-    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
-      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
-  \end{equation*}
-  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
-  we can rewrite this summation as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
-    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. Finally,
-  \begin{equation*}
-    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
-  \end{equation*}
-  using the same argument as \citet{Wes:96}.
-\end{proof}
-
-\section{Supporting results}
-
-\begin{lema}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{lema}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
-    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\begin{lema}\label{res:a2}
-  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
-  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
-  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
-  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
-  \end{enumerate}
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a2}]
-  We will prove each part in order.
-  \begin{enumerate}
-  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
-    the same mixing process as the original variables) by
-    Assumption~\ref{a3}, and the moment and size conditions in that
-    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
-    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
-    \begin{equation}\label{eq:2}
-      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
-    \end{equation}
-    where $W(\cdot)$ is a multivariate Gaussian process.
-
-    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
-    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
-    \begin{equation*}
-      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
-    \end{equation*}
-    and the limit in~\eqref{eq:2} is again almost surely 0. The
-    Continuous Mapping Theorem then implies that
-    \begin{equation*}
-      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
-    \end{equation*}
-  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
-    $-1/2$. As a result, we can use a maximal inequality of
-    \cite{Mcl:75} (also available as Corollary 16.10 in
-    \citealp{Dav:94}), giving
-    \begin{align*}
-      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item We have
-    \begin{multline*}
-      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
-    \end{multline*}
-    and both terms converge to zero in probability by Part 1 and by
-    assumption.
-  \item Similar to the previous argument, we have
-    \begin{multline*}
-      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
-    \end{multline*}
-    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\begin{lema}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{lema}
-
-\begin{proof}[Proof of Lemma~\ref{res:a4}]
-We can write
-\begin{equation*}
-  \Big\lvert \WesA \Big\rvert \leq
-  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
-  \sup_{t = R'+1,\dots,T} | H_t |.
-\end{equation*}
-From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
-that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
-establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
-and~\eqref{eq:13} are similar.
-\end{proof}
-
 \bibliography{texextra/AllRefs}

### 2014-10-31 appendix.tex

@@
 
-\newcommand{\WesA}[1][]{\oclt{t}
+\newcommand{\WesA}[1][]{\ocltb{t}
   (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
+\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
   B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\oclt{t}
+\newcommand{\WesC}[1][]{\ocltb{t}
   (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
@@
 Define the additional notation 
+$f_t = f_t(\btrue)$,
 $F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
 $F_t = F_t(\btrue)$,
+$h_t = h_t(\btrue)$,
 and
-$h_t = h_t(\btrue)$.
+\begin{equation*}
+  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
+\end{equation*}
+All of the proofs in this section will be presented for the case where
+there is a single alternative model. The Cram\'er-Wold device ensures
+that the corresponding multivariate results follow trivially.
 
@@
 \begin{proof}
-  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
-  statistic; this substitution does not affect its asymptotic
-  distribution.
-  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
-  $\btrue$ to get
+  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
+  \begin{equation*}
+    \sqrt{P} (\fb - \E \fb(\btrue))
+    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
+      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
+  \end{equation*}
+  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
+  we can rewrite this summation as
   \begin{align*}
-    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
-    \big(f_t - \E f_t\big) +
-    \E F_t B \oclt{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
+    \sqrt{P} (\fb - \E \fb(\btrue))
+    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
   \end{align*}
-  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
-  \begin{equation*}
-    w_{it} = \tfrac12 (\bh_t - \btrue)'
-    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
-    f_{it}(\bt_{it}) \Big]
-    (\bh_t - \btrue)
-  \end{equation*}
-  and each $\bt_{it}$ lies between $\bh_t$ and
-  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
-  Then, as before,
+  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
+
+  Lemma~\ref{res:a4} shows that
   \begin{gather}
     \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12}\\
+    \WesB \to^{p} 0 \label{eq:12} \\
     \intertext{and}
@@
   \end{gather}
-  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
-  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.
-
-  Note that \[f_t(\btrue)= 2 (y_{t+1} -
-  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
-  in \citet{ClW:07}, which is an \mds, so we do not need to use a
-  \hac\ estimator of the variance under the null.  Also observe that
-  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
-  y_{t+1})\] and the second term is an \mds\ under the null,
-  explaining the particular form of $g_t(\beta)$.
+  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
+  w_t = o_{p}(1)$. Finally,
+  \begin{equation*}
+    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
+  \end{equation*}
+  using the same argument as \citet{Wes:96}.
 \end{proof}
@@
 
+\begin{alem}\label{res:a1}
+  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
+  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$. Then
+  \begin{equation*}
+    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
+  \end{equation*}
+\end{alem}
+
+\begin{proof}
+  We can rewrite this summation as
+  \begin{multline*}
+    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
+    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
+    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
+  \end{multline*}
+  Each of these individual summations can be shown to converge to
+  zero in probability. First,
+  \begin{equation*}
+    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
+    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
+    = O(R'/\sqrt{P}).
+  \end{equation*}
+  Also,
+  \begin{align*}
+    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
+    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
+    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
+    & = O_p(R'/\sqrt{P})
+  \end{align*}
+  and
+  \begin{equation*}
+    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
+    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
+    = O_p(R'/\sqrt{P}).
+  \end{equation*}
+  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
+  construction, this completes the proof.
+\end{proof}
+
 \begin{alem}\label{res:a2}
-  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
-  hold.
+  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
+  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
+  \infty$ and $R' = o(\sqrt{P})$. Then
   \begin{enumerate}
-  \item $P^a \sup_t | H_{t} | \to^p 0$.
-  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
+  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
+  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
+  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
+  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
   \end{enumerate}
@@
 \begin{proof}
+  We will prove each part in order.
   \begin{enumerate}
-  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
-    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
-    \begin{equation}
-      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
-      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
-        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
+  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
+    the same mixing process as the original variables) by
+    Assumption~\ref{a3}, and the moment and size conditions in that
+    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
+    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
+    \begin{equation}\label{eq:2}
+      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
     \end{equation}
-    with the convergence following from the continuous mapping
-    theorem.
+    where $W(\cdot)$ is a multivariate Gaussian process.
+
+    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
+    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
+    \begin{equation*}
+      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
+    \end{equation*}
+    and the limit in~\eqref{eq:2} is again almost surely 0. The
+    Continuous Mapping Theorem then implies that
+    \begin{equation*}
+      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
+    \end{equation*}
+  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
+    $-1/2$. As a result, we can use a maximal inequality of
+    \cite{Mcl:75} (also available as Corollary 16.10 in
+    \citealp{Dav:94}), giving
+    \begin{align*}
+      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
+      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
+      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
+    \end{align*}
+    which converges to a finite limit.
   \item We have
-    \begin{equation}
-      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
-      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
-      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
-      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
-    \end{equation}
-    and both terms converge to zero in (conditional) probability by
-    the previous argument and by assumption.
-  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
-    \citepos{Jon:97} \clt, so the result is trivial.
+    \begin{multline*}
+      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
+      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
+      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
+      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
+    \end{multline*}
+    and both terms converge to zero in probability by Part 1 and by
+    assumption.
+  \item Similar to the previous argument, we have
+    \begin{multline*}
+      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
+      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
+      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
+      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
+    \end{multline*}
+    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
   \end{enumerate}
@@
 
-\begin{proof}[Proof of Lemma~\ref{res:a4}]
+\begin{proof}
 We can write
@@
   \Big\lvert \WesA \Big\rvert \leq
-  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
-  \sup_t | H_t |.
+  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
+  \sup_{t = R'+1,\dots,T} | H_t |.
 \end{equation*}
-From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
-(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
-of \eqref{eq:12} and \eqref{eq:13} are similar.
+From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
+that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
+establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
+and~\eqref{eq:13} are similar.
 \end{proof}

### 2014-10-31 mixedwindow.tex

@@
 \providecommand\empiricaltable{[missing]}
+\providecommand\empiricaldraws{[missing]}
+\providecommand\naivecriticalvalue{[missing]}
 
@@
 
+Asymptotic normality of the OOS average follows directly from the
+previous three assumptions without any other conditions. The proof is
+presented in the Appendix and follows \citet{Wes:96} directly.
+
 \begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
+
+Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
+\begin{equation*}
+  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
+\end{equation*}
+
+Clearly, the main use of this theorem is to test the null hypothesis
+$\E f_t = 0$.
 

### 2014-11-03 mixedwindow.tex
Tweak notation

@@
 performs well in simulations. Since the window length is finite,
-the estimators of $\beta_0$ do not converge to $\beta_0$.
+the estimators of $\btrue$ do not converge to $\btrue$.
 
@@
 \end{align*}
-with $P = T - R$. Also define $\beta_0$ to be the pseudotrue value of
+with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
+$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
+Also define $\btrue$ to be the pseudotrue value of
 $\beta$ that minimizes the MSE of the benchmark model,
@@
 \end{equation*}
-and let $\Sigma$ be the asymptotic variance of $\fb$, $\Sigma
-= \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
+and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
 The next assumption ensures that $\Sigma$ is positive definite.
@@
 \begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
+In Theorem~\ref{res:1}, define the variables
+$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
+$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
+$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.
 
-Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
+Null hypothesis: $y_{t+1} - x_t'\btrue$ is an MDS with respect to
 \begin{equation*}
@@
 \end{align*}
-
-Define the variables
-$g_t(\beta) = \Fh \Bh x_t(y_{t+1} - x_t'\beta)$,
-$\gh_t = g_t(\bh_t)$, and $\gb = \oavg{t} \gh_t$.
 

### 2014-11-03 appendix.tex
Tweak notation
Add proof of vcv consistency

@@
   \begin{equation*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
+    \sqrt{P} (\fb - \E \fb^*)
     = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
@@
   \begin{align*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
+    \sqrt{P} (\fb - \E \fb^*)
     &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
@@
 \begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
+We will only prove $\Sigmah_2 \to^p \Sigma$. The result for
+$\Sigmah_1$ is essentially the same, but uses \citet{JoD:00} instead
+of the simple \lln.
 \begin{proof}
-  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
-  \citet{RoW:05} complete the proof.
+  First
+  \begin{align*}
+    \Sh_{21} &= \oavg{t} (f_t - \E \fb(\btrue) + \fh_t - f_t - \fb + \E \fb(\btrue))^2 \\
+    \Sh_{22} &= \oavg{t} (f_t - \E \fb(\btrue) + \fh_t - f_t - \fb + \E \fb(\btrue))
+                        (g_t - \E \gb^* + \gh_t - g_t - \gb + \E \gb^*)
+    \intertext{and}
+    \Sh_{23} &= \oavg{t} (g_t - \E \gb^* + \gh_t - g_t - \gb + \E \gb^*)^2
+  \end{align*}
+  so $\Sigmah_2 \to^p \Sigma$ as long as
+  $\fb - \E \fb(\btrue) \to^p 0$,
+  $\gb - \E \gb^* \to^p 0$,
+  \begin{gather}
+    \oavg{t} (f_t - \E \fb^*)^2 \to^p \var(\sqrt{P} \fb^*) \label{eq:1} \\
+    \oavg{t} (g_t - \E \gb^*)^2 \to^p \var(\sqrt{P} \gb^*) \label{eq:3} \\
+    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
+    \intertext{and}
+    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
+  \end{gather}
+  The first two results are proven in Theorem~\ref{res:1}
+  and~\eqref{eq:1} and~\eqref{eq:3} follow from the \lln, so it
+  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.
+
+  As before, let $R'$ be a new sequence such that $R' \to \infty$ as
+  $T \to \infty$ and $R' = o(\sqrt{P})$.  Some algebra reveals
+  that~\eqref{eq:4} holds if
+  \begin{gather}
+    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
+    \intertext{and}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \label{eq:14}.
+  \end{gather}
+  Now~\eqref{eq:10} is bounded by
+  \begin{align*}
+    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
+    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
+    &\leq \sup_{t=R+1,\dots,R'} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \sup_{t=R'+1,\dots,T} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  by Lemma~\ref{res:a2} and the \lln.
+  A similar argument holds for the second term:
+  \begin{align*}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
+    &\leq \sup_{t=R+1,\dots,R'} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &\quad+ \sup_{t=R'+1,\dots,T} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
+  zero by construction. The proof of~\eqref{eq:5} is similar.
 \end{proof}

### 2014-11-04 mixedwindow.tex

@@
 \begin{asmp}\label{a3}%
-  The series $y_t$, $x_t$, and $z_t$ are $L_2$-NED of size
+  The series $y_t$, $x_t$, and $z_t$ are $L_2$-\ned\ of size
   $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size

### 2014-11-04 appendix.tex
Add additional acronyms and convert remaining mistakes

@@
   \begin{enumerate}
-  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
+  \item The process $x_{t-1} \ep_t$ is $L_2$-\ned\ of size $-1/2$ (on
     the same mixing process as the original variables) by

### 2014-11-04 mixedwindow.tex
Add additional acronyms and convert remaining mistakes

@@
     Meng-Feng Yen and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 NBER-NSF Time Series conference
+    Group meeting and the 2013 \nber-\nsf\ Time Series conference
     for helpful comments and discussions.  I'd also like to thank Amit
@@
 \footnote{Exceptions are \citepos{StW:07}
-  IMA(1,1) and UC-SV models of inflation.} %
+  \allcaps{IMA}(1,1) and \allcaps{UC}-\allcaps{SV} models of inflation.} %
 but the
@@
 power advantage and is similar in spirit to using a Likelihood Ratio
-Test instead of an LM or Wald test, which depend on just the
+Test instead of an \lm\ or Wald test, which depend on just the
 restricted or unrestricted model respectively.
@@
 
-\section{Theoretical results supporting the asympotically normal OOS statistic}
+\section{Theoretical results supporting the asympotically normal \oos\ statistic}
 \label{sec:1}
@@
 \citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the OOS average remains positive and the average obeys a \clt.%
+of the \oos\ average remains positive and the average obeys a \clt.%
 \footnote{This approach was first introduced by \citet{GiW:06}.} %
@@
 \end{equation*}
-is asymptotically normal with mean zero under Clark and West's MDS
-null for fairly
+is asymptotically normal with mean zero under Clark and West's
+\mds\ null for fairly
 arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
@@
 observed vector of predictors. The parameter $\beta$ is
-estimated with OLS using a recursive window as described by
+estimated with \ols\ using a recursive window as described by
 Equation~\eqref{eq:8}
@@
 Finally, we define some notation for the \oos\ statistic. The
-adjusted OOS loss for each alternative model and a hypothetical value
+adjusted \oos\ loss for each alternative model and a hypothetical value
 of $\beta$ is denoted by
@@
 
-Asymptotic normality of the OOS average follows directly from the
+Asymptotic normality of the \oos\ average follows directly from the
 previous three assumptions without any other conditions. The proof is
@@
 
-Null hypothesis: $y_{t+1} - x_t'\btrue$ is an MDS with respect to
+Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
 \begin{equation*}
@@
 
-Define the MDS covariance estimator:
+Define the \mds\ covariance estimator:
 \begin{align*}
@@
 \footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the MASS
+  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
   \citep[7.3-22]{VeR:02} package.} %
@@
     \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[CW roll.] shows the fraction of simulations for
+    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
     which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[CW rec.] shows the fraction of simulations for which
+    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
     their recursive-window statistic rejects; and Pr[new] shows the fraction of
@@
 in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
-the MDS null hypothesis, the continuous mapping theorem implies that
+the \mds\ null hypothesis, the continuous mapping theorem implies that
 $\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i

### 2014-11-04 appendix.tex
Revise theoretical component of paper

--- 2014-10-31 appendix.tex
@@
 
-\author{Gray Calhoun\thanks{ Economics Department; Iowa State
+\author{Gray Calhoun\thanks{Economics Department; Iowa State
     University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
@@
 \newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
+  (F_t^{#1} - F) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
   B^{#1}) H_t^{#1}}
 \newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
+  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
 
@@
 for the paper, ``An asymptotically normal out-of-sample test of equal
-predictive accuracy for nested models.''
-Define the additional notation 
-$f_t = f_t(\btrue)$,
-$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
-$F_t = F_t(\btrue)$,
-$h_t = h_t(\btrue)$,
-and
+predictive accuracy for nested models.''  Define the following
+additional terms:
 \begin{equation*}
-  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
+  F_t(\beta) = (4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t',
 \end{equation*}
-All of the proofs in this section will be presented for the case where
-there is a single alternative model. The Cram\'er-Wold device ensures
-that the corresponding multivariate results follow trivially.
+$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
+x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
+$H_t = \sum_{s=1}^{t-1} x_t \ep_{t+1} / (t-1)$.
+And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
 
@@
   and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
+  \begin{equation}\label{eq:6}
+    \sqrt{P} (\fb - \E \fb^*)
     = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
       + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
-  \end{equation*}
-  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
-  we can rewrite this summation as
+  \end{equation}
+  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
+  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
   \begin{align*}
-    \sqrt{P} (\fb - \E \fb(\btrue))
-    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
+    \sqrt{P} (\fb - \E \fb^*)
+    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
     & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
@@
   where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-
   Lemma~\ref{res:a4} shows that
@@
   and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. Finally,
+  w_t = o_{p}(1)$. The proof that
   \begin{equation*}
-    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
+    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
   \end{equation*}
-  using the same argument as \citet{Wes:96}.
+  follows the same argument as in \citet{Wes:96}.
 \end{proof}
@@
 \begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
+We will only prove $\sigmah_2 \to^p \sigma$. The result for
+$\sigmah_1$ is essentially the same, but uses \citepos{JoD:00} Theorem
+2.1 instead of an application of the \lln.
 \begin{proof}
-  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
-  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
-  \citet{RoW:05} complete the proof.
+  First, we can rewrite the components of the variance estimator as
+  \begin{align*}
+    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
+    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
+                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
+    \intertext{and}
+    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
+  \end{align*}
+  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
+  $\fb - \E \fb^* \to^p 0$,
+  $\gb - \E \gb^* \to^p 0$,
+  \begin{gather}
+    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
+    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
+    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
+    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
+    \intertext{and}
+    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
+  \end{gather}
+  The first two results are implied by the proof of Theorem~\ref{res:1}
+  and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7} follow from the \lln, so it
+  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.
+
+  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
+  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
+  that~\eqref{eq:4} holds if
+  \begin{gather}
+    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
+    \intertext{and}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
+  \end{gather}
+  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
+  \begin{align*}
+    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
+    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
+    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  by Lemma~\ref{res:a2} and the \lln.
+  A similar argument holds for the second term:
+  \begin{align*}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
+    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
+  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
 \end{proof}
@@
     \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
+    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
     + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
@@
   \begin{align*}
-    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
-    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
+    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
+    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t' \big\rVert
+    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
     & = O_p(R'/\sqrt{P})
@@
     \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
+    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
     = O_p(R'/\sqrt{P}).
@@
 \begin{alem}\label{res:a2}
-  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
+  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
   hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
@@
   \begin{enumerate}
-  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
-  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
-  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
-  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
+  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
+  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
+  \item $\omaxb{t} | B_t - B | \to^p 0$,
+  \item $\omaxc{t} | B_t - B | = O_p(1)$,
+  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
+  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
   \end{enumerate}
+  where the absolute value is taken as the largest of the
+  element-by-element absolute values.
 \end{alem}
 
+This Lemma establishes that \citepos{Wes:96} basic results hold under
+our weaker moment and dependence conditions and provides several
+extensions. To streamline the presentation, we'll assume in these
+proofs that $x_t$ is a scalar.
 \begin{proof}
@@
   \begin{enumerate}
-  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
-    the same mixing process as the original variables) by
-    Assumption~\ref{a3}, and the moment and size conditions in that
-    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
-    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
-    \begin{equation}\label{eq:2}
-      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
-    \end{equation}
-    where $W(\cdot)$ is a multivariate Gaussian process.
+  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
+    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
+    constants and coefficients. Note that $t^{a-1} x_t \ep_{t+1}$ is
+    also an $L_2$-mixingale array with constants $t^{a-1} c_s$ and
+    coefficients $\zeta_k$, since
+    \begin{align*}
+      \| \E_{t-k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \| \E_{t-k} x_t \ep_{t+1} \| \\
+      &\leq (t^{a-1} c_t) \zeta_k
+    \end{align*}
+    and
+    \begin{align*}
+      \| x_t \ep_{t+1} t^{a-1} - \E_{t+k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
+      &\leq (t^{a-1} c_t) \zeta_{k+1}.
+    \end{align*}
 
-    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
-    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
-    \begin{equation*}
-      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
-    \end{equation*}
-    and the limit in~\eqref{eq:2} is again almost surely 0. The
-    Continuous Mapping Theorem then implies that
-    \begin{equation*}
-      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
-    \end{equation*}
-  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
-    $-1/2$. As a result, we can use a maximal inequality of
-    \cite{Mcl:75} (also available as Corollary 16.10 in
-    \citealp{Dav:94}), giving
+    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
     \begin{align*}
-      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
+      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
+      &\leq (R'-1)^{-\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta/2} \Big|^2\Bigg] \\
+      &\leq (R'-1)^{-\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2a - 2 + \delta}
     \end{align*}
-    which converges to a finite limit.
+    where the second inequality follows from \citepos{Mcl:75} maximal
+    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
+    Corollary 16.10). The summation converges to a constant as $T \to
+    \infty$ and $(R'-1)^{-\delta} \to 0$, completing the proof.
+
+  \item As in Part 1, $x_t \ep_{t+1} t^{a-1}$ is an $L_2$-mixingale of size
+    $-1/2$ and we can use \citepos{Mcl:75} maximal inequality to get
+    \begin{align*}
+      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
+      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
+      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
+    \end{align*}
+    which again converges to a finite limit.
+  \item The same argument used in Part 1 implies that $\omaxb{t} |
+    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
+    the result follows.
+  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
   \item We have
-    \begin{multline*}
-      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
-    \end{multline*}
-    and both terms converge to zero in probability by Part 1 and by
-    assumption.
+    \begin{align*}
+      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
+      &\leq \omaxb{t} |\hat{B}_t - B|
+      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
+      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
+    \end{align*}
+    and both terms converge to zero in probability by Parts 1 and 3.
   \item Similar to the previous argument, we have
-    \begin{multline*}
-      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
-      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
-      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
-      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
-    \end{multline*}
-    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
+    \begin{align*}
+      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
+      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
+      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
+    \end{align*}
+    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
   \end{enumerate}
@@
   \Big\lvert \WesA \Big\rvert \leq
-  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
-  \sup_{t = R'+1,\dots,T} | H_t |.
+  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
+  \omaxb{t} \lVert H_t \rVert.
 \end{equation*}
-From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
-that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
+From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p 0$. The \clt\ implies
+that $\ocltb{t} (F_t - F) = O_p(1)$,
 establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
@@
 
-\bibliography{texextra/AllRefs}
+\bibliography{texextra/references}
 \end{document}

### 2014-11-04 mixedwindow.tex
Revise theoretical component of paper

@@
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
+    Michael McCracken, Pablo Pincheira, Allan Timmermann, Ken West, Stephane
     Meng-Feng Yen and participants at the 2011 Midwest Econometrics
@@
 
-\noindent JEL Classification Numbers: C22, C53
+\noindent \allcaps{JEL} Classification Numbers: C22, C53
 
@@
 
-\section{Introduction} This paper proposes an out-of-sample (\oos)
-test statistic that is asymptotically normal with mean zero even when
-the models studied are nested.  This paper also proves that common
-block bootstrap methods consistently estimate the statistic's
-distribution, and shows how the statistic can be used to study many
-models simultaneously while maintaining strong control of the
-familywise error (\fwe), i.e. ensuring that the probability that the
-hypothesis that the model has equal predictive ability to a benchmark
-is incorrectly rejected for any of the models is no higher than a
-preset level.
+\section{Introduction}
 
-\oos\ tests are commonly used in International Macroeconomics,
+This paper proposes an out-of-sample (\oos) test statistic that is
+asymptotically normal and correctly centered even when the models
+studied are nested. The test is based on one proposed by
+\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
+with a recursive window and the alternative models with a fixed length
+rolling window. The rolling window ensures asymptotic normality, as in
+\citet{GiW:06}, and the recursive window allows the null hypothesis to
+be a statement about the specification of the Data Generating Process,
+which is the focus of the vast majority of the \oos\ testing
+literature.%
+\footnote{In particular, this is the focus of \citet{Wes:96},
+  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
+  many others but not \citet{GiW:06}. See \citet{Wes:06} and
+  \citet{ClM:13} for a thorough overview of this literature.} %
+This combination of estimation windows also gives our test statistic
+high power against alternative \dgp s that cause the benchmark model
+to be unstable --- structural breaks, time-varying coefficients, or
+forms of nonlinearity, for example --- which is a common motivation
+for using these tests.
+
+\oos\ tests are common in International Macroeconomics,
 Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
@@
 beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.%
-\footnote{Other papers in this literature include
-  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
-  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
-  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
-  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
-  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
-  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
-  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
-  reviews of this literature and additional references, see
-  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
-  \citet{CoD:11}, and \citet{Gia:11}} %
+\citet{Wes:96}.
 In a pair of papers,
@@
 
-In this paper, I show that a modified version of their statistic is
+This paper shows that a modified version of their statistic is
 asymptotically normal even when the smaller model is estimated.  To
@@
 fixed-length rolling window.
+This approach has the further advantage over existing \oos\ tests for
+nested models that the alternative can be essentially arbitrary as
+long as high level moment conditions hold. In particular, researchers
+can use model selection techniques like the \aic\ or \bic\ to
+determine the number of lags to include, the particular exogenous
+variables to include, etc. Moreover, although we focus on nested
+models in this paper, the approach can be used with non-nested models
+as well. As \citet{ClM:11b} have recently pointed out,
+\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
+the benchmark and alternative models, which is allowable under the
+null. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
 
-Mixing window strategies is uncommon but needn't be. In most
-applications, the null hypothesis imposes stability as well as equal
-accuracy between the two models.  The benchmark model rarely allows
-for breaks, parameter drift, or other forms of
-instability,%
-\footnote{Exceptions are \citepos{StW:07}
-  \allcaps{IMA}(1,1) and \allcaps{UC}-\allcaps{SV} models of inflation.} %
-but the
-researcher is typically concerned about instability.  Indeed, concern
-about instability is often given as a reason for doing an \oos\
-analysis, especially with a short rolling window.%
-\footnote{This
-  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
-  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
-  \cite{GiR:09,GiR:10}, among others.} %
-A researcher could impose
-stability on both models by using a recursive window or relax
-stability for both by using a rolling window; either approach should
-not affect the test's size, but may affect power.  But the researcher
-could instead impose stability on the benchmark and relax it for the
-alternative by using a recursive window for the benchmark and a
-rolling window for the alternative model.  This approach could have a
-power advantage and is similar in spirit to using a Likelihood Ratio
-Test instead of an \lm\ or Wald test, which depend on just the
-restricted or unrestricted model respectively.
-
-This paper's statistic has a substantial advantage over existing \oos\
-tests for nested models: the alternative can be essentially arbitrary
-as long as high level moment conditions hold.  In particular,
-researchers can use model selection techniques like the \aic\ or \bic\
-to determine the number of lags to include, the particular exogenous
-variables to include, etc.  Other methods that test a similar
-hypothesis are unable to handle these models \citep[except][which does
-not allow the benchmark to be estimated]{ClW:06}; \citet{GiW:06} are
-able to handle such models for both the alternative and the benchmark
-but, as mentioned earlier, they test a different aspect of forecasting
-performance.
-
-This paper focuses on nested models, as they have received the most
-attention in the empirical and theoretical literature, but the
-statistic can be used with non-nested models as well.  This generality
-is useful, since \citepos{Wes:96} results do not apply to non-nested
-models if they both encompass the true \dgp,%
-\footnote{\citet{ClM:11b}
-  call this scenario, ``overlapping models.''} %
-which is allowable
-under the null: in the limit, both models will converge to the \dgp\
-and give identical forecasts.  Consequently, the naive \oos\ $t$-test
-is invalid, even after correcting the standard error if necessary to
-reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
-window \oos\ $t$-test remains normal for these models but the
-recursive and rolling windows (with the window size increasing to
-$\infty$) do not, and provide a procedure for pointwise (but not
-uniformly) valid tests for the recursive and rolling windows and
-uniformly valid tests for the fixed window.  The test proposed in this
-paper is uniformly valid and places fewer assumptions on the models
-under study and the true \dgp.
-
-The next section presents our new statistic. Section~\ref{sec:2} presents
+The next section presents the intuition and theory for our new statistic.
+Section~\ref{sec:2} presents
 simulations that compare our pairwise \oos\ test to \poscw\ original
-statistics. Section~\ref{sec:3} demonstrates the use of our statistic
+statistics and Section~\ref{sec:3} demonstrates the use of our statistic
 by reanalyzing \citepos{GoW:08} study of excess return
@@
 our results have been put in a separate Appendix along with
-some minor supporting arguments \citep{Cal:14}.
+some supporting results \citep{Cal:14b}.
 
@@
 predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$; also let $v_t$ be another random process that is believed to
-potentially contain information about $y_{t+1}$ and suppose that
+$x_t$, that $v_t$ is another random process that is believed to
+potentially contain information about $y_{t+1}$, and that
 $(y_t, x_t, v_t)$ is stationary and weakly dependent.
@@
 \end{equation}
-obeys an \mds\ \clt and is asymptotically normal as $P \to \infty$,%
+obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
 \footnote{This claim assumes that the asymptotic variance of the
@@
   address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value%
-\footnote{It will be clear momentarily why the summation begins at
-  $R+1$ instead of $1$.} %
-and $P = T - R$.%
-\footnote{Section~\ref{sec:1b} discusses conditions under which the
-  \mds\ condition holds. We will also present results that allow
-  $\ep_{t+1}$ to be serially correlated.} %
+with $R$ an arbitrary starting value
+and $P = T - R$.
 Straightforward algebra \citep{ClW:07} shows that
@@
   x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
+  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
 \end{equation}
+almost surely.
 
@@
 Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{1,t+1}$.) They use a rolling window of length
+$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
 $R$ to estimate $\yh_{t+1}$%
@@
 \citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
-an \mds. In the 2006 paper, Clark and West assume that the
+an \mds. In their 2006 paper, Clark and West assume that the
 coefficients on the benchmark model, $\btrue$, are zero under the null, making
 $\ep_{t+1}$ observed directly. This restriction is relaxed in
-the 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
+their 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
 rolling window. Now the estimated linear model's prediction errors,
@@
 but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$; i.e.
-\begin{equation}
+$\eph_{t+1}$:
+\begin{align}
   \label{eq:8}
-  \bh_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
-  \sum_{s=2}^t x_{t-1} y_t.
-\end{equation}
+  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
+  \sum_{s=1}^{t-1} x_{s} y_{s+1}
+  && \text{and}
+  &
+  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
+\end{align}
+for each $t$.
 \citepos{Wes:96} Theorem 4.1 implies that
@@
 to make the intuition as clear as possible. The next section lists the
-specific assumptions for a more general case.
+specific assumptions for the more general case.
 
@@
 where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is
-estimated with \ols\ using a recursive window as described by
-Equation~\eqref{eq:8}
-and the period-$t$ forecast is given by
-\begin{equation}\label{eq:3}
-  \yh_{0,t+1} = x_t'\bh_t.
-\end{equation}
-
-We deviate slightly from the previous section's introduction by
-allowing for multiple alternative models, as in \cite{HuW:10}. This
-allowance is crucial if we want the statistic to be empirically
-useful, since almost every empirical analysis considers several
-alternative models at once.  Each of these alternative models is
-denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estiatmed with a
+observed vector of predictors. The parameter $\beta$ is estimated with
+\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
+The alternative model is denoted $\yh_{1,t+1}$ and is estimated with a
 rolling window of length $R$.
 
-These conditions are summarized in the first assumption.
+The main conditions on the \dgp\ are summarized in the first
+assumption.  The weak dependence and moment conditions are
+standard. These assumptions are slightly weaker than similar
+assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only because we
+make use of more recent developments in limit theory, in particular
+the \clt\ for Near-Epoch Dependent (\ned) processes proven by
+\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.
 
 \begin{asmp}\label{a1}%
-  The benchmark forecast, $\yh_{0,t+1}$, is generated by
-  Equation~\eqref{eq:3}, where $\bh_t$ is constructed with a recursive
-  window and satisfies~\eqref{eq:8}. The alternative forecasts are
-  estimated using a rolling window of length $R$, so $\yh_{j,t+1} =
-  \psi_j(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi_j$ is a
-  known function and $z_t$ is a sequence of predictors that may
-  include $x_t$. The window length, $R$, remains finite as $T \to
-  \infty$.
+  The data are generated by the relationship
+  \begin{equation}
+    y_{t+1} = x_t'\btrue + \ep_{t+1}
+  \end{equation}
+  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
+  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
+  all $t$. Also assume that there is an additional sequence of random
+  vectors $z_t$ and the processes $\ep_{t+1}$, $x_t$, and $z_t$ are
+  $L_2$-\ned\ of size $-(r-1)/(r-2)$ for $r > 2$ on either a strong
+  mixing process of size $-r/(r-2)$ or a uniform mixing process of
+  size $-r/(2r-2)$.
 \end{asmp}
 
-Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
-conditions are standard. These assumptions are slightly weaker than
-similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
-because we make use of more recent developments in limit theory, in
-particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
-\cite{Jon:97}.
+The next assumption defines the forecasting models and adds additional
+constraints to the \dgp.
 
 \begin{asmp}\label{a3}%
-  The series $y_t$, $x_t$, and $z_t$ are $L_2$-\ned\ of size
-  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
-  $-r/(r-2)$ or a uniform mixing process of size
-  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
-  1,\dots,J$, have uniformly bounded $2 r$ moments.
+  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
+  with a recursive window according to~\eqref{eq:8}; the partial sums
+  $\sum_{s=1}^{t-1} x_s x_s' / (t-1)$ are almost surely invertible for
+  all $t \geq R$ (uniformly in $T$).  The alternative forecast
+  satisfies
+  \begin{equation}
+    \yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
+  \end{equation}
+  where $\psi$ is a known measurable function and the window length,
+  $R$, remains finite as $T \to \infty$. Moreover, the vector
+  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments and is
+  4th order stationary.
 \end{asmp}
 
-The requirement that the alternative forecasts satisfy a moment
-condition, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The functions $\psi_j$ that generate these
-forecasts is essentially unrestricted, so even well-behaved predictors
+The requirement that the alternative forecast satisfies moment
+conditions, rather than the underlying predictors $z_t$, is somewhat
+unappealing but necessary. The function $\psi$ that generates these
+forecasts is otherwise nearly unrestricted, so even well-behaved predictors
 could produce arbitrarily badly-behaved forecasts. For example, if
@@
 \end{equation*}
-setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
+setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
 since the forecast equals positive infinity with probability $1/2$. It
@@
 
-Finally, we define some notation for the \oos\ statistic. The
-adjusted \oos\ loss for each alternative model and a hypothetical value
-of $\beta$ is denoted by
+Our next assumption ensures that the asymptotic variance of the \oos\
+average is positive.
+\begin{asmp}\label{a4}%
+  The asymptotic variance-covariance matrix
   \begin{equation}
-  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
-  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
+    \var \Bigg(
+      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
+      \Bigg)
   \end{equation}
-and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
-Also define
-\begin{align*}
-  \fh_t &= f_t(\bh),
-  &\fb(\beta) &= \oavg{t} f_t(\beta),
-  &\text{and}&
-  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
-\end{align*}
-with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
-$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
-Also define $\btrue$ to be the pseudotrue value of
-$\beta$ that minimizes the MSE of the benchmark model,
-\begin{equation*}
-  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
-\end{equation*}
-and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
-The next assumption ensures that $\Sigma$ is positive definite.
-\begin{asmp}\label{a4}%
-  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
+  is uniformly positive definite (in $T$).
+\end{asmp}
+This assumption is much less restrictive than in \cite{Wes:96}.  As in
+\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
+rule out pathological cases --- for example, letting the alternative
+model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
+assumption is a restriction on the \dgp\ as well as the forecasting
+models, but in this paper it is a restriction only on the models.
+
+The last assumption restricts the class of \hac\ variance estimators
+we will consider. We use the same class of estimators studied by
+\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
+further discussion.
+\begin{asmp}\label{a5}%
+  $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
+  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
+  finite number of points, and
+  \begin{gather*}
+    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
+    \intertext{and}
+    \int_{-\infty}^{\infty} \Bigg\lvert
+    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
+  \end{gather*}
 \end{asmp}
 
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases---for example, letting both the benchmark
-and the alternative models be perfectly correlated white noise. In
-\citet{Wes:96}, this assumption is a restriction on the \dgp\ as well
-as the forecasting models, but in this paper it is a restriction only
-on the models.
+Last, we define some notation that will be used to derive the
+theoretical properties of our \oos\ statistics.  The information set
+that contains the information available for forecasting $y_{t+1}$ is
+\begin{equation*}
+  \Fs_t = \sigma(y_t, x_{t+1}, z_{t+1}, y_{t-1}, x_t, z_t,\dots).
+\end{equation*}
+The adjusted \oos\ loss for the alternative model using a hypothetical
+value of $\beta$ to produce the benchmark forecast is denoted by
+\begin{equation*}
+  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
+\end{equation*}
+Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
+\begin{gather*}
+  \gh_t = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{s+1}) x_s'\Bigg]\,
+          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
+  \intertext{and}
+  g_t = \E\Big[(4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
+\end{gather*}
+and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
+$\fb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
 
@@
 
-Asymptotic normality of the \oos\ average follows directly from the
-previous three assumptions without any other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} directly.
+Asymptotic normality of the \oos\ average now follows directly from the
+first three assumptions without other conditions. The proof is
+presented in the Appendix and follows \citet{Wes:96} closely.
 
 \begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-In Theorem~\ref{res:1}, define the variables
-$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
-$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
-$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.
 
-Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
-\begin{equation*}
-  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
-\end{equation*}
-
-Clearly, the main use of this theorem is to test the null hypothesis
-$\E f_t = 0$.
-
-The following remarks are relevant to Theorem~\ref{res:1}:
-
-\begin{rem}
-  Forecasters are usually interested in the one-sided alternative that
-  $\E f_t > 0$; i.e. that the alternative model is expected
-  to forecast better than the benchmark.
-\end{rem}
-
-\begin{rem}
-  These results are presented for one-period-ahead forecasting for
-  simplicity.  They can be extended to forecasting at a longer horizon
-  by appropriately modifying the variance-covariance matrix to account
-  for the correlation structure of the forecast errors. (i.e. for
-  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
-\end{rem}
-
-Define $\X' = [x_1,\dots,x_T]$
-
+To use this result, we need a consistent estimator of
+$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
+\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
+$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
 \begin{align*}
-  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
-  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
+  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
+  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
+  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
+  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
+\intertext{and}
+  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
+  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
 \end{align*}
 
-\newcommand{\K}[1]{K(\tfrac{#1}{w})}
-
-Define the general covariance estimator:
-\begin{align*}
-  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
-  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
-  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
-\end{align*}
-
-Define the \mds\ covariance estimator:
-\begin{align*}
-  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
-  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
-  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
-\end{align*}
+These estimators are consistent under similar assumptions to
+Theorem~\ref{res:1}.
 
@@
 
-\begin{rem}
-  The statistic we present tests the null hypothesis that the forecast
-  errors from the population version of the benchmark model are a
-  martingale difference sequence.  This hypothesis may not be
-  appropriate, depending on the loss function or utility function of
-  interest.  If one wants to test the less restrictive null hypothesis that
-  $y_{t} - \yh_{0t}$ is uncorrelated with $\yh_{1t}$ but not
-  necessarily an \mds, one can replace $\Sh_{21}$, $\Sh_{22}$
-  and $\Sh_{23}$ with their \hac\ counterparts.
-  Our statistic can also be modified to test implications of
-  optimal forecasts under other loss functions
-  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
-  a forecast encompassing test using the models' generalized forecast
-  errors.%
-\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.} %
-\end{rem}
+Note that these results allow misspecification; asymptotic normality
+follows from the weak dependence of the underlying series and from the
+design of the test statistic. These statistics have typically been
+used to test the null hypothesis that the benchmark model is correctly
+specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
+implies that $f_t(\btrue) - \E f_t(\btrue)$ is an \mds\ as discussed
+at the beginning of the Section. This is especially appealing in our
+framework, since the benchmark can be theoretically motivated so the
+\mds\ null would be a test of rationality. For example, \citet{GoW:08}
+test whether excess returns for the S\&P 500 are predictable
+out-of-sample, and any deviation from an \mds\ is potentially
+interesting. But the \mds\ null hypothesis only affects the estimator
+of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
+to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
+
+In other settings, a researcher may want to test the weaker hypothesis
+that $\E \fb^* = 0$ but the benchmark may be misspecified. This
+approach can then be interpreted as an encompassing test as in
+\citet{HLN:98}, and would test whether the alternative model contains
+additional information that would make the benchmark model more
+accurate. This interpretation comes from the combination forecasting
+model
+\begin{equation*}
+  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\beta + w \yh_{t+1}
+\end{equation*}
+which can be rewritten in terms of forecast errors as
+\[
+e_{\mathit{avg},t+1} = e_{0,t+1} + w (e_{0,t+1} - e_{1,t+1})
+\]
+with $e_{\mathit{avg},t+1} = y_{t+1} - \yh_{\mathit{avg},t+1}$,
+$e_{0,t+1} = y_{t+1} - x_t'\beta$, and $e_{1,t+1} = y_{t+1} -
+\yh_{1,t+1}$. The value
+\[
+w = \frac{\E e_{0,t+1} (e_{0,t+1} - e_{1,t+1})}{\E e_{0,t+1}^2}
+\]
+minimizes the \mse\ of the combination forecast, so the combination
+model will have smaller \mse\ than the benchmark model unless
+$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated, implying that
+the alternative uses information not in the benchmark.  As the
+discussion at the beginning of this section shows, the test in
+Theorem~\ref{res:1} is equivalent to a test of zero correlation
+between $e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$.
+
+The final Theorem puts together Theorem~\ref{res:1} and
+Lemma~\ref{lem:2} to produce our test statistics.  It is an immediate
+consequence of the previous two results and its proof is omitted.
+
+\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
+
+The test statistic proposed in Theorem~\ref{thm:3} can be easily
+extended in several ways. For longer-horizon forecasts (two or more
+periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
+will not --- the forecast errors for a correctly specified
+$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
+using a generalized $\sigmah_2$ that reflects this covariance
+structure restores consistency. To test optimality under loss
+functions other than squared-error, one can replace the forecast error
+with the generalized forecast error \citep[see, for
+example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
+corresponding $M$-estimator. And the benchmark model can be replaced
+in general with a nonlinear model that satisfies the assumptions of
+\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
+$f_t$ and $g_t$. (See \citealp{Wes:96} and \citealp{Mcc:00}
+for details.) The general approach of using a recursive window to
+estimate the benchmark and a fixed-length rolling window to estimate
+the alternative applies quite broadly.
 
@@
 Lemma~\ref{lem:2} to derive an appropriate critical value as
-in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \Sigma)$ under
+in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \sigma^2)$ under
 the \mds\ null hypothesis, the continuous mapping theorem implies that
 $\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
-\sim N(0, D^{-1/2} \Sigma D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
-\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \Sh
+\sim N(0, D^{-1/2} \sigma^2 D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
+\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \sh
 \hat D^{-1/2})$ distribution to generate a critical value for the
@@
 
-\section{Conclusion}\label{sec:4}
+\section{Discussion}\label{sec:4}
 This paper presents an \oos\ test statistic similar to \poscw\ that is
@@
 Normality is achieved by estimating the alternative model using a
-fixed-length rolling window---as do Clark and West---but estimating
+fixed-length rolling window --- as do Clark and West --- but estimating
 the benchmark model with a recursive window.  Simulations indicate

### 2014-12-17 mixedwindow.tex
Minor changes to phrasing of empirical results

--- 2014-11-04 mixedwindow.tex
@@
 We deviate slightly from the previous section's introduction by
-allowing for multiple alternative models, as in \cite{HuW:10}. This
-allowance is crucial if we want the statistic to be empirically
+allowing for multiple alternative models, as in \cite{Whi:00} and \cite{HuW:10}. This
+modification is crucial if we want the statistic to be empirically
 useful, since almost every empirical analysis considers several
 alternative models at once.  Each of these alternative models is
-denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estiatmed with a
+denoted $\yh_{j,t+1}$, for $j = 1,\dots,J$, and is estimated with a
 rolling window of length $R$.
@@
 particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
-\cite{Jon:97}.
+\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.
 
@@
 unappealing but necessary. The functions $\psi_j$ that generate these
-forecasts is essentially unrestricted, so even well-behaved predictors
+forecasts are otherwise unrestricted, so even well-behaved predictors
 could produce arbitrarily badly-behaved forecasts. For example, if
@@
 \end{align*}
-with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
-$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
+with $P = T - R$.
 Also define $\btrue$ to be the pseudotrue value of
@@
 and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
-The next assumption ensures that $\Sigma$ is positive definite.
+
+Our last assumption is on the asymptotic variance of $\fb^*$.
 \begin{asmp}\label{a4}%
-  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
+  The asymptotic variance of $\fb^*$ is positive definite.
 \end{asmp}
-
 This assumption is much less restrictive than in \cite{Wes:96}.  As in
@@
 previous three assumptions without any other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} directly.
+presented in the Appendix and follows \citet{Wes:96} closely.
 
 \begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-In Theorem~\ref{res:1}, define the variables
-$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
-$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
-$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.
+(define $F$ and $B$)
 
-Null hypothesis: $y_{t+1} - x_t'\btrue$ is an \mds\ with respect to
-\begin{equation*}
-  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
-\end{equation*}
+Note that Theorem~\ref{res:1} does not require any of the models to be
+correctly specified. Asymptotic normality follows from the weak
+dependence of the underlying series and from the design of the test
+statistic. Typically these statistics are used to test the null
+hypothesis that the benchmark model is correctly specified, which
+implies that $\fh_t - \E f_t^*$ is an \mds\ as discussed in
+Section~\ref{sec:1a}. This is especially appealing in our framework,
+since the benchmark can be theoretically motivated so the \mds\ null
+can be a test of forecaster rationality.
+But that null hypothesis only affects the
+estimator of $\Sigma$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1}
+continues to hold under alternatives that satisfy Assumptions
+\ref{a1} -- \ref{a4}.
 
-Clearly, the main use of this theorem is to test the null hypothesis
-$\E f_t = 0$.
+Moreover, Theorem~\ref{res:1} can be used with a \hac\ estimator of
+$\Sigma$ when a researcher wants to test the weaker hypothesis that
+$\E \fb^* = 0$ but the benchmark may be misspecified. This approach
+could be interpreted as an encompassing test as in \citet{HLN:98}, and
+would test whether the alternative models contain additional
+information not present in the benchmark model. In either case (\mds\
+or non-\mds), this test is designed to have power against the
+``encompassing'' alternative. The specific research question should
+then determine whether the test should also reject if there are other
+violations of rationality.
 
-The following remarks are relevant to Theorem~\ref{res:1}:
+\newcommand{\K}[1]{K((#1)/w)}
+For the next results, define the variables $\gh_t = \Fh \Bh
+x_t(y_{t+1} - x_t'\bh_t)$, $\gb = \oavg{t} \gh_t$, and
+\begin{align*}
+  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^{T-1} x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
+  &\text{and}&
+  \Bh &= \Big(\tfrac1P \sum_{s=R+1}^{T-1} x_s x_s' \Big)^{-1}
+\end{align*}
+Then define the \hac\ covariance estimator $\Sigmah_1$ and the \mds\
+covariance estimator $\Sigmah_2$ as
+\begin{align*}
+  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
+  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
+  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
+  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}
+  \intertext{and}
+  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
+  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
+  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
+  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)',
+\end{align*}
+where $K$ is a kernel that satisfies standard assumptions.
 
-\begin{rem}
-  Forecasters are usually interested in the one-sided alternative that
-  $\E f_t > 0$; i.e. that the alternative model is expected
-  to forecast better than the benchmark.
-\end{rem}
+\begin{asmp}\label{a5}
+  Fill in assumptions on $\K$.
+\end{asmp}
+
+\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
+
+Put a last result here about one-sided testing.
 
@@
 \end{rem}
-
-Define $\X' = [x_1,\dots,x_T]$
-
-\begin{align*}
-  \Fh &= \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \yh_{1,s+1}) \Big\}' &
-  \Bh &= \big(\tfrac1T \X'\X \big)^{-1}
-\end{align*}
-
-\newcommand{\K}[1]{K(\tfrac{#1}{w})}
-
-Define the general covariance estimator:
-\begin{align*}
-  \Sigmah_1 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{11} &= \oavg{s,t} (\fh_t - \fb) (\fh_t - \fb)' \K{t-s}, \\
-  \Sh_{12} &= \oavg{s,t} (\fh_t - \fb)(\gh_t - \gb)' \K{t-s}, &
-  \Sh_{13} &= \oavg{s,t} (\gh_t - \gb)(\gh_t - \gb)'  \K{t-s}.
-\end{align*}
-
-Define the \mds\ covariance estimator:
-\begin{align*}
-  \Sigmah_2 &= \Sh_{21} + \Sh_{22} + \Sh_{22}' + 2 \, \Sh_{23}, &
-  \Sh_{21} &= \oavg{t} (\fh_t - \fb) (\fh_t - \fb)', \\
-  \Sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb)', &
-  \Sh_{23} &= \oavg{t} (\gh_t - \gb)(\gh_t - \gb)'.
-\end{align*}
-
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
 

### 2015-01-07 mixedwindow.tex
Minor tweaks to text and exposition

--- 2014-11-04 mixedwindow.tex
@@
     thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
+    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
+    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
     Group meeting and the 2013 \nber-\nsf\ Time Series conference
@@
   resulting statistic is asymptotically normal even when the models
-  are nested.  Moreover, the alternative model can be estimated using
-  common model selection methods, such as the \aic\ or \bic, without
-  affecting the asymptotic distribution of this test statistic.  The
+  are nested. The
   paper also presents Monte Carlo evidence that this statistic has
@@
 \noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection
+Sequence, Model Selection, Forecast Encompassing
 
@@
 This combination of estimation windows also gives our test statistic
-high power against alternative \dgp s that cause the benchmark model
+high power against alternatives that cause the benchmark model
 to be unstable --- structural breaks, time-varying coefficients, or
@@
 fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic appropriately.  This statistic is especially
+centers the statistic to have mean-zero under the null.  This statistic is especially
 convenient because other \oos\ tests for similar hypotheses
@@
   which rules out nesting.} %
-
 However, Clark and West's statistic is only ``approximately normal''
@@
 
-This paper shows that a modified version of their statistic is
+This paper proposes a modified version of their statistic and shows that it is
 asymptotically normal even when the smaller model is estimated.  To
@@
 models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently pointed out,
+as well. As \citet{ClM:11b} have recently argued,
 \citepos{Wes:96} results do not hold when the true \dgp\ is nested by
 the benchmark and alternative models, which is allowable under the
-null. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
+null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
 
-The next section presents the intuition and theory for our new statistic.
-Section~\ref{sec:2} presents
-simulations that compare our pairwise \oos\ test to \poscw\ original
-statistics and Section~\ref{sec:3} demonstrates the use of our statistic
-by reanalyzing \citepos{GoW:08} study of excess return
-predictability and Section~\ref{sec:4} concludes. Proofs of
-our results have been put in a separate Appendix along with
-some supporting results \citep{Cal:14b}.
+The next section presents the intuition and theory for our new
+statistic.  Section~\ref{sec:2} presents simulations that compare our
+pairwise \oos\ test to \poscw\ original statistics.
+Section~\ref{sec:3} demonstrates the use of our statistic by
+reanalyzing \citepos{GoW:08} study of excess return predictability and
+demonstrates how our results can be used in settings with many
+alternative models. Section~\ref{sec:4} concludes. Proofs of our
+results have been put in a separate Appendix along with some
+supporting results \citep{Cal:15}.
 
@@
 This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistc, then present the paper's key
-assumptions in section~\ref{sec:1a} and present our formal theoretical
-results in section~\ref{sec:1b}.
+informal motivation of the statistic, then present the paper's key
+assumptions in Section~\ref{sec:1a} and present our formal theoretical
+results in Section~\ref{sec:1b}.
 
@@
 correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to the information set
-\begin{equation*}
-\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
-y_{t-1}),\dots),
-\end{equation*}
+to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
 and we can see immediately that
@@
 and $P = T - R$.
+
 Straightforward algebra \citep{ClW:07} shows that
@@
 almost surely.
-
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
+\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
 Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
 $v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$%
+$R$ to estimate $\yh_{t+1}$,%
 \footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
@@
 $\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window length $R$ prevents
+variables used to estimate it. Using a finite window prevents
 the degeneracy that can arise when comparing nested models out-of-sample (see
@@
 $\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
-rolling window. Now the estimated linear model's prediction errors,
+their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
+rolling window as the $\yh_{t+1}$. Now the estimated linear model's prediction errors,
 $\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
@@
 
-This overview has presented an especially simple version of the result
+So far, we have presented an especially simple version of the result
 to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case.
+specific assumptions for the more general case and defines additional notation.
 
@@
 \begin{align*}
-  y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t &
+  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
   \gamma_t &=
@@
   \end{cases}\\\nonumber
-  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
-  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
+  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
+  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
   \end{pmatrix}
@@
 \end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_t$
-on a constant, and the alternative regresses $y_t$ on a constant and
-$z_{t-1}$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
+Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
+on a constant, and the alternative regresses $y_{t+1}$ on a constant and
+$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
 pricing application similar to \citepos{GoW:08} which we study in
@@
 $R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recrusive window statistic at 82.3\%,
+our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
 again for a nominal size of 10\%.  In general, the statistics perform
@@
 \begin{equation*}
-  \mathit{excess~return}_{t} = \alpha_{0} + \alpha_{1}\
-  \mathit{predictor}_{t-1} + \ep_{t},
+  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
+  \mathit{predictor}_{t} + \ep_{t+1},
 \end{equation*}
-where $\alpha_{0}$ and
-$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the ``predictor'' column of
-Table~\ref{tab:em1} \citep[see][for a detailed description of the
-variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
+where $\beta_{0}$ and
+$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
+The predictors used are listed in the \emph{predictor} column of
+Table~\ref{tab:em1}. \citep[See][for a detailed description of the
+variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
 correction to the models, that the forecasts be bounded below by zero
@@
   premium and each alternative model is a constant and single lag of
-  the variable listed in the ``predictor'' column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The ``value'' column
-  lists the value of this paper's \oos\ statistic, the ``naive''
+  the variable listed in the \emph{predictor} column.  The dataset begins
+  in 1927 and ends in 2009 and is annual data. The \emph{value} column
+  lists the value of this paper's \oos\ statistic, the \emph{naive}
   column indicates whether the statistic is significant at standard
-  critical values, and the ``corrected'' column indicates significance
+  critical values, and the \emph{corrected} column indicates significance
   using critical values that
@@
 Table~\ref{tab:em1} presents the results for each model.  The column
-``value'' gives the value of the test statistic for each model, while
-the ``naive'' indicates whether the statistic is greater than the
-standard \bootsize\% critical value (\naivecriticalvalue) Three
-predictors are
-significant at the naive critical values for both the original and
+\emph{value} gives the value of the test statistic for each model,
+while \emph{naive} indicates whether the statistic is greater than the
+standard 10\% critical value (\naivecriticalvalue). Three predictors
+are significant at the naive critical values for both the original and
 bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio.
+book to market ratio, and the median forecast is significant as well.
+This could suggest that excess returns are not an \mds\ and that
+information in these three variables is useful for predicting returns.
 
@@
 the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance. A
-full treatment of this issue is beyond the scope of this paper,
-however, it is straightforward to use Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to derive an appropriate critical value as
-in~\citet{Whi:00}. Since $\sqrt{P} \fb \to^d N(0, \sigma^2)$ under
-the \mds\ null hypothesis, the continuous mapping theorem implies that
-$\max_i \sqrt{P} \fb_i/\sh_i \to^d \max_i W_i$, where $Z_i
-\sim N(0, D^{-1/2} \sigma^2 D^{-1/2})$ and $D = \diag(\sigma_1, \dots,
-\sigma_j)$. We can simulate from the $N(0, \hat D^{-1/2} \sh
-\hat D^{-1/2})$ distribution to generate a critical value for the
-\emph{largest} individual test statistic under the null ---
-\empiricalcriticalvalue, based on \empiricaldraws\ simulations. Using
-this critical value, none of the predictors are siginificant at
-\bootsize\%.%
+hypothesis tests, so it is likely that some will reject by chance.
+There are several approaches that could accommodate this multiplicity, and a full
+treatment is beyond the scope of this paper, however, it is
+straightforward to use Theorem~\ref{res:1} and Lemma~\ref{lem:2} to
+derive an appropriate critical value similar to~\citet{Whi:00}.
+
+Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
+forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
+multivariate $f_t$, so the continuous mapping theorem implies that
+\begin{equation*}
+  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
+\end{equation*}
+where $W \sim N(0, V)$ and $V$ is the $\nmod
+\times \nmod$ correlation matrix with elements
+\begin{equation*}
+  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
+\end{equation*}
+
+To estimate $V$, we use the correlation matrix associated with the
+multivariate analogue of $\sigmah_2$,
+\[
+\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
++ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
+\]
+where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
+\begin{gather*}
+  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
+  \intertext{and}
+  \gh_{it} = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{i,s+1}) x_s'\Bigg]\,
+            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
+\end{gather*}
+respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
+$1 - \alpha$ quantile of the distribution of $\max_i \hat W_i$, with
+$\hat W \sim N(0, \hat V)$.  Then
+\begin{equation*}
+  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{1i} > \hat c\Big] \leq \alpha,
+\end{equation*}
+under the null hypothesis that excess returns are an \mds\ with
+respect to all of the information contained in the variables listed in
+Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
+value.%
 \footnote{\citet{Han:05} makes the point that multiple one-sided
@@
   poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here. Moreover, I need to
-  explain why it's not a concern for these statistics in general.} %
+  model, so this issue is not a concern here.} %
+
+We calculate $\hat c$ by generating \empiricaldraws\ draws from
+$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
+\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
+remain significant at 10\% using this critical value. Using this
+critical value, none of the predictors are significant at 10\%, which
+gives additional support to \citepos{GoW:08} conclusion that excess
+returns are unpredictable and also demonstrates the importance of
+correcting for multiplicity in these studies.
 
@@
 Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but estimating
-the benchmark model with a recursive window.  Simulations indicate
-that the new statistic behaves similarly to Clark and West's original
-test when the \dgp\ is stable but can have much higher power when the
-\dgp\ has structural breaks.
+fixed-length rolling window --- as do Clark and West --- but
+estimating the benchmark model with a recursive window.  Simulations
+indicate that the new statistic behaves similarly to Clark and West's
+original test when the \dgp\ is stable but can have much higher power
+when the \dgp\ has structural breaks. We also have presented an
+empirical study of the equity premium that demonstrates how to use
+these results with several alternative models.
 

### 2015-01-07 appendix.tex
Several minor edits and corrections

@@
 \begin{equation*}
-  F_t(\beta) = (4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t',
+  F_t(\beta) = 2 (x_t'\beta - \yh_{t+1}) x_t',
 \end{equation*}
@@
     &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
+    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
     &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
@@
     \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t' \big\rVert
+    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
     \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
@@
     of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that $t^{a-1} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{a-1} c_s$ and
+    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
+    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
     coefficients $\zeta_k$, since
     \begin{align*}
-      \| \E_{t-k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{a-1} c_t) \zeta_k
+      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
+      &\leq (t^{b} c_t) \zeta_k
     \end{align*}
@@
     \begin{align*}
-      \| x_t \ep_{t+1} t^{a-1} - \E_{t+k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{a-1} c_t) \zeta_{k+1}.
+      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
+      &\leq (t^{b} c_t) \zeta_{k+1}.
     \end{align*}
@@
       \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta/2} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2a - 2 + \delta}
+      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
+      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
     \end{align*}
@@
     Corollary 16.10). The summation converges to a constant as $T \to
-    \infty$ and $(R'-1)^{-\delta} \to 0$, completing the proof.
+    \infty$ and $(R'-1)^{-2\delta} \to 0$, completing the proof.
 
-  \item As in Part 1, $x_t \ep_{t+1} t^{a-1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can use \citepos{Mcl:75} maximal inequality to get
+  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
+    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
     \begin{align*}
@@
     \end{align*}
-    which again converges to a finite limit.
+    which converges to a finite limit.
   \item The same argument used in Part 1 implies that $\omaxb{t} |

### 2015-01-07 mixedwindow.tex
Several minor edits and corrections

@@
 \citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative models with a fixed length
+with a recursive window and the alternative model with a fixed length
 rolling window. The rolling window ensures asymptotic normality, as in
@@
   not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  implicitly assume that the models do not converge to the same limit,
+  assume that the models do not converge to the same limit,
   which rules out nesting.} %
@@
 the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is a
-random walk \citep{ClW:06}. Estimating the parameters of the smaller
+asymptotically normal with mean zero when the benchmark model is
+not estimated \citep{ClW:06}. Estimating the parameters of the smaller
 model invalidates their proof.
 
-This paper proposes a modified version of their statistic and shows that it is
+This paper proposes a modified version of Clark and West's (2006,
+2007) statistic and shows that it is
 asymptotically normal even when the smaller model is estimated.  To
@@
 demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Proofs of our
-results have been put in a separate Appendix along with some
-supporting results \citep{Cal:15}.
+alternative models. Section~\ref{sec:4} concludes. Our results follow
+from arguments similar to \citepos{Wes:96} and have been put in a
+separate appendix along with some supporting lemmas \citep{Cal:15}.
 
@@
 
-\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
+\citet{ClW:06,ClW:07} propose using this as a test of whether $\ep_{t+1}$ is
 an \mds. In their 2006 paper, Clark and West assume that the
@@
 performs well in simulations. Since the window length is finite,
-the estimators of $\btrue$ do not converge to $\btrue$.
+the estimator of $\btrue$ does not converge to $\btrue$.
 
@@
 \begin{equation*}
-  \Fs_t = \sigma(y_t, x_{t+1}, z_{t+1}, y_{t-1}, x_t, z_t,\dots).
+  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
 \end{equation*}
@@
 \begin{gather*}
-  \gh_t = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{s+1}) x_s'\Bigg]\,
+  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
           \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
   \intertext{and}
-  g_t = \E\Big[(4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
+  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
 \end{gather*}
 and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
-$\fb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
+$\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
 
@@
 implies that $f_t(\btrue) - \E f_t(\btrue)$ is an \mds\ as discussed
-at the beginning of the Section. This is especially appealing in our
+at the beginning of this section. This is especially appealing in our
 framework, since the benchmark can be theoretically motivated so the
@@
 minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model unless
-$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated, implying that
-the alternative uses information not in the benchmark.  As the
-discussion at the beginning of this section shows, the test in
-Theorem~\ref{res:1} is equivalent to a test of zero correlation
-between $e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$.
+model will have smaller \mse\ than the benchmark model, implying that
+the alternative uses information not in the benchmark, unless
+$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated.
 
@@
 
-Here, I conduct the same analysis, but using this paper's \mds\ test.
+Here, we conduct the same analysis, but using this paper's \mds\ test.
 The benchmark model is the excess return's sample mean (as in the
@@
 hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity, and a full
+There are several approaches that could accommodate this multiplicity and a full
 treatment is beyond the scope of this paper, however, it is
-straightforward to use Theorem~\ref{res:1} and Lemma~\ref{lem:2} to
-derive an appropriate critical value similar to~\citet{Whi:00}.
+straightforward to use our results to
+derive a valid critical value similar to~\citet{Whi:00}.
 
@@
   \intertext{and}
-  \gh_{it} = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{i,s+1}) x_s'\Bigg]\,
+  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
             \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
@@
 respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$1 - \alpha$ quantile of the distribution of $\max_i \hat W_i$, with
+$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
 $\hat W \sim N(0, \hat V)$.  Then
 \begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{1i} > \hat c\Big] \leq \alpha,
+  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
 \end{equation*}
@@
 \emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% using this critical value. Using this
-critical value, none of the predictors are significant at 10\%, which
+remain significant at 10\% with this critical value. Using this
+critical value, none of the predictors are significant, which
 gives additional support to \citepos{GoW:08} conclusion that excess

### 2015-01-07 appendix.tex
Change paper name and fix date

@@
 
-\title{Supplemental Appendix for ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models''}
+\title{Supplemental appendix for ``An asymptotically normal
+  out-of-sample test based on mixed estimation windows''}
 
@@
 This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test of equal
-predictive accuracy for nested models.''  Define the following
+for the paper, ``An asymptotically normal out-of-sample test based on
+mixed estimation windows'' \citep{Cal:15}. Define the following
 additional terms:

### 2015-01-07 mixedwindow.tex
Change paper name and fix date

@@
     Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
+    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
+    circulated under the name ``An asymptotically normal out-of-sample
+  test of equal predictive accuracy for nested models.''}\\%
   Iowa State University}
 
-\title{An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models}
+\title{An asymptotically normal out-of-sample test based on
+  mixed estimation windows}
 
@@
 from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15}.
+separate appendix along with some supporting lemmas \citep{Cal:15b}.
 

### 2015-01-09 appendix.tex
Minor changes to text before submission

@@
 x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_t \ep_{t+1} / (t-1)$.
+$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
 And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
@@
     = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
-      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
+      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
   \end{equation}
@@
 
+\noindent%
 This Lemma establishes that \citepos{Wes:96} basic results hold under
 our weaker moment and dependence conditions and provides several
-extensions. To streamline the presentation, we'll assume in these
-proofs that $x_t$ is a scalar.
+extensions for the first few observations. To streamline the
+presentation, we'll assume in these proofs that $x_t$ is a scalar.
 \begin{proof}

### 2015-01-09 mixedwindow.tex
Minor changes to text before submission

@@
 
-\citet{ClW:06,ClW:07} propose using this as a test of whether $\ep_{t+1}$ is
-an \mds. In their 2006 paper, Clark and West assume that the
+\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
+In their 2006 paper, Clark and West assume that the
 coefficients on the benchmark model, $\btrue$, are zero under the null, making
@@
 their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as the $\yh_{t+1}$. Now the estimated linear model's prediction errors,
+rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
 $\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
@@
 \begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T+1
+  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
 \end{equation}
-where $\beta$ is an unknown $k$-vector of parameters and $x_t$ is an
+where $\beta$ is an unknown vector of parameters and $x_t$ is an
 observed vector of predictors. The parameter $\beta$ is estimated with
 \ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{1,t+1}$ and is estimated with a
+The alternative model is denoted $\yh_{t+1}$ and is estimated with a
 rolling window of length $R$.
@@
 by imposing moment conditions on the alternative models' forecasts.
+The stationarity condition holds whenever the vector
+$(\ep_{t+1}, x_t, z_t)$ is strictly stationary.
 
@@
 
-The last assumption restricts the class of \hac\ variance estimators
+The final assumption restricts the class of \hac\ variance estimators
 we will consider. We use the same class of estimators studied by
@@
 \begin{asmp}\label{a5}%
-  $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
+  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
   = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
@@
 \end{equation*}
-The adjusted \oos\ loss for the alternative model using a hypothetical
-value of $\beta$ to produce the benchmark forecast is denoted by
+The adjusted \oos\ loss difference using a hypothetical value of
+$\beta$ to produce the benchmark forecast is denoted by
 \begin{equation*}
@@
 specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t(\btrue) - \E f_t(\btrue)$ is an \mds\ as discussed
+implies that $f_t$ is an \mds\ as discussed
 at the beginning of this section. This is especially appealing in our
@@
 test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation from an \mds\ is potentially
+out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
 interesting. But the \mds\ null hypothesis only affects the estimator
@@
 In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. This
-approach can then be interpreted as an encompassing test as in
+that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
+statistic can then be interpreted as an encompassing test as in
 \citet{HLN:98}, and would test whether the alternative model contains
-additional information that would make the benchmark model more
-accurate. This interpretation comes from the combination forecasting
+additional information that could make the benchmark model more
+accurate. This interpretation can be motivated by the combination forecasting
 model
 \begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\beta + w \yh_{t+1}
+  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
 \end{equation*}
@@
 \[
-e_{\mathit{avg},t+1} = e_{0,t+1} + w (e_{0,t+1} - e_{1,t+1})
+y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
 \]
-with $e_{\mathit{avg},t+1} = y_{t+1} - \yh_{\mathit{avg},t+1}$,
-$e_{0,t+1} = y_{t+1} - x_t'\beta$, and $e_{1,t+1} = y_{t+1} -
-\yh_{1,t+1}$. The value
+The value
 \[
-w = \frac{\E e_{0,t+1} (e_{0,t+1} - e_{1,t+1})}{\E e_{0,t+1}^2}
+w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
 \]
@@
 the alternative uses information not in the benchmark, unless
-$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated.
+$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
+correlation is exactly the quantity measured by our statistic.
 
-The final Theorem puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics.  It is an immediate
-consequence of the previous two results and its proof is omitted.
+The final result puts together Theorem~\ref{res:1} and
+Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
+under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
+and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
+x_t = 0$ by construction. This result is an immediate consequence of
+the previous two results and its proof is omitted.
 

### 2015-01-09 appendix.tex
Last minute changes before ECMA sub

@@
 
+Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
+and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
+of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
+
 \begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
@@
   \end{equation*}
-  follows the same argument as in \citet{Wes:96}.
+  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
 \end{proof}
@@
 \begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
+\noindent%
 We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same, but uses \citepos{JoD:00} Theorem
-2.1 instead of an application of the \lln.
+$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
+2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
 \begin{proof}
@@
   \end{gather}
-  The first two results are implied by the proof of Theorem~\ref{res:1}
-  and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7} follow from the \lln, so it
-  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.
+  The first two results are implied by the proof of
+  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
+  follow from the \lln, since each summand is an $L_1$-mixingale of
+  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
+  prove~\eqref{eq:4} and~\eqref{eq:5}.
 
@@
 \noindent%
-This Lemma establishes that \citepos{Wes:96} basic results hold under
-our weaker moment and dependence conditions and provides several
-extensions for the first few observations. To streamline the
+To streamline the
 presentation, we'll assume in these proofs that $x_t$ is a scalar.
@@
   \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
+    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
+    and $\zeta_k$ denote its mixingale
     constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
@@
 \end{equation*}
-From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p 0$. The \clt\ implies
-that $\ocltb{t} (F_t - F) = O_p(1)$,
-establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
+From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
+0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
+O_p(1)$, establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
 and~\eqref{eq:13} are similar.

### 2015-01-09 mixedwindow.tex
Last minute changes before ECMA sub

@@
 
-\section{Theoretical results supporting the asympotically normal \oos\ statistic}
+\section{Theoretical results supporting the asymptotically normal \oos\ statistic}
 \label{sec:1}
@@
 \end{align}
-for each $t$.
+for each $t$.%
+\footnote{The matrix inversion in $\bh_t$ can be replaced with a
+  pseudo-inverse if necessary for some values of $t$ without changing
+  the forecast.} %
 \citepos{Wes:96} Theorem 4.1 implies that
@@
 assumption.  The weak dependence and moment conditions are
-standard. These assumptions are slightly weaker than similar
-assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only because we
-make use of more recent developments in limit theory, in particular
-the \clt\ for Near-Epoch Dependent (\ned) processes proven by
-\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.
+standard. The assumption of strict stationarity is stronger than
+necessary in practice --- once the alternative forecasting method is
+known, it is only necessary that the \oos\ adjusted loss difference be
+weak stationary, and even that can be relaxed further --- but this
+stronger assumption ensures that the results hold generally.
 
@@
   all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the processes $\ep_{t+1}$, $x_t$, and $z_t$ are
-  $L_2$-\ned\ of size $-(r-1)/(r-2)$ for $r > 2$ on either a strong
-  mixing process of size $-r/(r-2)$ or a uniform mixing process of
-  size $-r/(2r-2)$.
+  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
+  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
+  $-r/(2r-2)$, for $r > 2$.
 \end{asmp}
@@
   The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}; the partial sums
-  $\sum_{s=1}^{t-1} x_s x_s' / (t-1)$ are almost surely invertible for
-  all $t \geq R$ (uniformly in $T$).  The alternative forecast
-  satisfies
+  with a recursive window according to~\eqref{eq:8}. The alternative
+  forecast satisfies
   \begin{equation}
-    \yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
+    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
   \end{equation}
@@
   $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments and is
-  4th order stationary.
+  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
+  where $r$ is first defined in Assumption~\ref{a1}.
 \end{asmp}
@@
 by imposing moment conditions on the alternative models' forecasts.
-The stationarity condition holds whenever the vector
-$(\ep_{t+1}, x_t, z_t)$ is strictly stationary.
 
@@
 \end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
-$\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
+and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
+f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
 
@@
 \citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96} and \citealp{Mcc:00}
+$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
 for details.) The general approach of using a recursive window to

### 2015-03-20 mixedwindow.tex
Change versioning style and add explicit VERSION.tex file
Merge main paper and supplemental appendix files
One of the referees had trouble getting the appendix, so I've
merged it with the main file.

@@
 \documentclass[12pt,fleqn]{article}
+\input{VERSION}
 \input{tex/setup}
@@
 
+\appendix
+\section{Not-for-publication supplemental appendix}
+\newcommand{\WesA}[1][]{\ocltb{t}
+  (F_t^{#1} - F) B^{#1} H_t^{#1}}
+\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
+  B^{#1}) H_t^{#1}}
+\newcommand{\WesC}[1][]{\ocltb{t}
+  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
+
+This appendix contains mathematical proofs and some supporting Lemmas
+for the paper, ``An asymptotically normal out-of-sample test based on
+mixed estimation windows'' \citep{Cal:15}. Define the following
+additional terms:
+\begin{equation*}
+  F_t(\beta) = 2 (x_t'\beta - \yh_{t+1}) x_t',
+\end{equation*}
+$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
+x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
+$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
+And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
+
+Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
+and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
+of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
+
+\subsection*{Proof of Theorem \ref{res:1}}
+  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
+  \begin{equation}\label{eq:6}
+    \sqrt{P} (\fb - \E \fb^*)
+    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
+      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
+  \end{equation}
+  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
+  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
+  \begin{align*}
+    \sqrt{P} (\fb - \E \fb^*)
+    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
+    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
+  \end{align*}
+  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
+  Lemma~\ref{res:a4} shows that
+  \begin{gather}
+    \WesA \to^{p} 0 \label{eq:11} \\
+    \WesB \to^{p} 0 \label{eq:12} \\
+    \intertext{and}
+    \WesC \to^{p} 0 \label{eq:13}
+  \end{gather}
+  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
+  w_t = o_{p}(1)$. The proof that
+  \begin{equation*}
+    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
+  \end{equation*}
+  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
+
+\subsection*{Proof of Lemma~\ref{lem:2}}
+
+We will only prove $\sigmah_2 \to^p \sigma$. The result for
+$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
+2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
+
+  First, we can rewrite the components of the variance estimator as
+  \begin{align*}
+    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
+    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
+                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
+    \intertext{and}
+    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
+  \end{align*}
+  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
+  $\fb - \E \fb^* \to^p 0$,
+  $\gb - \E \gb^* \to^p 0$,
+  \begin{gather}
+    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
+    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
+    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
+    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
+    \intertext{and}
+    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
+  \end{gather}
+  The first two results are implied by the proof of
+  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
+  follow from the \lln, since each summand is an $L_1$-mixingale of
+  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
+  prove~\eqref{eq:4} and~\eqref{eq:5}.
+
+  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
+  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
+  that~\eqref{eq:4} holds if
+  \begin{gather}
+    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
+    \intertext{and}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
+  \end{gather}
+  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
+  \begin{align*}
+    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
+    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
+    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  by Lemma~\ref{res:a2} and the \lln.
+  A similar argument holds for the second term:
+  \begin{align*}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
+    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
+    &= O_p(R'/P) + o_p(1)
+  \end{align*}
+  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
+  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
+
+\subsection*{Supporting Results}
+
+\begin{alem}\label{res:a1}
+  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
+  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
+  and $R' = o(\sqrt{P})$. Then
+  \begin{equation*}
+    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
+  \end{equation*}
+\end{alem}
+
+\begin{proof}
+  We can rewrite this summation as
+  \begin{multline*}
+    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
+    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
+    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
+  \end{multline*}
+  Each of these individual summations can be shown to converge to
+  zero in probability. First,
+  \begin{equation*}
+    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
+    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
+    = O(R'/\sqrt{P}).
+  \end{equation*}
+  Also,
+  \begin{align*}
+    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
+    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
+    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
+    & = O_p(R'/\sqrt{P})
+  \end{align*}
+  and
+  \begin{equation*}
+    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
+    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
+    = O_p(R'/\sqrt{P}).
+  \end{equation*}
+  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
+  construction, this completes the proof.
+\end{proof}
+
+\begin{alem}\label{res:a2}
+  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
+  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
+  \infty$ and $R' = o(\sqrt{P})$. Then
+  \begin{enumerate}
+  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
+  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
+  \item $\omaxb{t} | B_t - B | \to^p 0$,
+  \item $\omaxc{t} | B_t - B | = O_p(1)$,
+  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
+  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
+  \end{enumerate}
+  where the absolute value is taken as the largest of the
+  element-by-element absolute values.
+\end{alem}
+
+\noindent%
+To streamline the
+presentation, we'll assume in these proofs that $x_t$ is a scalar.
+\begin{proof}
+  We will prove each part in order.
+  \begin{enumerate}
+  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
+    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
+    and $\zeta_k$ denote its mixingale
+    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
+    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
+    coefficients $\zeta_k$, since
+    \begin{align*}
+      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
+      &\leq (t^{b} c_t) \zeta_k
+    \end{align*}
+    and
+    \begin{align*}
+      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
+      &\leq (t^{b} c_t) \zeta_{k+1}.
+    \end{align*}
+
+    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
+    \begin{align*}
+      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
+      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
+      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
+    \end{align*}
+    where the second inequality follows from \citepos{Mcl:75} maximal
+    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
+    Corollary 16.10). The summation converges to a constant as $T \to
+    \infty$ and $(R'-1)^{-2\delta} \to 0$, completing the proof.
+
+  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
+    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
+    \begin{align*}
+      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
+      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
+      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
+    \end{align*}
+    which converges to a finite limit.
+  \item The same argument used in Part 1 implies that $\omaxb{t} |
+    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
+    the result follows.
+  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
+  \item We have
+    \begin{align*}
+      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
+      &\leq \omaxb{t} |\hat{B}_t - B|
+      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
+      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
+    \end{align*}
+    and both terms converge to zero in probability by Parts 1 and 3.
+  \item Similar to the previous argument, we have
+    \begin{align*}
+      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
+      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
+      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
+    \end{align*}
+    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
+  \end{enumerate}
+\end{proof}
+
+\begin{alem}\label{res:a4}
+  Under the conditions of Theorem~\ref{res:1}, Equations
+  \eqref{eq:11}--\eqref{eq:13} hold.
+\end{alem}
+
+\begin{proof}
+We can write
+\begin{equation*}
+  \Big\lvert \WesA \Big\rvert \leq
+  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
+  \omaxb{t} \lVert H_t \rVert.
+\end{equation*}
+From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
+0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
+O_p(1)$, establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
+and~\eqref{eq:13} are similar.
+\end{proof}
+
 \bibliography{texextra/references}

### 2015-04-21 mixedwindow.tex
Add link to bug tracker to main paper

@@
     \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
-    gcalhoun\guillemotright.
+    web: \guillemotleft http://gray.clhn.org\guillemotright.
+    If you find errors or mistakes in this paper, please email me or
+    open a new issue at
+    \guillemotleft https://git.ece.iastate.edu/gcalhoun/mixedwindow/issues\guillemotright.
     I'd like to
@@
   mixed estimation windows}
-
-% \date{March 14, 2013}
 

### 2015-04-21 talks/poster.tex
Start to write slides for U. Montreal

\documentclass[final]{beamer}
  \mode<presentation>
  {
% you can chose your theme here:
% \usetheme{Berlin}
% further beamerposter themes are available at 
% http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php
}
\usepackage{type1cm}
\usepackage{calc} 
\usepackage{xcolor}
\usepackage[orientation=landscape,size=a0,scale=1.25]{beamerposter}
\setlength{\paperwidth}{40in}
\setlength{\paperheight}{30in}
\setlength{\textwidth}{0.98\paperwidth}
\setlength{\textheight}{0.98\paperheight}

\input{tex/mcDef}
\input{tex/ap}
\input{tex/header}

\setbeamertemplate{frametitle}[default][center]
\setbeamertemplate{items}[circle]
\setbeamertemplate{navigation symbols}{}
\usecolortheme{dove}

% \setbeamercolor{frametitle}{fg=black}
% \setbeamercolor{sec title}{parent=titlelike}
% \setbeamertemplate{navigation symbols}{}

\setbeamerfont{sec title}{parent=title}
\newcommand*{\secpage}{\usebeamertemplate*{sec page}}
\setbeamercolor{frametitle}{fg=black}

\begin{document}
\begin{frame}{\\\centering \textbf{\huge An asymptotically normal out-of-sample
    test of equal predictive accuracy for nested models}}
  \centering

  Gray Calhoun, Iowa State University Economics Department

  Sept. 26, 2013, NBER-NSF Time Series Conference

  \begin{columns}[t]
    \begin{column}{.23\textwidth}

      \begin{block}{\textbf{Abstract / overview}}
        \begin{itemize}
        \item[] This paper proposes a modification of
          \citepos[\textit{J.  Econom.}]{ClW:07} adjusted
          out-of-sample $t$-test.  The alternative model is still
          estimated with a fixed-length rolling window, but the
          benchmark is estimated with a recursive window. The
          resulting statistic is asymptotically normal even when the
          models are nested.  Moreover, the alternative model can be
          estimated using common model selection methods, such as the
          AIC or BIC.  This paper also presents a method to compare
          multiple models simultaneously while controlling familywise
          error, and substantially improves existing block bootstrap
          methods for out-of-sample statistics.  This procedure is
          then used to analyze
          \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns
          dataset.
        \end{itemize}
      \end{block}
      \bigskip
      \begin{block}{\textbf{Test statistic for out-of-sample model
          comparisons (Theorem~1)}}
        \begin{itemize}
        \item Standard out-of-sample (OOS) model comparison:
          \begin{itemize}
          \item $R+1$ observations used as training/estimation sample
          \item $P$ used as test sample
          \item $T+1$ total observations ($T = R + P$)
          \end{itemize}
        \item $\hat{y}_{0t}$ and $\hat{y}_{1t}$ forecast the variable
          $y_t$
        \item $\hat{y}_{0,t+1}$, is estimated using OLS with a
          recursive window: $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$
          (benchmark model)
        \item $\hat{y}_{1t}$, is estimated using a rolling window of
          fixed length $R$ (less than $T$):
          \begin{equation*}
            \hat{y}_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
          \end{equation*}
          where $\psi$ is a known function
        \item Standard moment, dependence, and positive definiteness
          conditions hold (see paper)
        \item Null hypothesis: $y_t - \hat{y}_{0t}(\btrue)$
          is a martingale difference sequence with respect to the
          filtration $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1},
          z_{t-1}),\dots)$
        \item \textbf{Theorem 1:} $\sqrt{P} \bar f / \hat\sigma \to^d
          N(0,1)$, where
          \begin{multline*}
            \bar f = \tfrac{1}{P} \sum_{t=R+1}^T \Big[(y_{t+1} - \hat y_{0,t+1})^2
            - (y_{t+1} - \hat{y}_{1,t+1})^2
            \\ + (\hat y_{0,t+1} - \hat{y}_{1,t+1})^2 \Big],
          \end{multline*}
          formula for the variance defined in the paper
        \item Presented for one step ahead forecasting but can be
          extended to longer horizons
        \item Can be used to test for zero correlation (instead of
          MDS) or forecast optimality with different loss (other than
          MSE) with minor modifications
        \end{itemize}
      \end{block}
    \end{column}

    \begin{column}{.23\textwidth}
      \begin{block}{\textbf{Comparing several models (Theorem~2)}}
        \begin{itemize}
        \item Extends results in Theorem~1 to comparisons of many
          models
        \item $m$ alternative forecasting models,
          $\hat{y}_{1t},\dots, \hat{y}_{mt}$
          \item Data matrices $\X_R = (X_1,\dots,X_R)'$
            and $\X_{P} = (X_{R+1},\dots,X_{T-1})$ with
            \begin{equation*}
              X_t = \begin{cases}
                (y_{t+1}, x_t')' & t \leq R \\
                (y_{t+1}, x_t', \hat{y}_{1,t+1}, \dots, \hat{y}_{m,t+1})' & t > R.
              \end{cases}
            \end{equation*}
        \item Bootstrap procedure:
          \begin{enumerate}
          \item Draw $B$ samples of $P$ observations from $\X_{P}$
            with block bootstrap (stationary, circular, etc.)
          \item Denote each sample as $\X_{P, l}^{*}$ and let
            $\X_l^{*} = [\X_{R}', \X_{P,l}^{*\prime}]'$
          \item Estimate $\bar{f}^{*}_{li}$ and
            $\hat{\sigma}_{li}^{*}$ as in Theorem~1 for each bootstrap
            sample, $\X^{*}_l$, and each alternative model,
            $\hat{y}_{\ell t}$
          \end{enumerate}
        \item Test procedure (Theorem 2):
          \begin{enumerate}
          \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let
            $M_j = \{\ell : \tfrac1{\hat\sigma_l} \bar{f}_{\ell} >
            \hat{d}_j\}$, where $\hat{d}_j$ is the $1-\alpha$ quantile
            of $\max_{\ell \notin M_{j-1}}
            \tfrac{1}{\hat{\sigma}_\ell^{*}}(\bar{f}_{\ell}^{*} -
            \bar{f_\ell}(\btrue[*]))$.
          \item Reject all of the models $\ell$ with $\ell \in
            \bigcup_{j=1}^m M_j$
          \end{enumerate}
        \item $\bar f_\ell$ is Theorem 1's statistic for the $\ell$th
          alternative model
        \item Controls familywise error rate at level $\alpha$
        \item Similar assumptions on each model as in Theorem 1
        \end{itemize}
      \end{block}

      \bigskip

      \begin{block}{\textbf{Bootstrap for out-of-sample statistics (Theorem 3)}}
        \begin{itemize}
        \item This section concerns \emph{general} OOS comparisons
        \item Standard moment, dependence, positive definiteness and
          smoothness conditions (still) assumed
        \item \textbf{Theorem 3:}
          Then, for all $\epsilon > 0$,
          \begin{multline*}
            \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\tilde{\beta}_T))
            \leq x] \\ - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\btrue)) \leq x] | >
            \epsilon] \to 0
          \end{multline*}
          \begin{itemize}
          \item $\bar f^*$ is the bootstrapped OOS statistic
            (stationary, circular, or moving blocks)
          \item $\bar f$ is the OOS statistic
          \item $\E \bar f(\beta_0)$ is the population quantity of
            interest
          \item $\bar f(\tilde \beta_T)$ is the OOS average using
            the \emph{full-sample} parameter estimate
          \end{itemize}
        \item $R, P \to \infty$ as $T \to \infty$ and the (expected)
          block length $b$ satisfies $b \to \infty$ and $\frac{b}{P}
          \to 0$
        \item Other nonparametric bootstraps for OOS statistics
          require $(P/R) \log \log R \to 0$ or redefining
          $\hat\beta_t^*$
        \item Parametric bootstrap requires that the benchmark model
          be correctly specified
        \end{itemize}
      \end{block}
    \end{column}

    \begin{column}{.23\linewidth}
      \begin{block}{\textbf{Monte Carlo simulations}}
        \smallskip
        \bigskip
        {
          \footnotesize
          \input{tex/mc1}
        }
        \begin{itemize}
        \item Size and power of the OOS tests at \testsize\%
          confidence, based on \totalsims\ simulations
        \item Shows fraction of simulations for which each test rejects:
          \begin{itemize}
          \item Pr[\textsc{cw} roll.]: Clark and West's (2007)
            rolling-window
          \item Pr[\textsc{cw} rec.]: Clark and West's (2007)
            recursive-window
          \item Pr[new]: Our new mixed-strategy test statistic
          \end{itemize}
        \item DGP given by
          \begin{align*}
            y_t &= \gamma_{1t} + \gamma_{2t} z_{t-1} + e_t \\\\
            \gamma_t &=
            \begin{cases}
              (0.5, 0)    & \text{size simulations} \\
              (0.5, 0.35) & \text{power (stable)} \\
              (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
              (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
            \end{cases}\\\\
            z_t &= 0.15 + 0.95 z_{t-1} + v_t \\\\
            (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
            \end{pmatrix}
            , \begin{pmatrix} 18 & -
              0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
          \end{align*}
        \item Benchmark regresses $y_t$ on a constant
        \item Alternative regresses $y_t$ on a constant and $z_{t-1}$ (OLS)
        \item Mimics the asset pricing application studied later in the paper
          \citep{GoW:08}
        \end{itemize}
      \end{block}
    \end{column}

    \begin{column}{.23\linewidth}
      \begin{block}{\textbf{Application to equity premium predictability}}
        \smallskip
        \bigskip
        {
          \footnotesize
          \empiricaltable
        }

        \begin{itemize}
        \item OOS comparison of equity premium prediction models
          based on \citet{GoW:08}
        \item Benchmark is the recursive sample mean of the equity
          premium and each alternative model is a constant and single
          lag of the variable listed in the \emph{predictor} column
          (\emph{CT} indicates \citepos{CaT:08} correction to forecasts)
        \item Dataset begins in 1927 and ends in 2009, annual data
        \item \emph{Value} column lists the value of this paper's
          OOS statistic
        \item \emph{Naive} column indicates whether the statistic is
          significant at standard critical values
        \item \emph{Corrected} column indicates significance using
          critical values that account for the number of models
        \end{itemize}
      \end{block}

      \begin{block}{\textbf{Contact Information}}
        \begin{itemize}
        \item Economics Department; Iowa State University
        \item Telephone: (515) 294-6271.
        \item Email: gcalhoun@iastate.edu
        \item Web: http://gray.clhn.co
        \end{itemize}
      \end{block}

    \end{column}
  \end{columns}
\end{frame}
\begin{frame}<beamer:0>
    \bibliography{texextra/AllRefs}
\end{frame}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-PDF-mode: t

%  LocalWords:  NBER Econom ClW AIC familywise Finan GoW dataset MDS
%  LocalWords:  optimality MSE nonparametric DGP iid beamer texextra AllRefs

### 2016-01-13 mixedwindow.tex
Change url to GitHub repository
Why: the current version of the repository refers to a private
GitLab repository; it's more useful to direct people to the
public GitHub repository.

This change addresses this need by: changing the url to GitHub.

Closes #13
Add Table of Contents to the paper
Why: the working paper version of this document will be easier
for people to skim if it has a table of contents. This commit
adds one and also manually adds the assumptions and theoretical
results to the ToC.

@@
 
+\providecommand\phantomsection{}
+
 \author{Gray Calhoun\thanks{Economics Department; Iowa State
@@
     open a new issue at
-    \guillemotleft https://git.ece.iastate.edu/gcalhoun/mixedwindow/issues\guillemotright.
+    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
     I'd like to
@@
 
+\addcontentsline{toc}{section}{Abstract}
 \begin{abstract}
@@
 \end{abstract}
+\newpage
+
+\tableofcontents
 
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
 \begin{asmp}\label{a1}%
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
 \begin{asmp}\label{a3}%
@@
 average is positive.
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
 \begin{asmp}\label{a4}%
@@
 further discussion.
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
 \begin{asmp}\label{a5}%
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
 \begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
 \begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
 \begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
@@
 
+\newpage
+\phantomsection
+\addcontentsline{toc}{section}{References}
+\bibliography{texextra/references}
+
+\newpage
 \appendix
-\section{Not-for-publication supplemental appendix}
+\section{Supplemental appendix (not for publication)}
 \newcommand{\WesA}[1][]{\ocltb{t}
@@
 
-\subsection*{Proof of Theorem \ref{res:1}}
+\subsection{Proof of Theorem \ref{res:1}}
   Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
@@
 
-\subsection*{Proof of Lemma~\ref{lem:2}}
+\subsection{Proof of Lemma~\ref{lem:2}}
 
@@
 
-\subsection*{Supporting Results}
+\subsection{Supporting results}
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
 \begin{alem}\label{res:a1}
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
 \begin{alem}\label{res:a2}
@@
 
+\phantomsection
+\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
 \begin{alem}\label{res:a4}

### 2016-01-13 CHANGELOG.tex
Add CHANGELOG to repository
I'm trying out the idea of including a change log for my
academic papers to make them more informative to casual
readers interested in my research. This commit adds one
to this repository and embeds it in the final pdf.

Closes #12

\section{Changes to previous versions}
\subsection{Pending changes for the next release}

\begin{itemize}
\item Public urls for the source code have been changed from a private
GitLab repository to a public GitHub repsoitory.
\item Adds a table of contents to make skimming and navigation easier.
\item Adds this ``change log'' itself. :)
\end{itemize}

\subsection{2015-04-23}
This version was not released.

\begin{itemize}
\item Combine the supplemental appendix with the main document (for
convenience).
\end{itemize}

\subsection{2015-01-09}
This is an incomplete list of the changes made in the `2015-01-09'
version of the paper. This version was resubmitted to
\textit{Econometrica} after the 2013-03-14 version received ``reject
and resubmit.''

\begin{itemize}
\item Moves supporting theoretical results to a supplementary
appendix.
\item Separates the statement of assumptions from the theoretical
results.
\item Replaces the multiple testing results with a much simpler
version.
\item Changes the NED assumptions slightly (the previous version had
an error).
\item Makes several changes to the wording of the paper.
\item Adds an explicit variance-covariance matrix and proves
consistency.
\item Changes the typeface used in the paper and makes other small
changes to the formatting.
\end{itemize}

\subsection{2014-04-01}
\begin{itemize}
\item Removes all of the bootstrap material from the paper to move it
to a separate paper at the request of the \textit{Econometrica}
editor.
\end{itemize}

\subsection{2013-03-14}
First released version of the paper. This version was submitted

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "mixedwindow"
%%% End:

### 2016-02-03 lib/dbframe.Rcheck/dbframe-R-library.Rcheck/dbframe-Ex.R
[git-make all]: success building branch 'master'

@@ -1,0 +1,214 @@
+pkgname <- "dbframe"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+library('dbframe')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("booktabs")
+### * booktabs
+
+flush(stderr()); flush(stdout())
+
+### Name: booktabs
+### Title: Construct a nice table from a data frame
+### Aliases: booktabs
+### Keywords: methods printing
+
+### ** Examples
+
+data(chickwts)
+cat(booktabs(head(chickwts)))
+
+
+
+cleanEx()
+nameEx("clear")
+### * clear
+
+flush(stderr()); flush(stdout())
+
+### Name: clear
+### Title: Remove a table from the database
+### Aliases: clear clear-methods clear,dbframe-method
+### Keywords: database methods
+
+### ** Examples
+
+filename <- tempfile(fileext = ".db")
+example.dbframe <- dbframe("clear1", dbname = filename)
+example2.dbframe <- dbframe("clear2", dbname = filename)
+clear(example.dbframe, example2.dbframe)
+
+data(chickwts)
+insert(example.dbframe) <- chickwts
+head(example.dbframe)
+clear(example.dbframe)
+head(example.dbframe)
+unlink(filename)
+
+
+
+cleanEx()
+nameEx("dbframe-package")
+### * dbframe-package
+
+flush(stderr()); flush(stdout())
+
+### Name: dbframe-package
+### Title: An overview of the dbframe package
+### Aliases: dbframe-package
+### Keywords: package database
+
+### ** Examples
+
+filename <- tempfile(fileext = ".db")
+example.dbframe <- dbframe("package1", dbname = filename, clear = TRUE)
+data(chickwts)
+insert(example.dbframe) <- chickwts
+select(example.dbframe, "avg(weight)", group.by = "feed")
+unlink(filename)
+
+
+
+cleanEx()
+nameEx("dbframe")
+### * dbframe
+
+flush(stderr()); flush(stdout())
+
+### Name: dbframe
+### Title: Create a 'dbframe' object
+### Aliases: dbframe dbframe_sqlite dbframe_sqlite_temporary
+###   dbframe_unknown
+### Keywords: database interface
+
+### ** Examples
+
+data(chickwts)
+filename <- tempfile(fileext = ".db")
+example <- dbframe("dbframe1", dbname = "filename", dbdriver = "SQLite",
+                   data = chickwts)
[…]

### 2016-02-03 lib/dbframe.Rcheck/dbframe-R-library.Rcheck/tests/dbframe-package.R

@@ -1,0 +1,4 @@
+## Copyright (C) 2010-2015 Gray Calhoun; MIT license
+
+library(testthat)
+test_package("dbframe")

### 2016-02-03 lib/dbframe/tests/test-booktabs.R

@@ -1,0 +1,23 @@
+    library(testthat)
+    library(xtable)
+    filename <- tempfile(fileext = ".db")
+
+    data(longley)
+    test_that("booktabs executes at all", {
+      expect_that(booktabs(longley), is_a("character"))
+    })
+
+    test_that("Columns that are labeled 'numberformat' are formatted", {
+      d <- data.frame(x = c(-1.324, 0.93), y = c(10.443, 1.235))
+      expect_that(booktabs(d, numberformat = TRUE, 
+                           purgeduplicates = FALSE, digits = 2, align = "c"),
+        prints_text("\\$\\\\\\\\\\!\\\\\\\\\\!-1.32\\$ & \\$10.44\\$"))
+      expect_that(booktabs(d, numberformat = TRUE,
+                           purgeduplicates = FALSE, digits = 2, align = "c"),
+        prints_text("\\$\\\\\\\\enskip0.93\\$ & \\$\\\\\\\\enskip1.24\\$"))
+    })
+
+    test_that("Argument checking works as expected", {
+      expect_that(booktabs(longley, drop = "WXYZ"),
+        gives_warning("'drop' contains some columns not in 'dframe'"))
+    })

### 2016-02-03 lib/dbframe/tests/test-dbframe.R

@@ -1,0 +1,15 @@
+    library(testthat)
+
+    data(morley)
+    filename <- tempfile(fileext = ".db")
+
+    test_that("Basic constructor works", {
+      d1 <- dbframe("test1", dbname = filename, data = morley)
+      expect_that(d1, is_a("dbframe_sqlite"))
+      expect_that(morley, is_equivalent_to(select(d1)))
+    })
+
+    test_that("Simple methods work", {
+      d1 <- dbframe("test2", dbname = filename, data = morley)
+      expect_that(nrow(morley), equals(nrow(d1)))
+    })

### 2016-02-03 lib/dbframe/tests/test-head.R

@@ -1,0 +1,16 @@
+    library(testthat)
+    filename <- tempfile(fileext = ".db")
+
+    data(morley)
+    test_that("head and tail return the right number of records", {
+      dbf <- dbframe("tab1", dbname = filename, data = morley)
+      expect_that(nrow(head(dbf)), equals(6))
+      expect_that(nrow(tail(dbf)), equals(6))
+  
+      nrec <- sample(1:nrow(morley), 1)
+      expect_that(nrow(head(dbf, nrec)), equals(nrec))
+      expect_that(nrow(tail(dbf, nrec)), equals(nrec))
+
+      expect_that(nrow(head(dbf, -nrec)), equals(nrow(morley) - nrec))
+      expect_that(nrow(tail(dbf, -nrec)), equals(nrow(morley) - nrec))
+    })

### 2016-02-03 lib/dbframe/tests/test-select.R

@@ -1,0 +1,52 @@
+    library(testthat)
+    data(chickwts)
+    chickwts$feed <- as.character(chickwts$feed)
+    test_that("insert and select work", {
+          expect_that(chickwts, is_equivalent_to(select(chickwts)))
+              testdbfile <- tempfile(fileext = ".db")
+              testdbframe <- dbframe("select1", testdbfile)
+              clear(testdbframe)
+          insert(testdbframe) <- chickwts
+          expect_that(chickwts, is_equivalent_to(select(testdbframe)))
+              unlink(testdbfile)})
+    test_that("column renaming scheme works", {
+          expect_that(
+            c("feed", "AverageWeight"),
+            is_identical_to(names(select(chickwts,
+                 c(AverageWeight = "avg(weight)"), group.by = "feed"))))
+              testdbfile <- tempfile(fileext = ".db")
+              testdbframe <- dbframe("select1", testdbfile)
+              clear(testdbframe)
+          insert(testdbframe) <- chickwts
+          expect_that(
+            c("feed", "AverageWeight"),
+            is_identical_to(names(select(testdbframe,
+                 c(AverageWeight = "avg(weight)"), group.by = "feed"))))
+              unlink(testdbfile)})
+    ## test_that("joins work", {
+    ##           testdbfile <- tempfile(fileext = ".db")
+    ##           testdbframe <- dbframe("select1", testdbfile)
+    ##           clear(testdbframe)
+    ##       expect_that(select(list(A = chickwts,B =  chickwts),
+    ##                       c("feed", weightA = "A.weight", weightB = "B.weight"),
+    ##                       using = "feed", order.by = c("feed", "weightA", "weightB")),
+    ##                   equals({
+    ##                     d <- merge(chickwts, chickwts, by = "feed",
+    ##                                                            suffixes = c("A", "B"))
+    ##                     d$feed <- as.character(d$feed)
+    ##                     d[do.call(order, d),]
+    ##                   }, check.attributes = FALSE))
+
+    ##       avgwts <- dbframe("select2", dbname = testdbfile, clear = TRUE,
+    ##                          data = select(chickwts, c(averageweight = "avg(weight)"),
+    ##                                                   group.by = c(thefeed = "feed")))
+    ##       expect_that(select(list(a = chickwts, b = avgwts),
+    ##                          c("feed", "weight", "averageweight"),
+    ##                          on = ("feed = thefeed"), order.by = "feed, weight"),
+    ##                   equals({
[…]

### 2016-02-03 lib/oosanalysis.Rcheck/oosanalysis-R-library.Rcheck/oosanalysis-Ex.R

@@ -1,0 +1,316 @@
+pkgname <- "oosanalysis"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+library('oosanalysis')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("Classes")
+### * Classes
+
+flush(stderr()); flush(stdout())
+
+### Name: Classes
+### Title: Some classes to simplify making predictions
+### Aliases: Aggregate CT predict.CT predict.Aggregate HasMethod
+### Keywords: classes models
+
+### ** Examples
+
+  olddata <- data.frame(y = rnorm(30), x = rnorm(30))
+  newdata <- data.frame(y = rnorm(3), x = rnorm(3))
+
+  m1 <- lm(y ~ 1, data = olddata)
+  m2 <- lm(y ~ x, data = olddata)
+
+  m3 <- CT(m2)
+  m4 <- Aggregate(list(m1, m2, m3), median)
+
+  predict(m3, newdata)
+  predict(m4, newdata)
+
+  HasMethod(m1, c("plot", "print", "predict", "median"))
+
+
+
+cleanEx()
+nameEx("bootindex")
+### * bootindex
+
+flush(stderr()); flush(stdout())
+
+### Name: bootindex_circularblock
+### Title: Indices to induce block bootstraps
+### Aliases: bootindex_circularblock bootindex_movingblock
+###   bootindex_stationary
+### Keywords: htest distribution ts
+
+### ** Examples
+
+## Example of hypothesis test that mean = 0
+nobs <- 200
+nboot <- 299
+level <- .1
+X <- 2 + arima.sim(n = nobs, list(ma = c(0.5)))
+
+naive <- replicate(nboot, mean(X[sample(1:nobs, nobs, replace = TRUE)])) - mean(X)
+smart1 <- replicate(nboot, mean(X[bootindex_circularblock(nobs, 5)])) - mean(X)
+smart2 <- replicate(nboot, mean(X[bootindex_movingblock(nobs, 5)])) - mean(X)
+smart3 <- replicate(nboot, mean(X[bootindex_stationary(nobs, 5)])) - mean(X)
+
+## corresponding critical values
+quantile(naive, 1 - level)
+quantile(smart1, 1 - level)
+quantile(smart2, 1 - level)
+quantile(smart3, 1 - level)
+
+## Not run: 
+##D mc <- replicate(300, {
[…]

### 2016-02-03 lib/oosanalysis.Rcheck/oosanalysis-R-library.Rcheck/oosanalysis/tests/test-dmw_lambda.R

@@ -1,0 +1,10 @@
+## Copyright (C) 2011-2015 Gray Calhoun; MIT license
+
+test_that("dmw_lambda works as expected", {
+  expect_that(dmw_lambda(Inf, "recursive"), equals(list(fh = 1, hh = 2)))
+  expect_that(dmw_lambda(Inf, "rolling"),   equals(list(fh = 1, hh = 1)))
+  expect_that(dmw_lambda(Inf, "fixed"),     equals(list(fh = 0, hh = Inf)))
+  expect_that(dmw_lambda(0, "recursive"), equals(list(fh = 0, hh = 0)))
+  expect_that(dmw_lambda(0, "rolling"),   equals(list(fh = 0, hh = 0)))
+  expect_that(dmw_lambda(0, "fixed"),     equals(list(fh = 0, hh = 0)))
+})

### 2016-10-11 mixedwindow.tex
Add CHANGELOG to repository
I'm trying out the idea of including a change log for my
academic papers to make them more informative to casual
readers interested in my research. This commit adds one
to this repository and embeds it in the final pdf.

Closes #12
Add new code to stamp w/ git version and commit
This commit uses some new functionality introduced by the
latex-tools submodule (directory `texextra`) to automatically
generate and include version and commit information from the
git repository. This will make it much easier to keep track of
the different printouts as I'm editing.
[fix] Tw

@@
 \documentclass[12pt,fleqn]{article}
-\input{VERSION}
 \input{tex/setup}
@@
 \newpage
-
+\markboth{}{}
 \tableofcontents
-
 \newpage
@@
 
-\section{Theoretical results supporting the asymptotically normal \oos\ statistic}
+\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
 \label{sec:1}
@@
 \begin{equation*}
-  F_t(\beta) = 2 (x_t'\beta - \yh_{t+1}) x_t',
+  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
 \end{equation*}
@@
 And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-
 Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
@@
     inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant as $T \to
-    \infty$ and $(R'-1)^{-2\delta} \to 0$, completing the proof.
+    Corollary 16.10). The summation converges to a constant and
+    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
 
@@
 
-\bibliography{texextra/references}
+\setcounter{secnumdepth}{1}
+\include{CHANGELOG}
+
 \end{document}
@@
 % LocalWords:  stationarity mixingale mixingales texextra Timmermann
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% TeX-command-extra-options: "-shell-escape"
+%%% End:

### 2016-10-17 mixedwindow.tex
Make small change in proof of Theorem 1
[#18, #21] Add stubs for second and third part of Lemma A3's proof

@@
     \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
+    = \ocltb{t} (\fh_t - \E f_t)
       + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
@@
   Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
+  we can rewrite~\eqref{eq:6} as
   \begin{align*}
@@
 
-\begin{proof}
+\begin{proof}[Proof of~\eqref{eq:11}]
 We can write
@@
 0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
-O_p(1)$, establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
-and~\eqref{eq:13} are similar.
+O_p(1)$, establishing~\eqref{eq:11}.
+\end{proof}
+
+\begin{proof}[Proof of~\eqref{eq:12}]
+TBD
+\end{proof}
+
+\begin{proof}[Proof of~\eqref{eq:13}]
+TBD
 \end{proof}

### 2016-10-17 mixedwindow.tex
[#18] Rewrite Lemma A3, part 1 to fix errors
The original proof of Lemma A3 used a false inequality. This commit
changes the proof of the first part. The second and third parts were
proven by 'assertion' and need to be fixed as well.

@@
 \begin{proof}[Proof of~\eqref{eq:11}]
-We can write
-\begin{equation*}
-  \Big\lvert \WesA \Big\rvert \leq
-  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
-  \omaxb{t} \lVert H_t \rVert.
-\end{equation*}
-From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
-0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
-O_p(1)$, establishing~\eqref{eq:11}.
+Choose $\delta > 0$ and $a \in (0,1/2)$ and write
+\begin{multline}\label{eq:A3}
+  \WesA =
+  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
+  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
+\end{multline}
+For any $c > 0$,
+\begin{multline*}
+  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
+  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
+\end{multline*}
+which converges to zero by Lemma~\ref{res:a2}, so the first summation on
+the RHS of~\eqref{eq:A3} converges to zero i.p.
+
+For the second summation,
+\begin{equation*}
+  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
+    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
+   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
+\end{equation*}
+The expectation on the RHS is of order
+$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
+$L_2$-mixingale of size $-1/2$ by construction (see the proof of
+Lemma~\ref{res:a2} for a more detailed discussion), and converges to
+zero by Kronecker's Lemma.
 \end{proof}

### 2016-10-17 mixedwindow.tex
[#18] Make small formatting changes to proof of Lemma A3 part 1

@@
 which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
+the RHS of~\eqref{eq:A3} converges to zero i.p. For the second summation,
 \begin{equation*}
@@
     \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
+   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}}
+    \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
 \end{equation*}
@@
 $L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
+Lemma~\ref{res:a2} for a more detailed discussion of the mixingale
+argument), and converges to zero by Kronecker's Lemma.
 \end{proof}

### 2016-10-17 mixedwindow.tex
[#21] Add separate proof of part 2 of Lemma A3

@@
 \begin{proof}[Proof of~\eqref{eq:12}]
-TBD
+Note that
+\begin{equation*}
+  \Big\lvert \WesB \Big\rvert =
+  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
+  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert H_t \rvert \Bigg).
+\end{equation*}
+Lemma~\ref{res:a2} implies that the first component converges to
+zero in probability, so it suffices to show that the second is
+$O_p(1)$. As discussed in the proof of Lemma~\ref{res:a2},
+$x_t \varepsilon_{t+1}$ is an $L_2$-mixingale
+of size $-1/2$ and
+\begin{equation*}
+  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert H_t \rVert_2
+  = O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} t^{-1/2}\Bigg)
+\end{equation*}
+The last summation is $O(1)$ by Lemma A1 of \citet{Wes:96}, completing
+the proof.
 \end{proof}

### 2017-05-15 S0-frontmatter.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
 \maketitle
@@
 \tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
 
@@
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 S1-introduction.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
 \section{Introduction}
@@
 
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 S2-normality.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
 \section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
@@
 
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 S3-montecarlo.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
 \section{Monte Carlo Results}\label{sec:2}
@@
 
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 S4-empirics.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
 \section{Empirical Illustration}\label{sec:3}
@@
 
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 S5-conclusion.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
 \section{Discussion}\label{sec:4}
@@
 
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
-
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: t
+%%% TeX-master: "mixedwindow"
 %%% TeX-command-extra-options: "-shell-escape"

### 2017-05-15 X1-mathematics.tex
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
-\documentclass[12pt,fleqn]{article}
-\input{tex/setup}
-\input{tex/mcDef}
-\input{tex/ap}
-
-% These commands are generated when the Monte Carlo and applied
-% sections are run; I'm giving them definitions now so that LaTeX will
-% compile the document even if that code hasn't been run yet.
-\providecommand\bootsize{[missing]}
-\providecommand\empiricalcriticalvalue{[missing]}
-\providecommand\nboot{[missing]}
-\providecommand\nmod{[missing]}
-\providecommand\testsize{[missing]}
-\providecommand\totalsims{[missing]}
-\providecommand\windowlength{[missing]}
-\providecommand\empiricaltable{[missing]}
-\providecommand\empiricaldraws{[missing]}
-\providecommand\naivecriticalvalue{[missing]}
-
-\providecommand\phantomsection{}
-
-\author{Gray Calhoun\thanks{Economics Department; Iowa State
-    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
-    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
-    web: \guillemotleft http://gray.clhn.org\guillemotright.
-    If you find errors or mistakes in this paper, please email me or
-    open a new issue at
-    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
-    I'd like to
-    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
-    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
-    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
-    Group meeting and the 2013 \nber-\nsf\ Time Series conference
-    for helpful comments and discussions.  I'd also like to thank Amit
-    Goyal for providing computer code and data for his 2008
-    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
-    circulated under the name ``An asymptotically normal out-of-sample
-  test of equal predictive accuracy for nested models.''}\\%
-  Iowa State University}
-
-\title{An asymptotically normal out-of-sample test based on
-  mixed estimation windows}
-
-\begin{document}
-\maketitle
-
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
-\phantomsection
-\addcontentsline{toc}{section}{References}
-\bibliography{texextra/references}
-
-\newpage
-\appendix
 \section{Supplemental appendix (not for publication)}
@@
 \begin{proof}[Proof of~\eqref{eq:13}]
-TBD
+This proof is essentially the same as that of~\eqref{eq:12}. We have
+\begin{equation*}
+  \Big\lvert \WesC \Big\rvert =
+  O_p\Big(\max_{t=R',\dots,T-1} \lvert B_t - B\rvert\Big)\
+  O_p\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lvert (F_t - F) H_t \rvert \Bigg)
+\end{equation*}
+where the first component converges to zero in probability. Then
+\begin{equation*}
+  \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert (F_t - F) H_t \rVert_2
+  \leq \tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert F_t - F \rVert_2 \lVert  H_t \rVert_2
+  = O\Bigg(\tfrac{1}{\sqrt{P}} \sum_{t=R'}^{T-1} \lVert  H_t \rVert_2 \Bigg)
+\end{equation*}
+which is $O(1)$ as in the proof of~\eqref{eq:12}.
 \end{proof}
-
-\setcounter{secnumdepth}{1}
-\include{CHANGELOG}
-
-\end{document}
-
-% LocalWords:  ClW JEL ISI Google GiW Mcc ClM CoS CCS StW IMA GiR WeM fh X'X hh
-% LocalWords:  PaT AllRefs isi ima uc sv PeT GoW lm il GoK RoW Econometrica PoR
-% LocalWords:  Finan StepM studentizing studentization Whi HuW RSW recentering
-% LocalWords:  DiM LiS Kun McCracken lt filtrations GoJR JoD McCracken's Econom
-% LocalWords:  Corradi unstudentized studentized GoJ gcalhoun HLN li PoW
-% LocalWords:  Econometricians reestimate PPW resample miscentered AnG eq Helle
-% LocalWords:  Bunzel Yu Hsu Pincheira HHK th AtO ik DoH Wolak's Wol stepdown
-% LocalWords:  Hsu's iq mk Ames Amit Goyal rfs Ivo Welch Wes covariance MeR McW
-% LocalWords:  familywise prespecified CoD Gia pointwise misspecified InK MeP
-% LocalWords:  VeR xtable Dah dbframe oos parametrizations iid dgp return's CaT
-% LocalWords:  outperformance Hmisc Har nondifferentiable bT jt Meng
-% LocalWords:  stationarity mixingale mixingales texextra Timmermann
 

### 2017-05-15 mixedwindow.tex
[#21] Add proof of third part of Lemma A3
Split main LaTeX file into several smaller files

--- 2016-10-17 mixedwindow.tex
@@
 \begin{document}
-\maketitle
+\include{S0-frontmatter}
+\include{S1-introduction}
+\include{S2-normality}
+\include{S3-montecarlo}
+\include{S4-empirics}
+\include{S5-conclusion}
 
-\addcontentsline{toc}{section}{Abstract}
-\begin{abstract}
-  \noindent This paper develops a modification of \citepos[\textit{J.
-    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
-  using a recursive window to estimate the benchmark model but a
-  fixed-length rolling window to estimate the alternative. The
-  resulting statistic is asymptotically normal even when the models
-  are nested. The
-  paper also presents Monte Carlo evidence that this statistic has
-  much higher power than existing out-of-sample statistics in a common
-  use-case for these tests: when the \dgp\ is subject to instability.
-  This procedure is then used to analyze
-  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
-  and supports their finding that the equity premium is unpredictable
-  out-of-sample.
-
-\strut
-
-\noindent Keywords: Forecast Evaluation, Martingale Difference
-Sequence, Model Selection, Forecast Encompassing
-
-\strut
-
-\noindent \allcaps{JEL} Classification Numbers: C22, C53
-
-\end{abstract}
-\newpage
-\markboth{}{}
-\tableofcontents
-\newpage
-
-\section{Introduction}
-
-This paper proposes an out-of-sample (\oos) test statistic that is
-asymptotically normal and correctly centered even when the models
-studied are nested. The test is based on one proposed by
-\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
-with a recursive window and the alternative model with a fixed length
-rolling window. The rolling window ensures asymptotic normality, as in
-\citet{GiW:06}, and the recursive window allows the null hypothesis to
-be a statement about the specification of the Data Generating Process,
-which is the focus of the vast majority of the \oos\ testing
-literature.%
-\footnote{In particular, this is the focus of \citet{Wes:96},
-  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
-  many others but not \citet{GiW:06}. See \citet{Wes:06} and
-  \citet{ClM:13} for a thorough overview of this literature.} %
-This combination of estimation windows also gives our test statistic
-high power against alternatives that cause the benchmark model
-to be unstable --- structural breaks, time-varying coefficients, or
-forms of nonlinearity, for example --- which is a common motivation
-for using these tests.
-
-\oos\ tests are common in International Macroeconomics,
-Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
-\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
-literature developing the theoretical properties of these statistics,
-beginning primarily with \citet{DiM:95} and
-\citet{Wes:96}.
-In a pair of papers,
-\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
-that a small benchmark model is correctly specified.  Their test
-compares the forecasting performance of a pair of nested models, and
-the null hypothesis is that the innovations in the smaller model form
-a Martingale Difference Sequence (\mds).  This test procedure is popular, and
-one assumes that this is due in part to the statistic's convenience,
-the statistic is approximately normal after adjusting for the
-estimation error of the larger model.  Normality comes from a
-fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
-centers the statistic to have mean-zero under the null.  This statistic is especially
-convenient because other \oos\ tests for similar hypotheses
-(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
-and \citealt{Mcc:07}; among others) have a nonstandard limit
-distribution and place restrictions on the models under consideration,
-while other asymptotically normal statistics test a different null
-hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
-that are often violated in empirical work (\citealt{DiM:95};
-\citealt{Wes:96}; \citealt{WeM:98};
-\citealt{Mcc:00}).%
-\footnote{\citet{DiM:95} assume that the models are
-  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
-  assume that the models do not converge to the same limit,
-  which rules out nesting.} %
-However, Clark and West's statistic is only ``approximately normal''
-in an informal sense.  Clark and West present Monte Carlo evidence of
-the statistic's distribution, but only prove that the statistic is
-asymptotically normal with mean zero when the benchmark model is
-not estimated \citep{ClW:06}. Estimating the parameters of the smaller
-model invalidates their proof.
-
-This paper proposes a modified version of Clark and West's (2006,
-2007) statistic and shows that it is
-asymptotically normal even when the smaller model is estimated.  To
-achieve normality, the pseudotrue benchmark model must be estimated
-consistently, but the larger alternative model must continue to be
-estimated inconsistently so that the test statistic is not degenerate
-when the models are nested. We can meet both needs by
-using different window strategies for each model: the benchmark model
-is estimated using a recursive window and the alternative with a
-fixed-length rolling window.
-This approach has the further advantage over existing \oos\ tests for
-nested models that the alternative can be essentially arbitrary as
-long as high level moment conditions hold. In particular, researchers
-can use model selection techniques like the \aic\ or \bic\ to
-determine the number of lags to include, the particular exogenous
-variables to include, etc. Moreover, although we focus on nested
-models in this paper, the approach can be used with non-nested models
-as well. As \citet{ClM:11b} have recently argued,
-\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
-the benchmark and alternative models, which is allowable under the
-null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')
-
-The next section presents the intuition and theory for our new
-statistic.  Section~\ref{sec:2} presents simulations that compare our
-pairwise \oos\ test to \poscw\ original statistics.
-Section~\ref{sec:3} demonstrates the use of our statistic by
-reanalyzing \citepos{GoW:08} study of excess return predictability and
-demonstrates how our results can be used in settings with many
-alternative models. Section~\ref{sec:4} concludes. Our results follow
-from arguments similar to \citepos{Wes:96} and have been put in a
-separate appendix along with some supporting lemmas \citep{Cal:15b}.
-
-\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
-\label{sec:1}
-
-This section presents the new \oos\ statistic; first we give an
-informal motivation of the statistic, then present the paper's key
-assumptions in Section~\ref{sec:1a} and present our formal theoretical
-results in Section~\ref{sec:1b}.
-
-Suppose for now that a researcher is interested in
-predicting the target variable $y_{t+1}$ with a vector of regressors
-$x_t$, that $v_t$ is another random process that is believed to
-potentially contain information about $y_{t+1}$, and that
-$(y_t, x_t, v_t)$ is stationary and weakly dependent.
-In addition,
-let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
-coefficient for the regression of $y_{t+1}$ on $x_t$ and define
-$\ep_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
-correctly specified, then $\ep_{t+1}$ is an \mds\ with respect
-to $\sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$
-and we can see immediately that
-\begin{equation}
-  \label{eq:4}
-  \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
-\end{equation}
-obeys an \mds\ \clt\ and is asymptotically normal as $P \to \infty$,%
-\footnote{This claim assumes that the asymptotic variance of the
-  sample average is uniformly positive, a requirement that we will
-  address in Section~\ref{sec:1b}.} %
-with $R$ an arbitrary starting value
-and $P = T - R$.
-
-Straightforward algebra \citep{ClW:07} shows that
-\begin{equation}
-  \label{eq:5}
-  \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
-  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
-  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big]
-\end{equation}
-almost surely.
-\citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
-$v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
-$R$ to estimate $\yh_{t+1}$,%
-\footnote{Making $\yh_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
-\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
-dependent random process} %
-and $R$ is kept finite as $T \to \infty$ so that
-$\yh_{t+1}$ inherits the weak dependence properties of the
-variables used to estimate it. Using a finite window prevents
-the degeneracy that can arise when comparing nested models out-of-sample (see
-\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
-of the \oos\ average remains positive and the average obeys a \clt.%
-\footnote{This approach was first introduced by \citet{GiW:06}.} %
-
-\citet{ClW:06,ClW:07} propose using this as a test of whether the benchmark is correctly specified.
-In their 2006 paper, Clark and West assume that the
-coefficients on the benchmark model, $\btrue$, are zero under the null, making
-$\ep_{t+1}$ observed directly. This restriction is relaxed in
-their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
-rolling window as $\yh_{t+1}$. Now the estimated linear model's prediction errors,
-$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
-test statistic. Unfortunately, $\eph_{t+1}$ is not an
-\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
-asymptotically mean-zero normal, even though this approximation
-performs well in simulations. Since the window length is finite,
-the estimator of $\btrue$ does not converge to $\btrue$.
-
-This paper proposes using the same basic \oos\ statistic,
-but using a recursive window to estimate $\btrue$ and produce
-$\eph_{t+1}$:
-\begin{align}
-  \label{eq:8}
-  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
-  \sum_{s=1}^{t-1} x_{s} y_{s+1}
-  && \text{and}
-  &
-  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
-\end{align}
-for each $t$.%
-\footnote{The matrix inversion in $\bh_t$ can be replaced with a
-  pseudo-inverse if necessary for some values of $t$ without changing
-  the forecast.} %
-\citepos{Wes:96} Theorem 4.1 implies that
-\begin{equation*}
-  \oclt{t} \Big[(y_{t+1} -
-  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
-\end{equation*}
-is asymptotically normal with mean zero under Clark and West's
-\mds\ null for fairly
-arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
-the \oos\ statistic has uniformly positive variance.  Just as in
-\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
-another forecast of $y_{t+1}$ based on a fixed-length rolling window.
-
-So far, we have presented an especially simple version of the result
-to make the intuition as clear as possible. The next section lists the
-specific assumptions for the more general case and defines additional notation.
-
-\subsection{Theoretical assumptions}
-\label{sec:1a}
-
-Consider the following environment. There is a single linear
-benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
-  y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
-\end{equation}
-where $\beta$ is an unknown vector of parameters and $x_t$ is an
-observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
-The alternative model is denoted $\yh_{t+1}$ and is estimated with a
-rolling window of length $R$.
-
-The main conditions on the \dgp\ are summarized in the first
-assumption.  The weak dependence and moment conditions are
-standard. The assumption of strict stationarity is stronger than
-necessary in practice --- once the alternative forecasting method is
-known, it is only necessary that the \oos\ adjusted loss difference be
-weak stationary, and even that can be relaxed further --- but this
-stronger assumption ensures that the results hold generally.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a1}}
-\begin{asmp}\label{a1}%
-  The data are generated by the relationship
-  \begin{equation}
-    y_{t+1} = x_t'\btrue + \ep_{t+1}
-  \end{equation}
-  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
-  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
-  all $t$. Also assume that there is an additional sequence of random
-  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
-  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
-  $-r/(2r-2)$, for $r > 2$.
-\end{asmp}
-
-The next assumption defines the forecasting models and adds additional
-constraints to the \dgp.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a3}}
-\begin{asmp}\label{a3}%
-  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
-  forecast satisfies
-  \begin{equation}
-    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
-  \end{equation}
-  where $\psi$ is a known measurable function and the window length,
-  $R$, remains finite as $T \to \infty$. Moreover, the vector
-  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
-  where $r$ is first defined in Assumption~\ref{a1}.
-\end{asmp}
-
-The requirement that the alternative forecast satisfies moment
-conditions, rather than the underlying predictors $z_t$, is somewhat
-unappealing but necessary. The function $\psi$ that generates these
-forecasts is otherwise nearly unrestricted, so even well-behaved predictors
-could produce arbitrarily badly-behaved forecasts. For example, if
-\begin{equation*}
-  z_t \sim \iid~\bernoulli(1/2),
-\end{equation*}
-setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
-since the forecast equals positive infinity with probability $1/2$. It
-is easy to construct less obvious examples of problematic functions as
-well. Assumption~\ref{a3} implicitly rules out these functional forms
-by imposing moment conditions on the alternative models' forecasts.
-
-Our next assumption ensures that the asymptotic variance of the \oos\
-average is positive.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a4}}
-\begin{asmp}\label{a4}%
-  The asymptotic variance-covariance matrix
-  \begin{equation}
-    \var \Bigg(
-      \oclt{t} \begin{pmatrix} x_t \\ \yh_{t+1} \end{pmatrix} \ep_{t+1}
-      \Bigg)
-  \end{equation}
-  is uniformly positive definite (in $T$).
-\end{asmp}
-This assumption is much less restrictive than in \cite{Wes:96}.  As in
-\cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only serves to
-rule out pathological cases --- for example, letting the alternative
-model consist of only the first regressor of the benchmark. In \citet{Wes:96}, this
-assumption is a restriction on the \dgp\ as well as the forecasting
-models, but in this paper it is a restriction only on the models.
-
-The final assumption restricts the class of \hac\ variance estimators
-we will consider. We use the same class of estimators studied by
-\citet{JoD:00} (their class $\mathcal{K}$); see their paper for
-further discussion.
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Assumption \ref{a5}}
-\begin{asmp}\label{a5}%
-  The kernel $K$ is a function from $\Re$ to $[-1,1]$ such that $K(0) = 1$, $K(x)
-  = K(-x)$ for all $x$, $K(\cdot)$ is continuous at zero and all but a
-  finite number of points, and
-  \begin{gather*}
-    \int_{-\infty}^{\infty} \lvert K(x) \rvert\, dx < \infty,
-    \intertext{and}
-    \int_{-\infty}^{\infty} \Bigg\lvert
-    \int_{-\infty}^{\infty} K(z) e^{ixz}\,dz \Bigg\rvert\, dx < \infty.
-  \end{gather*}
-\end{asmp}
-
-Last, we define some notation that will be used to derive the
-theoretical properties of our \oos\ statistics.  The information set
-that contains the information available for forecasting $y_{t+1}$ is
-\begin{equation*}
-  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
-\end{equation*}
-The adjusted \oos\ loss difference using a hypothetical value of
-$\beta$ to produce the benchmark forecast is denoted by
-\begin{equation*}
-  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
-\end{equation*}
-Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
-\begin{gather*}
-  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
-          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-  \intertext{and}
-  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
-\end{gather*}
-and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t}
-f_t/P$, $\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.
-
-\subsection{Theoretical results}
-\label{sec:1b}
-
-Asymptotic normality of the \oos\ average now follows directly from the
-first three assumptions without other conditions. The proof is
-presented in the Appendix and follows \citet{Wes:96} closely.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
-
-To use this result, we need a consistent estimator of
-$\sigma^2$. Define the \hac\ covariance estimator $\sigmah^2_1 =
-\sh_{11} + 2 (\sh_{12} + \sh_{13})$ and the \mds\ covariance estimator
-$\sigmah^2_2 = \sh_{21} + 2(\sh_{22} + \sh_{23})$ with
-\begin{align*}
-  \sh_{11} &= \oavg{s,t} (\fh_s - \fb) (\fh_t - \fb) K(\tfrac{t-s}{P}), &
-  \sh_{21} &= \oavg{t} (\fh_t - \fb)^2, \\
-  \sh_{12} &= \oavg{s,t} (\fh_s - \fb)(\gh_t - \gb) K(\tfrac{t-s}{P}), &
-  \sh_{22} &= \oavg{t} (\fh_t - \fb)(\gh_t - \gb),
-\intertext{and}
-  \sh_{13} &= \oavg{s,t} (\gh_s - \gb) (\gh_t - \gb), &
-  \sh_{23} &= \oavg{t} (\gh_t - \gb)^2.
-\end{align*}
-
-These estimators are consistent under similar assumptions to
-Theorem~\ref{res:1}.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
-
-Note that these results allow misspecification; asymptotic normality
-follows from the weak dependence of the underlying series and from the
-design of the test statistic. These statistics have typically been
-used to test the null hypothesis that the benchmark model is correctly
-specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
-implies that $f_t$ is an \mds\ as discussed
-at the beginning of this section. This is especially appealing in our
-framework, since the benchmark can be theoretically motivated so the
-\mds\ null would be a test of rationality. For example, \citet{GoW:08}
-test whether excess returns for the S\&P 500 are predictable
-out-of-sample, and any deviation of $\ep_{t+1}$ from an \mds\ is potentially
-interesting. But the \mds\ null hypothesis only affects the estimator
-of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
-to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.
-
-In other settings, a researcher may want to test the weaker hypothesis
-that $\E \fb^* = 0$ but the benchmark may be misspecified. Our
-statistic can then be interpreted as an encompassing test as in
-\citet{HLN:98}, and would test whether the alternative model contains
-additional information that could make the benchmark model more
-accurate. This interpretation can be motivated by the combination forecasting
-model
-\begin{equation*}
-  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\btrue + w \yh_{t+1}
-\end{equation*}
-which can be rewritten in terms of forecast errors as
-\[
-y_{t+1} - \yh_{\mathit{avg},t+1} = \ep_{t+1} + w (x_t'\btrue - \yh_{t+1}).
-\]
-The value
-\[
-w = \frac{\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)}{\E (x_t'\btrue - \yh_{t+1})^2}
-\]
-minimizes the \mse\ of the combination forecast, so the combination
-model will have smaller \mse\ than the benchmark model, implying that
-the alternative uses information not in the benchmark, unless
-$\ep_{t+1}$ and $\yh_{t+1} - x_t'\btrue$ are uncorrelated. This
-correlation is exactly the quantity measured by our statistic.
-
-The final result puts together Theorem~\ref{res:1} and
-Lemma~\ref{lem:2} to produce our test statistics. The null hypothesis
-under misspecification is written in terms of $\E \ep_{t+1} \yh_{t+1}$
-and not $\E \ep_{t+1} (\yh_{t+1} - x_t'\btrue)$, since $\E \ep_{t+1}
-x_t = 0$ by construction. This result is an immediate consequence of
-the previous two results and its proof is omitted.
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
-
-The test statistic proposed in Theorem~\ref{thm:3} can be easily
-extended in several ways. For longer-horizon forecasts (two or more
-periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
-will not --- the forecast errors for a correctly specified
-$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
-using a generalized $\sigmah_2$ that reflects this covariance
-structure restores consistency. To test optimality under loss
-functions other than squared-error, one can replace the forecast error
-with the generalized forecast error \citep[see, for
-example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
-corresponding $M$-estimator. And the benchmark model can be replaced
-in general with a nonlinear model that satisfies the assumptions of
-\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
-$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
-for details.) The general approach of using a recursive window to
-estimate the benchmark and a fixed-length rolling window to estimate
-the alternative applies quite broadly.
-
-\section{Monte Carlo Results}\label{sec:2}
-This section presents Monte Carlo experiments demonstrating that
-this paper's modified version of \citepos{ClW:07} statistic performs
-similarly to their original test in the situations they study, but can
-have substantially higher power when the \dgp\ has a structural
-break.%
-\footnote{All of these simulations were programmed in R
-  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
-  \citep[7.3-22]{VeR:02} package.} %
-
-The \dgp\ has three different parametrizations: one to study the
-tests' size, one to study power under stationarity, and one to study
-power if there is a single break in the relationship between the
-target and predictors.  The \dgp\ is:
-\begin{align*}
-  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
-  \gamma_t &=
-  \begin{cases}
-    (0.5, 0)    & \text{size simulations} \\
-    (0.5, 0.35) & \text{power (stable)} \\
-    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
-    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
-  \end{cases}\\\nonumber
-  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
-  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
-  \end{pmatrix}
-   , \begin{pmatrix} 18 & -
-    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
-  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
-\end{align*}
-Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
-on a constant, and the alternative regresses $y_{t+1}$ on a constant and
-$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
-pricing application similar to \citepos{GoW:08} which we study in
-Section~\ref{sec:3}.
-
-For comparison, we study this paper's new statistic as well as
-\poscw\ rolling-window and recursive-window test statistics.  Clark and West
-only prove that their rolling-window statistic is asymptotically
-normal, and only then if the benchmark model is not estimated, but
-their recursive-window statistic is popular in practice and in
-simulations tends to perform similarly to their rolling window test.
-We use all three of these statistics to test the null that the
-benchmark model's innovation is an \mds.%
-\footnote{\citet{ClW:07}
-  report the performance of the tests proposed by \citet{CCS:01} and
-  \citet{ClM:05} as well, and of tests based on the naive Gaussian
-  statistic.} %
-
-\begin{table}[tb]
-  \centering
-  \input{tex/mc1}
-  \caption{Size and power of the \oos\ tests in the simulations
-    described by Section~\ref{sec:2}, at
-    \testsize\% confidence.  These percentages are calculated from \totalsims\
-    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
-    which Clark and West's (2007) rolling-window statistic rejects;
-    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
-    their recursive-window statistic rejects; and Pr[new] shows the fraction of
-    simulations for which this paper's test rejects.}
-\label{tab:mc1}
-\end{table}
-
-Table~\ref{tab:mc1} presents the simulation results.  For all of the
-stable parameter values, the proposed new statistic has similar
-rejection probability to \citepos{ClW:07}.  Both of Clark and West's
-tests are generally slightly undersized relative to our new test,
-which is itself slightly undersized: when $R$ is 120 and $P$ is 360
-our test statistic has size 7.6\% and Clark and West's rolling and
-recursive window tests have size 7.5\% and 6.2\% respectively, at a
-nominal size of 10\%.  For the stable alternative, our new statistic
-typically has slightly higher power than Clark and West's rolling
-window and lower power than their recursive window.  For example, when
-$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
-our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
-again for a nominal size of 10\%.  In general, the statistics perform
-similarly under stability.
-
-For the simulations with a single break, the new statistic has
-considerably higher power than \poscw\ original tests across all of
-the choices of $R$ and $P$; the rejection probability is more than
-twice as large for most parametrizations.  When $R$ is 120 and $P$ is
-360 with a nominal size of 10\%, for example, the new statistic
-rejects at 96.4\% while the rolling and recursive window statistics
-reject at 35.5\% and 32.9\% respectively.  Results for other choices
-of nominal size and sample split give similar results.  So mixing
-window strategies can give a large power advantage when testing for
-time-varying predictability, and performs similarly to the original
-test when testing for stable outperformance.
-
-\section{Empirical Illustration}\label{sec:3}
-
-This section demonstrates the use of our new statistic by revisiting
-\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
-that many variables thought to predict excess returns (measured as the
-difference between the yearly log return of the S\&P 500 index and the
-T-bill interest rate) on the basis of in-sample evidence fail to do so
-out-of-sample.  To show this, Goyal and Welch look at the forecasting
-performance of models using a lag of the variable of interest, and
-show that these models do not significantly outperform the excess
-return's recursive sample mean.
-
-Here, we conduct the same analysis, but using this paper's \mds\ test.
-The benchmark model is the excess return's sample mean (as in the
-original) and the alternative models are of the form
-\begin{equation*}
-  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
-  \mathit{predictor}_{t} + \ep_{t+1},
-\end{equation*}
-where $\beta_{0}$ and
-$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
-The predictors used are listed in the \emph{predictor} column of
-Table~\ref{tab:em1}. \citep[See][for a detailed description of the
-variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
-correction to the models, that the forecasts be bounded below by zero
-since negative forecasts are incredible, as well as two simple
-combination forecasts, the mean and the median (over both the original
-and the non-negative forecasts).  The data set is annual data
-beginning in 1927 and ending in 2009, and the rolling window uses
-\windowlength\ observations.%
-\footnote{This statistical analysis was conducted in R \citep{R} and
-  uses the MASS \citep[7.3-22]{VeR:02} package.} %
-
-\begin{table}[tb!]
-  \centering
-  \empiricaltable
-\caption{Results from \oos\ comparison of equity premium prediction
-  models; the benchmark is the recursive sample mean of the equity
-  premium and each alternative model is a constant and single lag of
-  the variable listed in the \emph{predictor} column.  The dataset begins
-  in 1927 and ends in 2009 and is annual data. The \emph{value} column
-  lists the value of this paper's \oos\ statistic, the \emph{naive}
-  column indicates whether the statistic is significant at standard
-  critical values, and the \emph{corrected} column indicates significance
-  using critical values that
-  account for the number of models.  See Section~\ref{sec:3} for details.}
-\label{tab:em1}
-\end{table}
-
-Table~\ref{tab:em1} presents the results for each model.  The column
-\emph{value} gives the value of the test statistic for each model,
-while \emph{naive} indicates whether the statistic is greater than the
-standard 10\% critical value (\naivecriticalvalue). Three predictors
-are significant at the naive critical values for both the original and
-bounded forecasts: the dividend yield, long term interest rate, and
-book to market ratio, and the median forecast is significant as well.
-This could suggest that excess returns are not an \mds\ and that
-information in these three variables is useful for predicting returns.
-
-However, we know that this is an extremely optimistic assessment of
-the models' performance. We are conducting \nmod\ simultaneous
-hypothesis tests, so it is likely that some will reject by chance.
-There are several approaches that could accommodate this multiplicity and a full
-treatment is beyond the scope of this paper, however, it is
-straightforward to use our results to
-derive a valid critical value similar to~\citet{Whi:00}.
-
-Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
-forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
-multivariate $f_t$, so the continuous mapping theorem implies that
-\begin{equation*}
-  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
-\end{equation*}
-where $W \sim N(0, V)$ and $V$ is the $\nmod
-\times \nmod$ correlation matrix with elements
-\begin{equation*}
-  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
-\end{equation*}
-
-To estimate $V$, we use the correlation matrix associated with the
-multivariate analogue of $\sigmah_2$,
-\[
-\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
-+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
-\]
-where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
-\begin{gather*}
-  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
-  \intertext{and}
-  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
-            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
-\end{gather*}
-respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
-$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
-$\hat W \sim N(0, \hat V)$.  Then
-\begin{equation*}
-  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
-\end{equation*}
-under the null hypothesis that excess returns are an \mds\ with
-respect to all of the information contained in the variables listed in
-Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
-value.%
-\footnote{\citet{Han:05} makes the point that multiple one-sided
-  comparisons can have poor power if irrelevant predictors are
-  included in these tests and proposes a threshold for discarding very
-  poor forecasts. His threshold is well below our worst performing
-  model, so this issue is not a concern here.} %
-
-We calculate $\hat c$ by generating \empiricaldraws\ draws from
-$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
-\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
-remain significant at 10\% with this critical value. Using this
-critical value, none of the predictors are significant, which
-gives additional support to \citepos{GoW:08} conclusion that excess
-returns are unpredictable and also demonstrates the importance of
-correcting for multiplicity in these studies.
-
-\section{Discussion}\label{sec:4}
-This paper presents an \oos\ test statistic similar to \poscw\ that is
-asymptotically normal when comparing nested or non-nested models.
-Normality is achieved by estimating the alternative model using a
-fixed-length rolling window --- as do Clark and West --- but
-estimating the benchmark model with a recursive window.  Simulations
-indicate that the new statistic behaves similarly to Clark and West's
-original test when the \dgp\ is stable but can have much higher power
-when the \dgp\ has structural breaks. We also have presented an
-empirical study of the equity premium that demonstrates how to use
-these results with several alternative models.
-
-\newpage
 \phantomsection
@@
 
-\newpage
 \appendix
-\section{Supplemental appendix (not for publication)}
-\newcommand{\WesA}[1][]{\ocltb{t}
-  (F_t^{#1} - F) B^{#1} H_t^{#1}}
-\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
-  B^{#1}) H_t^{#1}}
-\newcommand{\WesC}[1][]{\ocltb{t}
-  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}
 
-This appendix contains mathematical proofs and some supporting Lemmas
-for the paper, ``An asymptotically normal out-of-sample test based on
-mixed estimation windows'' \citep{Cal:15}. Define the following
-additional terms:
-\begin{equation*}
-  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
-\end{equation*}
-$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
-x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
-$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
-And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
-Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
-and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
-of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.
-
-\subsection{Proof of Theorem \ref{res:1}}
-  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
-    \sqrt{P} (\fb - \E \fb^*)
-    = \ocltb{t} (\fh_t - \E f_t)
-      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
-  \end{equation}
-  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
-  \begin{align*}
-    \sqrt{P} (\fb - \E \fb^*)
-    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
-    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
-  \end{align*}
-  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
-  Lemma~\ref{res:a4} shows that
-  \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
-    \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
-  \end{gather}
-  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
-  w_t = o_{p}(1)$. The proof that
-  \begin{equation*}
-    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
-  \end{equation*}
-  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
-
-\subsection{Proof of Lemma~\ref{lem:2}}
-
-We will only prove $\sigmah_2 \to^p \sigma$. The result for
-$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
-
-  First, we can rewrite the components of the variance estimator as
-  \begin{align*}
-    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
-    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
-                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
-    \intertext{and}
-    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
-  \end{align*}
-  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
-  $\fb - \E \fb^* \to^p 0$,
-  $\gb - \E \gb^* \to^p 0$,
-  \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
-    \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
-  \end{gather}
-  The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
-  follow from the \lln, since each summand is an $L_1$-mixingale of
-  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
-
-  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
-  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
-  \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
-    \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
-  \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
-  \begin{align*}
-    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
-    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  by Lemma~\ref{res:a2} and the \lln.
-  A similar argument holds for the second term:
-  \begin{align*}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
-    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
-    &= O_p(R'/P) + o_p(1)
-  \end{align*}
-  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
-
-\subsection{Supporting results}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
-\begin{alem}\label{res:a1}
-  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
-  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
-  and $R' = o(\sqrt{P})$. Then
-  \begin{equation*}
-    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
-  \end{equation*}
-\end{alem}
-
-\begin{proof}
-  We can rewrite this summation as
-  \begin{multline*}
-    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
-    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
-    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
-  \end{multline*}
-  Each of these individual summations can be shown to converge to
-  zero in probability. First,
-  \begin{equation*}
-    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
-    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
-    = O(R'/\sqrt{P}).
-  \end{equation*}
-  Also,
-  \begin{align*}
-    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
-    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
-    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
-    & = O_p(R'/\sqrt{P})
-  \end{align*}
-  and
-  \begin{equation*}
-    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
-    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
-    = O_p(R'/\sqrt{P}).
-  \end{equation*}
-  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
-  construction, this completes the proof.
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
-\begin{alem}\label{res:a2}
-  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
-  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
-  \infty$ and $R' = o(\sqrt{P})$. Then
-  \begin{enumerate}
-  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
-  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
-  \item $\omaxb{t} | B_t - B | \to^p 0$,
-  \item $\omaxc{t} | B_t - B | = O_p(1)$,
-  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
-  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
-  \end{enumerate}
-  where the absolute value is taken as the largest of the
-  element-by-element absolute values.
-\end{alem}
-
-\noindent%
-To streamline the
-presentation, we'll assume in these proofs that $x_t$ is a scalar.
-\begin{proof}
-  We will prove each part in order.
-  \begin{enumerate}
-  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
-    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
-    and $\zeta_k$ denote its mixingale
-    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
-    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
-    coefficients $\zeta_k$, since
-    \begin{align*}
-      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_k
-    \end{align*}
-    and
-    \begin{align*}
-      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
-      &\leq (t^{b} c_t) \zeta_{k+1}.
-    \end{align*}
-
-    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
-    \begin{align*}
-      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
-      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
-    \end{align*}
-    where the second inequality follows from \citepos{Mcl:75} maximal
-    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
-    Corollary 16.10). The summation converges to a constant and
-    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.
-
-  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
-    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
-    \begin{align*}
-      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
-      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
-      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
-    \end{align*}
-    which converges to a finite limit.
-  \item The same argument used in Part 1 implies that $\omaxb{t} |
-    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
-    the result follows.
-  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
-  \item We have
-    \begin{align*}
-      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      &\leq \omaxb{t} |\hat{B}_t - B|
-      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
-    \end{align*}
-    and both terms converge to zero in probability by Parts 1 and 3.
-  \item Similar to the previous argument, we have
-    \begin{align*}
-      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
-      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
-      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
-    \end{align*}
-    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
-  \end{enumerate}
-\end{proof}
-
-\phantomsection
-\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
-\begin{alem}\label{res:a4}
-  Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
-\end{alem}
-
-\begin{proof}[Proof of~\eqref{eq:11}]
-Choose $\delta > 0$ and $a \in (0,1/2)$ and write
-\begin{multline}\label{eq:A3}
-  \WesA =
-  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
-  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
-\end{multline}
-For any $c > 0$,
-\begin{multline*}
-  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
-  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
-\end{multline*}
-which converges to zero by Lemma~\ref{res:a2}, so the first summation on
-the RHS of~\eqref{eq:A3} converges to zero i.p.
-
-For the second summation,
-\begin{equation*}
-  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
-    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
-   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
-\end{equation*}
-The expectation on the RHS is of order
-$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
-$L_2$-mixingale of size $-1/2$ by construction (see the proof of
-Lemma~\ref{res:a2} for a more detailed discussion), and converges to
-zero by Kronecker's Lemma.
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:12}]
-TBD
-\end{proof}
-
-\begin{proof}[Proof of~\eqref{eq:13}]
-TBD
-\end{proof}
-
+\include{X1-mathematics}
 \setcounter{secnumdepth}{1}

### 2017-05-18 S2-normality.tex
Automatic equation renumbering
This commit renumbers the equations in the paper so that they
are in order and are (more importantly) unique.

@@
 \begin{equation}
-  \label{eq:4}
+  \label{eq:1}
   \oclt{t} \ep_{t+1} (v_t - x_t'\btrue)
@@
 \begin{equation}
-  \label{eq:5}
+  \label{eq:2}
   \tfrac{1}{\sqrt{P}} \osum{t} \ep_{t+1} (v_t -
@@
 \citet{ClW:06,ClW:07} base their \oos\ statistics on the \allcaps{RHS} of
-Equation~\eqref{eq:5}, but use a second forecast of $y_{t+1}$ as
+Equation~\eqref{eq:2}, but use a second forecast of $y_{t+1}$ as
 $v_t$. (Call it $\yh_{t+1}$.) They use a rolling window of length
@@
 \begin{align}
-  \label{eq:8}
+  \label{eq:3}
   \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
@@
 benchmark model of the target variable, $y_{t+1}$:
-\begin{equation}\label{eq:1}
+\begin{equation}\label{eq:4}
   y_{t+1} = x_t'\beta + \ep_{t+1}, \quad t = 1,\dots,T-1
@@
 observed vector of predictors. The parameter $\beta$ is estimated with
-\ols\ using a recursive window as described by Equation~\eqref{eq:8}.
+\ols\ using a recursive window as described by Equation~\eqref{eq:3}.
 The alternative model is denoted $\yh_{t+1}$ and is estimated with a
@@
   The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
-  with a recursive window according to~\eqref{eq:8}. The alternative
+  with a recursive window according to~\eqref{eq:3}. The alternative
   forecast satisfies

### 2017-05-18 X1-mathematics.tex
Automatic equation renumbering
This commit renumbers the equations in the paper so that they
are in order and are (more importantly) unique.

@@
   and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
-  \begin{equation}\label{eq:6}
+  \begin{equation}\label{eq:5}
     \sqrt{P} (\fb - \E \fb^*)
@@
   Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
-  we can rewrite~\eqref{eq:6} as
+  we can rewrite~\eqref{eq:5} as
   \begin{align*}
@@
   \begin{gather}
-    \WesA \to^{p} 0 \label{eq:11} \\
-    \WesB \to^{p} 0 \label{eq:12} \\
+    \WesA \to^{p} 0 \label{eq:6} \\
+    \WesB \to^{p} 0 \label{eq:7} \\
     \intertext{and}
-    \WesC \to^{p} 0 \label{eq:13}
+    \WesC \to^{p} 0 \label{eq:8}
   \end{gather}
@@
 $\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
-2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
+2.1 for the \hac\ equivalent of Equations~\eqref{eq:9}--\eqref{eq:11}.
 
@@
   \begin{gather}
-    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
-    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
-    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
-    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
+    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:9} \\
+    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:10} \\
+    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:11} \\
+    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:12}
     \intertext{and}
-    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
+    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:13}
   \end{gather}
   The first two results are implied by the proof of
-  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
+  Theorem~\ref{res:1} and~\eqref{eq:9}, \eqref{eq:10}, and~\eqref{eq:11}
   follow from the \lln, since each summand is an $L_1$-mixingale of
   size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
-  prove~\eqref{eq:4} and~\eqref{eq:5}.
+  prove~\eqref{eq:12} and~\eqref{eq:13}.
 
@@
   $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
-  that~\eqref{eq:4} holds if
+  that~\eqref{eq:12} holds if
   \begin{gather}
-    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
+    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:14}
     \intertext{and}
-    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
+    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:15}
   \end{gather}
-  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
+  The \allcaps{LHS} of~\eqref{eq:14} is bounded by
   \begin{align*}
@@
   again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
-  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
+  zero in probability by construction. The proof of~\eqref{eq:13} is similar.
 
@@
   Under the conditions of Theorem~\ref{res:1}, Equations
-  \eqref{eq:11}--\eqref{eq:13} hold.
+  \eqref{eq:6}--\eqref{eq:8} hold.
 \end{alem}
 
-\begin{proof}[Proof of~\eqref{eq:11}]
+\begin{proof}[Proof of~\eqref{eq:6}]
 Choose $\delta > 0$ and $a \in (0,1/2)$ and write
@@
 
-\begin{proof}[Proof of~\eqref{eq:12}]
+\begin{proof}[Proof of~\eqref{eq:7}]
 Note that
@@
 
-\begin{proof}[Proof of~\eqref{eq:13}]
-This proof is essentially the same as that of~\eqref{eq:12}. We have
+\begin{proof}[Proof of~\eqref{eq:8}]
+This proof is essentially the same as that of~\eqref{eq:7}. We have
 \begin{equation*}
@@
 \end{equation*}
-which is $O(1)$ as in the proof of~\eqref{eq:12}.
+which is $O(1)$ as in the proof of~\eqref{eq:7}.
 \end{proof}

### 2017-05-19 S2-normality.tex
Move Theorem and Lemma source code to main LaTeX files

@@
 \addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
-\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
+\begin{thm}\label{res:1}
+  If Assumptions~\ref{a1}--\ref{a4} hold then
+  \begin{equation*}
+    \sqrt{P} (\fb - \E \fb^*) \to^d N(0, \sigma^2),
+  \end{equation*}
+  with $\sigma^2 = s_1 + 2(s_2 + s_3)$ and
+  \begin{align*}
+    s_1  &= \lim \var(\sqrt{P}\, \fb^*), &
+    s_2  &= \lim \cov(\sqrt{P}\, \fb^*, \sqrt{P}\, \gb^*), &
+    s_3  &= \lim \var(\sqrt{P}\, \gb^*).
+  \end{align*}
+\end{thm}
 
@@
 \addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
-\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}
+\begin{lem}\label{lem:2}
+  If Assumptions~\ref{a1}--\ref{a5} hold then
+  \begin{equation*}
+    \sigmah_1^2 \to^p \sigma^2.
+  \end{equation*}
+  If Assumptions~\ref{a1}--\ref{a4} hold and $\{\varepsilon_{t},
+  \Fs_t\}$ is an \mds\ then
+  \begin{equation*}
+    \sigmah_2^2 \to^p \sigma^2.
+  \end{equation*}
+\end{lem}
 
@@
 \addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
-\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}
+\begin{thm}\label{thm:3}
+  If Assumptions~\ref{a1}--\ref{a5} hold, then
+  \begin{equation*}
+    \sqrt{P} \fb / \sigmah_1 \to^d N(0, 1)
+  \end{equation*}
+  under the null hypothesis $\E(\varepsilon_{t+1} \yh_{t+1}) = 0$ for
+  all $t = R,\dots,T-1$.  If, instead, Assumptions~\ref{a1}--\ref{a4}
+  hold, then
+  \begin{equation*}
+    \sqrt{P} \fb / \sigmah_2 \to^d N(0, 1)
+  \end{equation*}
+  under the null hypothesis that $\{\varepsilon_t, \Fs_t\}$ is an \mds.
+\end{thm}
 
